### 2022-06-15 article_1/article_1.tex
Add first article: Introduction

%\documentclass[paper]{geophysics}
\documentclass[manuscript,revised]{geophysics}

\usepackage{setspace}
\usepackage[colorlinks]{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}

% An example of defining macros
\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
\newcommand{\rr}[1]{\mbox{\rm #1}}

\begin{document}

\title{An example \emph{Geophysics} article, \\ with a two-line title}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{GEO-Example} % manuscript number

\address{
\footnotemark[1]BP UTG, \\
200 Westlake Park Blvd, \\
Houston, TX, 77079 \\
\footnotemark[2]Bureau of Economic Geology, \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924}

\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
\date{}
\footer{Example}
\lefthead{Dellinger \& Fomel}
\righthead{\emph{Geophysics} example}

\maketitle

\begin{abstract}
\begin{singlespace}
Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s). Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields. The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers. To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field. This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution. Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections. If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.

\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
\end{singlespace}
\end{abstract}

\section{Introduction}
%\onehalfspacing
\doublespacing

\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}. It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}

\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}. Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}. When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field. In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}. On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field. In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties. All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}

\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$. The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}. although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}. With the possibility of isolating the individual contributions of a fairly large number (N $>10^6$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}

\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}. In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}. However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the micromagnetic microscopy itself.}

\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information. In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained. We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}

\section{Methodology}

\section{Results}

\section{Discussion}

\section{Conclusion}

\begin{singlespace}
\doublespacing
\bibliographystyle{agu}  % style file is seg.bst
\bibliography{article1}
\end{singlespace}
\end{document}

### 2022-06-21 article_1/article_1.tex
Add first article: Methodology

@@
 \usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
+\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
+
+\usepackage{amsmath}
+\usepackage[utf8x]{inputenc}
+\usepackage{graphicx}
+\graphicspath{ {./images/} } % images path
+
+\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
+
+\usepackage[document]{ragged2e} % to justify text
+
+%\usepackage{ragged2e}
+\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
+%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
+%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
+\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
+\captionsetup{compatibility=false, justification=justified, format=custom}
 
@@
 
+% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{blindtext} % Package to generate dummy text throughout this template 
+\usepackage[sc]{mathpazo} % Use the Palatino font
+\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
+\linespread{1.05} % Line spacing - Palatino needs more space between lines
+\usepackage{microtype} % Slightly tweak font spacing for aesthetics
+\usepackage[english]{babel} % Language hyphenation and typographical rules
+
+\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
+\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
+
+\usepackage{enumitem} % Customized lists
+\setlist[itemize]{noitemsep} % Make itemize lists more compact
+
+\usepackage{fancyhdr} % Headers and footers
+\pagestyle{fancy} % All pages have headers and footers
+\fancyhead{} % Blank out the default header
+\fancyfoot{} % Blank out the default footer
+\fancyhead[L]{Manuscript} % Custom header text
+\fancyfoot[RO,LE]{\thepage} % Custom footer text
+
+\setlength\parindent{24pt}
+%\usepackage{float}
+\usepackage{floatrow}
+\usepackage{pdfpages}
+\newsavebox\mysavebox
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\title{An example \emph{Geophysics} article, \\ with a two-line title}
-
+\title{?????????????????}
 \renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-
 \ms{GEO-Example} % manuscript number
@@
 \author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{}
+\date{June 2022}
 \footer{Example}
@@
 \maketitle
+\justify
 
@@
 although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number (N $>10^6$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
+With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
 
@@
 In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the micromagnetic microscopy itself.}
+However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}
 
@@
 
+%%%%%%%%%%%%%
+
 \section{Methodology}
+%%%
+\subsection{Scanning Magnetic Microscopy}
 
+\noindent{Scanning magnetic microscopy (SMM) is the imaging technique in which a thin-section sample of geological material is horizontally displaced under a high-precision (fixed) micromagnetometer to obtain magnetization \citep{Weiss2007}.
+The SMM performed at a fixed height above the sample also has the advantage of facilitating the subtraction of the ambient field (constant), to which it might be subject during the scan \citep{Lima2013}.
+The availability of high-performance and low-cost magnetic sensors has promoted a great advance in the application of SMM in recent years.
+However, its sensitivity is still a few orders of magnitude lower than that of superconducting quantum interference devices (SQUIDs), the latter being between 10$^{-12}$ and 10$^{-15}$ Am$^2$ \citep{Lima2013}.
+This disadvantage is offset by (i) the high spatial resolution of the SMM, as it is performed at a few tens of micrometers from the sampled surface; and (ii) SQUID magnetic microscopy is performed at low temperatures ($<$ 100K), which can cause changes in the original NRM of the sample, while SMM is performed at room temperature \citep{Lima2013, Weiss2007}.}
+
+\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
+An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
+Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
+Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{QDM.png}
+\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
+The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a 	minimum sensor-sample distance of 5 μm.
+The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
+Source: \cite{Fu2020}.}
+\label{fig:QDM}
+\end{figure}
+
+\noindent{Due to the similarities between magnetic microscopy techniques and aeromagnetic surveys, the methodologies of data inversion of the latter, densely studied in the last decades, can be adapted for magnetic microscopy.
+However, \cite{Lima2013} report important distinctions between SMM and aeromagnetic surveys, namely: (i) the source distribution in the SMM can often be accurately modeled in a two-dimensional model; (ii) the SMM measures the field produced directly by the sample's NRM; (iii) the sensor positioning is very accurate in the SMM, and the vertical component of the magnetic field is usually measured, rather than the total field; (iv) there is no need for correction to bring all measurements to the same surface or to grid the data; and (v) the distributions of the magnetization sources are finite and known.}
+
+%%%
+\subsection{Magnetic Inversion}
+
+\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination).
+This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
+In this way it is possible to estimate the direction of magnetization from multiple sources.
+The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
+
+\noindent{Currently, the main inversion limitations for these type of data are: (i) in part because the sampling scale during measurement is insufficiently accurate and (ii) because of the non-singularity of the magnetic inversion  \citep{Lima2013}.
+The basic mathematical structure associated with the inverse problem of aeromagnetic data can be adapted and used in SMM data due to its similarity, despite the non-singularity caused by the infinite number of solutions for the same observed magnetic field  \citep{Weiss2007}.
+Assigning as much information as possible about the analyzed sample and the experimental environment can reduce this ambiguity by recovering the magnetization direction.
+In particles with unidirectional magnetization, and without magnetization sources outside the sample area, it is possible to guarantee singularity for the inverse problem in SMM  \citep{Baratchart2013}.
+Associating the fact that there is a singularity in the response of uniformly magnetized particles and that ferromagnetic particles (\emph{l.s.}) with stable magnetization have such a characteristic, therefore, the inversion method becomes ideal for the purpose of this project.}
+
+%%
+\subsubsection{Direct Model}
+
+\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
+In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
+In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions.
+Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources.
+According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}
+
+\begin{equation} \label{eq:sphere1}
+\centering
+b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot m \cdot \hat{m} \cdot \frac{1}{r^2} \cdot \hat{r}
+\end{equation}
+
+\noindent{Whereas the magnetic sources can be represented by a set of L uniformly magnetized spheres.
+In this case, each sphere will have a contribution in the field measured at the position ($x_i$, $y_i$, $z_i$):}
+
+\begin{equation} \label{eq:sphere2}
+\centering
+{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{m}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
+\end{equation}
+
+\begin{tabular}{ l }
+\noindent{Where: $C_m=\ \frac{\mu_0}{4\pi}=\ {10}^{-7}\frac{\ H}{m}$; $R_j$ is the radius of the j-th sphere; $r_{i,j}$ is the distance}   \\ 
+\noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
+\noindent{i = 1, 2, . .. N; and ${\bar{m}}^j=\left[{mx}_j\ {my}_j\ {mz}_j\right]^T$ is the vector formed by the cartesian} \\
+\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{m}}^j)$.}
+\end{tabular}
+
+\bigskip
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.5\textwidth]{MODEL.png}
+\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (points black).
+In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
+Modified from: \cite{OliveiraJr.2015}.}
+\label{fig:MODEL}
+\end{figure}
+
+\noindent{Thus, the total magnetization measured at the position ($x_i$, $y_i$, $z_i$) will be the sum of contributions from the L spheres, given by:}
+
+\begin{equation} \label{eq:sphere3}
+\centering
+B_i=\sum_{j=1}^{L}b_i^j
+\end{equation}
+
+\noindent{According to \cite{OliveiraJr.2015} the \cref{eq:sphere2} can be segmented into two members: (i) the first being a matrix $M_i^j$ encompassing the vector relationship with the positioning for each source and (ii) the second being $h_j$, which is the vector that encompasses the cartesian components of the magnetization of each sphere:}
+
+\begin{equation} \label{eq:sphere4}
+\small M_i^j =\left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
+h_j =\left[\begin{matrix}{{mx}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+\end{equation}
+
+\begin{FlushRight}
+\noindent{Where: $\frac{1}{r_j}\equiv\frac{1}{\sqrt{\left(x_i-{xc}_j\right)^2+\left(y_i-{yc}_j\right)^2+\left(z_i-{zc}_j\right)^2}}$}
+\end{FlushRight}
+
+\noindent{Subsequently, the components of the total magnetizing field can be obtained (from \cref{eq:sphere3}), as shown below:}
+
+\begin{equation} \label{eq:sphere5}
+\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}\cdot\ \left[\begin{matrix}{{mx}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
+\end{equation}
+
+\noindent{As in the specific case in the study of magnetic microscopy, in the routine practice, the vertical component of magnetization is usually measured.
+In this case, there is a need to adapt the \cref{eq:sphere5} to isolate the response from the vertical component ($B_z$).
+Therefore, the equation of the direct model will be given by:}
+
+\begin{equation} \label{eq:sphere6}
+\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}\cdot\ \left[\begin{matrix}{{mx}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
+\end{equation}
+
+\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
+Thus, the vector ${\bar{m}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
+
+\begin{equation} \label{eq:sphere7}
+\small \left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+\end{equation}
+
+\noindent{We can simplify the \cref{eq:sphere6} to:}
+
+\begin{equation} \label{eq:sphere8}
+\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}\cdot\ \left[\begin{matrix}{hx}_j\\{hy}_j\\{hz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
+\end{equation}
+
+\noindent{With this, the \cref{eq:sphere8} can be rewritten in linear form, given by:}
+
+\begin{equation} \label{eq:sphere9}
+\centering
+\small \bar{\bar{M}}\cdot{\bar{h}}_j={\bar{B}}_z
+\end{equation}
+
+%%
+\subsubsection{Inverse Model}
+
+\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers.
+Also assuming that there is no induced magnetization component, only that of the NRM.
+Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z and \bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}
+
+\noindent{The problem of estimating a parameter vector $\bar{h}$ containing the spheres' magnetization vectors can be solved by minimizing the objective function $f\left(\bar{h}\right)$:}
+
+\begin{equation} \label{eq:sphere10}
+\centering
+\small f\left(\bar{h}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{M}} \cdot \bar{h}-\bar{d})}^T \cdot ~ (\bar{\bar{M}} \cdot \bar{h}-\bar{B_z})
+\end{equation}
+
+\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{h}$ and equating the result to the zero vector ($\frac{\partial f}{\partial h_k}=\bar{0}$).
+Then we obtain the normal equation for estimating least squares solution given by:}
+
+\begin{equation} \label{eq:sphere11}
+\centering
+\small \bar{h}\ =\left({\bar{\bar{M}}}^T\cdot\bar{\bar{M}}\right)^{-1}\cdot ~ \left({\bar{\bar{M}}}^T\cdot{\bar{B}}_z\right)\ 
+\end{equation}
+
+\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
+To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
+
+\begin{equation} \label{eq:sphere12}
+\centering
+\small f\left(\widetilde{h}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{M}} \cdot \bar{h} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
+\end{equation}
+
+\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
+A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
+In this algorithm, at each iteration k, the following linear system is solved:}
+
+\begin{equation} \label{eq:sphere13}
+\centering
+\small {\widetilde{h}}^{k+1}=\left({\bar{\bar{M}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{M}}\right)^{-1}\cdot\left({\bar{\bar{M}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
+\end{equation}
+
+\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
+
+\begin{equation} \label{eq:sphere14}
+{r_i}^k=\frac{1}{\left|\left(\bar{\bar{M}}\cdot\bar{h}\right)_i-{{\bar{B_z}}}_i+e\right|}
+\end{equation}
+
+\begin{FlushRight}
+\noindent{Where: $e$ is a small positive number used to prevent singularities}
+\end{FlushRight}
+
+\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
+From this initial approximation ${\widetilde{h}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
+Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{h}}^1$.
+Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{h}}^ 2$, and so on.
+As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{h}$, which is called robust estimate \citep{OliveiraJr.2015}.
+According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
+
+\begin{equation} \label{eq:sphere15}
+\centering
+\frac{\lVert {\widetilde{h}}^{k+1} - {\widetilde{h}}^{k} \lVert}{1 + \lVert \widetilde{h}^{k+1} \lVert} ≤ \tau
+\end{equation}
+
+\begin{FlushRight}
+\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
+\end{FlushRight}
+
+%%
+\subsubsection{Directions of Magnetization and Uncertainty Propagation}
+
+\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
+These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.5\textwidth]{VECTORS.png}
+\caption{Schematic representation of vector $h_j$ (\cref{eq:sphere8}) with elements $hx_j$, $hy_j$ and $hz_j$ in cartesian coordinates.
+This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
+L.
+Source: \cite{OliveiraJr.2015}.}
+\label{fig:VECTORS}
+\end{figure}
+
+\noindent{In this way, it is possible to determine the magnetization directions $D_j$ and $I_j$ for the j-th sphere of the set of L spheres by using:}
+
+\begin{equation} \label{eq:sphere16}
+\centering
+\small D_j=\tan^{-1}{\left(\frac{{hy}_j}{{hx}_j}\right)}
+\end{equation}
+
+\begin{equation} \label{eq:sphere17}
+\centering
+\small I_j=\tan^{-1}{\left(\frac{{hz}_j}{\sqrt{\left({hx}_j\right)^2+\left({hy}_j\right)^2}}\right)}
+\end{equation}
+
+\noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
+Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{h}}_j$, regardless of the method used.
+Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
+The covariance matrix of these parameters will be given by:}
+
+\begin{equation} \label{eq:sphere18}
+\centering
+\small \bar{\bar{Cov}}\left({\bar{h}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{M}}}^T\cdot ~ \bar{\bar{M}}\right)^{-1} \ \ \text{(\emph{least square})}
+\end{equation}
+
+\begin{equation} \label{eq:sphere19}
+\centering
+\small \bar{\bar{Cov}}\left(\widetilde{h_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{M}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{M}}\right)^{-1} \ \ \text{(\emph{robust})}
+\end{equation}
+
+\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
+
+\begin{equation} \label{eq:sphere20}
+\centering
+\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({hx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({hy}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({hz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({hx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({hy}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({hz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
+\end{equation}
+
+\bigskip
+
+\noindent{Thus, for the j-th sphere:}
+
+\begin{equation} \label{eq:sphere20}
+\centering
+\sigma_{{hx}_j}=\sqrt{Var({hx}_j)},\ \ \ \  \sigma_{{hy}_j}=\sqrt{Var({hy}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{hz}_j}=\sqrt{Var({hz}_j)}
+\end{equation}
+
+\noindent{Thus, the propagation of uncertainties of the declination ($D_j$) and slope ($I_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
+
+\begin{equation} \label{eq:sphere21}
+\centering
+\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{hx}_j}\right)^2\cdot\ \left(\sigma_{{hx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{hy}_j}\right)^2\cdot\ \left(\sigma_{{hy}_j}\right)^2}
+\end{equation}
+
+\begin{equation} \label{eq:sphere22}
+\centering
+\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{hx}_j}\right)^2\cdot\ \left(\sigma_{{hx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{hy}_j}\right)^2\cdot\ \left(\sigma_{{hy}_j}\right)^2+\left(\frac{\partial I_j}{\partial{hz}_j}\right)^2\cdot\ \left(\sigma_{{hz}_j}\right)^2}
+\end{equation}
+
+\noindent{Where:}
+
+\begin{equation} \label{eq:sphere23}
+\centering
+\frac{\partial D_j}{\partial{hx}_j}=\frac{-{hy}_j}{{{hx}_j}^2+{{hy}_j}^2}
+\end{equation}
+
+\begin{equation} \label{eq:sphere24}
+\centering
+\frac{\partial D_j}{\partial{hy}_j}=\frac{{hx}_j}{{{hx}_j}^2+{{hy}_j}^2}
+\end{equation}
+
+\begin{equation} \label{eq:sphere25}
+\centering
+\frac{\partial I_j}{\partial{hx}_j}=\frac{-{hx}_j\cdot \ {hz}_j}{\sqrt{{{hx}_j}^2+{{hy}_j}^2}\cdot \left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\end{equation}
+
+\begin{equation} \label{eq:sphere26}
+\centering
+\frac{\partial I_j}{\partial{hy}_j}=\frac{-{hy}_j\cdot \ {hz}_j}{\sqrt{{{hx}_j}^2+{{hy}_j}^2}\cdot \left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\end{equation}
+
+\begin{equation} \label{eq:sphere27}
+\centering
+\frac{\partial I_j}{\partial{hz}_j}=\frac{\sqrt{{{hx}_j}^2+{{hy}_j}^2}}{\left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\end{equation}
+
+%%%
+\subsection{Euler Deconvolution}
+
+\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
+Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
+Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
+It is the application of a mobile operator in a small data window over the sampled data set.
+The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
+
+\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
+In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
+As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
+\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
+The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
+Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
+
+\begin{equation} \label{eq:HG}
+\centering
+\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
+\end{equation}
+
+%%%
+\subsubsection{Euler Deconvolution Formulation}
+
+\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_0$, y$_0$ and z$_0$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
+
+\begin{equation} \label{eq:euler1}
+\centering
+(x-x_0) \cdot \frac{\partial F}{\partial x} + (y-y_0) \cdot \frac{\partial F}{\partial y}+(z-z_0) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
+\end{equation}
+
+\begin{tabular}{ l }
+\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
+\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
+\end{tabular}
+
+\bigskip
+
+\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
+The structural index is the only necessary a priori knowledge.
+Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
+
+\begin{equation} \label{eq:euler2}
+\centering
+x_0 \cdot \frac{\partial F}{\partial x} + y_0 \cdot \frac{\partial F}{\partial y} + z_0 \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
+\end{equation}
+
+\noindent{The \cref{eq:euler2} can be written in matrix form as:}
+
+\begin{equation} \label{eq:euler3}
+\centering
+\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_0\\y_0\\z_0\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
+\end{equation}
+
+\begin{tabular}{ l }
+\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
+\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
+\noindent{represent the cartesian coordinates at the i-th observation point.}
+\end{tabular}
+
+\bigskip
+
+\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{m}=\bar{d}$ and its objective function $f(\bar{m} )$ expressed by:}
+
+\begin{equation} \label{eq:euler4}
+\centering
+f(\bar{m} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{m}-\bar{d})
+\end{equation}
+
+\noindent{The solution $\bar{m}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial m_k}=\bar{0})$ through the least squares estimator given by:}
+
+\begin{equation} \label{eq:euler5}
+\centering
+\bar{m}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
+\end{equation}
+
+\noindent{Thus, $\bar{m}=\left[x_0\ \ y_0\ \ z_0\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_0$, $y_0$, $z_0$) and the base level (b).}
+
+%%%%%%%%%%%%%
 \section{Results}

### 2022-10-12 article_1/New_model_LaTeX/abstract.tex
Add Total Grad function and optimize the code

--- 2022-06-15 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
-
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-\begin{document}
-
-\title{An example \emph{Geophysics} article, \\ with a two-line title}
-
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-
-\begin{abstract}
 \begin{singlespace}
@@
 \end{singlespace}
-\end{abstract}
-
-\section{Introduction}
-%\onehalfspacing
-\doublespacing
-
-\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}.
-It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}
-
-\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}.
-Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}.
-When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field.
-In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}.
-On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field.
-In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties.
-All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}
-
-\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$.
-The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number (N $>10^6$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
-
-\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}.
-In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the micromagnetic microscopy itself.}
-
-\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information.
-In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained.
-We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}
-
-\section{Methodology}
-
-\section{Results}
-
-\section{Discussion}
-
-\section{Conclusion}
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-\end{document}

### 2022-10-12 article_1/New_model_LaTeX/content.tex
Add Total Grad function and optimize the code

--- 2022-06-21 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
-
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-\usepackage{amsmath}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\graphicspath{ {./images/} } % images path
-
-\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
-
-\usepackage[document]{ragged2e} % to justify text
-
-%\usepackage{ragged2e}
-\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
-%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
-%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
-\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
-\captionsetup{compatibility=false, justification=justified, format=custom}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{blindtext} % Package to generate dummy text throughout this template 
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.05} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage[english]{babel} % Language hyphenation and typographical rules
-
-\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-
-\usepackage{enumitem} % Customized lists
-\setlist[itemize]{noitemsep} % Make itemize lists more compact
-
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[L]{Manuscript} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
-
-\setlength\parindent{24pt}
-%\usepackage{float}
-\usepackage{floatrow}
-\usepackage{pdfpages}
-\newsavebox\mysavebox
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{?????????????????}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{June 2022}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-\justify
-
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
-
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
-
 \section{Introduction}
@@
 Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z and \bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}
+Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}
 
@@
 
+%%%
+\subsection{Synthetic Data}
+
+\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}.
+Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm.
+Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}
+
+\floatsetup[table]{capposition=top} % to put the caption on the top of the table
+
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\begin{table}[htbp]
+\caption{Initial position and magnetization parameters for each spherical source.}
+\label{tab:directmodel}
+\centering
+\begin{tabular}[width=1.0\textwidth]{ccccccc}
+\rowcolor[HTML]{E7E7E7} 
+\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
+\rowcolor[HTML]{E7E7E7} 
+\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
+1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
+\rowcolor[HTML]{E7E7E7} 
+2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
+3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
+\rowcolor[HTML]{E7E7E7} 
+4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
+\end{tabular}
+\end{table}
+
+\subsubsection{Euler Solution}
+
+\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
+In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
+\cite{VanderWalt2014}.}
+
+\begin{table}[htbp]
+\caption{Central positions of sources input vs Euler deconvolution solutions.}
+\label{tab:eulerresults}
+\centering
+\begin{tabular}[width=1.0\textwidth]{ccccccc}
+\rowcolor[HTML]{E7E7E7} 
+\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
+\rowcolor[HTML]{E7E7E7} 
+\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
+1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
+\rowcolor[HTML]{E7E7E7} 
+2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
+3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
+\rowcolor[HTML]{E7E7E7} 
+4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
+\end{tabular}
+\end{table}
+
+\begin{table}[htbp]
+\caption{Input magnetization directions vs inversion solutions and their error propagation.}
+\label{tab:inversionresults}
+\centering
+\begin{tabular}[width=1.0\textwidth]{ccccccc}
+\rowcolor[HTML]{E7E7E7} 
+\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
+\rowcolor[HTML]{E7E7E7} 
+\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
+1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
+\rowcolor[HTML]{E7E7E7} 
+2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
+3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
+\rowcolor[HTML]{E7E7E7} 
+4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
+\end{tabular}
+\end{table}
+
 \section{Discussion}
@@
 
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-\end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data and code availability}
+
+The Python source code used to produce all results and figures presented here
+is available at
+\url{https://doi.org/10.6084/m9.figshare.13604360} and
+\url{https://github.com/compgeolab/eql-gradient-boosted}
+under the BSD 3-clause open-source license.
+
+The gradient-boosted equivalent sources implementation is based on the
+equivalent source code in the Harmonica library \citep{harmonica2020}.
+Other software used in this study includes:
+Pooch \citep{pooch2020} for downloading and caching datasets,
+Verde \citep{verde2018} for block reductions and coordinate manipulations,
+Boule \citep{boule2020} for normal gravity calculations,
+xarray \citep{xarray2017} and Numpy \citep{numpy2020} for handling
+multidimensional arrays and numerical computations,
+Numba \citep{numba2015} for just-in-time compilation and parallelization,
+scikit-learn \citep{sklearn2011} for cross-validation,
+Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
+the figures and maps,
+and the Jupyter notebook programming environment \citep{jupyter2016}.
+Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
+\citep{fatiando2013}.
+
+All datasets used are open-access and publicly available.
+The synthetic surveys were generated using
+a public domain gravity dataset for Southern Africa distributed by the
+NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
+and the Great Britain Aeromagnetic
+Survey distributed by the
+British Geological Survey (BGS) under an Open Government License
+(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
+The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
+\citet{tozer2019}.
+The Australian ground gravity
+data is based on a compilation distributed by Geoscience Australia under a
+Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
+was filtered and referenced to the WGS84 ellipsoid by
+\citet{australia_compilation} and is distributed under the same license
+(\url{https://doi.org/10.6084/m9.figshare.13643837}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Acknowledgements}
+
+We are indebted to the developers and maintainers of the open-source software
+without which this work would not have been possible.
+We would also like to thank Editor Frederik Simons, Assistant Editor Fern
+Storey, and two anonymous reviewers for their constructive comments.
+S.R. Soler is supported by a scholarship from CONICET, Argentina.
+This work contains British Geological Survey materials ©~UKRI.
+S.R. Soler and L. Uieda jointly developed the initial idea, analysed the
+results, and wrote the paper. S.R. Soler produced all results and developed the
+software implementation with the assistance of L. Uieda.

### 2022-10-12 article_1/article_1.tex
Add Total Grad function and optimize the code

@@
 \graphicspath{ {./images/} } % images path
+
+\usepackage{multirow} % for tables
+\usepackage[table,xcdraw]{xcolor}
+\usepackage{floatrow} % for caption on the top of the table
 

### 2022-10-12 article_1/code/Synthetic/functions.py
Separate functions into a functions.py file

@@ -1,0 +1,676 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+from skimage.feature import blob_log
+from apsg import *
+
+
+microm2m = 1.0E-6
+m2microm = 1.0E6
+
+def cartesian_components(D, I, Q, R):
+    
+    """
+    Calculates the cartesian components of  natural remanent magnetization (NRM)
+    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
+
+    Parameters:
+        * D: 1D-array containing magnetization declination (0 to 360 degrees)
+        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
+        * Q: 1D-array containing magnetization intensity (A/m)
+        * R: 1D-array containing sphere's radius (m)
+
+    """
+    
+    m = []
+
+    for i in range(np.size(D)):
+        m_sphere =  np.matrix([[(Q[i]*np.cos(I[i]*(np.pi/180))*np.cos(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
+                               [(Q[i]*np.cos(I[i]*(np.pi/180))*np.sin(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
+                               [(Q[i]*np.sin(I[i]*(np.pi/180)))*((4.0*np.pi*R[i]**3)/3.0)                            ]])
+
+        m = np.append(m,m_sphere)
+        
+    return(np.array(m))
+
+
+
+def sensibility_matrix(X, Y, Z, Xc, Yc, Zc): 
+    
+    """
+    Generates the sensibility matrix for vertical component of magnetization
+
+    Parameters:
+        *  X,  Y,  Z: 1D-arrays with x, y and z data positions
+        * Xc, Yc, Zc: 1D-arrays with x, y and z data  of the sphere's center positions
+
+    Constant:
+        * cm: is a constant given by 4*np.pi/µo = 10**(-7) 
+            where µo is the vaccum magnetic permeability
+    """
+
+    cm = 10**(-7) # H/m  == T·m/A
+
+    Mz = np.empty( (np.size(Xc)*3, np.size(Z)) )
+
+    
+    k = 0
+    l = 1
+    m = 2 
+
+    for j in range(len(Xc)):
+        
[…]

### 2022-11-09 article_1/article_1.tex
Add complex examples

@@
 %%%
+\subsection{Euler Deconvolution}
+
+\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
+Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
+Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
+It is the application of a mobile operator in a small data window over the sampled data set.
+The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
+
+\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
+In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
+As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
+\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
+The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
+Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
+
+\begin{equation} \label{eq:HG}
+\centering
+\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
+\end{equation}
+
+%%%
+\subsubsection{Euler Deconvolution Formulation}
+
+\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_0$, y$_0$ and z$_0$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
+
+\begin{equation} \label{eq:euler1}
+\centering
+(x-x_0) \cdot \frac{\partial F}{\partial x} + (y-y_0) \cdot \frac{\partial F}{\partial y}+(z-z_0) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
+\end{equation}
+
+\begin{tabular}{ l }
+\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
+\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
+\end{tabular}
+
+\bigskip
+
+\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
+The structural index is the only necessary a priori knowledge.
+Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
+
+\begin{equation} \label{eq:euler2}
+\centering
+x_0 \cdot \frac{\partial F}{\partial x} + y_0 \cdot \frac{\partial F}{\partial y} + z_0 \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
+\end{equation}
+
+\noindent{The \cref{eq:euler2} can be written in matrix form as:}
+
+\begin{equation} \label{eq:euler3}
+\centering
+\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_0\\y_0\\z_0\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
+\end{equation}
+
+\begin{tabular}{ l }
+\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
+\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
+\noindent{represent the cartesian coordinates at the i-th observation point.}
+\end{tabular}
+
+\bigskip
+
+\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{m}=\bar{d}$ and its objective function $f(\bar{m} )$ expressed by:}
+
+\begin{equation} \label{eq:euler4}
+\centering
+f(\bar{m} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{m}-\bar{d})
+\end{equation}
+
+\noindent{The solution $\bar{m}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial m_k}=\bar{0})$ through the least squares estimator given by:}
+
+\begin{equation} \label{eq:euler5}
+\centering
+\bar{m}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
+\end{equation}
+
+\noindent{Thus, $\bar{m}=\left[x_0\ \ y_0\ \ z_0\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_0$, $y_0$, $z_0$) and the base level (b).}
+
+%%%
 \subsection{Magnetic Inversion}
@@
 This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
-In this way it is possible to estimate the direction of magnetization from multiple sources.
+In this way, it is possible to estimate the direction of magnetization from multiple sources.
 The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
@@
 %%
-\subsubsection{Direct Model}
+\subsubsection{Parametrization and Forward Model}
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{VECTORS.png}
+\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
 \caption{Schematic representation of vector $h_j$ (\cref{eq:sphere8}) with elements $hx_j$, $hy_j$ and $hz_j$ in cartesian coordinates.
@@
 
-%%%
-\subsection{Euler Deconvolution}
-
-\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
-It is the application of a mobile operator in a small data window over the sampled data set.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
-
-\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
-As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
-\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
-The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
-Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
-
-\begin{equation} \label{eq:HG}
-\centering
-\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
-\end{equation}
-
-%%%
-\subsubsection{Euler Deconvolution Formulation}
-
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_0$, y$_0$ and z$_0$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
-
-\begin{equation} \label{eq:euler1}
-\centering
-(x-x_0) \cdot \frac{\partial F}{\partial x} + (y-y_0) \cdot \frac{\partial F}{\partial y}+(z-z_0) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
-\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
-\end{tabular}
-
-\bigskip
-
-\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
-The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
-
-\begin{equation} \label{eq:euler2}
-\centering
-x_0 \cdot \frac{\partial F}{\partial x} + y_0 \cdot \frac{\partial F}{\partial y} + z_0 \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
-\end{equation}
-
-\noindent{The \cref{eq:euler2} can be written in matrix form as:}
-
-\begin{equation} \label{eq:euler3}
-\centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_0\\y_0\\z_0\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
-\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
-\noindent{represent the cartesian coordinates at the i-th observation point.}
-\end{tabular}
-
-\bigskip
-
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{m}=\bar{d}$ and its objective function $f(\bar{m} )$ expressed by:}
-
-\begin{equation} \label{eq:euler4}
-\centering
-f(\bar{m} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{m}-\bar{d})
-\end{equation}
-
-\noindent{The solution $\bar{m}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial m_k}=\bar{0})$ through the least squares estimator given by:}
-
-\begin{equation} \label{eq:euler5}
-\centering
-\bar{m}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
-\end{equation}
-
-\noindent{Thus, $\bar{m}=\left[x_0\ \ y_0\ \ z_0\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_0$, $y_0$, $z_0$) and the base level (b).}
-
 %%%%%%%%%%%%%
@@
 \section{Conclusion}
+\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
+Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
+This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
+}
+
+\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
+In this way, reducing the numerous solutions to just one data window per source.
+After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
+
+\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
+This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
+Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
+Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
+
+\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
 

### 2022-11-09 article_1/code/Complex_Synthetic/functions.py

@@ -1,0 +1,676 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+from skimage.feature import blob_log
+from apsg import *
+
+
+microm2m = 1.0E-6
+m2microm = 1.0E6
+
+def cartesian_components(D, I, Q, R):
+    
+    """
+    Calculates the cartesian components of  natural remanent magnetization (NRM)
+    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
+
+    Parameters:
+        * D: 1D-array containing magnetization declination (0 to 360 degrees)
+        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
+        * Q: 1D-array containing magnetization intensity (A/m)
+        * R: 1D-array containing sphere's radius (m)
+
+    """
+    
+    m = []
+
+    for i in range(np.size(D)):
+        m_sphere =  np.matrix([[(Q[i]*np.cos(I[i]*(np.pi/180))*np.cos(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
+                               [(Q[i]*np.cos(I[i]*(np.pi/180))*np.sin(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
+                               [(Q[i]*np.sin(I[i]*(np.pi/180)))*((4.0*np.pi*R[i]**3)/3.0)                            ]])
+
+        m = np.append(m,m_sphere)
+        
+    return(np.array(m))
+
+
+
+def sensibility_matrix(X, Y, Z, Xc, Yc, Zc): 
+    
+    """
+    Generates the sensibility matrix for vertical component of magnetization
+
+    Parameters:
+        *  X,  Y,  Z: 1D-arrays with x, y and z data positions
+        * Xc, Yc, Zc: 1D-arrays with x, y and z data  of the sphere's center positions
+
+    Constant:
+        * cm: is a constant given by 4*np.pi/µo = 10**(-7) 
+            where µo is the vaccum magnetic permeability
+    """
+
+    cm = 10**(-7) # H/m  == T·m/A
+
+    Mz = np.empty( (np.size(Xc)*3, np.size(Z)) )
+
+    
+    k = 0
+    l = 1
+    m = 2 
+
+    for j in range(len(Xc)):
+        
[…]

### 2022-11-09 codes/synthetic_data/functions.py

@@ -371,7 +371,7 @@ def euler_windows_view(X_, Y_, Z_, d_, euler_windows_T, show_windows=False, colo
     x_step = (np.max(X_)*m2microm - np.min(X_)*m2microm) / (nx-1)
     
     plt.figure(figsize=figsize)
-    plt.contourf(Y_*m2microm, X_*m2microm, d_, cmap='jet')
+    plt.contourf(Y_*m2microm, X_*m2microm, d_, cmap='viridis')
     
     for i in range(np.shape(euler_windows_T)[0]):
         x1 = int(euler_windows_T[i,0]) * x_step

### 2022-11-10 article_1/article_1.tex
Change the equations format in article 1

@@
 
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_0$, y$_0$ and z$_0$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
+\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_c$, y$_c$ and z$_c$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
 
@@
 \centering
-(x-x_0) \cdot \frac{\partial F}{\partial x} + (y-y_0) \cdot \frac{\partial F}{\partial y}+(z-z_0) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
+(x-x_c) \cdot \frac{\partial F}{\partial x} + (y-y_c) \cdot \frac{\partial F}{\partial y}+(z-z_c) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
 \end{equation}
@@
 \centering
-x_0 \cdot \frac{\partial F}{\partial x} + y_0 \cdot \frac{\partial F}{\partial y} + z_0 \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
+x_c \cdot \frac{\partial F}{\partial x} + y_c \cdot \frac{\partial F}{\partial y} + z_c \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
 \end{equation}
@@
 \centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_0\\y_0\\z_0\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
+\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_c\\y_c\\z_c\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
 \end{equation}
@@
 
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{m}=\bar{d}$ and its objective function $f(\bar{m} )$ expressed by:}
+\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{p}=\bar{d}$ and its objective function $f(\bar{p} )$ expressed by:}
 
@@
 \centering
-f(\bar{m} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{m}-\bar{d})
+f(\bar{p} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{p}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{p}-\bar{d})
 \end{equation}
 
-\noindent{The solution $\bar{m}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial m_k}=\bar{0})$ through the least squares estimator given by:}
+\noindent{The solution $\bar{p}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial p_k}=\bar{0})$ through the least squares estimator given by:}
 
@@
 \centering
-\bar{m}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
+\bar{p}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
 \end{equation}
 
-\noindent{Thus, $\bar{m}=\left[x_0\ \ y_0\ \ z_0\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_0$, $y_0$, $z_0$) and the base level (b).}
+\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}
 
@@
 \centering
-b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot m \cdot \hat{m} \cdot \frac{1}{r^2} \cdot \hat{r}
+b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot M \cdot \hat{M} \cdot \frac{1}{r^2} \cdot \hat{r}
 \end{equation}
@@
 \centering
-{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{m}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
+{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{M}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
 \end{equation}
@@
 \noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
-\noindent{i = 1, 2, . .. N; and ${\bar{m}}^j=\left[{mx}_j\ {my}_j\ {mz}_j\right]^T$ is the vector formed by the cartesian} \\
-\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{m}}^j)$.}
+\noindent{i = 1, 2, . .. N; and ${\bar{M}}^j=\left[{Mx}_j\ {My}_j\ {Mz}_j\right]^T$ is the vector formed by the cartesian} \\
+\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{M}}^j)$.}
 \end{tabular}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{MODEL.png}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (points black).
+\includegraphics[width=0.5\textwidth]{MODEL.pdf}
+\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
 In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
@@
 
-\noindent{According to \cite{OliveiraJr.2015} the \cref{eq:sphere2} can be segmented into two members: (i) the first being a matrix $M_i^j$ encompassing the vector relationship with the positioning for each source and (ii) the second being $h_j$, which is the vector that encompasses the cartesian components of the magnetization of each sphere:}
+\noindent{The \cref{eq:sphere2} presents the sensitive matrix $A_i^j$ and the $m_j$, which is the vector that encompasses the cartesian components of the magnetc moment (magnetization times volume) of each sphere:}
 
 \begin{equation} \label{eq:sphere4}
-\small M_i^j =\left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
-h_j =\left[\begin{matrix}{{mx}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+\small A_i^j ={C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
+m_j =\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
 \end{equation}
@@
 \begin{equation} \label{eq:sphere5}
-\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}\cdot\ \left[\begin{matrix}{{mx}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
+\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}
+\cdot\ 
+\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
 \end{equation}
@@
 \begin{equation} \label{eq:sphere6}
-\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}\cdot\ \left[\begin{matrix}{{mx}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{my}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\{{mz}_{j\ \cdot}C}_m\cdot\frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
+\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
+\cdot\ 
+\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
 \end{equation}
@@
 \noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
-Thus, the vector ${\bar{m}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
+Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
 
 \begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
 \end{equation}
@@
 \begin{equation} \label{eq:sphere8}
-\small \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}\cdot\ \left[\begin{matrix}{hx}_j\\{hy}_j\\{hz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
+\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
+\cdot\ 
+\left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
 \end{equation}
@@
 \centering
-\small \bar{\bar{M}}\cdot{\bar{h}}_j={\bar{B}}_z
+\small \bar{\bar{A}}\cdot{\bar{m}}={\bar{B}}_z
 \end{equation}
@@
 Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{h}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{M}}$, the latter being obtained previously with the Euler Deconvolution.}
+Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{m}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{A}}$, the latter being obtained previously with the Euler Deconvolution.}
 
-\noindent{The problem of estimating a parameter vector $\bar{h}$ containing the spheres' magnetization vectors can be solved by minimizing the objective function $f\left(\bar{h}\right)$:}
+\noindent{The problem of estimating a parameter vector $\bar{m}$ containing the spheres' magnetic moment vectors can be solved by minimizing the objective function $f\left(\bar{m}\right)$:}
 
@@
 \centering
-\small f\left(\bar{h}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{M}} \cdot \bar{h}-\bar{d})}^T \cdot ~ (\bar{\bar{M}} \cdot \bar{h}-\bar{B_z})
+\small f\left(\bar{m}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{A}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{A}} \cdot \bar{m}-\bar{B_z})
 \end{equation}
 
-\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{h}$ and equating the result to the zero vector ($\frac{\partial f}{\partial h_k}=\bar{0}$).
+\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{m}$ and equating the result to the zero vector ($\frac{\partial f}{\partial m_k}=\bar{0}$).
 Then we obtain the normal equation for estimating least squares solution given by:}
@@
 \centering
-\small \bar{h}\ =\left({\bar{\bar{M}}}^T\cdot\bar{\bar{M}}\right)^{-1}\cdot ~ \left({\bar{\bar{M}}}^T\cdot{\bar{B}}_z\right)\ 
+\small \bar{m}\ =\left({\bar{\bar{A}}}^T\cdot\bar{\bar{A}}\right)^{-1}\cdot ~ \left({\bar{\bar{A}}}^T\cdot{\bar{B}}_z\right)\ 
 \end{equation}
@@
 \centering
-\small f\left(\widetilde{h}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{M}} \cdot \bar{h} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
+\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
 \end{equation}
@@
 \centering
-\small {\widetilde{h}}^{k+1}=\left({\bar{\bar{M}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{M}}\right)^{-1}\cdot\left({\bar{\bar{M}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
+\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
 \end{equation}
@@
 \begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{M}}\cdot\bar{h}\right)_i-{{\bar{B_z}}}_i+e\right|}
+{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
 \end{equation}
@@
 \noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{h}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{h}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{h}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{h}$, which is called robust estimate \citep{OliveiraJr.2015}.
+From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
+Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
+Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
+As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
 According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
@@
 \centering
-\frac{\lVert {\widetilde{h}}^{k+1} - {\widetilde{h}}^{k} \lVert}{1 + \lVert \widetilde{h}^{k+1} \lVert} ≤ \tau
+\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
 \end{equation}
@@
 \includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $h_j$ (\cref{eq:sphere8}) with elements $hx_j$, $hy_j$ and $hz_j$ in cartesian coordinates.
+\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
 This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
 L.
-Source: \cite{OliveiraJr.2015}.}
+Modified from: \cite{OliveiraJr.2015}.}
 \label{fig:VECTORS}
@@
 
-\noindent{In this way, it is possible to determine the magnetization directions $D_j$ and $I_j$ for the j-th sphere of the set of L spheres by using:}
+\noindent{In this way, it is possible to determine the directions ($D_j$ and $I_j$) and magnetic moment ($m_j$) for the j-th sphere of the set of L spheres by using:}
 
@@
 \centering
-\small D_j=\tan^{-1}{\left(\frac{{hy}_j}{{hx}_j}\right)}
+\small D_j=\tan^{-1}{\left(\frac{{my}_j}{{mx}_j}\right)}
 \end{equation}
@@
 \centering
-\small I_j=\tan^{-1}{\left(\frac{{hz}_j}{\sqrt{\left({hx}_j\right)^2+\left({hy}_j\right)^2}}\right)}
+\small I_j=\tan^{-1}{\left(\frac{{mz}_j}{\sqrt{\left({mx}_j\right)^2+\left({my}_j\right)^2}}\right)}
+\end{equation}
+
+\begin{equation} \label{eq:sphere17_m}
+\centering
+\small m_j=\sqrt{ {\left({mx}_j\right)}^{2} + {\left({my}_j\right)}^{2} + {\left({mz}_j\right)}^{2} } 
 \end{equation}
@@
 \noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
-Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{h}}_j$, regardless of the method used.
+Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{m}}_j$, regardless of the method used.
 Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
@@
 \centering
-\small \bar{\bar{Cov}}\left({\bar{h}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{M}}}^T\cdot ~ \bar{\bar{M}}\right)^{-1} \ \ \text{(\emph{least square})}
+\small \bar{\bar{Cov}}\left({\bar{m}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{least square})}
 \end{equation}
@@
 \centering
-\small \bar{\bar{Cov}}\left(\widetilde{h_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{M}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{M}}\right)^{-1} \ \ \text{(\emph{robust})}
+\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
 \end{equation}
@@
 \centering
-\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({hx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({hy}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({hz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({hx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({hy}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({hz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
+\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
 \end{equation}
@@
 \centering
-\sigma_{{hx}_j}=\sqrt{Var({hx}_j)},\ \ \ \  \sigma_{{hy}_j}=\sqrt{Var({hy}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{hz}_j}=\sqrt{Var({hz}_j)}
+\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
 \end{equation}
 
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$) and slope ($I_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
+\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
 
@@
 \centering
-\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{hx}_j}\right)^2\cdot\ \left(\sigma_{{hx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{hy}_j}\right)^2\cdot\ \left(\sigma_{{hy}_j}\right)^2}
+\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
 \end{equation}
@@
 \centering
-\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{hx}_j}\right)^2\cdot\ \left(\sigma_{{hx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{hy}_j}\right)^2\cdot\ \left(\sigma_{{hy}_j}\right)^2+\left(\frac{\partial I_j}{\partial{hz}_j}\right)^2\cdot\ \left(\sigma_{{hz}_j}\right)^2}
+\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
+\end{equation}
+
+\begin{equation} \label{eq:sphere22_m}
+\centering
+\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
 \end{equation}
@@
 \centering
-\frac{\partial D_j}{\partial{hx}_j}=\frac{-{hy}_j}{{{hx}_j}^2+{{hy}_j}^2}
+\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
 \end{equation}
@@
 \centering
-\frac{\partial D_j}{\partial{hy}_j}=\frac{{hx}_j}{{{hx}_j}^2+{{hy}_j}^2}
+\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
 \end{equation}
@@
 \centering
-\frac{\partial I_j}{\partial{hx}_j}=\frac{-{hx}_j\cdot \ {hz}_j}{\sqrt{{{hx}_j}^2+{{hy}_j}^2}\cdot \left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
 \end{equation}
@@
 \centering
-\frac{\partial I_j}{\partial{hy}_j}=\frac{-{hy}_j\cdot \ {hz}_j}{\sqrt{{{hx}_j}^2+{{hy}_j}^2}\cdot \left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
 \end{equation}
@@
 \centering
-\frac{\partial I_j}{\partial{hz}_j}=\frac{\sqrt{{{hx}_j}^2+{{hy}_j}^2}}{\left({{hx}_j}^2+{{hy}_j}^2+{{hz}_j}^2\right)}
+\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
+\end{equation}
+
+\begin{equation} \label{eq:sphere28}
+\centering
+\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
+\end{equation}
+
+\begin{equation} \label{eq:sphere29}
+\centering
+\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
+\end{equation}
+
+\begin{equation} \label{eq:sphere30}
+\centering
+\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
 \end{equation}

### 2022-11-11 article_1/article_1.tex
Add a better description for the Euler deconvolution technique

@@
 
-\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
-It is the application of a mobile operator in a small data window over the sampled data set.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
+\noindent{\cite{Thompson1982} proposed the Euler Deconvolution technique, which is a consolidated method classically applied to data from aeromagnetic surveys that uses first order x, y and z derivatives to determine the positioning and depth of ideal targets (e.g., sphere, cylinder), each characterized by a structural index \citep{Nabighian2005}.
+Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990}.
+Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).}
 
-\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
-As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
-\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
-The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
-Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
+\noindent{The classic Euler approach is basically the application of a mobile operator in a small data window over the sampled dataset.
+The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.
+Despite this, this methodology usually yields a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
+In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest a previous application of a method for delimitating the region of each source that generates the potential field and later the application of Euler's Deconvolution.
+Hence giving a single system of linear equations to be solved for each source.}
+
+\noindent{Derivative-based filters are widely used to emphisize the potencial anomaly signal of shallower sources and applied in modern methods for edge/position detection, as of the solution of Euler equation itself requires the gradient of the potential field.
+Since the calculation of first order derivatives is a must in this case, we might as well give preference to filtering techniques that use the same products.
+One good filtering example is the so called horizontal gradient method ($\nabla H$, \cref{eq:HG}) \citep{Cordell1982}, which is a source edge detection methodology where the response of a target's horizontal gradient tends to overlap its own limits, thus obtaining a two-dimensional robust map of the sources location \cite{Blakely1996}.
+Another popular method for locating edges of magnetic bodies is the total gradient ($\nabla T$, \cref{eq:TG}), which places the source's maximum anomaly values over the area inside its boundaries, despite of  geomagnetic latitude, magnetization direction or source dip/geometry \citep{Nabighian2005}.
+Both total and horizontal gradients are reliable techniques to be applied with the SMM data.}
 
@@
 \end{equation}
+
+\begin{equation} \label{eq:TG}
+\centering
+\nabla T= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2+{\left( \frac{∂F}{∂z} \right)}^2 }
+\end{equation}
+
+\noindent{After pre processing the data with derivative-based filter, highlighting the sources edges, it is possible to apply blob detection techniques.
+The latter refers to visual algorithms and/or modules with the ability of detecting points/regions that are either darker or brighter than the neighborhood.
+The most common and accurate approach to detect brighter blobs on dark surroundings is the Laplacian of Gaussian (LoG), its downside is also being slower than other approaches \citep{Han2016, Kong2013}.
+We used the \href{https://scikit-image.org/docs/stable/auto_examples/features_detection/plot_blob.html#sphx-glr-auto-examples-features-detection-plot-blob-py}{scikit-image blob detection} python library \citep{VanderWalt2014} to identify the window region of data that embraces each isolated source by applying the algorithm on the highlighted sources map ($\nabla T$ or $\nabla H$).
+Therefore, the blobs selected are local maxima obtained with successively LoG images.
+Once the target location window is determined, subsequently, the Euler Deconvolution can applied in this single static data window yeilding only one solution per source.
+Thus, being an automatic, faster and easier way than the classical methodology of solving the Euler equation.}
 

### 2022-11-18 article_1/article_1.tex
Export latex tables automatically from the Notebook

@@
 \newsavebox\mysavebox
+
+\usepackage{booktabs} % to import tables directly from python
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
+Although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
 With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
@@
 
-\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}
+\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates source center ($x_c$, $y_c$, $z_c$) and the base level (b).}
 
@@
 
-\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
+\noindent{The magnetization is usually represented in spherical coordinates of intensity (M (A/m)), declination (D (°)) and inclination (I (°)).
 Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
@@
 \begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
+\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=M_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
 \end{equation}
@@
 
-\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
-To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
-
-\begin{equation} \label{eq:sphere12}
-\centering
-\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
-\end{equation}
-
-\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
-A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
-In this algorithm, at each iteration k, the following linear system is solved:}
-
-\begin{equation} \label{eq:sphere13}
-\centering
-\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
-\end{equation}
-
-\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
-
-\begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $e$ is a small positive number used to prevent singularities}
-\end{FlushRight}
-
-\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
-According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
-
-\begin{equation} \label{eq:sphere15}
-\centering
-\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
-\end{FlushRight}
-
 %%
@@
 \noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
+These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
 
@@
 \centering
-\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
+\small \bar{\bar{Cov}}= \left[~ \text{\emph{diag}}\left(\begin{matrix}{\sigma_{{mx}_1}}^2&{\sigma_{{my}_1}}^2&{\sigma_{{mz}_1}}^2&\cdots&{\sigma_{{mz}_L}}^2\end{matrix}\right) \right]_{\text{\tiny 3L $\times$ 3L}}\
 \end{equation}
@@
 \centering
-\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
+\sigma_{{mx}_j}=\sqrt{{\sigma_{{mx}_j}}^2},\ \ \ \  \sigma_{{my}_j}=\sqrt{{\sigma_{{my}_j}}^2}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{{\sigma_{{mz}_j}}^2}
 \end{equation}
 
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
+\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in Appendix A.2) obtained in \cref{eq:sphere20}:}
 
@@
 \centering
-\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
+\small \sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
 \end{equation}
@@
 \centering
-\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
+\small \sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
 \end{equation}
@@
 \centering
-\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
+\small \sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
 \end{equation}
 
-\noindent{Where:}
+%%%%%%%%%%%%%
+\section{Results}
+
+%%%
+\subsection{Synthetic Data}
+
+\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}.
+Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm.
+Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
+\caption{blablabla.}
+\label{fig:SimpleSynthetic}
+\end{figure}
+
+\floatsetup[table]{capposition=top} % to put the caption on the top of the table
+
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\input{input_par_table}
+
+\subsubsection{Euler Solution}
+
+\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
+In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
+\cite{VanderWalt2014}.}
+
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\input{solution_par_table}
+
+\section{Discussion}
+
+\section{Conclusion}
+\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
+Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
+This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
+}
+
+\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
+In this way, reducing the numerous solutions to just one data window per source.
+After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
+
+\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
+This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
+Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
+Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
+
+\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }
+
+\begin{singlespace}
+\doublespacing
+\bibliographystyle{agu}  % style file is seg.bst
+\bibliography{article1}
+\end{singlespace}
+
+\section{Appendix A}
+\subsection{Appendix A.1} \label{AppendixA.1}
+
+\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
+To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
+
+\begin{equation} \label{eq:sphere12}
+\centering
+\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
+\end{equation}
+
+\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
+A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
+In this algorithm, at each iteration k, the following linear system is solved:}
+
+\begin{equation} \label{eq:sphere13}
+\centering
+\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
+\end{equation}
+
+\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
+
+\begin{equation} \label{eq:sphere14}
+{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
+\end{equation}
+
+\begin{FlushRight}
+\noindent{Where: $e$ is a small positive number used to prevent singularities}
+\end{FlushRight}
+
+\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
+From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
+Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
+Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
+As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
+According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
+
+\begin{equation} \label{eq:sphere15}
+\centering
+\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
+\end{equation}
+
+\begin{FlushRight}
+\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
+\end{FlushRight}
+
+\subsection{Appendix A.2} \label{AppendixA.2}
 
@@
 
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm.
-Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\begin{table}[htbp]
-\caption{Initial position and magnetization parameters for each spherical source.}
-\label{tab:directmodel}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
-1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
-3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
-\end{tabular}
-\end{table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-\begin{table}[htbp]
-\caption{Central positions of sources input vs Euler deconvolution solutions.}
-\label{tab:eulerresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
-1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
-3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
-\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-\caption{Input magnetization directions vs inversion solutions and their error propagation.}
-\label{tab:inversionresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
-1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
-3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
-\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
-}
-
-\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
-
-\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
-This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
-
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
 \end{document}

### 2022-11-18 article_1/input_par_table.tex
Export latex tables automatically from the Notebook

\begin{table}[htbp]
\caption{Initial position and magnetization parameters for each spherical source.}
\label{tab:ModelTab}
\resizebox{1.0\textwidth}{!}{
\tiny
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.00                       & 250.00                       & 5.30                       & 8.70e-15               & -140.00                        & -30.00                 \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 500.00                       & 500.00                       & 7.75                       & 7.63e-15               & 0.00                        & 62.00                 \\
3                                                & 750.00                       & 750.00                       & 8.50                       & 6.21e-15               & -70.00                        & -50.00                 \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.00                       & 800.00                       & 10.00                       & 6.66e-15               & 125.00                        & 22.00                  \\ \hline                 
\end{tabular}
}
\end{table}

### 2022-11-18 article_1/solution_par_table.tex
Export latex tables automatically from the Notebook

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.03           & 249.99           & 5.33           & 8.75e-15  $\pm$  2.30e-17           & -140.04  $\pm$  0.19           & -29.76  $\pm$  0.13           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 499.96           & 500.05           & 7.70           & 7.60e-15  $\pm$  2.90e-17           & 1.17  $\pm$  0.61           & 62.50  $\pm$  0.27           \\
3                                                & 750.12           & 750.04           & 8.47           & 6.19e-15  $\pm$  3.52e-17           & -71.88  $\pm$  0.60           & -50.02  $\pm$  0.35           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.02           & 799.73           & 10.08           & 6.73e-15  $\pm$  5.05e-17           & 124.28  $\pm$  0.48           & 22.78  $\pm$  0.34           \\ \hline                 
\end{tabular}
}
\end{table}

### 2022-11-22 article_1/Appendix.tex
Split LaTeX files

--- 2022-11-10 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
-
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-\usepackage{amsmath}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\graphicspath{ {./images/} } % images path
-
-\usepackage{multirow} % for tables
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{floatrow} % for caption on the top of the table
-
-\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
-
-\usepackage[document]{ragged2e} % to justify text
-
-%\usepackage{ragged2e}
-\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
-%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
-%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
-\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
-\captionsetup{compatibility=false, justification=justified, format=custom}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{blindtext} % Package to generate dummy text throughout this template 
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.05} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage[english]{babel} % Language hyphenation and typographical rules
-
-\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-
-\usepackage{enumitem} % Customized lists
-\setlist[itemize]{noitemsep} % Make itemize lists more compact
-
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[L]{Manuscript} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
-
-\setlength\parindent{24pt}
-%\usepackage{float}
-\usepackage{floatrow}
-\usepackage{pdfpages}
-\newsavebox\mysavebox
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{?????????????????}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{June 2022}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-\justify
-
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
-
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
-
-\section{Introduction}
-%\onehalfspacing
-\doublespacing
-
-\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}.
-It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}
-
-\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}.
-Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}.
-When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field.
-In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}.
-On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field.
-In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties.
-All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}
-
-\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$.
-The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
-
-\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}.
-In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}
-
-\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information.
-In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained.
-We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}
-
-%%%%%%%%%%%%%
-
-\section{Methodology}
-%%%
-\subsection{Scanning Magnetic Microscopy}
-
-\noindent{Scanning magnetic microscopy (SMM) is the imaging technique in which a thin-section sample of geological material is horizontally displaced under a high-precision (fixed) micromagnetometer to obtain magnetization \citep{Weiss2007}.
-The SMM performed at a fixed height above the sample also has the advantage of facilitating the subtraction of the ambient field (constant), to which it might be subject during the scan \citep{Lima2013}.
-The availability of high-performance and low-cost magnetic sensors has promoted a great advance in the application of SMM in recent years.
-However, its sensitivity is still a few orders of magnitude lower than that of superconducting quantum interference devices (SQUIDs), the latter being between 10$^{-12}$ and 10$^{-15}$ Am$^2$ \citep{Lima2013}.
-This disadvantage is offset by (i) the high spatial resolution of the SMM, as it is performed at a few tens of micrometers from the sampled surface; and (ii) SQUID magnetic microscopy is performed at low temperatures ($<$ 100K), which can cause changes in the original NRM of the sample, while SMM is performed at room temperature \citep{Lima2013, Weiss2007}.}
-
-\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
-An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
-Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
-Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{QDM.png}
-\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
-The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a 	minimum sensor-sample distance of 5 μm.
-The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
-Source: \cite{Fu2020}.}
-\label{fig:QDM}
-\end{figure}
-
-\noindent{Due to the similarities between magnetic microscopy techniques and aeromagnetic surveys, the methodologies of data inversion of the latter, densely studied in the last decades, can be adapted for magnetic microscopy.
-However, \cite{Lima2013} report important distinctions between SMM and aeromagnetic surveys, namely: (i) the source distribution in the SMM can often be accurately modeled in a two-dimensional model; (ii) the SMM measures the field produced directly by the sample's NRM; (iii) the sensor positioning is very accurate in the SMM, and the vertical component of the magnetic field is usually measured, rather than the total field; (iv) there is no need for correction to bring all measurements to the same surface or to grid the data; and (v) the distributions of the magnetization sources are finite and known.}
-
-%%%
-\subsection{Euler Deconvolution}
-
-\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
-It is the application of a mobile operator in a small data window over the sampled data set.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
-
-\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
-As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
-\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
-The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
-Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
-
-\begin{equation} \label{eq:HG}
-\centering
-\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
-\end{equation}
-
-%%%
-\subsubsection{Euler Deconvolution Formulation}
-
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_c$, y$_c$ and z$_c$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
-
-\begin{equation} \label{eq:euler1}
-\centering
-(x-x_c) \cdot \frac{\partial F}{\partial x} + (y-y_c) \cdot \frac{\partial F}{\partial y}+(z-z_c) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
-\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
-\end{tabular}
-
-\bigskip
-
-\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
-The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
-
-\begin{equation} \label{eq:euler2}
-\centering
-x_c \cdot \frac{\partial F}{\partial x} + y_c \cdot \frac{\partial F}{\partial y} + z_c \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
-\end{equation}
-
-\noindent{The \cref{eq:euler2} can be written in matrix form as:}
-
-\begin{equation} \label{eq:euler3}
-\centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_c\\y_c\\z_c\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
-\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
-\noindent{represent the cartesian coordinates at the i-th observation point.}
-\end{tabular}
-
-\bigskip
-
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{p}=\bar{d}$ and its objective function $f(\bar{p} )$ expressed by:}
-
-\begin{equation} \label{eq:euler4}
-\centering
-f(\bar{p} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{p}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{p}-\bar{d})
-\end{equation}
-
-\noindent{The solution $\bar{p}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial p_k}=\bar{0})$ through the least squares estimator given by:}
-
-\begin{equation} \label{eq:euler5}
-\centering
-\bar{p}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
-\end{equation}
-
-\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}
-
-%%%
-\subsection{Magnetic Inversion}
-
-\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination).
-This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
-In this way, it is possible to estimate the direction of magnetization from multiple sources.
-The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
-
-\noindent{Currently, the main inversion limitations for these type of data are: (i) in part because the sampling scale during measurement is insufficiently accurate and (ii) because of the non-singularity of the magnetic inversion  \citep{Lima2013}.
-The basic mathematical structure associated with the inverse problem of aeromagnetic data can be adapted and used in SMM data due to its similarity, despite the non-singularity caused by the infinite number of solutions for the same observed magnetic field  \citep{Weiss2007}.
-Assigning as much information as possible about the analyzed sample and the experimental environment can reduce this ambiguity by recovering the magnetization direction.
-In particles with unidirectional magnetization, and without magnetization sources outside the sample area, it is possible to guarantee singularity for the inverse problem in SMM  \citep{Baratchart2013}.
-Associating the fact that there is a singularity in the response of uniformly magnetized particles and that ferromagnetic particles (\emph{l.s.}) with stable magnetization have such a characteristic, therefore, the inversion method becomes ideal for the purpose of this project.}
-
-%%
-\subsubsection{Parametrization and Forward Model}
-
-\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions.
-Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources.
-According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}
-
-\begin{equation} \label{eq:sphere1}
-\centering
-b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot M \cdot \hat{M} \cdot \frac{1}{r^2} \cdot \hat{r}
-\end{equation}
-
-\noindent{Whereas the magnetic sources can be represented by a set of L uniformly magnetized spheres.
-In this case, each sphere will have a contribution in the field measured at the position ($x_i$, $y_i$, $z_i$):}
-
-\begin{equation} \label{eq:sphere2}
-\centering
-{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{M}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $C_m=\ \frac{\mu_0}{4\pi}=\ {10}^{-7}\frac{\ H}{m}$; $R_j$ is the radius of the j-th sphere; $r_{i,j}$ is the distance}   \\ 
-\noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
-\noindent{i = 1, 2, . .. N; and ${\bar{M}}^j=\left[{Mx}_j\ {My}_j\ {Mz}_j\right]^T$ is the vector formed by the cartesian} \\
-\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{M}}^j)$.}
-\end{tabular}
-
-\bigskip
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{MODEL.pdf}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:MODEL}
-\end{figure}
-
-\noindent{Thus, the total magnetization measured at the position ($x_i$, $y_i$, $z_i$) will be the sum of contributions from the L spheres, given by:}
-
-\begin{equation} \label{eq:sphere3}
-\centering
-B_i=\sum_{j=1}^{L}b_i^j
-\end{equation}
-
-\noindent{The \cref{eq:sphere2} presents the sensitive matrix $A_i^j$ and the $m_j$, which is the vector that encompasses the cartesian components of the magnetc moment (magnetization times volume) of each sphere:}
-
-\begin{equation} \label{eq:sphere4}
-\small A_i^j ={C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
-m_j =\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\frac{1}{r_j}\equiv\frac{1}{\sqrt{\left(x_i-{xc}_j\right)^2+\left(y_i-{yc}_j\right)^2+\left(z_i-{zc}_j\right)^2}}$}
-\end{FlushRight}
-
-\noindent{Subsequently, the components of the total magnetizing field can be obtained (from \cref{eq:sphere3}), as shown below:}
-
-\begin{equation} \label{eq:sphere5}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
-\end{equation}
-
-\noindent{As in the specific case in the study of magnetic microscopy, in the routine practice, the vertical component of magnetization is usually measured.
-In this case, there is a need to adapt the \cref{eq:sphere5} to isolate the response from the vertical component ($B_z$).
-Therefore, the equation of the direct model will be given by:}
-
-\begin{equation} \label{eq:sphere6}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
-Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
-
-\begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\noindent{We can simplify the \cref{eq:sphere6} to:}
-
-\begin{equation} \label{eq:sphere8}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{With this, the \cref{eq:sphere8} can be rewritten in linear form, given by:}
-
-\begin{equation} \label{eq:sphere9}
-\centering
-\small \bar{\bar{A}}\cdot{\bar{m}}={\bar{B}}_z
-\end{equation}
-
-%%
-\subsubsection{Inverse Model}
-
-\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers.
-Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{m}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{A}}$, the latter being obtained previously with the Euler Deconvolution.}
-
-\noindent{The problem of estimating a parameter vector $\bar{m}$ containing the spheres' magnetic moment vectors can be solved by minimizing the objective function $f\left(\bar{m}\right)$:}
-
-\begin{equation} \label{eq:sphere10}
-\centering
-\small f\left(\bar{m}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{A}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{A}} \cdot \bar{m}-\bar{B_z})
-\end{equation}
-
-\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{m}$ and equating the result to the zero vector ($\frac{\partial f}{\partial m_k}=\bar{0}$).
-Then we obtain the normal equation for estimating least squares solution given by:}
-
-\begin{equation} \label{eq:sphere11}
-\centering
-\small \bar{m}\ =\left({\bar{\bar{A}}}^T\cdot\bar{\bar{A}}\right)^{-1}\cdot ~ \left({\bar{\bar{A}}}^T\cdot{\bar{B}}_z\right)\ 
-\end{equation}
+\section{Appendix A}
+\subsection{Appendix A.1}
+\label{AppendixA1}
 
@@
 
-%%
-\subsubsection{Directions of Magnetization and Uncertainty Propagation}
-
-\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
-This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
-L.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:VECTORS}
-\end{figure}
-
-\noindent{In this way, it is possible to determine the directions ($D_j$ and $I_j$) and magnetic moment ($m_j$) for the j-th sphere of the set of L spheres by using:}
-
-\begin{equation} \label{eq:sphere16}
-\centering
-\small D_j=\tan^{-1}{\left(\frac{{my}_j}{{mx}_j}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17}
-\centering
-\small I_j=\tan^{-1}{\left(\frac{{mz}_j}{\sqrt{\left({mx}_j\right)^2+\left({my}_j\right)^2}}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17_m}
-\centering
-\small m_j=\sqrt{ {\left({mx}_j\right)}^{2} + {\left({my}_j\right)}^{2} + {\left({mz}_j\right)}^{2} } 
-\end{equation}
-
-\noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
-Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{m}}_j$, regardless of the method used.
-Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
-The covariance matrix of these parameters will be given by:}
-
-\begin{equation} \label{eq:sphere18}
-\centering
-\small \bar{\bar{Cov}}\left({\bar{m}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{least square})}
-\end{equation}
+\noindent{The convariance matrix for the uncertainties propagation also is updated with the ${\bar{\bar{R}}}^k$, as shown in the \cref{eq:sphere19}:}
 
@@
 
-\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
+\subsection{Appendix A.2} 
+\label{AppendixA2}
 
-\begin{equation} \label{eq:sphere20}
-\centering
-\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
-\end{equation}
-
-\bigskip
-
-\noindent{Thus, for the j-th sphere:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
-\end{equation}
-
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
-
-\begin{equation} \label{eq:sphere21}
-\centering
-\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22}
-\centering
-\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22_m}
-\centering
-\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\noindent{Where:}
+\noindent{The derivatives of the propagation functions of the uncertainties of the declination ($\sigma_{D_j}$), inclination ($\sigma_{I_j}$) and magnetic moment ($\sigma_{m_j}$) in relation to each parameter ($mx_j, my_j, mz_j$) are detailed below:}
 
@@
 \end{equation}
-
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm.
-Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\begin{table}[htbp]
-\caption{Initial position and magnetization parameters for each spherical source.}
-\label{tab:directmodel}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
-1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
-3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
-\end{tabular}
-\end{table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-\begin{table}[htbp]
-\caption{Central positions of sources input vs Euler deconvolution solutions.}
-\label{tab:eulerresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
-1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
-3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
-\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-\caption{Input magnetization directions vs inversion solutions and their error propagation.}
-\label{tab:inversionresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
-1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
-3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
-\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
-}
-
-\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
-
-\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
-This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
-
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-\end{document}

### 2022-11-22 article_1/Conclusion.tex
Split LaTeX files

--- 2022-11-10 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
+\section{Conclusion}
 
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-\usepackage{amsmath}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\graphicspath{ {./images/} } % images path
-
-\usepackage{multirow} % for tables
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{floatrow} % for caption on the top of the table
-
-\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
-
-\usepackage[document]{ragged2e} % to justify text
-
-%\usepackage{ragged2e}
-\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
-%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
-%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
-\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
-\captionsetup{compatibility=false, justification=justified, format=custom}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{blindtext} % Package to generate dummy text throughout this template 
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.05} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage[english]{babel} % Language hyphenation and typographical rules
-
-\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-
-\usepackage{enumitem} % Customized lists
-\setlist[itemize]{noitemsep} % Make itemize lists more compact
-
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[L]{Manuscript} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
-
-\setlength\parindent{24pt}
-%\usepackage{float}
-\usepackage{floatrow}
-\usepackage{pdfpages}
-\newsavebox\mysavebox
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{?????????????????}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{June 2022}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-\justify
-
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
-
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
-
-\section{Introduction}
-%\onehalfspacing
-\doublespacing
-
-\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}.
-It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}
-
-\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}.
-Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}.
-When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field.
-In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}.
-On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field.
-In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties.
-All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}
-
-\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$.
-The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
-
-\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}.
-In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}
-
-\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information.
-In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained.
-We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}
-
-%%%%%%%%%%%%%
-
-\section{Methodology}
-%%%
-\subsection{Scanning Magnetic Microscopy}
-
-\noindent{Scanning magnetic microscopy (SMM) is the imaging technique in which a thin-section sample of geological material is horizontally displaced under a high-precision (fixed) micromagnetometer to obtain magnetization \citep{Weiss2007}.
-The SMM performed at a fixed height above the sample also has the advantage of facilitating the subtraction of the ambient field (constant), to which it might be subject during the scan \citep{Lima2013}.
-The availability of high-performance and low-cost magnetic sensors has promoted a great advance in the application of SMM in recent years.
-However, its sensitivity is still a few orders of magnitude lower than that of superconducting quantum interference devices (SQUIDs), the latter being between 10$^{-12}$ and 10$^{-15}$ Am$^2$ \citep{Lima2013}.
-This disadvantage is offset by (i) the high spatial resolution of the SMM, as it is performed at a few tens of micrometers from the sampled surface; and (ii) SQUID magnetic microscopy is performed at low temperatures ($<$ 100K), which can cause changes in the original NRM of the sample, while SMM is performed at room temperature \citep{Lima2013, Weiss2007}.}
-
-\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
-An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
-Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
-Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{QDM.png}
-\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
-The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a 	minimum sensor-sample distance of 5 μm.
-The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
-Source: \cite{Fu2020}.}
-\label{fig:QDM}
-\end{figure}
-
-\noindent{Due to the similarities between magnetic microscopy techniques and aeromagnetic surveys, the methodologies of data inversion of the latter, densely studied in the last decades, can be adapted for magnetic microscopy.
-However, \cite{Lima2013} report important distinctions between SMM and aeromagnetic surveys, namely: (i) the source distribution in the SMM can often be accurately modeled in a two-dimensional model; (ii) the SMM measures the field produced directly by the sample's NRM; (iii) the sensor positioning is very accurate in the SMM, and the vertical component of the magnetic field is usually measured, rather than the total field; (iv) there is no need for correction to bring all measurements to the same surface or to grid the data; and (v) the distributions of the magnetization sources are finite and known.}
-
-%%%
-\subsection{Euler Deconvolution}
-
-\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
-It is the application of a mobile operator in a small data window over the sampled data set.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
-
-\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
-As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
-\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
-The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
-Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
-
-\begin{equation} \label{eq:HG}
-\centering
-\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
-\end{equation}
-
-%%%
-\subsubsection{Euler Deconvolution Formulation}
-
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_c$, y$_c$ and z$_c$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
-
-\begin{equation} \label{eq:euler1}
-\centering
-(x-x_c) \cdot \frac{\partial F}{\partial x} + (y-y_c) \cdot \frac{\partial F}{\partial y}+(z-z_c) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
-\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
-\end{tabular}
-
-\bigskip
-
-\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
-The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
-
-\begin{equation} \label{eq:euler2}
-\centering
-x_c \cdot \frac{\partial F}{\partial x} + y_c \cdot \frac{\partial F}{\partial y} + z_c \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
-\end{equation}
-
-\noindent{The \cref{eq:euler2} can be written in matrix form as:}
-
-\begin{equation} \label{eq:euler3}
-\centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_c\\y_c\\z_c\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
-\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
-\noindent{represent the cartesian coordinates at the i-th observation point.}
-\end{tabular}
-
-\bigskip
-
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{p}=\bar{d}$ and its objective function $f(\bar{p} )$ expressed by:}
-
-\begin{equation} \label{eq:euler4}
-\centering
-f(\bar{p} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{p}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{p}-\bar{d})
-\end{equation}
-
-\noindent{The solution $\bar{p}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial p_k}=\bar{0})$ through the least squares estimator given by:}
-
-\begin{equation} \label{eq:euler5}
-\centering
-\bar{p}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
-\end{equation}
-
-\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}
-
-%%%
-\subsection{Magnetic Inversion}
-
-\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination).
-This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
-In this way, it is possible to estimate the direction of magnetization from multiple sources.
-The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
-
-\noindent{Currently, the main inversion limitations for these type of data are: (i) in part because the sampling scale during measurement is insufficiently accurate and (ii) because of the non-singularity of the magnetic inversion  \citep{Lima2013}.
-The basic mathematical structure associated with the inverse problem of aeromagnetic data can be adapted and used in SMM data due to its similarity, despite the non-singularity caused by the infinite number of solutions for the same observed magnetic field  \citep{Weiss2007}.
-Assigning as much information as possible about the analyzed sample and the experimental environment can reduce this ambiguity by recovering the magnetization direction.
-In particles with unidirectional magnetization, and without magnetization sources outside the sample area, it is possible to guarantee singularity for the inverse problem in SMM  \citep{Baratchart2013}.
-Associating the fact that there is a singularity in the response of uniformly magnetized particles and that ferromagnetic particles (\emph{l.s.}) with stable magnetization have such a characteristic, therefore, the inversion method becomes ideal for the purpose of this project.}
-
-%%
-\subsubsection{Parametrization and Forward Model}
-
-\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions.
-Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources.
-According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}
-
-\begin{equation} \label{eq:sphere1}
-\centering
-b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot M \cdot \hat{M} \cdot \frac{1}{r^2} \cdot \hat{r}
-\end{equation}
-
-\noindent{Whereas the magnetic sources can be represented by a set of L uniformly magnetized spheres.
-In this case, each sphere will have a contribution in the field measured at the position ($x_i$, $y_i$, $z_i$):}
-
-\begin{equation} \label{eq:sphere2}
-\centering
-{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{M}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $C_m=\ \frac{\mu_0}{4\pi}=\ {10}^{-7}\frac{\ H}{m}$; $R_j$ is the radius of the j-th sphere; $r_{i,j}$ is the distance}   \\ 
-\noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
-\noindent{i = 1, 2, . .. N; and ${\bar{M}}^j=\left[{Mx}_j\ {My}_j\ {Mz}_j\right]^T$ is the vector formed by the cartesian} \\
-\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{M}}^j)$.}
-\end{tabular}
-
-\bigskip
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{MODEL.pdf}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:MODEL}
-\end{figure}
-
-\noindent{Thus, the total magnetization measured at the position ($x_i$, $y_i$, $z_i$) will be the sum of contributions from the L spheres, given by:}
-
-\begin{equation} \label{eq:sphere3}
-\centering
-B_i=\sum_{j=1}^{L}b_i^j
-\end{equation}
-
-\noindent{The \cref{eq:sphere2} presents the sensitive matrix $A_i^j$ and the $m_j$, which is the vector that encompasses the cartesian components of the magnetc moment (magnetization times volume) of each sphere:}
-
-\begin{equation} \label{eq:sphere4}
-\small A_i^j ={C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
-m_j =\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\frac{1}{r_j}\equiv\frac{1}{\sqrt{\left(x_i-{xc}_j\right)^2+\left(y_i-{yc}_j\right)^2+\left(z_i-{zc}_j\right)^2}}$}
-\end{FlushRight}
-
-\noindent{Subsequently, the components of the total magnetizing field can be obtained (from \cref{eq:sphere3}), as shown below:}
-
-\begin{equation} \label{eq:sphere5}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
-\end{equation}
-
-\noindent{As in the specific case in the study of magnetic microscopy, in the routine practice, the vertical component of magnetization is usually measured.
-In this case, there is a need to adapt the \cref{eq:sphere5} to isolate the response from the vertical component ($B_z$).
-Therefore, the equation of the direct model will be given by:}
-
-\begin{equation} \label{eq:sphere6}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
-Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
-
-\begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\noindent{We can simplify the \cref{eq:sphere6} to:}
-
-\begin{equation} \label{eq:sphere8}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{With this, the \cref{eq:sphere8} can be rewritten in linear form, given by:}
-
-\begin{equation} \label{eq:sphere9}
-\centering
-\small \bar{\bar{A}}\cdot{\bar{m}}={\bar{B}}_z
-\end{equation}
-
-%%
-\subsubsection{Inverse Model}
-
-\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers.
-Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{m}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{A}}$, the latter being obtained previously with the Euler Deconvolution.}
-
-\noindent{The problem of estimating a parameter vector $\bar{m}$ containing the spheres' magnetic moment vectors can be solved by minimizing the objective function $f\left(\bar{m}\right)$:}
-
-\begin{equation} \label{eq:sphere10}
-\centering
-\small f\left(\bar{m}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{A}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{A}} \cdot \bar{m}-\bar{B_z})
-\end{equation}
-
-\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{m}$ and equating the result to the zero vector ($\frac{\partial f}{\partial m_k}=\bar{0}$).
-Then we obtain the normal equation for estimating least squares solution given by:}
-
-\begin{equation} \label{eq:sphere11}
-\centering
-\small \bar{m}\ =\left({\bar{\bar{A}}}^T\cdot\bar{\bar{A}}\right)^{-1}\cdot ~ \left({\bar{\bar{A}}}^T\cdot{\bar{B}}_z\right)\ 
-\end{equation}
-
-\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
-To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
-
-\begin{equation} \label{eq:sphere12}
-\centering
-\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
-\end{equation}
-
-\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
-A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
-In this algorithm, at each iteration k, the following linear system is solved:}
-
-\begin{equation} \label{eq:sphere13}
-\centering
-\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
-\end{equation}
-
-\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
-
-\begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $e$ is a small positive number used to prevent singularities}
-\end{FlushRight}
-
-\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
-According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
-
-\begin{equation} \label{eq:sphere15}
-\centering
-\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
-\end{FlushRight}
-
-%%
-\subsubsection{Directions of Magnetization and Uncertainty Propagation}
-
-\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
-This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
-L.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:VECTORS}
-\end{figure}
-
-\noindent{In this way, it is possible to determine the directions ($D_j$ and $I_j$) and magnetic moment ($m_j$) for the j-th sphere of the set of L spheres by using:}
-
-\begin{equation} \label{eq:sphere16}
-\centering
-\small D_j=\tan^{-1}{\left(\frac{{my}_j}{{mx}_j}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17}
-\centering
-\small I_j=\tan^{-1}{\left(\frac{{mz}_j}{\sqrt{\left({mx}_j\right)^2+\left({my}_j\right)^2}}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17_m}
-\centering
-\small m_j=\sqrt{ {\left({mx}_j\right)}^{2} + {\left({my}_j\right)}^{2} + {\left({mz}_j\right)}^{2} } 
-\end{equation}
-
-\noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
-Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{m}}_j$, regardless of the method used.
-Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
-The covariance matrix of these parameters will be given by:}
-
-\begin{equation} \label{eq:sphere18}
-\centering
-\small \bar{\bar{Cov}}\left({\bar{m}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{least square})}
-\end{equation}
-
-\begin{equation} \label{eq:sphere19}
-\centering
-\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
-\end{equation}
-
-\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
-\end{equation}
-
-\bigskip
-
-\noindent{Thus, for the j-th sphere:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
-\end{equation}
-
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
-
-\begin{equation} \label{eq:sphere21}
-\centering
-\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22}
-\centering
-\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22_m}
-\centering
-\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\noindent{Where:}
-
-\begin{equation} \label{eq:sphere23}
-\centering
-\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere24}
-\centering
-\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere25}
-\centering
-\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere26}
-\centering
-\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere27}
-\centering
-\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere28}
-\centering
-\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere29}
-\centering
-\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere30}
-\centering
-\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm.
-Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\begin{table}[htbp]
-\caption{Initial position and magnetization parameters for each spherical source.}
-\label{tab:directmodel}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
-1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
-3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
-\end{tabular}
-\end{table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-\begin{table}[htbp]
-\caption{Central positions of sources input vs Euler deconvolution solutions.}
-\label{tab:eulerresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
-1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
-3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
-\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-\caption{Input magnetization directions vs inversion solutions and their error propagation.}
-\label{tab:inversionresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
-1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
-3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
-\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
 \noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
@@
 In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
+After estimating the structural index (N = 3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
 
@@
 
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-\end{document}
+\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }

### 2022-11-22 article_1/Introduction.tex
Split LaTeX files

--- 2022-11-18 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
-
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-\usepackage{amsmath}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\graphicspath{ {./images/} } % images path
-
-\usepackage{multirow} % for tables
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{floatrow} % for caption on the top of the table
-
-\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
-
-\usepackage[document]{ragged2e} % to justify text
-
-%\usepackage{ragged2e}
-\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
-%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
-%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
-\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
-\captionsetup{compatibility=false, justification=justified, format=custom}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{blindtext} % Package to generate dummy text throughout this template 
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.05} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage[english]{babel} % Language hyphenation and typographical rules
-
-\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-
-\usepackage{enumitem} % Customized lists
-\setlist[itemize]{noitemsep} % Make itemize lists more compact
-
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[L]{Manuscript} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
-
-\setlength\parindent{24pt}
-%\usepackage{float}
-\usepackage{floatrow}
-\usepackage{pdfpages}
-\newsavebox\mysavebox
-
-\usepackage{booktabs} % to import tables directly from python
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{?????????????????}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{June 2022}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-\justify
-
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
-
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
-
 \section{Introduction}
@@
 %%%%%%%%%%%%%
-
-\section{Methodology}
-%%%
-\subsection{Scanning Magnetic Microscopy}
-
-\noindent{Scanning magnetic microscopy (SMM) is the imaging technique in which a thin-section sample of geological material is horizontally displaced under a high-precision (fixed) micromagnetometer to obtain magnetization \citep{Weiss2007}.
-The SMM performed at a fixed height above the sample also has the advantage of facilitating the subtraction of the ambient field (constant), to which it might be subject during the scan \citep{Lima2013}.
-The availability of high-performance and low-cost magnetic sensors has promoted a great advance in the application of SMM in recent years.
-However, its sensitivity is still a few orders of magnitude lower than that of superconducting quantum interference devices (SQUIDs), the latter being between 10$^{-12}$ and 10$^{-15}$ Am$^2$ \citep{Lima2013}.
-This disadvantage is offset by (i) the high spatial resolution of the SMM, as it is performed at a few tens of micrometers from the sampled surface; and (ii) SQUID magnetic microscopy is performed at low temperatures ($<$ 100K), which can cause changes in the original NRM of the sample, while SMM is performed at room temperature \citep{Lima2013, Weiss2007}.}
-
-\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
-An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
-Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
-Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{QDM.png}
-\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
-The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a minimum sensor-sample distance of 5 μm.
-The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
-Source: \cite{Fu2020}.}
-\label{fig:QDM}
-\end{figure}
-
-\noindent{Due to the similarities between magnetic microscopy techniques and aeromagnetic surveys, the methodologies of data inversion of the latter, densely studied in the last decades, can be adapted for magnetic microscopy.
-However, \cite{Lima2013} report important distinctions between SMM and aeromagnetic surveys, namely: (i) the source distribution in the SMM can often be accurately modeled in a two-dimensional model; (ii) the SMM measures the field produced directly by the sample's NRM; (iii) the sensor positioning is very accurate in the SMM, and the vertical component of the magnetic field is usually measured, rather than the total field; (iv) there is no need for correction to bring all measurements to the same surface or to grid the data; and (v) the distributions of the magnetization sources are finite and known.}
-
-%%%
-\subsection{Euler Deconvolution}
-
-\noindent{\cite{Thompson1982} proposed the Euler Deconvolution technique, which is a consolidated method classically applied to data from aeromagnetic surveys that uses first order x, y and z derivatives to determine the positioning and depth of ideal targets (e.g., sphere, cylinder), each characterized by a structural index \citep{Nabighian2005}.
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990}.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).}
-
-\noindent{The classic Euler approach is basically the application of a mobile operator in a small data window over the sampled dataset.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.
-Despite this, this methodology usually yields a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest a previous application of a method for delimitating the region of each source that generates the potential field and later the application of Euler's Deconvolution.
-Hence giving a single system of linear equations to be solved for each source.}
-
-\noindent{Derivative-based filters are widely used to emphisize the potencial anomaly signal of shallower sources and applied in modern methods for edge/position detection, as of the solution of Euler equation itself requires the gradient of the potential field.
-Since the calculation of first order derivatives is a must in this case, we might as well give preference to filtering techniques that use the same products.
-One good filtering example is the so called horizontal gradient method ($\nabla H$, \cref{eq:HG}) \citep{Cordell1982}, which is a source edge detection methodology where the response of a target's horizontal gradient tends to overlap its own limits, thus obtaining a two-dimensional robust map of the sources location \cite{Blakely1996}.
-Another popular method for locating edges of magnetic bodies is the total gradient ($\nabla T$, \cref{eq:TG}), which places the source's maximum anomaly values over the area inside its boundaries, despite of  geomagnetic latitude, magnetization direction or source dip/geometry \citep{Nabighian2005}.
-Both total and horizontal gradients are reliable techniques to be applied with the SMM data.}
-
-\begin{equation} \label{eq:HG}
-\centering
-\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
-\end{equation}
-
-\begin{equation} \label{eq:TG}
-\centering
-\nabla T= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2+{\left( \frac{∂F}{∂z} \right)}^2 }
-\end{equation}
-
-\noindent{After pre processing the data with derivative-based filter, highlighting the sources edges, it is possible to apply blob detection techniques.
-The latter refers to visual algorithms and/or modules with the ability of detecting points/regions that are either darker or brighter than the neighborhood.
-The most common and accurate approach to detect brighter blobs on dark surroundings is the Laplacian of Gaussian (LoG), its downside is also being slower than other approaches \citep{Han2016, Kong2013}.
-We used the \href{https://scikit-image.org/docs/stable/auto_examples/features_detection/plot_blob.html#sphx-glr-auto-examples-features-detection-plot-blob-py}{scikit-image blob detection} python library \citep{VanderWalt2014} to identify the window region of data that embraces each isolated source by applying the algorithm on the highlighted sources map ($\nabla T$ or $\nabla H$).
-Therefore, the blobs selected are local maxima obtained with successively LoG images.
-Once the target location window is determined, subsequently, the Euler Deconvolution can applied in this single static data window yeilding only one solution per source.
-Thus, being an automatic, faster and easier way than the classical methodology of solving the Euler equation.}
-
-%%%
-\subsubsection{Euler Deconvolution Formulation}
-
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_c$, y$_c$ and z$_c$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
-
-\begin{equation} \label{eq:euler1}
-\centering
-(x-x_c) \cdot \frac{\partial F}{\partial x} + (y-y_c) \cdot \frac{\partial F}{\partial y}+(z-z_c) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
-\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
-\end{tabular}
-
-\bigskip
-
-\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
-The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
-
-\begin{equation} \label{eq:euler2}
-\centering
-x_c \cdot \frac{\partial F}{\partial x} + y_c \cdot \frac{\partial F}{\partial y} + z_c \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
-\end{equation}
-
-\noindent{The \cref{eq:euler2} can be written in matrix form as:}
-
-\begin{equation} \label{eq:euler3}
-\centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_c\\y_c\\z_c\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
-\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
-\noindent{represent the cartesian coordinates at the i-th observation point.}
-\end{tabular}
-
-\bigskip
-
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{p}=\bar{d}$ and its objective function $f(\bar{p} )$ expressed by:}
-
-\begin{equation} \label{eq:euler4}
-\centering
-f(\bar{p} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{p}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{p}-\bar{d})
-\end{equation}
-
-\noindent{The solution $\bar{p}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial p_k}=\bar{0})$ through the least squares estimator given by:}
-
-\begin{equation} \label{eq:euler5}
-\centering
-\bar{p}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
-\end{equation}
-
-\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates source center ($x_c$, $y_c$, $z_c$) and the base level (b).}
-
-%%%
-\subsection{Magnetic Inversion}
-
-\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination).
-This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
-In this way, it is possible to estimate the direction of magnetization from multiple sources.
-The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
-
-\noindent{Currently, the main inversion limitations for these type of data are: (i) in part because the sampling scale during measurement is insufficiently accurate and (ii) because of the non-singularity of the magnetic inversion  \citep{Lima2013}.
-The basic mathematical structure associated with the inverse problem of aeromagnetic data can be adapted and used in SMM data due to its similarity, despite the non-singularity caused by the infinite number of solutions for the same observed magnetic field  \citep{Weiss2007}.
-Assigning as much information as possible about the analyzed sample and the experimental environment can reduce this ambiguity by recovering the magnetization direction.
-In particles with unidirectional magnetization, and without magnetization sources outside the sample area, it is possible to guarantee singularity for the inverse problem in SMM  \citep{Baratchart2013}.
-Associating the fact that there is a singularity in the response of uniformly magnetized particles and that ferromagnetic particles (\emph{l.s.}) with stable magnetization have such a characteristic, therefore, the inversion method becomes ideal for the purpose of this project.}
-
-%%
-\subsubsection{Parametrization and Forward Model}
-
-\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions.
-Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources.
-According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}
-
-\begin{equation} \label{eq:sphere1}
-\centering
-b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot M \cdot \hat{M} \cdot \frac{1}{r^2} \cdot \hat{r}
-\end{equation}
-
-\noindent{Whereas the magnetic sources can be represented by a set of L uniformly magnetized spheres.
-In this case, each sphere will have a contribution in the field measured at the position ($x_i$, $y_i$, $z_i$):}
-
-\begin{equation} \label{eq:sphere2}
-\centering
-{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{M}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $C_m=\ \frac{\mu_0}{4\pi}=\ {10}^{-7}\frac{\ H}{m}$; $R_j$ is the radius of the j-th sphere; $r_{i,j}$ is the distance}   \\ 
-\noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
-\noindent{i = 1, 2, . .. N; and ${\bar{M}}^j=\left[{Mx}_j\ {My}_j\ {Mz}_j\right]^T$ is the vector formed by the cartesian} \\
-\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{M}}^j)$.}
-\end{tabular}
-
-\bigskip
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{MODEL.pdf}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:MODEL}
-\end{figure}
-
-\noindent{Thus, the total magnetization measured at the position ($x_i$, $y_i$, $z_i$) will be the sum of contributions from the L spheres, given by:}
-
-\begin{equation} \label{eq:sphere3}
-\centering
-B_i=\sum_{j=1}^{L}b_i^j
-\end{equation}
-
-\noindent{The \cref{eq:sphere2} presents the sensitive matrix $A_i^j$ and the $m_j$, which is the vector that encompasses the cartesian components of the magnetc moment (magnetization times volume) of each sphere:}
-
-\begin{equation} \label{eq:sphere4}
-\small A_i^j ={C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
-m_j =\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\frac{1}{r_j}\equiv\frac{1}{\sqrt{\left(x_i-{xc}_j\right)^2+\left(y_i-{yc}_j\right)^2+\left(z_i-{zc}_j\right)^2}}$}
-\end{FlushRight}
-
-\noindent{Subsequently, the components of the total magnetizing field can be obtained (from \cref{eq:sphere3}), as shown below:}
-
-\begin{equation} \label{eq:sphere5}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
-\end{equation}
-
-\noindent{As in the specific case in the study of magnetic microscopy, in the routine practice, the vertical component of magnetization is usually measured.
-In this case, there is a need to adapt the \cref{eq:sphere5} to isolate the response from the vertical component ($B_z$).
-Therefore, the equation of the direct model will be given by:}
-
-\begin{equation} \label{eq:sphere6}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{The magnetization is usually represented in spherical coordinates of intensity (M (A/m)), declination (D (°)) and inclination (I (°)).
-Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
-
-\begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=M_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\noindent{We can simplify the \cref{eq:sphere6} to:}
-
-\begin{equation} \label{eq:sphere8}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{With this, the \cref{eq:sphere8} can be rewritten in linear form, given by:}
-
-\begin{equation} \label{eq:sphere9}
-\centering
-\small \bar{\bar{A}}\cdot{\bar{m}}={\bar{B}}_z
-\end{equation}
-
-%%
-\subsubsection{Inverse Model}
-
-\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers.
-Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{m}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{A}}$, the latter being obtained previously with the Euler Deconvolution.}
-
-\noindent{The problem of estimating a parameter vector $\bar{m}$ containing the spheres' magnetic moment vectors can be solved by minimizing the objective function $f\left(\bar{m}\right)$:}
-
-\begin{equation} \label{eq:sphere10}
-\centering
-\small f\left(\bar{m}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{A}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{A}} \cdot \bar{m}-\bar{B_z})
-\end{equation}
-
-\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{m}$ and equating the result to the zero vector ($\frac{\partial f}{\partial m_k}=\bar{0}$).
-Then we obtain the normal equation for estimating least squares solution given by:}
-
-\begin{equation} \label{eq:sphere11}
-\centering
-\small \bar{m}\ =\left({\bar{\bar{A}}}^T\cdot\bar{\bar{A}}\right)^{-1}\cdot ~ \left({\bar{\bar{A}}}^T\cdot{\bar{B}}_z\right)\ 
-\end{equation}
-
-%%
-\subsubsection{Directions of Magnetization and Uncertainty Propagation}
-
-\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
-This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
-L.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:VECTORS}
-\end{figure}
-
-\noindent{In this way, it is possible to determine the directions ($D_j$ and $I_j$) and magnetic moment ($m_j$) for the j-th sphere of the set of L spheres by using:}
-
-\begin{equation} \label{eq:sphere16}
-\centering
-\small D_j=\tan^{-1}{\left(\frac{{my}_j}{{mx}_j}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17}
-\centering
-\small I_j=\tan^{-1}{\left(\frac{{mz}_j}{\sqrt{\left({mx}_j\right)^2+\left({my}_j\right)^2}}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17_m}
-\centering
-\small m_j=\sqrt{ {\left({mx}_j\right)}^{2} + {\left({my}_j\right)}^{2} + {\left({mz}_j\right)}^{2} } 
-\end{equation}
-
-\noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
-Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{m}}_j$, regardless of the method used.
-Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
-The covariance matrix of these parameters will be given by:}
-
-\begin{equation} \label{eq:sphere18}
-\centering
-\small \bar{\bar{Cov}}\left({\bar{m}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{least square})}
-\end{equation}
-
-\begin{equation} \label{eq:sphere19}
-\centering
-\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
-\end{equation}
-
-\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\small \bar{\bar{Cov}}= \left[~ \text{\emph{diag}}\left(\begin{matrix}{\sigma_{{mx}_1}}^2&{\sigma_{{my}_1}}^2&{\sigma_{{mz}_1}}^2&\cdots&{\sigma_{{mz}_L}}^2\end{matrix}\right) \right]_{\text{\tiny 3L $\times$ 3L}}\
-\end{equation}
-
-\bigskip
-
-\noindent{Thus, for the j-th sphere:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\sigma_{{mx}_j}=\sqrt{{\sigma_{{mx}_j}}^2},\ \ \ \  \sigma_{{my}_j}=\sqrt{{\sigma_{{my}_j}}^2}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{{\sigma_{{mz}_j}}^2}
-\end{equation}
-
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in Appendix A.2) obtained in \cref{eq:sphere20}:}
-
-\begin{equation} \label{eq:sphere21}
-\centering
-\small \sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22}
-\centering
-\small \sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22_m}
-\centering
-\small \sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm.
-Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
-\caption{blablabla.}
-\label{fig:SimpleSynthetic}
-\end{figure}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{input_par_table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{solution_par_table}
-
-\section{Discussion}
-
-\section{Conclusion}
-\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
-}
-
-\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
-
-\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
-This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
-
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-
-\section{Appendix A}
-\subsection{Appendix A.1} \label{AppendixA.1}
-
-\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
-To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
-
-\begin{equation} \label{eq:sphere12}
-\centering
-\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
-\end{equation}
-
-\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
-A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
-In this algorithm, at each iteration k, the following linear system is solved:}
-
-\begin{equation} \label{eq:sphere13}
-\centering
-\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
-\end{equation}
-
-\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
-
-\begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $e$ is a small positive number used to prevent singularities}
-\end{FlushRight}
-
-\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
-According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
-
-\begin{equation} \label{eq:sphere15}
-\centering
-\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
-\end{FlushRight}
-
-\subsection{Appendix A.2} \label{AppendixA.2}
-
-\begin{equation} \label{eq:sphere23}
-\centering
-\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere24}
-\centering
-\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere25}
-\centering
-\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere26}
-\centering
-\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere27}
-\centering
-\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere28}
-\centering
-\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere29}
-\centering
-\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere30}
-\centering
-\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\end{document}

### 2022-11-22 article_1/Methodology.tex
Split LaTeX files

--- 2022-11-18 article_1/article_1.tex
@@
-%\documentclass[paper]{geophysics}
-\documentclass[manuscript,revised]{geophysics}
-
-\usepackage{setspace}
-\usepackage[colorlinks]{hyperref}
-\hypersetup{colorlinks=true,linkcolor={blue},citecolor={blue},urlcolor={red}}
-
-\usepackage{amsmath}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\graphicspath{ {./images/} } % images path
-
-\usepackage{multirow} % for tables
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{floatrow} % for caption on the top of the table
-
-\usepackage[nameinlink, capitalise, noabbrev]{cleveref} % enhance refs
-
-\usepackage[document]{ragged2e} % to justify text
-
-%\usepackage{ragged2e}
-\DeclareCaptionJustification{justified}{\justifying} 			% to justify figure caption
-%\captionsetup{compatibility=false,justification=justified} 		% to justify figure caption
-%\DeclareCaptionFormat{custom}{\textbf{#1#2}\textit{\small #3}}
-\DeclareCaptionFormat{custom}{\textbf{#1#2}{\small #3}}
-\captionsetup{compatibility=false, justification=justified, format=custom}
-
-% An example of defining macros
-\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
-\newcommand{\rr}[1]{\mbox{\rm #1}}
-
-% found it here: https://stackoverflow.com/questions/70705684/latex-get-figure-caption-to-align-with-image
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{blindtext} % Package to generate dummy text throughout this template 
-\usepackage[sc]{mathpazo} % Use the Palatino font
-\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
-\linespread{1.05} % Line spacing - Palatino needs more space between lines
-\usepackage{microtype} % Slightly tweak font spacing for aesthetics
-\usepackage[english]{babel} % Language hyphenation and typographical rules
-
-\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
-\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
-
-\usepackage{enumitem} % Customized lists
-\setlist[itemize]{noitemsep} % Make itemize lists more compact
-
-\usepackage{fancyhdr} % Headers and footers
-\pagestyle{fancy} % All pages have headers and footers
-\fancyhead{} % Blank out the default header
-\fancyfoot{} % Blank out the default footer
-\fancyhead[L]{Manuscript} % Custom header text
-\fancyfoot[RO,LE]{\thepage} % Custom footer text
-
-\setlength\parindent{24pt}
-%\usepackage{float}
-\usepackage{floatrow}
-\usepackage{pdfpages}
-\newsavebox\mysavebox
-
-\usepackage{booktabs} % to import tables directly from python
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\title{?????????????????}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} 
-\ms{GEO-Example} % manuscript number
-
-\address{
-\footnotemark[1]BP UTG, \\
-200 Westlake Park Blvd, \\
-Houston, TX, 77079 \\
-\footnotemark[2]Bureau of Economic Geology, \\
-John A. and Katherine G. Jackson School of Geosciences \\
-The University of Texas at Austin \\
-University Station, Box X \\
-Austin, TX 78713-8924}
-
-\author{Gelson Ferreira de Souza-Junior\footnotemark[1], Ricardo Ivan Ferreira da Trindade\footnotemark[1],  Leonardo Uieda\footnotemark[2]}
-\date{June 2022}
-\footer{Example}
-\lefthead{Dellinger \& Fomel}
-\righthead{\emph{Geophysics} example}
-
-\maketitle
-\justify
-
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
-
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
-
-\section{Introduction}
-%\onehalfspacing
-\doublespacing
-
-\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}.
-It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}
-
-\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}.
-Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}.
-When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field.
-In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}.
-On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field.
-In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties.
-All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}
-
-\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$.
-The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-Although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
-
-\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}.
-In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}
-
-\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information.
-In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained.
-We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}
-
-%%%%%%%%%%%%%
-
 \section{Methodology}
@@
 
-\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
+\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:model_plus_vector}a).
 In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{MODEL.pdf}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
+\includegraphics[width=0.8\textwidth]{model_plus_vector.pdf}
+\caption{a) Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
+In this cartesian coordinate system x, y and z corresponds to geographic north, east and z, respectively.
+b) Schematic cartesian representation of vector $m_j$ with elements $mx_j$, $my_j$ and $mz_j$, with declination $D_j$ (positive clockwise) and inclination $I_j$ (positive downwards), j = 1, 2, ...
+L.
 Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:MODEL}
+\label{fig:model_plus_vector}
 \end{figure}
@@
 
+\noindent{The least squares estimator is also known to be affected by outliers in the data set \citep{Aster2019}.
+Since the environment of an SMM acquisition is very well controlled, the probability of occurrence of ouliers is considerably low.
+With that, in case there is an exception to the rule, we also implement a robust estimator to remove the influence of outliers \citep[Also adapted from:][]{OliveiraJr.2015}.
+This formulation is detailed in the~\nameref{AppendixA1}.}
+
 %%
@@
 \noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
-This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
-L.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:VECTORS}
-\end{figure}
+These are given as a function of the magnetization vector ${\bar{m}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:model_plus_vector}b).}
 
@@
 
-\begin{equation} \label{eq:sphere19}
-\centering
-\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
-\end{equation}
-
-\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
+\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} contains the variance of each member of the parameter vector, as expressed below:}
 
@@
 
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in Appendix A.2) obtained in \cref{eq:sphere20}:}
+\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters (detailed in \nameref{AppendixA2}) obtained in \cref{eq:sphere20}:}
 
@@
 \end{equation}
-
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm.
-Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
-\caption{blablabla.}
-\label{fig:SimpleSynthetic}
-\end{figure}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{input_par_table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{solution_par_table}
-
-\section{Discussion}
-
-\section{Conclusion}
-\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
-}
-
-\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
-
-\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
-This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
-
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
-
-\section{Appendix A}
-\subsection{Appendix A.1} \label{AppendixA.1}
-
-\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
-To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
-
-\begin{equation} \label{eq:sphere12}
-\centering
-\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
-\end{equation}
-
-\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
-A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
-In this algorithm, at each iteration k, the following linear system is solved:}
-
-\begin{equation} \label{eq:sphere13}
-\centering
-\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
-\end{equation}
-
-\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
-
-\begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $e$ is a small positive number used to prevent singularities}
-\end{FlushRight}
-
-\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
-According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
-
-\begin{equation} \label{eq:sphere15}
-\centering
-\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
-\end{FlushRight}
-
-\subsection{Appendix A.2} \label{AppendixA.2}
-
-\begin{equation} \label{eq:sphere23}
-\centering
-\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere24}
-\centering
-\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere25}
-\centering
-\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere26}
-\centering
-\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere27}
-\centering
-\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere28}
-\centering
-\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere29}
-\centering
-\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere30}
-\centering
-\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\end{document}

### 2022-11-22 article_1/Result1.tex
Split LaTeX files

%%%%%%%%%%%%%
\section{Aplication to Synthetic Data}

%%%
\subsection{Simple Simulation: Validating the Methodology}

\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}. Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm. Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}

\bigskip

\floatsetup[table]{capposition=top} % to put the caption on the top of the table
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{input_par_table}

\bigskip

\noindent{The first step is to apply the upward continuaton filter, which transforms the potencial field measured on a surface into one measured at a higher surface level \citep{Blakely1996}, therefore smoothing out high frequency noise. This first step is always needed in high frequency noisy data, since the Euler equation requires the first derivatives of potencial field. If this step is negleted or badly elaborated, the high frequency noise propagation during the application of the derivative filters will cause future errors in the next methodological stage.}

\noindent{The next step is to calculate the magnetic total gradient (or horizontal gradient) filter in order to highlight the anomaly signal of each source within its own boundaries, then we apply the blob detection algorithm \citep{VanderWalt2014} to obtain a robust positioning of each source data window (\cref{fig:SimpleSynthetic}b).}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.0\textwidth]{SimpleSynthetic.png}
\caption{a) Synthetic data contaminated with psedo-random normal noise. b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
\label{fig:SimpleSynthetic}
\end{figure}

\bigskip

\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source (N = 3). Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}

\noindent{The last step consists of using the central positions of each source, obtained with Euler's method, as an input parameter for inverting the original noisy data (\cref{fig:SimpleSynthetic}a) to find the least squares (or robust) approximation solution for the vector of cartesian magnetic moments ($\bar{m}$). With this, the magnetization directions (D and I) and the intensity of the magnetic moment can be estimated using equations (\cref{eq:sphere16,eq:sphere17,eq:sphere17_m}), as well as the uncertainty propagation of this inversion, using equations (\cref{eq:sphere21,eq:sphere22,eq:sphere22_m}) and considering $\sigma$ = 25nT. The results obtained with the least squares estimator can also be seen in \cref{tab:InversionTab}.}

\bigskip

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\input{solution_par_table}

\noindent{It is important to emphasize that \cite{OliveiraJr.2015} proved that the magnetization directions (D and I) recovered by the least squares estimator is sensitive to variations in the horizontal coordinates (x and y) of the magnetic sources central positions. While, the same being practically insensitive to variations in depths. Thus, the same authors consider Euler deconvolution method as an adequate technique to estimate the central positions that will be used as a priori information for inversion. This occurs mainly because, when well performed, the recovery of the horizontal coordinates of sources central position is considerably accurate, while the vertical coordinate can undergo greater variation \citep{Silva2003, Melo2013}, even so the inversion will still provide extremely satisfactory results. The high sensitivity of Euler deconvolution to high frequency noise can also be easily overcome with the proper application of the upward continuation filter.}

\subsection{Complex Simulation: Testing Applicability}

### 2022-11-22 article_1/article_1.tex
Split LaTeX files

--- 2022-11-10 article_1/article_1.tex
@@
 
-\begin{abstract}
-\begin{singlespace}
-Paleomagnetism is the main tool used in paleogeographic reconstructions, in which directional information of the past magnetic field is retrieved from ferromagnetic grains (l.s).
-Magnetic minerals have a wide range of size and composition that influence their magnetic properties and, consequently, their ability to record the directions of paleomagnetic fields.
-The signals obtained with classical paleomagnetic methodologies are vector averages that include all magnetic grains present in the samples, including the stable and unstable carriers.
-To improve the quality of the magnetic signal, it would be necessary to individually identify the magnetizations of the carriers of remanent magnetization, in order to isolate only the good registers of the geomagnetic field.
-This would allow obtaining more reliable paleomagnetic information, as well as possibly being effective for the paleomagnetic study of older rocks (e.g., Archean rocks), meteorites and even bodies with complex geological evolution.
-Therefore, this project aims to apply magnetic microscopy to identify the remanent magnetization directions of stable magnetic grains and, subsequently, invert these data in an attempt to recover the individual paleomagnetic directions of the magnetic carriers present in the thin-sections.
-If successful, a new precision methodology for paleomagnetic data acquisition will be implemented.
+\input{Abstract}
 
-\noindent{\textbf{Keywords}: Paleomagnetism, magnetic microscopy, Euler deconvolution, inversion of magnetic data.}
-\end{singlespace}
-\end{abstract}
+\input{Introduction}
 
-\section{Introduction}
-%\onehalfspacing
-\doublespacing
+\input{Methodology}
 
-\noindent{Paleomagnetism is the study of the record of the Earth's magnetic field preserved in rocks, being the main tool, and the only quantitative method, used during paleogeographic reconstruction~\citep{Butler1992}.
-It is based on three basic assumptions: (i) the geomagnetic field can be approximated to the field created by a geocentric axial dipole (GAD) aligned with the Earth's axis of rotation over a period that eliminates paleosecular variation ($>10^4$ years)~\citep{McElhinny2000}; (ii) ferromagnetic minerals (l.s.) acquire natural remanent magnetization (NRM) parallel to the Earth's geomagnetic field~\citep{Dunlop1997, Tauxe2018}; and (iii) this acquired magnetization is recorded for a long period of time, depending on the physicochemical characteristics of the magnetized mineral, following Neél's Theory~\citep{Neel1949, Neel1955} and being also influenced by the geological processes by which the rocks were submitted.}
+\input{Result1}
 
-\noindent{The thermoremanent magnetizations (TRMs) of magnetic particles in geological materials are the main records of the direction of the geomagnetic field of the past \citep{DeGroot2014}.
-Iron oxides, such as magnetite, which is the most common magnetic mineral present in rocks~\citep{OReilly1984} and acquire TRM as they cool below their Curie temperature and subsequently this direction of magnetization is “frozen” upon reaching blocking temperature~\citep{Dunlop1997}.
-When the grains are small enough, and the magnetization is unidirectional homogeneous (single domain - SD), the acquisition and preservation of magnetic signals is physically supported by Néel's theory~\citep{Neel1949, Neel1955}, conserving the remanent magnetization for long periods of time, on the order of billions of years, and for this reason, they are considered “good recorders” of the paleomagnetic field.
-In addition to SD, pseudo-single domain (PSD) particles, in the flower and stable vortex states, can also preserve magnetization for periods on the order of the solar system age~\citep{Nagy2017}.
-On the other hand, Néel's theory does not cover larger particles (multi domain - MD), which have unstable remanent magnetization (e.g., caused by viscous reordering of magnetic domains,~\cite{DeGroot2014}), so they are particles with limited ability to record the geomagnetic field.
-In addition to the magnetic domain state, particles can still vary in composition, size and shape which causes changes in their magnetic properties.
-All these factors are crucial in determining stable remanence directions used in the calculation of paleomagnetic poles.}
+\input{Result2}
 
-\noindent{Classic techniques for obtaining paleomagnetic data, e.g., thermal demagnetization and alternating fields, are based on the progressive acquisition of the magnetization contained in cylindrical samples, usually of 10 cm$^3$.
-The magnetic signal of a single specimen is the result of the sum of moments contained in the assembly of ferromagnetic grains, including stable and unstable registers~\citep{DeGroot2021}.
-although there are recent well-structured studies of imaging magnetic minerals in thin-sections \citep[e.g.,][]{Almeida2014, Farchi2017,  Glenn2017, Lima2014, Lima2009, Nichols2016, Weiss2007, DeGroot2018, DeGroot2021}, obtaining NRM directions of individual grains in the rock fabric remains, to the best of our knowledge, a challenge deeply explored only by \cite{DeGroot2021}.
-With the possibility of isolating the individual contributions of a fairly large number ($10^6$ $>$ N $>$ $10^7$) of stable magnetic particles (SD/PSD) the magnetic directions recovered, using the average of their NRM vectors, would have an accurate paleomagnetic response \citep{Berndt2016}, however such number of observations is unfeasible for the currently insufficient measurements scales of the equipaments \citep{DeGroot2018}.}
+\input{Discussion}
 
-\noindent{Several branches of Earth Sciences have demonstrated the importance of the “spatiality" of data on a microscopic scale, mainly in Geochemistry and Geochronology, where it is possible to perform punctual analyzes and compositional maps, which allowed significant advances in the understanding of igneous, metamorphic and sedimentary processes~\citep[e.g.,][]{ Barnes2019, Davidson2007, Verberne2020}.
-In Paleomagnetism there has been an interest in point magnetic analyses, or microscale magnetic maps, from magnetic microscopy techniques~\citep{DeGroot2014, DeGroot2018, Lima2014, Weiss2007}.
-However, despite recent advances in this area, still there is no well-established inversion protocol to determine the magnetic vector direction of each individual ferromagnetic grains, nor the intensity of magnetization, without using additional information of the positioning and shape of these sources, such as micromagnetic tomography \citep[e.g.,][]{DeGroot2018, DeGroot2021, Fabian2019}, which is a measurement spatially even more limited than the magnetic microscopy itself.}
+\input{Conclusion}
 
-\noindent{This paper aims to give a new perspective in the methodological routine that carry out paleomagnetic studies in microscale allowing to retrieve the individual remanent magnetization direction of these stable magnetic carriers (SD and PSD), semi automatically and without any additional information.
-In this way, a larger area of the thin section can be scanned with the objective of increasing the number of observations and, therefore, increasing the reliability of the directional data obtained.
-We also intend to generate a micromagnetic analysis protocol in an open source software, based on the techniques that will be described below.}
+\input{References}
 
-%%%%%%%%%%%%%
+\input{Appendix}
 
-\section{Methodology}
-%%%
-\subsection{Scanning Magnetic Microscopy}
-
-\noindent{Scanning magnetic microscopy (SMM) is the imaging technique in which a thin-section sample of geological material is horizontally displaced under a high-precision (fixed) micromagnetometer to obtain magnetization \citep{Weiss2007}.
-The SMM performed at a fixed height above the sample also has the advantage of facilitating the subtraction of the ambient field (constant), to which it might be subject during the scan \citep{Lima2013}.
-The availability of high-performance and low-cost magnetic sensors has promoted a great advance in the application of SMM in recent years.
-However, its sensitivity is still a few orders of magnitude lower than that of superconducting quantum interference devices (SQUIDs), the latter being between 10$^{-12}$ and 10$^{-15}$ Am$^2$ \citep{Lima2013}.
-This disadvantage is offset by (i) the high spatial resolution of the SMM, as it is performed at a few tens of micrometers from the sampled surface; and (ii) SQUID magnetic microscopy is performed at low temperatures ($<$ 100K), which can cause changes in the original NRM of the sample, while SMM is performed at room temperature \citep{Lima2013, Weiss2007}.}
-
-\noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
-An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
-Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
-Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{QDM.png}
-\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
-The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a 	minimum sensor-sample distance of 5 μm.
-The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
-Source: \cite{Fu2020}.}
-\label{fig:QDM}
-\end{figure}
-
-\noindent{Due to the similarities between magnetic microscopy techniques and aeromagnetic surveys, the methodologies of data inversion of the latter, densely studied in the last decades, can be adapted for magnetic microscopy.
-However, \cite{Lima2013} report important distinctions between SMM and aeromagnetic surveys, namely: (i) the source distribution in the SMM can often be accurately modeled in a two-dimensional model; (ii) the SMM measures the field produced directly by the sample's NRM; (iii) the sensor positioning is very accurate in the SMM, and the vertical component of the magnetic field is usually measured, rather than the total field; (iv) there is no need for correction to bring all measurements to the same surface or to grid the data; and (v) the distributions of the magnetization sources are finite and known.}
-
-%%%
-\subsection{Euler Deconvolution}
-
-\noindent{Euler Deconvolution is a consolidated method classically applied to data from aeromagnetic surveys.
-Given the similarities between SMM and aeromagnetic data, its application becomes plausible for determining the positions of magnetic sources caused by ferromagnetic minerals (l.s).
-Euler deconvolution is one of the most useful methods for estimating the three-dimensional positioning of magnetic sources/geological bodies \citep{Reid1990, Thompson1982}.
-It is the application of a mobile operator in a small data window over the sampled data set.
-The observations made within this window are used to estimate the horizontal and vertical positions of the source by solving a small linear system of equations using the gradients of the potential field, provided that the shapes of the sources are assumed.}
-
-\noindent{Despite this, this system usually has a large number of solutions \citep{Barbosa2011}, which becomes a limitation for the method.
-In an attempt to circumvent the problem of this expressive cloud of solutions, we suggest the previous application of a method of delimitation of the contours of the sources generating the potential field and later the application of Euler's Deconvolution, which becomes unique for each source (one data window per source).
-As the method itself already requires the gradients of the potential field, therefore, the method of delimitation chosen was the horizontal gradient \citep{Cordell1982}.
-\cite{Blakely1996} states that the response of a source's horizontal gradient tends to overlap its limits, thus obtaining a two-dimensional robust map of the sources location.
-The amplitude of the horizontal gradient ($\nabla H$) is expressed by~\cref{eq:HG}.
-Once the source positions are determined by this preliminary method then, subsequently, Euler Deconvolution is applied and a static window for each source generating the potential field.}
-
-\begin{equation} \label{eq:HG}
-\centering
-\nabla H= \sqrt{ {\left( \frac{∂F}{∂x} \right)}^2+{\left( \frac{∂F}{∂y} \right)}^2 }
-\end{equation}
-
-%%%
-\subsubsection{Euler Deconvolution Formulation}
-
-\noindent{The anomaly of a potential field F produced by a three-dimensional source, whose cartesian coordinates of its central position are x$_c$, y$_c$ and z$_c$, satisfies the homogeneous Euler equation \citep{Reid1990} expressed by:}
-
-\begin{equation} \label{eq:euler1}
-\centering
-(x-x_c) \cdot \frac{\partial F}{\partial x} + (y-y_c) \cdot \frac{\partial F}{\partial y}+(z-z_c) \cdot \frac{\partial F}{\partial z}=n \cdot (b-F)  \ \ 
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{where: n is the structural index, that is, a gauge of the geometric shape of the}  \\
-\noindent{sources causing the anomaly; and b is the constant, and unknown, base level.}  \\
-\end{tabular}
-
-\bigskip
-
-\noindent{The Euler's Deconvolution uses the gradient of a potential field and the structural index, which can be defined by the geometric nature of the sources.
-The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
-
-\begin{equation} \label{eq:euler2}
-\centering
-x_c \cdot \frac{\partial F}{\partial x} + y_c \cdot \frac{\partial F}{\partial y} + z_c \cdot \frac{\partial F}{\partial z} + n \cdot b = x \cdot \frac{\partial F}{\partial x} + y \cdot \frac{\partial F}{\partial y} + z \cdot \frac{\partial F}{\partial z} + n \cdot F  \ \
-\end{equation}
-
-\noindent{The \cref{eq:euler2} can be written in matrix form as:}
-
-\begin{equation} \label{eq:euler3}
-\centering
-\left[\begin{matrix}{Fx}_1&{Fy}_1&{Fz}_1&n\\{Fx}_2&{Fy}_2&{Fz}_2&n\\\vdots&\vdots&\vdots&\vdots\\{Fx}_N&{Fy}_N&{Fz}_N&n\\\end{matrix}\right]\left[\begin{matrix}x_c\\y_c\\z_c\\b\\\end{matrix}\right]=\left[\begin{matrix}x_1\cdot{Fx}_1+y_1 \cdot {Fy}_1+z_1 \cdot {Fz}_1+n\cdot F_1\\x_2\cdot{Fx}_2+y_2\cdot{Fy}_2+z_2\cdot{Fz}_2+n\cdot F_2\\\vdots\\x_N\cdot{Fx}_N+y_N\cdot{Fy}_N+z_N\cdot{Fz}_N+n\cdot F_N\\\end{matrix}\right]\
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $Fx_i$, $Fy_i$ and $Fz_i$ represent, respectively, the gradients $\frac{\partial F}{\partial x}$, $\frac{\partial F}{\partial y}$ and $\frac{\partial F}{\partial z}$}   \\
-\noindent{evaluated on the i-th observation point ($i=1,2, ..., N$). While $x_i$, $y_i$ and $z_i$}   \\
-\noindent{represent the cartesian coordinates at the i-th observation point.}
-\end{tabular}
-
-\bigskip
-
-\noindent{Note that \cref{eq:euler3} is a linear system $\bar{\bar{G}} \cdot \bar{p}=\bar{d}$ and its objective function $f(\bar{p} )$ expressed by:}
-
-\begin{equation} \label{eq:euler4}
-\centering
-f(\bar{p} ) = {\lVert e\lVert}^2 = {(\bar{\bar{G}} \cdot \bar{p}-\bar{d})}^T \cdot ~ (\bar{\bar{G}} \cdot \bar{p}-\bar{d})
-\end{equation}
-
-\noindent{The solution $\bar{p}$ of the system can be obtained by minimizing the objective function $(\frac{\partial f}{\partial p_k}=\bar{0})$ through the least squares estimator given by:}
-
-\begin{equation} \label{eq:euler5}
-\centering
-\bar{p}=\left({\bar{\bar{G}}}^T\cdot ~ \bar{\bar{G}}\right)^{-1} \cdot \ \left({\bar{\bar{G}}}^T\cdot ~ \bar{d}\right)
-\end{equation}
-
-\noindent{Thus, $\bar{p}=\left[x_c\ \ y_c\ \ z_c\ \ b\right]^T$ will be the solution vector that satisfies Euler's Equation with the least possible error containing the position coordinates font center ($x_c$, $y_c$, $z_c$) and the base level (b).}
-
-%%%
-\subsection{Magnetic Inversion}
-
-\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination).
-This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem.
-In this way, it is possible to estimate the direction of magnetization from multiple sources.
-The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}
-
-\noindent{Currently, the main inversion limitations for these type of data are: (i) in part because the sampling scale during measurement is insufficiently accurate and (ii) because of the non-singularity of the magnetic inversion  \citep{Lima2013}.
-The basic mathematical structure associated with the inverse problem of aeromagnetic data can be adapted and used in SMM data due to its similarity, despite the non-singularity caused by the infinite number of solutions for the same observed magnetic field  \citep{Weiss2007}.
-Assigning as much information as possible about the analyzed sample and the experimental environment can reduce this ambiguity by recovering the magnetization direction.
-In particles with unidirectional magnetization, and without magnetization sources outside the sample area, it is possible to guarantee singularity for the inverse problem in SMM  \citep{Baratchart2013}.
-Associating the fact that there is a singularity in the response of uniformly magnetized particles and that ferromagnetic particles (\emph{l.s.}) with stable magnetization have such a characteristic, therefore, the inversion method becomes ideal for the purpose of this project.}
-
-%%
-\subsubsection{Parametrization and Forward Model}
-
-\noindent{Let $\bar{B}$ be the observed data vector, whose i-th element ${\bar{B}}_i$, $i= 1, 2, ..., N$, is a total field anomaly, resulting from the NRM contribution of each ferromagnetic particle (\emph{l.s.}), measured at position ($x_i$, $y_i$, $z_i$) (black dots, \cref{fig:MODEL}).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-In general, the magnetic field that is produced in the thin section is the result solely and exclusively of the NRM contribution of the particles without considering the induced component, since the measurements carried out in the magnetic microscope are usually made under magnetic shielding conditions.
-Thereby, approximating the shape of ferromagnetic minerals (\emph{l.s.}) to NRM magnetizing spheric/punctual sources.
-According to \cite{Blakely1996} the equation of a uniformly magnetized sphere is given by:}
-
-\begin{equation} \label{eq:sphere1}
-\centering
-b =\ C_m \cdot \frac{4}{3} \cdot \pi \cdot R^3 \cdot M \cdot \hat{M} \cdot \frac{1}{r^2} \cdot \hat{r}
-\end{equation}
-
-\noindent{Whereas the magnetic sources can be represented by a set of L uniformly magnetized spheres.
-In this case, each sphere will have a contribution in the field measured at the position ($x_i$, $y_i$, $z_i$):}
-
-\begin{equation} \label{eq:sphere2}
-\centering
-{b_i}^j=\ C_m \cdot \frac{4}{3}\pi \cdot {R_j}^3 \cdot {\bar{M}}^j\cdot\frac{1}{r_{i,j}^2}\cdot{\hat{r}}_{i,j}\ ,\ \ j=1,\ 2\ldots,\ L
-\end{equation}
-
-\begin{tabular}{ l }
-\noindent{Where: $C_m=\ \frac{\mu_0}{4\pi}=\ {10}^{-7}\frac{\ H}{m}$; $R_j$ is the radius of the j-th sphere; $r_{i,j}$ is the distance}   \\ 
-\noindent{(unit vector ${\hat{r}}_{i,j}$) between the center of the j-th sphere and the observation point i,}    \\  
-\noindent{i = 1, 2, . .. N; and ${\bar{M}}^j=\left[{Mx}_j\ {My}_j\ {Mz}_j\right]^T$ is the vector formed by the cartesian} \\
-\noindent{components of the magnetization of the j-th sphere (unit vector ${\hat{M}}^j)$.}
-\end{tabular}
-
-\bigskip
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{MODEL.pdf}
-\caption{Schematic representation of spheres (L = 2) uniformly magnetized in the subsurface, whose magnetic effect, produced by these spheres, can be observed at points ($x_i$, $ y_i$, $z_i$), i = 1, 2, ..., N (black dots).
-In this cartesian coordinate system, x points to geographic north, y points east, and z points down.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:MODEL}
-\end{figure}
-
-\noindent{Thus, the total magnetization measured at the position ($x_i$, $y_i$, $z_i$) will be the sum of contributions from the L spheres, given by:}
-
-\begin{equation} \label{eq:sphere3}
-\centering
-B_i=\sum_{j=1}^{L}b_i^j
-\end{equation}
-
-\noindent{The \cref{eq:sphere2} presents the sensitive matrix $A_i^j$ and the $m_j$, which is the vector that encompasses the cartesian components of the magnetc moment (magnetization times volume) of each sphere:}
-
-\begin{equation} \label{eq:sphere4}
-\small A_i^j ={C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}},
-m_j =\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\frac{1}{r_j}\equiv\frac{1}{\sqrt{\left(x_i-{xc}_j\right)^2+\left(y_i-{yc}_j\right)^2+\left(z_i-{zc}_j\right)^2}}$}
-\end{FlushRight}
-
-\noindent{Subsequently, the components of the total magnetizing field can be obtained (from \cref{eq:sphere3}), as shown below:}
-
-\begin{equation} \label{eq:sphere5}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial x}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial y}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[\begin{matrix}{Bx}_{i\ }\\{By}_{i\ }\\{Bz}_{i\ }\\\end{matrix}\right]_{\text{\tiny 3N $\times$ 1}}
-\end{equation}
-
-\noindent{As in the specific case in the study of magnetic microscopy, in the routine practice, the vertical component of magnetization is usually measured.
-In this case, there is a need to adapt the \cref{eq:sphere5} to isolate the response from the vertical component ($B_z$).
-Therefore, the equation of the direct model will be given by:}
-
-\begin{equation} \label{eq:sphere6}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{{Mx}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{My}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\{{Mz}_{j\ }} \cdot \frac{4}{3}\pi\cdot R_j^3\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{The magnetization is usually represented in spherical coordinates of intensity (Q (A/m)), declination (D (°)) and inclination (I (°)).
-Thus, the vector ${\bar{M}}_j$, containing the cartesian coordinates of magnetization, of the direct model can also be calculated as follows:}
-
-\begin{equation} \label{eq:sphere7}
-\small \left[\begin{matrix}{Mx}_j\\{My}_j\\{Mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}=Q_j\cdot\left[\begin{matrix}cos\left(I_j\right)\cdot c o s\left(D_j\right)\\cos\left(I_j\right)\cdot s i n\left(D_j\right)\\sin\left(I_j\right)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-\end{equation}
-
-\noindent{We can simplify the \cref{eq:sphere6} to:}
-
-\begin{equation} \label{eq:sphere8}
-\small {C}_{m} \cdot \left[\begin{matrix}\left(\frac{\partial^2}{\partial x\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial y\partial z}\cdot\frac{1}{r_{i,j}}\right)&\left(\frac{\partial^2}{\partial z\partial z}\cdot\frac{1}{r_{i,j}}\right)\\\end{matrix}\right]_{\text{\tiny N $\times$ 3L}}
-\cdot\ 
-\left[\begin{matrix}{mx}_j\\{my}_j\\{mz}_j\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 1}}
-=\left[{Bz}_{i\ }\right]_{\text{\tiny N $\times$ 1}}
-\end{equation}
-
-\noindent{With this, the \cref{eq:sphere8} can be rewritten in linear form, given by:}
-
-\begin{equation} \label{eq:sphere9}
-\centering
-\small \bar{\bar{A}}\cdot{\bar{m}}={\bar{B}}_z
-\end{equation}
-
-%%
-\subsubsection{Inverse Model}
-
-\noindent{Assuming that the ferromagnetic minerals (\emph{l.s.}) that give rise to the observed magnetization component data vector ${\bar{B}}_z$ can be approximated by a set of L uniformly magnetized spheres with known coordinates ($xc_j$, $yc_j$, $zc_j$), j = 1, 2, ..., L, of their centers.
-Also assuming that there is no induced magnetization component, only that of the NRM.
-Under these assumptions, a superdetermined inverse linear problem is formulated to estimate the vector of parameters $\bar{m}$ (\cref{eq:sphere9}) from the observed data ${\bar{B}}_z$ and $\bar{\bar{A}}$, the latter being obtained previously with the Euler Deconvolution.}
-
-\noindent{The problem of estimating a parameter vector $\bar{m}$ containing the spheres' magnetic moment vectors can be solved by minimizing the objective function $f\left(\bar{m}\right)$:}
-
-\begin{equation} \label{eq:sphere10}
-\centering
-\small f\left(\bar{m}\right)={\lVert e\lVert}^2= e^T\cdot e = {(\bar{\bar{A}} \cdot \bar{m}-\bar{d})}^T \cdot ~ (\bar{\bar{A}} \cdot \bar{m}-\bar{B_z})
-\end{equation}
-
-\noindent{When differentiating the (\cref{eq:sphere10}) by $\bar{m}$ and equating the result to the zero vector ($\frac{\partial f}{\partial m_k}=\bar{0}$).
-Then we obtain the normal equation for estimating least squares solution given by:}
-
-\begin{equation} \label{eq:sphere11}
-\centering
-\small \bar{m}\ =\left({\bar{\bar{A}}}^T\cdot\bar{\bar{A}}\right)^{-1}\cdot ~ \left({\bar{\bar{A}}}^T\cdot{\bar{B}}_z\right)\ 
-\end{equation}
-
-\noindent{As the least squares estimate (\cref{eq:sphere11}) is very sensitive to the presence of outliers in the observed data, the estimated parameters could be seriously misleading.
-To counteract this problem \cite{OliveiraJr.2015} suggest a robust scheme based on the minimization of the objective function obtained with the absolute error:}
-
-\begin{equation} \label{eq:sphere12}
-\centering
-\small f\left(\widetilde{m}\right)=\left(\sum_{i=1}^{N}\left| { \left(\bar{\bar{A}} \cdot \bar{m} \right)}_{i} - {{\bar{\left(B_z\right)}}}_{i} \right|\right)
-\end{equation}
-
-\noindent{Unlike the solution presented for the objective function in \cref{eq:sphere11}, the parameter vector minimizing \cref{eq:sphere12} cannot be obtained as a simple linear system.
-A practical way is the iteratively reweighted least squares algorithm \citep{Aster2019, OliveiraJr.2015}.
-In this algorithm, at each iteration k, the following linear system is solved:}
-
-\begin{equation} \label{eq:sphere13}
-\centering
-\small {\widetilde{m}}^{k+1}=\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot\bar{\bar{A}}\right)^{-1}\cdot\left({\bar{\bar{A}}}^T\cdot{\bar{\bar{R}}}^k\cdot{\bar{B}}_z\right)\ \ 
-\end{equation}
-
-\noindent{The term ${\bar{\bar{R}}}^k$ is an N $\times$ N diagonal matrix whose i-th element $r_i^k$ (i = 1, 2, ..., N) is given by:}
-
-\begin{equation} \label{eq:sphere14}
-{r_i}^k=\frac{1}{\left|\left(\bar{\bar{A}}\cdot\bar{m}\right)_i-{{\bar{B_z}}}_i+e\right|}
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $e$ is a small positive number used to prevent singularities}
-\end{FlushRight}
-
-\noindent{This iterative process starts (k = 0) with the solution vector obtained by the least squares estimator (\cref{eq:sphere11}).
-From this initial approximation ${\widetilde{m}}^0$, we calculate the matrix ${\bar{\bar{R}}}^0$ (\cref{eq:sphere14}).
-Which is used in the solution of the linear system given by \cref{eq:sphere13} to obtain the estimate ${\widetilde{m}}^1$.
-Later using this updated estimate to calculate the new matrix ${\bar{\bar{R}}}^1$ (\cref{eq:sphere14}), we solve the linear system (\cref{eq:sphere13}) to obtain a new estimate ${\widetilde{m}}^ 2$, and so on.
-As the iterations progress, this iterative procedure tends to converge and estimate $\widetilde{m}$, which is called robust estimate \citep{OliveiraJr.2015}.
-According to \cite{Aster2019} this convergence can be limited by a tolerance $\tau$, given by:}
-
-\begin{equation} \label{eq:sphere15}
-\centering
-\frac{\lVert {\widetilde{m}}^{k+1} - {\widetilde{m}}^{k} \lVert}{1 + \lVert \widetilde{m}^{k+1} \lVert} ≤ \tau
-\end{equation}
-
-\begin{FlushRight}
-\noindent{Where: $\tau$ is a positive number (\emph{e.g.}, ${10}^{-2}$) chosen by the algorithm user.}
-\end{FlushRight}
-
-%%
-\subsubsection{Directions of Magnetization and Uncertainty Propagation}
-
-\noindent{In paleomagnetic studies the magnetization vectors are represented in terms of their declination (D) and inclination (I).
-These are given as a function of the magnetization vector ${\bar{h}}_j$ (\cref{eq:sphere8}) and represented in spherical coordinates (as shown in \cref{fig:VECTORS}).}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
-\caption{Schematic representation of vector $m_j$ (\cref{eq:sphere8}) with elements $mx_j$, $my_j$ and $mz_j$ in cartesian coordinates.
-This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ...
-L.
-Modified from: \cite{OliveiraJr.2015}.}
-\label{fig:VECTORS}
-\end{figure}
-
-\noindent{In this way, it is possible to determine the directions ($D_j$ and $I_j$) and magnetic moment ($m_j$) for the j-th sphere of the set of L spheres by using:}
-
-\begin{equation} \label{eq:sphere16}
-\centering
-\small D_j=\tan^{-1}{\left(\frac{{my}_j}{{mx}_j}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17}
-\centering
-\small I_j=\tan^{-1}{\left(\frac{{mz}_j}{\sqrt{\left({mx}_j\right)^2+\left({my}_j\right)^2}}\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere17_m}
-\centering
-\small m_j=\sqrt{ {\left({mx}_j\right)}^{2} + {\left({my}_j\right)}^{2} + {\left({mz}_j\right)}^{2} } 
-\end{equation}
-
-\noindent{In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors and equipment inaccuracies.
-Noise in the observed data vector ${\bar{B}}_z$ affects the solution of the estimated parameter vector ${\bar{m}}_j$, regardless of the method used.
-Assuming that the noise during the measurement of the observed data is independent and with variance ${\sigma_0}^2$, one can quantify this effect on the estimated parameters through propagation of the covariance \citep{Aster2019}.
-The covariance matrix of these parameters will be given by:}
-
-\begin{equation} \label{eq:sphere18}
-\centering
-\small \bar{\bar{Cov}}\left({\bar{m}}_j\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{least square})}
-\end{equation}
-
-\begin{equation} \label{eq:sphere19}
-\centering
-\small \bar{\bar{Cov}}\left(\widetilde{m_j}\right)=\ {\sigma_0}^2\cdot\left({\bar{\bar{A}}}^T\cdot ~ {\bar{\bar{R}}}^k\cdot ~ \bar{\bar{A}}\right)^{-1} \ \ \text{(\emph{robust})}
-\end{equation}
-
-\noindent{The main diagonal of the covariance matrix  (\cref{eq:sphere18} and \cref{eq:sphere19}) contains the variance of each member of the parameter vector, as expressed below:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\footnotesize \bar{\bar{Cov}} =\left[\begin{matrix}Var({mx}_1)&\cdots&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&Var({my}_1)&\cdots&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&Var({mz}_1)&\cdots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\ddots&\cdots&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&Var({mx}_L)&\cdots&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&Var({my}_L)&\cdots\\\cdots&\cdots&\cdots&\cdots&\cdots&\cdots&Var({mz}_L)\\\end{matrix}\right]_{\text{\tiny 3L $\times$ 3L}}\
-\end{equation}
-
-\bigskip
-
-\noindent{Thus, for the j-th sphere:}
-
-\begin{equation} \label{eq:sphere20}
-\centering
-\sigma_{{mx}_j}=\sqrt{Var({mx}_j)},\ \ \ \  \sigma_{{my}_j}=\sqrt{Var({my}_j)}\ \ \ \text{and}\ \ \ \  \sigma_{{mz}_j}=\sqrt{Var({mz}_j)}
-\end{equation}
-
-\noindent{Thus, the propagation of uncertainties of the declination ($D_j$), inclination ($I_j$) and magnetic moment ($m_j$) results are given as a function of the parameters obtained in \cref{eq:sphere20}:}
-
-\begin{equation} \label{eq:sphere21}
-\centering
-\sigma_{D_j}=\sqrt{\left(\frac{\partial D_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial D_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22}
-\centering
-\sigma_{I_j}=\sqrt{\left(\frac{\partial I_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial I_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial I_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere22_m}
-\centering
-\sigma_{m_j}=\sqrt{\left(\frac{\partial m_j}{\partial{mx}_j}\right)^2\cdot\ \left(\sigma_{{mx}_j}\right)^2+\left(\frac{\partial m_j}{\partial{my}_j}\right)^2\cdot\ \left(\sigma_{{my}_j}\right)^2+\left(\frac{\partial m_j}{\partial{mz}_j}\right)^2\cdot\ \left(\sigma_{{mz}_j}\right)^2}
-\end{equation}
-
-\noindent{Where:}
-
-\begin{equation} \label{eq:sphere23}
-\centering
-\frac{\partial D_j}{\partial{mx}_j}=\frac{-{my}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere24}
-\centering
-\frac{\partial D_j}{\partial{my}_j}=\frac{{mx}_j}{{{mx}_j}^2+{{my}_j}^2}
-\end{equation}
-
-\begin{equation} \label{eq:sphere25}
-\centering
-\frac{\partial I_j}{\partial{mx}_j}=\frac{-{mx}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere26}
-\centering
-\frac{\partial I_j}{\partial{my}_j}=\frac{-{my}_j\cdot \ {mz}_j}{\sqrt{{{mx}_j}^2+{{my}_j}^2}\cdot \left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere27}
-\centering
-\frac{\partial I_j}{\partial{mz}_j}=\frac{\sqrt{{{mx}_j}^2+{{my}_j}^2}}{\left({{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2\right)}
-\end{equation}
-
-\begin{equation} \label{eq:sphere28}
-\centering
-\frac{\partial m_j}{\partial{mx}_j}=\frac{{mx}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere29}
-\centering
-\frac{\partial m_j}{\partial{my}_j}=\frac{{my}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-\begin{equation} \label{eq:sphere30}
-\centering
-\frac{\partial m_j}{\partial{mz}_j}=\frac{{mz}_j}{ \sqrt{{{mx}_j}^2+{{my}_j}^2+{{mz}_j}^2} }
-\end{equation}
-
-%%%%%%%%%%%%%
-\section{Results}
-
-%%%
-\subsection{Synthetic Data}
-
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but different directions), according to \cref{tab:directmodel}.
-Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a spacing of 1 μm.
-Subsequently, a pseudorandom noise of normal Gaussian distribution, with a zero mean and standard variation ≅ 5\% of the anomaly amplitude, was added to the data as shown in Figure XX.}
-
-\floatsetup[table]{capposition=top} % to put the caption on the top of the table
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\begin{table}[htbp]
-\caption{Initial position and magnetization parameters for each spherical source.}
-\label{tab:directmodel}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Center coordinates} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Magnetization} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Sphere} & X (µm)              & Y (µm)             & Z (µm)             & Q (A/m)            & D (°)            & I (°)            \\
-1                                                & 250                 & 250                & 8.50               & 6.0                & -140             & -30              \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                 & 500                & 10.0               & 6.0                & 0                & 62               \\
-3                                                & 750                 & 750                & 5.30               & 6.0                & -70              & -50              \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                 & 800                & 7.75               & 6.0                & 125              & 22              
-\end{tabular}
-\end{table}
-
-\subsubsection{Euler Solution}
-
-\noindent{The first step is to calculate the magnetic horizontal gradient in order to isolate the window data of each source.
-In the horizontal gradient, the magnetic anomaly caused by a body tends to overlap its limits, thus obtaining a robust positioning \citep{Blakely1996}.
-\cite{VanderWalt2014}.}
-
-\begin{table}[htbp]
-\caption{Central positions of sources input vs Euler deconvolution solutions.}
-\label{tab:eulerresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Posição do Centro de   Entrada} & \multicolumn{3}{c}{\cellcolor[HTML]{E7E7E7}Solução de Euler} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & X (µm)                  & Y (µm)                  & Z (µm)                 & X (µm)             & Y (µm)             & Z (µm)             \\
-1                                                & 250                     & 250                     & 8.50                   & 249.144984         & 250.084691         & 8.17863468         \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 500                     & 500                     & 10.0                   & 500.213134         & 500.443637         & 9.85904976         \\
-3                                                & 750                     & 750                     & 5.30                   & 749.873747         & 750.127834         & 5.26685529         \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 200                     & 800                     & 7.75                   & 200.177971         & 800.331017         & 7.82974687        
-\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-\caption{Input magnetization directions vs inversion solutions and their error propagation.}
-\label{tab:inversionresults}
-\centering
-\begin{tabular}[width=1.0\textwidth]{ccccccc}
-\rowcolor[HTML]{E7E7E7} 
-\cellcolor[HTML]{E7E7E7}                         & \multicolumn{2}{c}{\cellcolor[HTML]{E7E7E7}Direção de Entrada} & \multicolumn{4}{c}{\cellcolor[HTML]{E7E7E7}Direções Recuperadas e   Incertezas} \\
-\rowcolor[HTML]{E7E7E7} 
-\multirow{-2}{*}{\cellcolor[HTML]{E7E7E7}Esfera} & D (°)                          & I (°)                         & D (°)               & $\sigma$ D (°)            & I (°)             & $\sigma$ I (°)           \\
-1                                                & -140                           & -30                           & -137.0294           & ± 0.7641          & -32.6550          & ± 0.5169          \\
-\rowcolor[HTML]{E7E7E7} 
-2                                                & 0                              & 62                            & 2.5167              & ± 1.5004          & 60.5473           & ± 0.6917          \\
-3                                                & -70                            & -50                           & -68.3316            & ± 0.6752          & -49.0172          & ± 0.3923          \\
-\rowcolor[HTML]{E7E7E7} 
-4                                                & 125                            & 22                            & 124.8320            & ± 0.6449          & 21.9940           & ± 0.4515         
-\end{tabular}
-\end{table}
-
-\section{Discussion}
-
-\section{Conclusion}
-\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
-}
-
-\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
-
-\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform.
-This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}
-
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
-
-\begin{singlespace}
-\doublespacing
-\bibliographystyle{agu}  % style file is seg.bst
-\bibliography{article1}
-\end{singlespace}
 \end{document}

### 2022-11-22 article_1/Conclusion.tex
Export the images directly to the LaTeX images folder

@@
 
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions \ref{AppendixA.1} }
+\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }

### 2022-11-24 article_1/Result1.tex
Export the images directly to the LaTeX images folder
Add random function with seeds and change variable names

@@
 %%%%%%%%%%%%%
+\begin{singlespace}
 \section{Aplication to Synthetic Data}
+
+\noindent{In order to test the efficiency of the proposed inversion method, we applied it to two sets of synthetic data contaminated by high and/or low frequency noise. }
+
+\noindent{The first synthetic test is performed by generating a simple set of four spheres with similar magnetization intensity and radius, but completely different magnetization directions.
+Generating a data set contaminated by high frequency noise.
+In this simulation, the magnetization directions and magnetic moment intensity are directly compared with the initial input parameters.
+This first simplified test is basically done to investigate the efficiency of the inversions used for Euler positioning and magnetization parameters, thus being a validation of the methodology.}
+
+\noindent{The second data set is data generated by a more complex model containing one hundred spheres with different radius and magnetization intensity, but magnetized in a similar direction within one standard deviation.
+This data set is corrupted by both low and high frequency noise.
+In this second application there is also validation using the comparison of the model data with the retrieved data.
+The complexity of this synthetic data seeks to more faithfully simulate the applicability of the proposed method to real SMM data.}
 
@@
 \subsection{Complex Simulation: Testing Applicability}
+
+\begin{figure}[hbpt]
+\centering
+\includegraphics[width=1.0\textwidth]{ComplexSynthetic.png}
+\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise.
+b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
+\label{fig:ComplexSynthetic}
+\end{figure}
+
+\end{singlespace}

### 2022-11-24 article_1/input_par_table.tex
Add random function with seeds and change variable names

@@
 \multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
-1                                                & 250.00                       & 250.00                       & 5.30                       & 8.70e-15               & -140.00                        & -30.00                 \\
+1                                                & 250.00                       & 250.00                       & 5.30                       & -5.77e-15               & -140.00                        & -30.00                 \\
 \rowcolor[HTML]{FFFFFF} 
-2                                                & 500.00                       & 500.00                       & 7.75                       & 7.63e-15               & 0.00                        & 62.00                 \\
-3                                                & 750.00                       & 750.00                       & 8.50                       & 6.21e-15               & -70.00                        & -50.00                 \\
+2                                                & 500.00                       & 500.00                       & 7.75                       & -4.84e-15               & 0.00                        & 62.00                 \\
+3                                                & 750.00                       & 750.00                       & 8.50                       & -4.35e-15               & -70.00                        & -50.00                 \\
 \rowcolor[HTML]{FFFFFF} 
-4                                                & 200.00                       & 800.00                       & 10.00                       & 6.66e-15               & 125.00                        & 22.00                  \\ \hline
+4                                                & 200.00                       & 800.00                       & 10.00                       & 3.58e-15               & 125.00                        & 22.00                  \\ \hline
 \end{tabular}

### 2022-11-24 article_1/solution_par_table.tex
Add random function with seeds and change variable names

@@
 \multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
-1                                                & 250.03           & 249.99           & 5.33           & 8.75e-15  $\pm$  2.30e-17           & -140.04  $\pm$  0.19           & -29.76  $\pm$  0.13           \\
+1                                                & 250.07           & 250.04           & 5.36           & 8.83e-15  $\pm$  2.32e-17           & -140.03  $\pm$  0.18           & -29.45  $\pm$  0.13           \\
 \rowcolor[HTML]{FFFFFF} 
-2                                                & 499.96           & 500.05           & 7.70           & 7.60e-15  $\pm$  2.90e-17           & 1.17  $\pm$  0.61           & 62.50  $\pm$  0.27           \\
-3                                                & 750.12           & 750.04           & 8.47           & 6.19e-15  $\pm$  3.52e-17           & -71.88  $\pm$  0.60           & -50.02  $\pm$  0.35           \\
+2                                                & 500.00           & 500.01           & 7.71           & 7.57e-15  $\pm$  2.91e-17           & 0.23  $\pm$  0.60           & 61.79  $\pm$  0.27           \\
+3                                                & 749.92           & 749.98           & 8.38           & 6.10e-15  $\pm$  3.46e-17           & -69.93  $\pm$  0.61           & -50.50  $\pm$  0.35           \\
 \rowcolor[HTML]{FFFFFF} 
-4                                                & 200.02           & 799.73           & 10.08           & 6.73e-15  $\pm$  5.05e-17           & 124.28  $\pm$  0.48           & 22.78  $\pm$  0.34           \\ \hline
+4                                                & 199.94           & 800.21           & 10.10           & 6.78e-15  $\pm$  5.09e-17           & 125.09  $\pm$  0.48           & 21.02  $\pm$  0.33           \\ \hline
 \end{tabular}

### 2022-11-24 article_1/code/Complex_Synthetic/functions.py

@@ -9,7 +9,43 @@ from apsg import *
 microm2m = 1.0E-6
 m2microm = 1.0E6
 
-def cartesian_components(D, I, Q, R):
+def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * mean_value: float number, corresponds to the mean of the normal distribution
+        * std_dev: float number, corresponds to the standart deviation of the normal distribution
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
+    
+    return(normal_Gaussian_distribution)
+
+def random_randint_seeded(min_value, max_value, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * min_value: float number, corresponds to the minimum value pickable
+        * min_value: float number, corresponds to the maximum value pickable
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    distribution_array = np.random.randint(min_value, max_value, size)
+    
+    return(distribution_array)
+
+def cartesian_components(D, I, M, R):
     
     """
     Calculates the cartesian components of  natural remanent magnetization (NRM)
@@ -18,7 +54,7 @@ def cartesian_components(D, I, Q, R):
     Parameters:
         * D: 1D-array containing magnetization declination (0 to 360 degrees)
         * I: 1D-array containing magnetization inclination (-90 to 90  degress)
-        * Q: 1D-array containing magnetization intensity (A/m)
+        * M: 1D-array containing magnetization intensity (A/m)
         * R: 1D-array containing sphere's radius (m)
 
     """
[…]

### 2022-11-24 article_1/code/Demag_Simulation/Simu_1/functions.py

@@ -1,676 +1,0 @@
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-from skimage.feature import blob_log
-from apsg import *
-
-
-microm2m = 1.0E-6
-m2microm = 1.0E6
-
-def cartesian_components(D, I, Q, R):
-    
-    """
-    Calculates the cartesian components of  natural remanent magnetization (NRM)
-    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
-
-    Parameters:
-        * D: 1D-array containing magnetization declination (0 to 360 degrees)
-        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
-        * Q: 1D-array containing magnetization intensity (A/m)
-        * R: 1D-array containing sphere's radius (m)
-
-    """
-    
-    m = []
-
-    for i in range(np.size(D)):
-        m_sphere =  np.matrix([[(Q[i]*np.cos(I[i]*(np.pi/180))*np.cos(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
-                               [(Q[i]*np.cos(I[i]*(np.pi/180))*np.sin(D[i]*(np.pi/180))) * ((4.0*np.pi*R[i]**3)/3.0) ],
-                               [(Q[i]*np.sin(I[i]*(np.pi/180)))*((4.0*np.pi*R[i]**3)/3.0)                            ]])
-
-        m = np.append(m,m_sphere)
-        
-    return(np.array(m))
-
-
-
-def sensibility_matrix(X, Y, Z, Xc, Yc, Zc): 
-    
-    """
-    Generates the sensibility matrix for vertical component of magnetization
-
-    Parameters:
-        *  X,  Y,  Z: 1D-arrays with x, y and z data positions
-        * Xc, Yc, Zc: 1D-arrays with x, y and z data  of the sphere's center positions
-
-    Constant:
-        * cm: is a constant given by 4*np.pi/µo = 10**(-7) 
-            where µo is the vaccum magnetic permeability
-    """
-
-    cm = 10**(-7) # H/m  == T·m/A
-
-    Mz = np.empty( (np.size(Xc)*3, np.size(Z)) )
-
-    
-    k = 0
-    l = 1
-    m = 2 
-
-    for j in range(len(Xc)):
-        
[…]

### 2022-12-01 article_1/Result1.tex
Change results (tables and figures) and update apsg library

@@
 
-\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:ModelTab}.
+\noindent{We applied the proposed method in a numerical simulation of a geological thin-section of dimensions 1000 μm x 1000 μm in a regular grid (1000 x 1000) for estimating the magnetization directions of four spherical sources uniformly magnetized (but with different directions), according to \cref{tab:SimpleSyntheic}.
 Totaling an observation number N = $10^6$ obtained at a sensor-sample distance of 5 μm and a grid spacing of 1 μm.
-Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 25 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}
+Subsequently, the data vector was contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and 15 nT standard deviation, as shown in \cref{fig:SimpleSynthetic}a.}
 
@@
 % If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{input_par_table}
+\input{simple_synthetic_table}
 
@@
 
-\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source (N = 3).
+\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$).
 Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}
@@
 With this, the magnetization directions (D and I) and the intensity of the magnetic moment can be estimated using equations (\cref{eq:sphere16,eq:sphere17,eq:sphere17_m}), as well as the uncertainty propagation of this inversion, using equations (\cref{eq:sphere21,eq:sphere22,eq:sphere22_m}) and considering $\sigma$ = 25nT.
-The results obtained with the least squares estimator can also be seen in \cref{tab:InversionTab}.}
-
-\bigskip
-
-% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
-\input{solution_par_table}
+The results obtained with the least squares estimator can also be seen in \cref{tab:SimpleSyntheic}.}
 
@@
 
+\begin{figure}[hbpt]
+\centering
+\includegraphics[width=1.0\textwidth]{ComplexComparison.png}
+\caption{blablabla.}
+\label{fig:ComplexSynthetic2}
+\end{figure}
+
+\begin{figure}[hbpt]
+\centering
+\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
+\caption{blablabla.}
+\label{fig:ComplexSynthetic3}
+\end{figure}
+
 \end{singlespace}

### 2022-12-01 article_1/code/Complex_Synthetic/functions.py

@@ -690,9 +690,6 @@ def least_square_solver(X, Y, Z, Xc, Yc, Zc, Bz):
     """
 
     Bz = np.squeeze(np.reshape(Bz, (np.size(Bz),1))) # to avoid matrix dimension miss match
-    background = Bz.mean()
-
-    Bz = Bz - background # remove signal caused by deeper sources
 
     A = sensibility_matrix(X, Y, Z, Xc, Yc, Zc)
     m = np.linalg.solve(A.T@A, A.T@Bz)
@@ -712,7 +709,7 @@ def least_square_solver(X, Y, Z, Xc, Yc, Zc, Bz):
         mz = np.append(mz, m_T[row, 2] )
         
     
-    forward_model = (A@m) + background
+    forward_model = (A@m)
 
     return(mx, my, mz, A, forward_model)
 
@@ -744,8 +741,9 @@ def directions(mx, my, mz, plot = False, show_mean = False, show_alpha95 = False
             
         
     if plot == True:
-        settings['figsize'] = (7, 7)
-        
+        from apsg.feature import LineationSet
+    
+        fig = plt.figure(figsize=(5, 5))
         s = StereoNet(grid=True, legend=True)
         
         group = []
@@ -760,25 +758,25 @@ def directions(mx, my, mz, plot = False, show_mean = False, show_alpha95 = False
                 color = 'k'
             
             if w == 0:
-                s.line((Lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
-                group.append((Lin(float(D[w]), np.round(np.absolute(I[w])))))
+                s.line((lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
+                group.append((lin(float(D[w]), np.round(np.absolute(I[w])))))
 
             else:
-                s.line((Lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
-                group.append((Lin(float(D[w]), np.round(np.absolute(I[w])))))
-        
-        group = Group(group) # create a group variable with all lines
+                s.line((lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
+                group.append((lin(float(D[w]), np.round(np.absolute(I[w])))))
+         
+        group = LineationSet(group) # create a group variable with all lines
         
         if show_mean == True:
             mean = group.R
             s.line(mean,'b.')
[…]

### 2022-12-02 article_1/Methodology.tex
Add random function with seeds and change variable names
Change results (tables and figures) and update apsg library
Add stereograms mean directions and remove methodology figure

@@
+\begin{singlespace}
+
 \section{Methodology}
@@
 \noindent{The SMM can also be considered as a form of aeromagnetic survey, carried out at microscales on sources of flat topography, with high spatial resolution and greater sensitivity to magnetic moment \citep{Lima2013}.
-An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface \citep{Fu2020} capable of detecting the magnetic signals of SD magnetite particles (\cref{fig:QDM}).
+An emerging magnetic imaging technology is the quantum diamond microscope (QDM) with very high spatial resolution ($≅$ 1 μm), and can recover magnetic moments as weak as 10$^{-17}$ Am$^2$, through magnetic sensors located at altitudes between 1 and 5 µm relative to the sample surface capable of detecting the magnetic signals of SD magnetite particles \citep{Fu2020}.
 Another promising type of magnetic microscope is the magnetic tunnel junction (MTJ) with a spatial resolution greater than 7 µm, a magnetic moment sensitivity of up to 10$^{-14}$ Am$^2$ and sample-sensor distance of 7 µm.
 Its advantages reside in the fact that these MTJ devices do not require high bias current to operate (few tens of µA), which avoids induced magnetization signals created by artificial magnetic field during the measurements \citep{Lima2014}.}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{QDM.png}
-\caption{Sample classes accessible to QDM, SQUID microscope and 2G Enterprises SRM.
-The accessible region for the QDM was calculated assuming a magnetic field noise threshold of 5 nT and a minimum sensor-sample distance of 5 μm.
-The calculation for the SQUID microscope assumed field noise values of 15 pT and sensor-sample distance of 150 μm.
-Source: \cite{Fu2020}.}
-\label{fig:QDM}
-\end{figure}
 
@@
 The structural index is the only necessary a priori knowledge.
-Once a value for n is assumed (n = 3 for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
+Once a value for n is assumed ($n = 3$ for spherical/punctual magnetic sources), the homogeneous Euler equation can be rearranged as follows:}
 
@@
 
-\bigskip
-
 \noindent{Thus, for the j-th sphere:}
@@
 \end{equation}
+
+\end{singlespace}

### 2022-12-02 article_1/code/Complex_Synthetic/functions.py

@@ -768,8 +768,6 @@ def directions(mx, my, mz, plot = False, show_mean = False, show_alpha95 = False
         group = LineationSet(group) # create a group variable with all lines
         
         if show_mean == True:
-            mean = group.R
-            s.line(mean,'b.')
             s.line((lin(float(D_mean), np.round(np.absolute(I_mean)))), color='g', marker='o')
             print('Mean direction: '+str(D_mean)+' / '+str(I_mean))
         if show_alpha95 == True:

### 2022-12-02 article/Conclusion.tex
Rename to article since there will be only 1 in this repo

--- 2022-11-22 article_1/Conclusion.tex
@@
+\begin{singlespace}
+
 \section{Conclusion}
@@
 In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index (N = 3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
+After estimating the structural index ($n = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}
 
@@
 \noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
+
+\end{singlespace}

### 2022-12-02 article/Result1.tex
Rename to article since there will be only 1 in this repo

--- 2022-12-01 article_1/Result1.tex
@@
 \noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$).
-Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}
+Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:SimpleSyntheic}.}
 

### 2022-12-02 article/solution_par_table.tex
Rename to article since there will be only 1 in this repo

\begin{table}[htbp]
\caption{Positioning and magnetization parameters recovered with the inversion.}
\label{tab:InversionTab}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{ccccccc}
\hline   
\rowcolor[HTML]{FFFFFF} 
\cellcolor[HTML]{FFFFFF}                         & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Center coordinates}                    & \multicolumn{3}{c}{\cellcolor[HTML]{FFFFFF}Magnetization}     \\
\rowcolor[HTML]{FFFFFF} 
\multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
1                                                & 250.03           & 249.94           & 5.37           & 8.80e-15  $\pm$  1.39e-17           & -140.22  $\pm$  0.11           & -30.04  $\pm$  0.08           \\
\rowcolor[HTML]{FFFFFF} 
2                                                & 499.96           & 500.00           & 7.76           & 7.65e-15  $\pm$  1.89e-17           & -69.42  $\pm$  0.26           & -49.85  $\pm$  0.15           \\
3                                                & 749.98           & 749.97           & 8.56           & 6.29e-15  $\pm$  1.98e-17           & 9.06  $\pm$  0.50           & 62.34  $\pm$  0.22           \\
\rowcolor[HTML]{FFFFFF} 
4                                                & 200.10           & 800.12           & 9.99           & 4.92e-15  $\pm$  3.00e-17           & 124.63  $\pm$  0.39           & 21.76  $\pm$  0.27           \\ \hline                 
\end{tabular}
}
\end{table}

### 2022-12-05 article_1/Result1.tex
Add discussion in complex synthetic section

@@
 
-\bigskip
-
-\noindent{After isolante the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$).
-Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:InversionTab}.}
+\noindent{After isolating the potencial field data and first derivatives for each source, we can solve the 3D Euler deconvolution \cref{eq:euler2} proposed by  \cite{Reid1990}, one for each subarea selected (window data), by assuming the structural index of a sphere/punctual source ($n = 3$).
+Thus, obtaining a sturdy result for the central positioning (Xc, Yc, Zc) of each source causing the magnetic potential anomaly in the observed data set, as shown in \cref{tab:SimpleSyntheic}.}
 
@@
 
+\noindent{This test tries to replicate a more complicated scenario by simulating a hundred sources randomly distributed in the imaged area of ​​the synthetic thin section of 2000 x 1400 $\mu m$, with 2 $\mu m$ grid spacing and 5 $\mu m$ sample-sensor distance.
+For greater fidelity with real samples, the magnetic sources have different diameters, magnetizations and depths.
+The depths of the spheres vary between 1 and 19 $\mu m$, while the radii have values ​​that range from 0.01 to 0.95 $\mu m$.
+The magnetization acquisition simulates an induced field with both declination and inclination directions of 45\textdegree.
+However, as seen in real data, these directions have both varying declination and inclination, but averaging centered in the direction of the induced field.
+Therefore, both the NRM declination and inclination of the particles were selected using pseudo-random normal distribution with mean 45\textdegree and standard deviation of 8\textdegree.
+Finally, high (pseudo-random normal with zero mean and standard deviation of 5 nT) and low frequency noises were added to the anomaly data of the vertical field component of the magnetic field, which can be seen in \cref{fig:ComplexSynthetic}a.}
+
+\noindent{After applying the same filtering steps described earlier on the simple synthetic sample, the blob detection algorithm was applied on the total gradient anomaly map and the individual source windows were selected (\cref{fig:ComplexSynthetic}b).
+The latter was able to detect 84 magnetic particles.
+The solution of Euler's equation was then determined for each data window to later be used as input data for inversion of magnetic moments.}
+
 \begin{figure}[hbpt]
@@
 
+\noindent{The spatiality of the inversion results is one of the great differences between the application of magnetic microscopy and the classic techniques of paleomagnetism.
+Thus, the validation of these results is expressed individually in the windows obtained with the blob detection through the declination, inclination and magnetic moment misfits (\cref{fig:ComplexSynthetic2}a-c, respectively), in addition to the determination coefficient R$^2$ obtained by comparing the forward model and the observed data (\cref{fig:ComplexSynthetic2}d).
+As both the depth and the size of the particles influence the magnetic signal generated by them, this information is also given in these graphs in the form of a cross bar.
+Where the vertical bars scale with the depth of the sources (max = 19 $\mu m$), while the horizontal bars scale with the radius (max = 0.95 $\mu m$).}
+
 \begin{figure}[hbpt]
@@
 \includegraphics[width=1.0\textwidth]{ComplexComparison.png}
-\caption{blablabla.}
+\caption{The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being directions of (a) declination and (b) inclination and (c) intensity of magnetic moment , in addition to the R$^2$ score (d) obtained by comparing the forward model and the actual data.
+The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 19 $\mu m$) and the horizontal bar by the radius (0.01 - 0.95 $\mu m$).}
 \label{fig:ComplexSynthetic2}
 \end{figure}
+
+\noindent{The application in complex synthetic data also allows observing the strengths and limitations of the proposed methodology.
+Some of the strengths that can be mentioned are: (i) the fact that the applied technique not only detects most of the modeled sources, but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the declination and inclination directions, usually less than 5\textdegree (\cref{fig:ComplexSynthetic2}a-b).
+(iii) The magnetic moments obtained also tend to not deviate much from the real values (\cref{fig:ComplexSynthetic2}c) when the R$^2$ scores are high (\cref{fig:ComplexSynthetic2}d).
+(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some weak signal but isolated particles.}
+
+\noindent{While, the limitations observed were already expected, namely (i) the blob detection is insensitive when there are sources that are very close, grouping them in the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+(ii) The very same occurs when there is a source under another, in this case the magnetic signal is a sum of both.
+(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion}
+
+\noindent{Apparently there is a direct relationship between the vertical position and depth with the observed errors.
+It is clear from cross bars on the \cref{fig:ComplexSynthetic2} that deep particles and/or with small radii generate worse results than those more superficial particles with larger radii, this is mainly because these two properties will influence the signal picked up by the sensor.
+Small particles have weaker magnetic moment signal, in addition, very deep sources have their signal considerably attenuated at the height of the sensor, when both characteristics are present at the same time the error tends to be greater.
+The opposite is also true, larger particles and superficial particles have their signal better captured by the sensor.
+Small and superficial particles might also generate low errors because, despite having lower magnetic moments, the sensor-sample distance is sufficient to generate a good signal.}
+
+\noindent{The modeled magnetization directions not only generate an average direction coincident with the simulated induced field, but also have relatively small Fisher cones of confidence \citep{Fisher1987} due to their clustering (\cref{fig:ComplexSynthetic3}a).
+On the other hand, the recovered directions may be more sparse, despite this the mean direction obtained is statically the same as the field modeled inside the 95\% confidence cone (\cref{fig:ComplexSynthetic3}b).
+If necessary, the data can be filtered according to the highest adjustments obtained with the coefficient of determination (R$^2$).
+The value of R$^2$ can vary from $-\infty$ to 1, with values closest to 1 corresponding to the best modeling results.
+Thus, filtering the results obtained with the magnetic inversion with R$^2 \geq 0.7$ we obtain the directions closest to the average and less sparse, maintaining the high reliability result (\cref{fig:ComplexSynthetic3}c).}
 
@@
 \includegraphics[width=1.0\textwidth]{ComplexStereo.png}
-\caption{blablabla.}
+\caption{a) The real data models a thin section of rock with particles uniformly magnetized in the average direction of the induced field 45\textdegree/45\textdegree.
+b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction.
+(c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
 \label{fig:ComplexSynthetic3}

### 2022-12-05 article_1/Result1.tex
Replace apsg library with mplstereonet

@@
 b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction.
-(c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
+c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
 \label{fig:ComplexSynthetic3}

### 2022-12-05 article_1/code/Complex_Synthetic/functions.py

@@ -3,7 +3,7 @@ import scipy as sp
 import matplotlib.pyplot as plt
 import math
 from skimage.feature import blob_log
-from apsg import *
+import mplstereonet as mpl
 
 
 microm2m = 1.0E-6
@@ -727,7 +727,7 @@ def directions(mx, my, mz, plot = False, show_mean = False, show_alpha95 = False
         * show_mean: boolean, if plot = True the mean direction will also be plotted
         * show_alpha95: boolean, if plot = True the alpha95 cone will also be plotted
     """
-
+    confidence = 95
     D = []
     I = []
     
@@ -739,45 +739,50 @@ def directions(mx, my, mz, plot = False, show_mean = False, show_alpha95 = False
         I = np.append( I, (math.atan2( mz[i], (np.sqrt(my[i]**2+mx[i]**2)) ) )* (180/np.pi))
         D = np.append( D, (math.atan2( my[i],  mx[i] ) * (180/np.pi) ) )
             
-        
+            
     if plot == True:
-        from apsg.feature import LineationSet
-    
-        fig = plt.figure(figsize=(5, 5))
-        s = StereoNet(grid=True, legend=True)
-        
-        group = []
-        
-        for w in range (np.size(D)):
-            
-            if I[w] >= 0:
-                symbol = '.'
+
+        fig = plt.figure()
+        ax = fig.add_subplot(111, projection='stereonet')
+           
+
+        for i in range(len(D)):
+            if I[i]>0:
                 color = 'r'
+                marker='.'
             else:
-                symbol = '.'
-                color = 'k'
-            
-            if w == 0:
-                s.line((lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
-                group.append((lin(float(D[w]), np.round(np.absolute(I[w])))))
+                color='k'
+                marker='.'
+            ax.line(abs(I[i]), D[i], color=color, marker=marker, markersize=4)
 
-            else:
-                s.line((lin(float(D[w]), np.round(np.absolute(I[w])))), color=color, marker=symbol)
-                group.append((lin(float(D[w]), np.round(np.absolute(I[w])))))
-         
-        group = LineationSet(group) # create a group variable with all lines
-        
+
         if show_mean == True:
-            s.line((lin(float(D_mean), np.round(np.absolute(I_mean)))), color='g', marker='o')
[…]

### 2022-12-06 article/code/Complex_Synthetic/functions.py
Start moving code to a single folder and removing duplication
Still a long way to go but made a start of simplifying things a bit.

@@ -1,916 +1,0 @@
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-from skimage.feature import blob_log
-from apsg import *
-
-
-microm2m = 1.0E-6
-m2microm = 1.0E6
-
-def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
-
-    """
-    Generates pseudo-random normal gaussian distribution, but the seed
-    gives more controllable results.
-
-    Parameters:
-        * mean_value: float number, corresponds to the mean of the normal distribution
-        * std_dev: float number, corresponds to the standart deviation of the normal distribution
-        * size: scalar number, corresponds to the size of the distribution array
-        * seed_value: float number, it is the seed for the distribution
-    """
-    
-    np.random.seed(seed_value)
-    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
-    
-    return(normal_Gaussian_distribution)
-
-def random_randint_seeded(min_value, max_value, size, seed_value=0):
-
-    """
-    Generates pseudo-random normal gaussian distribution, but the seed
-    gives more controllable results.
-
-    Parameters:
-        * min_value: float number, corresponds to the minimum value pickable
-        * min_value: float number, corresponds to the maximum value pickable
-        * size: scalar number, corresponds to the size of the distribution array
-        * seed_value: float number, it is the seed for the distribution
-    """
-    
-    np.random.seed(seed_value)
-    distribution_array = np.random.randint(min_value, max_value, size)
-    
-    return(distribution_array)
-
-def cartesian_components(D, I, M, R):
-    
-    """
-    Calculates the cartesian components of  natural remanent magnetization (NRM)
-    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
-
-    Parameters:
-        * D: 1D-array containing magnetization declination (0 to 360 degrees)
-        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
[…]

### 2022-12-06 code/functions.py

@@ -1,0 +1,913 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+from skimage.feature import blob_log
+from apsg import *
+
+
+microm2m = 1.0E-6
+m2microm = 1.0E6
+cm = 10**(-7) # H/m  == T·m/A
+
+
+def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * mean_value: float number, corresponds to the mean of the normal distribution
+        * std_dev: float number, corresponds to the standart deviation of the normal distribution
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
+    
+    return(normal_Gaussian_distribution)
+
+def random_randint_seeded(min_value, max_value, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * min_value: float number, corresponds to the minimum value pickable
+        * min_value: float number, corresponds to the maximum value pickable
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    distribution_array = np.random.randint(min_value, max_value, size)
+    
+    return(distribution_array)
+
+
+
+def magnetic_moment_vector(declination, inclination, magnetization, radius):    
+    """
+    Calculates the cartesian components of natural remanent magnetization (NRM)
+    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
+
+    Parameters
+    ----------
+    declination : array
+        Array containing magnetization declination (0 to 360 degrees)
+    inclination : array
[…]

### 2022-12-19 article_1/code/Real_Data/functions.py
Generate the synthetic data separately

@@ -1,0 +1,921 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import math
+from skimage.feature import blob_log
+import mplstereonet as mpl
+
+
+microm2m = 1.0E-6
+m2microm = 1.0E6
+
+def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * mean_value: float number, corresponds to the mean of the normal distribution
+        * std_dev: float number, corresponds to the standart deviation of the normal distribution
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
+    
+    return(normal_Gaussian_distribution)
+
+def random_randint_seeded(min_value, max_value, size, seed_value=0):
+
+    """
+    Generates pseudo-random normal gaussian distribution, but the seed
+    gives more controllable results.
+
+    Parameters:
+        * min_value: float number, corresponds to the minimum value pickable
+        * min_value: float number, corresponds to the maximum value pickable
+        * size: scalar number, corresponds to the size of the distribution array
+        * seed_value: float number, it is the seed for the distribution
+    """
+    
+    np.random.seed(seed_value)
+    distribution_array = np.random.randint(min_value, max_value, size)
+    
+    return(distribution_array)
+
+def cartesian_components(D, I, M, R):
+    
+    """
+    Calculates the cartesian components of  natural remanent magnetization (NRM)
+    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
+
+    Parameters:
+        * D: 1D-array containing magnetization declination (0 to 360 degrees)
+        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
[…]

### 2022-12-19 article_1/Conclusion.tex
Add random function with seeds and change variable names
Delete unused images

@@
 
-\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
+\noindent{The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precisely center positions, but also retrieve de magnetization directions and intensity even under considerable effect of high frequency noise (15 nT).
+While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low frequency noise.}
+
+\end{singlespace}

### 2022-12-19 article_1/Result1.tex
Delete unused images

@@
 
-\noindent{The modeled magnetization directions not only generate an average direction coincident with the simulated induced field, but also have relatively small Fisher cones of confidence \citep{Fisher1987} due to their clustering (\cref{fig:ComplexSynthetic3}a).
+\noindent{The modelled magnetization directions not only generate an average direction coincident with the simulated induced field, but also have relatively small Fisher cones of confidence \citep{Fisher1987} due to their clustering (\cref{fig:ComplexSynthetic3}a).
 On the other hand, the recovered directions may be more sparse, despite this the mean direction obtained is statically the same as the field modeled inside the 95\% confidence cone (\cref{fig:ComplexSynthetic3}b).
 If necessary, the data can be filtered according to the highest adjustments obtained with the coefficient of determination (R$^2$).
-The value of R$^2$ can vary from $-\infty$ to 1, with values closest to 1 corresponding to the best modeling results.
-Thus, filtering the results obtained with the magnetic inversion with R$^2 \geq 0.7$ we obtain the directions closest to the average and less sparse, maintaining the high reliability result (\cref{fig:ComplexSynthetic3}c).}
+The value of R$^2$ can vary from $-\infty$ to 1, with values closest to 1 corresponding to the best modelling results.
+Thus, filtering the results obtained with the magnetic inversion with R$^2 \geq 0.9$ we obtain the directions closest to the average and less sparse, maintaining the high reliability result (\cref{fig:ComplexSynthetic3}c).}
 
@@
 b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction.
-c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
+c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.9$) to ensure better grouping of the directions around the mean value.}
 \label{fig:ComplexSynthetic3}

### 2022-12-19 article_1/solution_par_table.tex
Delete unused images

@@
 \multirow{-2}{*}{\cellcolor[HTML]{FFFFFF}Sphere} & Xc ($\mu m$) & Yc ($\mu m$) & Zc ($\mu m$) & m ($A \cdot m^2$) & D (\textdegree) & I (\textdegree) \\  \hline   
-1                                                & 250.07           & 250.04           & 5.36           & 8.83e-15  $\pm$  2.32e-17           & -140.03  $\pm$  0.18           & -29.45  $\pm$  0.13           \\
+1                                                & 250.28           & 250.19           & 5.38           & 8.82e-15  $\pm$  1.39e-17           & -140.22  $\pm$  0.11           & -30.04  $\pm$  0.08           \\
 \rowcolor[HTML]{FFFFFF} 
-2                                                & 500.00           & 500.01           & 7.71           & 7.57e-15  $\pm$  2.91e-17           & 0.23  $\pm$  0.60           & 61.79  $\pm$  0.27           \\
-3                                                & 749.92           & 749.98           & 8.38           & 6.10e-15  $\pm$  3.46e-17           & -69.93  $\pm$  0.61           & -50.50  $\pm$  0.35           \\
+2                                                & 500.46           & 500.50           & 7.77           & 7.67e-15  $\pm$  1.90e-17           & -69.42  $\pm$  0.26           & -49.85  $\pm$  0.15           \\
+3                                                & 750.73           & 750.72           & 8.57           & 6.31e-15  $\pm$  1.99e-17           & 9.06  $\pm$  0.50           & 62.34  $\pm$  0.22           \\
 \rowcolor[HTML]{FFFFFF} 
-4                                                & 199.94           & 800.21           & 10.10           & 6.78e-15  $\pm$  5.09e-17           & 125.09  $\pm$  0.48           & 21.02  $\pm$  0.33           \\ \hline
+4                                                & 200.30           & 800.92           & 10.00           & 4.94e-15  $\pm$  3.01e-17           & 124.63  $\pm$  0.39           & 21.76  $\pm$  0.27           \\ \hline
 \end{tabular}

### 2023-02-15 article_1/code/Synthetic/functions.py
Start moving files around to organize the repository

@@ -1,1187 +1,0 @@
-import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-from skimage.feature import blob_log
-import mplstereonet as mpl
-import pandas as pd
-
-microm2m = 1.0E-6
-m2microm = 1.0E6
-
-def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
-
-    """
-    Generates pseudo-random normal gaussian distribution, but the seed
-    gives more controllable results.
-
-    Parameters:
-        * mean_value: float number, corresponds to the mean of the normal distribution
-        * std_dev: float number, corresponds to the standart deviation of the normal distribution
-        * size: scalar number, corresponds to the size of the distribution array
-        * seed_value: float number, it is the seed for the distribution
-    """
-    
-    np.random.seed(seed_value)
-    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
-    
-    return(normal_Gaussian_distribution)
-
-def random_randint_seeded(min_value, max_value, size, seed_value=0):
-
-    """
-    Generates pseudo-random normal gaussian distribution, but the seed
-    gives more controllable results.
-
-    Parameters:
-        * min_value: float number, corresponds to the minimum value pickable
-        * min_value: float number, corresponds to the maximum value pickable
-        * size: scalar number, corresponds to the size of the distribution array
-        * seed_value: float number, it is the seed for the distribution
-    """
-    
-    np.random.seed(seed_value)
-    distribution_array = np.random.randint(min_value, max_value, size)
-    
-    return(distribution_array)
-
-def cartesian_components(D, I, M, R):
-    
-    """
-    Calculates the cartesian components of  natural remanent magnetization (NRM)
-    for uniformily magnetized spheres (mx, my, mz) required in the forward model.
-
-    Parameters:
-        * D: 1D-array containing magnetization declination (0 to 360 degrees)
-        * I: 1D-array containing magnetization inclination (-90 to 90  degress)
[…]

### 2023-02-15 code/micromag.py
Refactor up to the blob detection method
Reused most of the code but optimized the implementation and used
xarray, verde, and the latest harmonica filters.

@@ -1,1187 +1,175 @@
+# Copyright (c) 2023 Gelson Ferreira de Souza-Junior, Leonardo Uieda.
+# Distributed under the terms of the MIT License.
+# SPDX-License-Identifier: MIT
+"""
+Functions for performing the processing and inversion of the microscopy data.
+"""
 import numpy as np
-import scipy as sp
-import matplotlib.pyplot as plt
-import math
-from skimage.feature import blob_log
-import mplstereonet as mpl
-import pandas as pd
+import xarray as xr
+import skimage.feature
+import numba
+import harmonica as hm
+import choclo
 
-microm2m = 1.0E-6
-m2microm = 1.0E6
 
-def random_normal_seeded(mean_value, std_dev, size, seed_value=0):
+TESLA_TO_NANOTESLA = 1e9
+MICROMETER_TO_METER = 1e-6
 
+
+def cartesian_vector(inclination, declination, amplitude):
     """
-    Generates pseudo-random normal gaussian distribution, but the seed
-    gives more controllable results.
+    Generate a 3-component vector from inclination, declination, and amplitude
 
-    Parameters:
-        * mean_value: float number, corresponds to the mean of the normal distribution
-        * std_dev: float number, corresponds to the standart deviation of the normal distribution
-        * size: scalar number, corresponds to the size of the distribution array
-        * seed_value: float number, it is the seed for the distribution
+    Inclination is positive downwards and declination is the angle with the x
+    component. The vector has x, y, and z (downward) Cartesian components.
+
+    Parameters
+    ----------
+    inclination : float or array
+        The inclination values in degrees.
+    declination : float or array
+        The declination values in degrees.
+    amplitude : float or array
+        The vector amplitude values.
+
+    Returns
+    -------
+    x, y, z : floats or arrays
+        The calculated x, y, z vector components.
     """
-    
-    np.random.seed(seed_value)
-    normal_Gaussian_distribution = np.random.normal(mean_value, std_dev, size)
-    
-    return(normal_Gaussian_distribution)
+    inclination = np.radians(inclination)
+    declination = np.radians(declination)
+    amplitude = np.asarray(amplitude)
[…]

### 2023-02-15 code/micromag.py
Swap the coordinate system for z upward
Makes everything compatible with Fatiando and much easier to use Verde
and Harmonica without making mistakes.

@@ -20,8 +20,8 @@ def cartesian_vector(inclination, declination, amplitude):
     """
     Generate a 3-component vector from inclination, declination, and amplitude
 
-    Inclination is positive downwards and declination is the angle with the x
-    component. The vector has x, y, and z (downward) Cartesian components.
+    Inclination is positive downwards and declination is the angle with the y
+    component. The vector has x, y, and z (upward) Cartesian components.
 
     Parameters
     ----------
@@ -40,19 +40,19 @@ def cartesian_vector(inclination, declination, amplitude):
     inclination = np.radians(inclination)
     declination = np.radians(declination)
     amplitude = np.asarray(amplitude)
-    cos_inc = np.cos(inclination)
-    sin_inc = np.sqrt(1 - cos_inc**2)
+    sin_inc = np.sin(-inclination)
+    cos_inc = np.cos(-inclination)
+    sin_dec = np.sin(declination)
     cos_dec = np.cos(declination)
-    sin_dec = np.sqrt(1 - cos_dec**2)
-    y = cos_inc * sin_dec * amplitude
-    x = cos_inc * cos_dec * amplitude
+    x = cos_inc * sin_dec * amplitude
+    y = cos_inc * cos_dec * amplitude
     z = sin_inc * amplitude
     return x, y, z
 
 
 def dipole_bz(coordinates, dipole_coordinates, dipole_moments):
     """
-    Calculate the z component (downward) of the magnetic field of dipoles
+    Calculate the z component (upward) of the magnetic field of dipoles
 
     Units:
 
@@ -76,7 +76,7 @@ def dipole_bz(coordinates, dipole_coordinates, dipole_moments):
     Returns
     -------
     bz : array
-        The calculated bz (positive downward) in nT. The array will have the
+        The calculated bz (positive upward) in nT. The array will have the
         same shape as the input coordinate arrays.
     """
     # Save the data coordinate shape so we can reshape the bz afterwards
@@ -92,7 +92,7 @@ def dipole_bz(coordinates, dipole_coordinates, dipole_moments):
         dipole_moments = np.array([dipole_moments])
     # Initialize and allocate the output array for bz
     bz = np.zeros(coordinates[0].shape)
-    _dipole_bz_fast(
+    _dipole_bu_fast(
         coordinates[0],
         coordinates[1],
         coordinates[2],
[…]

### 2023-02-15 code/micromag.py
Move the euler code to the python module

@@ -9,6 +9,7 @@ import xarray as xr
 import skimage.feature
 import numba
 import harmonica as hm
+import verde as vd
 import choclo
 
 
@@ -157,6 +158,7 @@ def data_gradients(data):
 
 def detect_anomalies(data, size_range, size_increment=2, nsizes=10, threshold=0.5, overlap=0.5):
     """
+    Run the blob detection and produce bounding boxes in data coordinates
     """
     min_sigma, max_sigma = [0.5 * i for i in size_range]
     spacing = np.mean([np.abs(data.x[1] - data.x[0]), np.abs(data.y[1] - data.y[0])])
@@ -175,3 +177,31 @@ def detect_anomalies(data, size_range, size_increment=2, nsizes=10, threshold=0.
         for size, x, y in zip(blob_sizes, *blob_coords)
     ]
     return windows
+
+
+def euler_deconvolution(data, x_deriv, y_deriv, z_deriv):
+    """
+    Estimate the (x, y, z) position and base level by Euler Deconvolution
+    """
+    si = 3
+    grids = xr.Dataset(
+        dict(field=data, x_deriv=x_deriv, y_deriv=y_deriv, z_deriv=z_deriv)
+    )
+    table = vd.grid_to_table(grids)
+    # Verde drops non-dimension coordinates so we have to add z back.
+    # This is a bug in Verde.
+    table["z"] = grids.z.values.ravel()
+    n_data = table.shape[0]
+    G = np.empty((n_data, 4))
+    G[:, 0] = table.x_deriv
+    G[:, 1] = table.y_deriv
+    G[:, 2] = table.z_deriv
+    G[:, 3] = si
+    h = (
+        table.x * table.x_deriv
+        + table.y * table.y_deriv
+        + table.z * table.z_deriv
+        + si * table.field
+    )
+    p = np.linalg.solve(G.T @ G, G.T @ h)
+    return p[:3], p[3]

### 2023-02-16 code/micromag.py
Implement the inversion and uncertainty propagation
Make some figures for the paper as well. Just missing the table output
revision for the manuscript.

@@ -17,7 +17,16 @@ TESLA_TO_NANOTESLA = 1e9
 MICROMETER_TO_METER = 1e-6
 
 
-def cartesian_vector(inclination, declination, amplitude):
+def gaussian_noise(error, shape, seed=None):
+    """
+    Generate a pseudo-random noise array of the given shape.
+    """
+    rng = np.random.default_rng(seed)
+    noise = rng.normal(loc=0, scale=error, size=shape)
+    return noise
+
+
+def angles_to_vector(inclination, declination, amplitude):
     """
     Generate a 3-component vector from inclination, declination, and amplitude
 
@@ -35,8 +44,10 @@ def cartesian_vector(inclination, declination, amplitude):
 
     Returns
     -------
-    x, y, z : floats or arrays
-        The calculated x, y, z vector components.
+    vector : 1D or 2D array
+        The calculated x, y, z vector components. 1D if it's a single vector.
+        If N vectors are calculated, the "vector" will have shape (N, 3) with
+        each vector in a row of the array.
     """
     inclination = np.radians(inclination)
     declination = np.radians(declination)
@@ -48,7 +59,40 @@ def cartesian_vector(inclination, declination, amplitude):
     x = cos_inc * sin_dec * amplitude
     y = cos_inc * cos_dec * amplitude
     z = sin_inc * amplitude
-    return x, y, z
+    return np.transpose([x, y, z])
+
+
+def vector_to_angles(vector):
+    """
+    Generate inclination, declination, and amplitude from a 3-component vector
+
+    Inclination is positive downwards and declination is the angle with the y
+    component. The vector has x, y, and z (upward) Cartesian components.
+
+    Parameters
+    ----------
+    vector : 1D or 2D array
+        The x, y, z vector components. Can be a 1D array for a single vector
+        or 2D for multiple. If 2D, then each vector should be a row of the
+        array.
+
+    Returns
+    -------
+    inclination : float or array
+        The inclination values in degrees.
+    declination : float or array
+        The declination values in degrees.
+    amplitude : float or array
+        The vector amplitude values.
+    """
+    vector = np.asarray(vector)
+    # if vector.ndim == 1:
+        # vector = np.array([vector])
+    x, y, z = vector.T
[…]

### 2023-02-16 code/micromag.py
Minor tweaks to the code and notebook

@@ -86,8 +86,6 @@ def vector_to_angles(vector):
         The vector amplitude values.
     """
     vector = np.asarray(vector)
-    # if vector.ndim == 1:
-        # vector = np.array([vector])
     x, y, z = vector.T
     amplitude = np.sqrt(x**2 + y**2 + z**2)
     inclination = -np.degrees(np.arctan2(z, np.hypot(x, y)))
@@ -218,9 +216,9 @@ def dipole_moment_inversion(data, dipole_coordinates):
     residuals = d - A @ dipole_moment
     residuals_sum_sq = np.sum(residuals**2)
     # Estimate of the true error variance (since we'll never know it)
-    chi_squared =  residuals_sum_sq / (n_data - n_params)
+    chi_squared = residuals_sum_sq / (n_data - n_params)
     covariance = chi_squared * np.linalg.inv(hessian)
-    r2 = 1 - residuals_sum_sq / np.linalg.norm(d - d.mean())**2
+    r2 = 1 - residuals_sum_sq / np.linalg.norm(d - d.mean()) ** 2
 
     return dipole_moment, covariance, r2
 
@@ -234,7 +232,12 @@ def _dipole_jacobian_fast(e, n, u, de, dn, du, jacobian):
     for i in numba.prange(e.size):
         # Calculating the distance only once saves a lot of computation time
         distance = choclo.utils.distance_cartesian(
-            e[i], n[i], u[i], de, dn, du,
+            e[i],
+            n[i],
+            u[i],
+            de,
+            dn,
+            du,
         )
         # These are the second derivatives of 1/r
         jacobian[i, 0] = constant * choclo.point.kernel_eu(
@@ -275,11 +278,11 @@ def covariance_to_angle_std(dipole_moment, covariance):
     var_x, var_y, var_z = np.diag(covariance)
     sigma_inc = np.degrees(
         np.sqrt(
-            (mx2 * mz2 * var_x + my2 * mz2 * var_y + (mx2 + my2)**2 * var_z)
+            (mx2 * mz2 * var_x + my2 * mz2 * var_y + (mx2 + my2) ** 2 * var_z)
             / ((mx2 + my2) * m**4)
         )
     )
-    sigma_dec = np.degrees(np.sqrt((my2 * var_x + mx2 * var_y) / (mx2 + my2)**2))
+    sigma_dec = np.degrees(np.sqrt((my2 * var_x + mx2 * var_y) / (mx2 + my2) ** 2))
[…]

### 2023-02-16 paper/content.tex
Start moving the paper latex back to this repository

\section{Introduction}

Several branches of Earth Sciences have demonstrated the importance of the
``spatiality" of the data on a microscopic scale, mainly in geochemistry and
geochronology applications where it is possible to perform punctual analysis
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
in analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
{\textasciitilde}10 cm³ would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below 1 µm, to large ($\gg 1$ µm) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of stepwise thermal and magnetic treatments are
needed to unveil the more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of performing magnetic maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
to recover from the magnetic images a large amount of individual magnetic
moments, corresponding to at least tens of thousands of stable fine-grained
grains (\textless1 µm), in order to provide statistical significance to the
remanence vector \citep[e.g.][]{Berndt2016}. Nowadays, with the development of
magnetic microscopy techniques, this task is no longer limited by the
resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
ambiguity in the inversion of potential field data \citep{Barbosa2011,
DeGroot2021, Oliveira2015Estimation}, and ultimately by the lack of a fast and
automated way to recover such a large number of individual magnetic moments
from a set of magnetic images \citep{CortesOrtuno2022, Lima2013, Lima2009}. A
solution to the non-uniqueness of magnetic moment inversion is to add
independent a priori information, such as the position of the ferromagnetic
particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
computed tomography \citep[microCT; ][]{Fabian2019, DeGroot2021, DeGroot2018}.
Nonetheless, the standard microCT techniques do not provide adequate resolution
to resolve the finer and more stable magnetic grains \citep{CortesOrtuno2022,
DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
too time-consuming to be routinely used in paleomagnetic studies.

Another route to be explored in the inversion of magnetic microscopy images is
to obtain all the information, i.e. the magnetic moment and the position of the
sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
explore the techniques developed in exploration geophysics, in spite of the
differences between aeromagnetic surveys and magnetic microscopy
\citep{Lima2013}. Magnetic microscopy images commonly show the combined signal
of multiple magnetic particles and can vary greatly in wavelength, strength,
and spatial separation, depending on the NRM and location of each particle. We
usually assume that the signal measured by the magnetic microscope is the
vertical component of the magnetic induction vector ($b_z$), the measurements
are performed on a regular grid with evenly spaced grid points and at a
constant height, and the data are contaminated with random Gaussian noise and
long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
we provide a methodological routine to retrieve the individual magnetic moment
of ferromagnetic grains in magnetic microscopy images following the approach
devised by \citet{Oliveira2015Estimation} for the interpretation of
aeromagnetic anomalies. The method we propose allows one to quickly and
semi-automatically estimate the individual magnetic moment vector of the stable
magnetic carriers, making use of only the magnetic images themselves and an
assumption of approximately dipolar sources. If used on a large scale, the
method provides the means to scan large areas of the rock sample, attaining
potentially the number of magnetic moments necessary for paleomagnetic studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

We will achieve the goal of estimating the dipole moment of several individual
grains per image in a semi-automatic fashion by dividing the task into three
parts that can be performed independently:

\begin{enumerate}
\item \textbf{Source detection and separation:} Identify and spatially isolate
  the magnetic field caused by each source. We will do this through a
  combination of classic potential field data processing (\textit{total
  gradient amplitude}) and image processing (histogram stretching and
  equalization) and segmentation methods (watershed segmentation).
\item \textbf{Position estimation}: Estimate the 3D position of a magnetic
  particle based on the magnetic field measurements and the assumption of a
  dipolar source. This can be achieved by applying the Euler Deconvolution
  method to the data segment identified in step 1.
\item \textbf{Magnetic moment inversion:} Estimate the 3-component dipole
  moment vector by inverting the magnetic field data using the position
  obtained from Euler Deconvolution as a constraint and the assumption of a
  dipolar source. This leads to a linear inverse problem that is stable and
  computationally efficient, particularly since the inversion is performed
  separately for each data segment identified in step 1.
\end{enumerate}

In the sections below, we describe the methodology used in each step of our
proposed workflow.

\subsection{Automatic source detection and separation}

Our first task is to automatically identify the signal of individual particles
and spatially segregate the data into windows, each containing the signal of a
single particle. We implemented the following workflow to achieve this:

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA)
  \citep{Roest1992Magnetic} of the observed vertical component of the magnetic
  field. The TGA is entirely positive and tends to be more concentrated on top
  of the magnetic field sources than the observed magnetic field. The
  derivative calculation also acts as a high-pass filter, removing
  long-wavelength noise from the data.
\item Apply a contrast stretching method to rescale the TGA to a new range
  defined by the lower and upper percentiles of the data in order to highlight
  the weaker signals, either coming from small or from deep-seated particles.
\item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
  rescaled TGA data to estimate the position and size of data windows
  containing the signal of each particle.
\end{enumerate}

The total gradient amplitude (TGA) was devised as a filter that can be applied
to aeromagnetic data to reduce the signal's dependence on the direction of
magnetization of the source and that concentrates the signal above the sources
\citep{Roest1992Magnetic, Nabighian2005}. The TGA is defined as the norm of the
gradient vector of a scalar field $f(x, y, z)$

\begin{equation}
\label{FeY0gwnRIU}
\|\vec{\mathbf{\nabla}}f(x, y, z)\|  = \sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}\ ,
\end{equation}

in which $\partial_x f$ is the partial derivative of $f$ with respect to $x$
and likewise for the $y$ and $z$ directions. The partial derivatives are best
approximated using a second-order accurate central finite-difference scheme

\begin{equation}
\label{DEJCQQSFoD}
\partial_x f(x, y, z) \approx \dfrac{f(x + \Delta x, y, z) - f(x - \Delta x, y, z)}{2 \Delta x} \ ,
\end{equation}

and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
component, $\Delta z$ is a small value (here set to $0.1\ \mu m$ by
trail-and-error) and $f(x, y, z + \Delta z)$ and $f(x, y, z - \Delta z)$ are
calculated by upward and downward continuation, respectively, performed in the
wavenumber domain. The 2D maps of the $x$, $y$, and $z$ derivates will also be
used in the Euler Deconvolution step described below, which is known to be
highly sensitive to noise in the derivatives \citep{Saleh2012Applying}. This is
why e prefer the finite-differences based derivatives, which are less prone to
amplifying short-wavelength noise than those calculated in the wavenumber
domain through the Fast Fourier Transform (FFT).

Once we have obtained a TGA image, we apply a contrast stretching method to
rescale the TGA values in order to highlight the weaker signals present in the
image. This is a necessary step to make sure that the blob detection algorithm
is able to identify particles causing both weak and strong signals. The
following contrast stretching operation is performed per pixel of the TGA image

\begin{equation}
\label{mQIpUM2TkF}
\text{TGA}_{rescaled} = 2\left(\dfrac{\text{TGA} - v_{min}}{v_{max} - v_{min}}\right) - 1 \ ,
\end{equation}

in which $v_{min}$ and $v_{max}$ are the upper and lower bounds of TGA values
that will be stretched to the range $[ -1, 1]$. By experimentation, we found
that values of $v_{min} = 1^\text{st}$ and $v_{max} = 99^\text{th}$
percentiles of the TGA range work well on real magnetic microscopy datasets.

The rescaled TGA image is then used as input for a Laplacian of Gaussian (LoG)
blob detection algorithm \citep{Kong2013}. This method is able to identify the
location and size of multiple windows in the image containing ``blobs''. In our
case, the blobs are the rescaled TGA field of each particle and the LoG method
detects the local TGA maxima. The LoG method is particularly well suited for
the detection of bright blobs on a dark background at the expense of a longer
computation time \citep{Han2016}. For the image sizes routinely found in
magnetic microscopy, the computation is fast and only needs to be performed
once per image.

\subsection{Euler Deconvolution}

Once the locations and sizes of the windows containing the isolated signals of
each particle are determined, we can apply the Euler Deconvolution (ED)
estimate of the $x$, $y$, and $z$ positions of the center of the particles
under a dipolar approximation. This technique was first proposed by
\citet{Thompson1982} under the name EULDPH and later extended to three
dimensions and renamed ``Euler Deconvolution'' by \citet{Reid1990}. ED is
traditionally performed on a set of moving windows that scan the entire
dataset, producing a large scatter of position estimates, most of which are
spurious \citep{Silva20033D}. This is only done because it is impractical to
segment an aeromagnetic dataset into individual anomalies. Fortunately,
magnetic microscopy images contain fewer elongated features (e.g., dikes and
suture zones) and regional signals (e.g., Curie depth variations) that are
difficult to separate. This makes it possible for us to produce isolated
signals for each magnetic particle through the source detection step described
above. Since each data window contains only the signal of a single particle, we
are able to apply ED and generate only a single position estimate per particle.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\linewidth]{figures/coordinate-system-sketch.png}
\caption{Caption needed.}
\label{yflpcyrggj}
\end{figure}

Euler Deconvolution is formulated as a least-squares inversion of Euler's
homogeneity equation

\begin{equation}
\label{I3VD2haX7z}
(x - x_c)\partial_x f
+ (y - y_c)\partial_y f
+ (z - z_c)\partial_z f
= (b - f)\eta
\ ,
\end{equation}

in which $(x_c, y_c, z_c)$ are the coordinates of the magnetic field source
(Figure~\ref{V1wGQXY2TA}), $b$ is the base level representing a constant shift
in the signal, and $\eta$ is the structural index corresponding to the nature
of the source \citep{Reid1990}. This equation holds true for simple geometric
sources, like spheres, dipoles, and vertical cylinders. Here, we assume that
the magnetic particles are small enough and the sensor is far enough away that
the sources can be represented by dipoles, yielding an $\eta=3$.

The inversion is performed by rearranging (\ref{I3VD2haX7z}) into a
pseudo-parametric model with parameters $x_c$, $y_c$, $z_c$, and $b$

\begin{equation}
\label{GXMwpUoOoH}
x_c \partial_x f + y_c \partial_x f + z_c \partial_x f + \eta b
=
x \partial_x f + y \partial_y f + z \partial_z f + \eta f
\ .
\end{equation}

Given a set of $N$ observations of the magnetic field as the harmonic function $f$ and its spatial derivatives, we can form the $N \times 4$ system of equations

\begin{equation}
\label{BoqTDcY8gR}
\begin{bmatrix}
{\partial_x f}_1 & {\partial_y f}_1 & {\partial_z f}_1 & \eta \\
{\partial_x f}_2 & {\partial_y f}_2 & {\partial_z f}_2 & \eta \\
\vdots & \vdots & \vdots & \vdots \\
{\partial_x f}_N & {\partial_y f}_N & {\partial_z f}_N & \eta
\end{bmatrix}
\begin{bmatrix}
x_c \\ y_c \\ z_c \\ b
\end{bmatrix}
=
\begin{bmatrix}
x_1 {\partial_x f}_1 + y_1 {\partial_y f}_1 + z_1 {\partial_z f}_1 + \eta f_1 \\
x_2 {\partial_x f}_2 + y_2 {\partial_y f}_2 + z_2 {\partial_z f}_2 + \eta f_2 \\
\vdots \\
x_N {\partial_x f}_N + y_N {\partial_y f}_N + z_N {\partial_z f}_N + \eta f_N \\
\end{bmatrix}
\ .
\end{equation}

In matrix notation, this linear system can be written as

\begin{equation}
\label{ef59ZPDbY0}
\mathbf{G} \mathbf{p} = \mathbf{h} \ .
\end{equation}

We can arrive at a solution to (\ref{ef59ZPDbY0}) by assuming that the three spatial derivatives of $f$ have negligible error and minimizing the misfit $\phi(\mathbf{p})$ between a pseudo-observation vector $\mathbf{h}^o$ and the predictions $\mathbf{h}$. The least-squares misfit $\phi(\mathbf{p})$ is defined as

\begin{equation}
\label{ZTSuSBbL16}
\phi(\mathbf{p}) = \|\mathbf{h}^o - \mathbf{h}\|^2 = (\mathbf{h}^o - \mathbf{G}\mathbf{p})^T (\mathbf{h}^o - \mathbf{G}\mathbf{p})\ .
\end{equation}

The minimum of $\phi(\mathbf{p})$ is obtained by solving the $4 \times 4$ system of normal equations

\begin{equation}
\mathbf{G}^T \mathbf{G} \mathbf{p} = \mathbf{G}^T \mathbf{h}^o\ .
\end{equation}

The solution vector $\hat{\mathbf{p}} = \begin{bmatrix}x_c & y_c & z_c & b \end{bmatrix}^T$ provides an estimate of the position and base level $b$ for the source located inside of a data window. Repeating this process for each window produced by the source detection algorithm will yield the horizontal locations and depths of each magnetic particle.

\subsection{Magnetic moment inversion}

Once the source position is known and we can assume that it is approximately spherical or dipolar, we can apply the method developed by \citet{Oliveira2015Estimation} to estimate the dipole moment vector $\mathbf{m}$ of the source. We begin by following \citet{Oliveira2015Estimation} in formulating the magnetic induction vector $\mathbf{b}$ of a dipole as

\begin{equation}
\label{D7jZ9mepI2}
\mathbf{b}
=
\begin{bmatrix}
b_x \\ b_y \\ b_z
\end{bmatrix}
= \dfrac{\mu_0}{4\pi}
\begin{bmatrix}
\dfrac{\partial^2}{\partial x \partial x} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial x \partial y} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial x \partial z} \dfrac{1}{r}
\\
\dfrac{\partial^2}{\partial y \partial x} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial y \partial y} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial y \partial z} \dfrac{1}{r}
\\
\dfrac{\partial^2}{\partial z \partial x} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial z \partial y} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial z \partial z} \dfrac{1}{r}
\end{bmatrix}
\begin{bmatrix}
m_x \\ m_y \\ m_z
\end{bmatrix}
= \dfrac{\mu_0}{4\pi} \mathbf{M}\,\mathbf{m}
\ ,
\end{equation}

in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian distance between the observation point $(x, y, z)$ and the source $(x_c, y_c, z_c)$ and $\mu_0$ is the vacuum magnetic permeability. Most magnetic microscopes provide measurements of only the vertical component $b_z$, which can be isolated from (\ref{D7jZ9mepI2}) as

\begin{equation}
\label{as4SGlTmGf}
b_z
= \dfrac{\mu_0}{4\pi}
\begin{bmatrix}
\dfrac{\partial^2}{\partial z \partial x} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial z \partial y} \dfrac{1}{r}
& \dfrac{\partial^2}{\partial z \partial z} \dfrac{1}{r}
\end{bmatrix}
\begin{bmatrix}
m_x \\ m_y \\ m_z
\end{bmatrix}
= \dfrac{\mu_0}{4\pi} \mathbf{M_z}\,\mathbf{m}
\ .
\end{equation}

The three second-order derivatives in (\ref{as4SGlTmGf}) are

\begin{equation}
\begin{align*}
\dfrac{\partial^2}{\partial z \partial x} \dfrac{1}{r} &=
\dfrac{3(z - z_c)(x - x_c)}{r^5}\ ,
\\
\dfrac{\partial^2}{\partial z \partial y} \dfrac{1}{r} &=
\dfrac{3(z - z_c)(y - y_c)}{r^5}\ ,
\\
\dfrac{\partial^2}{\partial z \partial z} \dfrac{1}{r} &=
\dfrac{3(z - z_c)^2}{r^5} - \dfrac{1}{r^3}\ .
\end{align*}
\end{equation}

Given a set of $N$ observations of $b_z$ made inside a window containing a single source, we can form the $N \times 3$linear equation system

\begin{equation}
\label{CgjOtKLQKT}
\begin{bmatrix}
\dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(x_1 - x_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(y_1 - y_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_1 - z_c)^2}{r_1^5} - \dfrac{1}{r_1^3}\right)
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(x_2 - x_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(y_2 - y_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_2 - z_c)^2}{r_2^5} - \dfrac{1}{r_2^3}\right)
\\
\vdots & \vdots & \vdots
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(x_N - x_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(y_N - y_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_N - z_c)^2}{r_N^5} - \dfrac{1}{r_N^3}\right)
\end{bmatrix}
\begin{bmatrix}
m_x \\ m_y \\ m_z
\end{bmatrix}
=
\begin{bmatrix}
{b_z}_1 \\ {b_z}_2 \\ \vdots \\ {b_z}_L
\end{bmatrix}
\ ,
\end{equation}

which can also be expressed in matrix form as

\begin{equation}
\label{qdhqM4s9Ln}
\mathbf{A} \mathbf{m} = \mathbf{d} \ .
\end{equation}

As with Euler Deconvolution, we can find a dipole moment vector that best fits a set of $N$ observations of the vertical component of the magnetic field $\mathbf{d}^o$ in a least-squares sense by minimizing the misfit function

\begin{equation}
\label{uV9pRVYO4l}
\Gamma (\mathbf{m}) = \| \mathbf{d}^o - \mathbf{d} \|^2 = (\mathbf{d}^o - \mathbf{A}\mathbf{m})^T  (\mathbf{d}^o - \mathbf{A}\mathbf{m})\ .
\end{equation}

The dipole moment vector that minimizes $\Gamma (\mathbf{m})$ can be found by solving the $3 \times 3$ normal equation system

\begin{equation}
\mathbf{A}^T \mathbf{A} \mathbf{m} = \mathbf{A}^T\mathbf{d}^o\ .
\end{equation}

The estimated dipole moment vector $\hat{\mathbf{m}} = \begin{bmatrix}m_x & m_y & m_z \end{bmatrix}^T$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so

\begin{equation}
\begin{align*}
D &= \tan^{-1}\left(\dfrac{m_y}{m_x}\right) \ , \\
I &= \tan^{-1}\left(\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}}\right) \ , \\
m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
\end{align*}
\end{equation}

It's important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system. To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of \ref{FNPcqF44iJ}.

\begin{equation}
\label{lPOQaqlV3N}
\mathbf{C} =
\begin{bmatrix}
\sigma_x^2 & \sigma_{xy} & \sigma_{xz} \\
\sigma_{yx} & \sigma_y^2 & \sigma_{yz} \\
\sigma_{zx} & \sigma_{zy} & \sigma_z^2
\end{bmatrix}
=
\sigma_0^2 (\mathbf{A}^T\mathbf{A})^{-1}
\end{equation}

From the main diagonal of $\mathbf{C}$ we can obtain the variances of the declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$ by propagation of uncertainties

\begin{equation}
\begin{align*}
\sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
\sigma_I^2 &= \dfrac{m_x^2 m_z^2 \sigma_x^2 + m_y^2 m_z^2 \sigma_y^2 + \left(m_x^2 + m_y^2\right)^2\sigma_z^2}{\left(m_x^2 + m_y^2\right) m^4} \ , \\
\sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
\end{align*}
\end{equation}

These variances reflect the sensitivity of the estimated dipole moment to random noise in the magnetic field observations. However, they do not capture other, often larger, sources of uncertainty like systematic errors in the observations, data positioning errors, and the validity of the dipolar approximation. Therefore, we recommend that these estimated variances be treated with caution and should not be interpreted as ``the degree of certainty that the estimated values are the true values''.

[FALAR SOBRE O CALCULO DE R2]

[INCLUIR A ESTIMATIVA DE NÃO-DIPOLARIDADE]

\section{Application to synthetic data}

\begin{table}[t]
  \begin{center}
    \small
  \input{simple-synthetic-results.tex}
  \end{center}
  \caption{Meh}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.

### 2023-02-17 paper/content.tex
Finish preprint style and more intro and methods fully

@@
 \citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
-{\textasciitilde}10 cm³ would contain hundreds of thousands
+approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
 to millions of magnetic particles with sizes varying from magnetically stable
 single-domain (SD) and vortex state grains (also called pseudo-single domain,
-PSD) with sizes below 1 µm, to large ($\gg 1$ µm) grains with
+PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
 multi-domain (MD) magnetic structures, which are less stable magnetic recorders
@@
 moments, corresponding to at least tens of thousands of stable fine-grained
-grains (\textless1 µm), in order to provide statistical significance to the
+grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
 remanence vector \citep[e.g.][]{Berndt2016}. Nowadays, with the development of
@@
 \begin{enumerate}
-\item Calculate the \textit{total gradient amplitude} (TGA)
-  \citep{Roest1992Magnetic} of the observed vertical component of the magnetic
-  field. The TGA is entirely positive and tends to be more concentrated on top
-  of the magnetic field sources than the observed magnetic field. The
-  derivative calculation also acts as a high-pass filter, removing
-  long-wavelength noise from the data.
+\item Calculate the \textit{total gradient amplitude} (TGA), also known as the
+  3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical
+  component of the magnetic field. The TGA is entirely positive and tends to be
+  more concentrated on top of the magnetic field sources than the observed
+  magnetic field. The derivative calculation also acts as a high-pass filter,
+  removing long-wavelength noise from the data.
 \item Apply a contrast stretching method to rescale the TGA to a new range
@@
 \begin{equation}
-\label{FeY0gwnRIU}
 \|\vec{\mathbf{\nabla}}f(x, y, z)\|  = \sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}\ ,
@@
 
+\noindent
 in which $\partial_x f$ is the partial derivative of $f$ with respect to $x$
@@
 \begin{equation}
-\label{DEJCQQSFoD}
 \partial_x f(x, y, z) \approx \dfrac{f(x + \Delta x, y, z) - f(x - \Delta x, y, z)}{2 \Delta x} \ ,
@@
 
+\noindent
 and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
 spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
-component, $\Delta z$ is a small value (here set to $0.1\ \mu m$ by
-trail-and-error) and $f(x, y, z + \Delta z)$ and $f(x, y, z - \Delta z)$ are
-calculated by upward and downward continuation, respectively, performed in the
-wavenumber domain. The 2D maps of the $x$, $y$, and $z$ derivates will also be
-used in the Euler Deconvolution step described below, which is known to be
-highly sensitive to noise in the derivatives \citep{Saleh2012Applying}. This is
-why e prefer the finite-differences based derivatives, which are less prone to
-amplifying short-wavelength noise than those calculated in the wavenumber
-domain through the Fast Fourier Transform (FFT).
+component, $\Delta z = \Delta x$ and $f(x, y, z + \Delta z)$ and
+$f(x, y, z - \Delta z)$ are calculated by upward and downward continuation,
+respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
+and $z$ derivates will also be used in the Euler Deconvolution step described
+below, which is known to be highly sensitive to noise in the derivatives
+\citep{Saleh2012Applying}. This is why e prefer the finite-differences based
+derivatives, which are less prone to amplifying short-wavelength noise than
+those calculated in the wavenumber domain through the Fast Fourier Transform
+(FFT).
 
@@
 \begin{equation}
-\label{mQIpUM2TkF}
 \text{TGA}_{rescaled} = 2\left(\dfrac{\text{TGA} - v_{min}}{v_{max} - v_{min}}\right) - 1 \ ,
@@
 
+\noindent
 in which $v_{min}$ and $v_{max}$ are the upper and lower bounds of TGA values
-that will be stretched to the range $[ -1, 1]$. By experimentation, we found
+that will be stretched to the range $[0, 1]$. By experimentation, we found
 that values of $v_{min} = 1^\text{st}$ and $v_{max} = 99^\text{th}$
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[t]
 \centering
-\includegraphics[width=1\linewidth]{figures/coordinate-system-sketch.png}
+\includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
 \caption{Caption needed.}
-\label{yflpcyrggj}
+\label{fig_coordinate_systems}
 \end{figure}
@@
 \begin{equation}
-\label{I3VD2haX7z}
+\label{eq_euler_homogeneity}
 (x - x_c)\partial_x f
@@
 
+\noindent
 in which $(x_c, y_c, z_c)$ are the coordinates of the magnetic field source
-(Figure~\ref{V1wGQXY2TA}), $b$ is the base level representing a constant shift
-in the signal, and $\eta$ is the structural index corresponding to the nature
-of the source \citep{Reid1990}. This equation holds true for simple geometric
-sources, like spheres, dipoles, and vertical cylinders. Here, we assume that
-the magnetic particles are small enough and the sensor is far enough away that
-the sources can be represented by dipoles, yielding an $\eta=3$.
+(Figure~\ref{fig_coordinate_systems}), $b$ is the base level representing a
+constant shift in the signal, and $\eta$ is the structural index corresponding
+to the nature of the source \citep{Reid1990}. This equation holds true for
+simple geometric sources, like spheres, dipoles, and vertical cylinders. Here,
+we assume that the magnetic particles are small enough and the sensor is far
+enough away that the sources can be represented by dipoles, yielding an
+$\eta=3$.
 
-The inversion is performed by rearranging (\ref{I3VD2haX7z}) into a
-pseudo-parametric model with parameters $x_c$, $y_c$, $z_c$, and $b$
+The inversion is performed by rearranging Equation~\ref{eq_euler_homogeneity}
+into a pseudo-parametric model with parameters $x_c$, $y_c$, $z_c$, and $b$
 
 \begin{equation}
-\label{GXMwpUoOoH}
 x_c \partial_x f + y_c \partial_x f + z_c \partial_x f + \eta b
@@
 
-Given a set of $N$ observations of the magnetic field as the harmonic function $f$ and its spatial derivatives, we can form the $N \times 4$ system of equations
+Given a set of $N$ observations of the magnetic field as the harmonic function
+$f$ and its spatial derivatives, we can form the $N \times 4$ system of
+equations
 
 \begin{equation}
-\label{BoqTDcY8gR}
 \begin{bmatrix}
@@
 \begin{equation}
-\label{ef59ZPDbY0}
+\label{eq_euler_forward}
 \mathbf{G} \mathbf{p} = \mathbf{h} \ .
@@
 
-We can arrive at a solution to (\ref{ef59ZPDbY0}) by assuming that the three spatial derivatives of $f$ have negligible error and minimizing the misfit $\phi(\mathbf{p})$ between a pseudo-observation vector $\mathbf{h}^o$ and the predictions $\mathbf{h}$.
-The least-squares misfit $\phi(\mathbf{p})$ is defined as
+We can arrive at a solution to Equation~\ref{eq_euler_forward} by assuming that
+the three spatial derivatives of $f$ have negligible error and minimizing the
+misfit $\phi(\mathbf{p})$ between a pseudo-observation vector $\mathbf{h}^o$
+and the predictions $\mathbf{h}$. The least-squares misfit $\phi(\mathbf{p})$
+is defined as
 
@@
 
-The minimum of $\phi(\mathbf{p})$ is obtained by solving the $4 \times 4$ system of normal equations
+The minimum of $\phi(\mathbf{p})$ is obtained by solving the $4 \times 4$
+system of normal equations
 
@@
 
-The solution vector $\hat{\mathbf{p}} = \begin{bmatrix}x_c & y_c & z_c & b \end{bmatrix}^T$ provides an estimate of the position and base level $b$ for the source located inside of a data window.
-Repeating this process for each window produced by the source detection algorithm will yield the horizontal locations and depths of each magnetic particle.
+The solution vector $\hat{\mathbf{p}}$ provides an estimate of the position
+$(x_c, y_c, z_c)$ and base level $b$ for the source located inside of a data
+window. Repeating this process for each window produced by the source detection
+algorithm will yield the horizontal locations and depths of each magnetic
+particle.
 
@@
 
-Once the source position is known and we can assume that it is approximately spherical or dipolar, we can apply the method developed by \citet{Oliveira2015Estimation} to estimate the dipole moment vector $\mathbf{m}$ of the source.
-We begin by following \citet{Oliveira2015Estimation} in formulating the magnetic induction vector $\mathbf{b}$ of a dipole as
+Once the source position is known and we can assume that it is approximately
+spherical or dipolar, we can apply the method developed by
+\citet{Oliveira2015Estimation} to estimate the dipole moment vector
+$\mathbf{m}$ of the source. We begin by following
+\citet{Oliveira2015Estimation} in formulating the magnetic induction vector
+$\mathbf{b}$ of a dipole as
 
 \begin{equation}
-\label{D7jZ9mepI2}
+\label{eq_vector_dipole_field}
 \mathbf{b}
@@
 
-in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian distance between the observation point $(x, y, z)$ and the source $(x_c, y_c, z_c)$ and $\mu_0$ is the vacuum magnetic permeability.
-Most magnetic microscopes provide measurements of only the vertical component $b_z$, which can be isolated from (\ref{D7jZ9mepI2}) as
+\noindent
+in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian
+distance between the observation point $(x, y, z)$ and the source $(x_c, y_c,
+z_c)$ and $\mu_0$ is the vacuum magnetic permeability. Most magnetic
+microscopes provide measurements of only the vertical component $b_z$, which
+can be isolated from Equation~\ref{eq_vector_dipole_field} as
 
 \begin{equation}
-\label{as4SGlTmGf}
+\label{eq_dipole_bz}
 b_z
@@
 
-The three second-order derivatives in (\ref{as4SGlTmGf}) are
+The three second-order derivatives in Equation~\ref{eq_dipole_bz} are
 
 \begin{equation}
-\begin{align*}
+\begin{aligned}
 \dfrac{\partial^2}{\partial z \partial x} \dfrac{1}{r} &=
@@
 \dfrac{3(z - z_c)^2}{r^5} - \dfrac{1}{r^3}\ .
-\end{align*}
+\end{aligned}
 \end{equation}
 
-Given a set of $N$ observations of $b_z$ made inside a window containing a single source, we can form the $N \times 3$linear equation system
+Given a set of $N$ observations of $b_z$ made inside a window containing a
+single source, we can form the $N \times 3$ linear equation system
 
@@
 
+\noindent
 which can also be expressed in matrix form as
@@
 
-As with Euler Deconvolution, we can find a dipole moment vector that best fits a set of $N$ observations of the vertical component of the magnetic field $\mathbf{d}^o$ in a least-squares sense by minimizing the misfit function
+As with Euler Deconvolution, we can find a dipole moment vector that best fits
+a set of $N$ observations of the vertical component of the magnetic field
+$\mathbf{d}^o$ in a least-squares sense by minimizing the misfit function
 
@@
 
-The dipole moment vector that minimizes $\Gamma (\mathbf{m})$ can be found by solving the $3 \times 3$ normal equation system
+\noindent
+The dipole moment vector that minimizes $\Gamma (\mathbf{m})$ can be found by
+solving the $3 \times 3$ normal equation system
 
@@
 
-The estimated dipole moment vector $\hat{\mathbf{m}} = \begin{bmatrix}m_x & m_y & m_z \end{bmatrix}^T$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so
+\noindent
+The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into
+declination $D$, inclination $I$, and magnitude $m$, which are more intuitive
+quantities for interpreting paleomagnetic results, like so
 
 \begin{equation}
-\begin{align*}
-D &= \tan^{-1}\left(\dfrac{m_y}{m_x}\right) \ , \\
+  \label{eq_vector_to_incdec}
+\begin{aligned}
 I &= \tan^{-1}\left(\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}}\right) \ , \\
+D &= \tan^{-1}\left(\dfrac{m_x}{m_y}\right) \ , \\
 m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
-\end{align*}
+\end{aligned}
 \end{equation}
 
-It's important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system.
-To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of \ref{FNPcqF44iJ}.
+It's important to note that these are not paleomagnetic declination and
+inclination angles, but are instead related to the sample coordinate system. To
+obtain the paleomagnetic direction, the dipole moment vector must be rotated to
+the sample field orientation prior to the application of
+Equation~\ref{eq_vector_to_incdec}.
+
+MISSING PARAGRAPH ABOUT THE COVARIANCE ESTIMATION AND $\sigma_0$.
 
@@
 
-From the main diagonal of $\mathbf{C}$ we can obtain the variances of the declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$ by propagation of uncertainties
+From the main diagonal of $\mathbf{C}$ we can obtain the variances of the
+declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
+by propagation of uncertainties
 
 \begin{equation}
-\begin{align*}
+\begin{aligned}
 \sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
@@
 \sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
-\end{align*}
+\end{aligned}
 \end{equation}
 
-These variances reflect the sensitivity of the estimated dipole moment to random noise in the magnetic field observations.
-However, they do not capture other, often larger, sources of uncertainty like systematic errors in the observations, data positioning errors, and the validity of the dipolar approximation.
-Therefore, we recommend that these estimated variances be treated with caution and should not be interpreted as ``the degree of certainty that the estimated values are the true values''.
+\noindent
+These variances reflect the sensitivity of the estimated dipole moment to
+random noise in the magnetic field observations. However, they do not capture
+other, often larger, sources of uncertainty like systematic errors in the
+observations, data positioning errors, and the validity of the dipolar
+approximation. Therefore, we recommend that these estimated variances be
+treated with caution and should not be interpreted as ``the degree of certainty
+that the estimated values are the true values''.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Application to synthetic data}
+
+We first applied our inversion workflow to synthetic data to evaluate its
+strengths and limitations. The first set of synthetic data is simple and
+intended to test the method's performance under ideal circumstances. The second
+set is more complex, with a greater number of magnetic particles and
+long-wavelength noise, and is intended to demonstrate the capabilities and
+limitations of the method under real-world scenarios.
+
+The first synthetic model was performed by generating the vertical magnetic
+field derived from a simple set of four spheres with similar magnetization
+intensity and radius, but completely different magnetization directions,
+contaminated by high-frequency noise. This simplified test model is basically
+done to investigate the efficiency of the inversions used for Euler positioning
+and magnetization parameters, thus being a validation of the methodology.
+
+The second model contains one hundred spheres with different radii and
+magnetization intensities but magnetized in a similar direction within one
+standard deviation. The magnetic field generated from these sources is
+corrupted by both low and high-frequency noise. The complexity of this
+synthetic data seeks to more faithfully emulate real magnetic microscopy data.
+
+\subsection{Simple simulation: Validating the methodology}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
+\caption{
+  a) Synthetic data contaminated with psedo-random normal noise. b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
+}
+\label{fig_synthetic_simple_data}
+\end{figure}
+
+Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field
+$b_z$ over a synthetic rock section containing four uniformly magnetized
+spherical sources. The map covers a surface of $\qty{1000}{\um} \times
+\qty{1000}{\um}$ with
+data points in a regular grid of \qty{1}{\um} ($N = 10^6$ observations)
+obtained at a sensor-sample distance of \qty{5}{\um}. The magnetic field data is
+contaminated with a pseudo-random noise of normal Gaussian distribution with a
+zero mean and \qty{20}{\nano\tesla} standard deviation.
+
+We first applied an upward continuation filter to smooth out high-frequency
+noise \citep{Blakely1996}, since it strongly affects the first derivatives of
+the potential field required by the Euler equation. Then, we calculated the
+magnetic total gradient (or horizontal gradient) filter and applied the blob
+detection algorithm to the total gradient map to obtain the position of the
+data window for each source (Figure~\ref{fig_coordinate_systems}b). The ED was
+run for each selected source by assuming the structural index of a
+sphere/punctual source, therefore obtaining the Cartesian coordinates of each
+source causing the magnetic potential anomaly in the observed data set (Table
+1).
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
+\caption{
+  CAPTION NEEDED
+}
+\label{fig_synthetic_simple_results}
+\end{figure}
+
+The central positions of each source obtained with ED were used as an input
+parameter for inverting the vertical magnetic field. The inversion produced a
+least squares (or robust) approximation solution for the vector of Cartesian
+magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions
+(D and I) and intensity of magnetic moment $m$. We also obtained the
+uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
+and considering $\sigma$ = 15 nT.\\
 
@@
 
+\citet{Oliveira2015Estimation} proved that the magnetization directions (D and
+I) recovered by the least squares estimator are sensitive to variations in the
+horizontal coordinates of the center of the magnetic sources, but are
+practically insensitive to variations in depth. Thus, they consider the Euler
+deconvolution method as an adequate technique to estimate the central positions
+that will be used as a priori information for inversion. This occurs mainly
+because, when well performed, the recovery of the horizontal coordinates of the
+source central position is considerably accurate, while the vertical coordinate
+can undergo greater variation even though it still provides satisfactory
+results \citep{Silva20033D, Melo2013}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Acknowledgements}

### 2023-02-17 paper/content.tex
Fix some typos (from overleaf)

@@
 \citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
-and PSD grains, and techniques of stepwise thermal and magnetic treatments are
+and PSD grains, and techniques of step-wise thermal and magnetic treatments are
 needed to unveil the more stable and reliable magnetic record
@@
 grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
-remanence vector \citep[e.g.][]{Berndt2016}. Nowadays, with the development of
+remanence vector \citep[e.g., ][]{Berndt2016}. Nowadays, with the development of
 magnetic microscopy techniques, this task is no longer limited by the
@@
 solution to the non-uniqueness of magnetic moment inversion is to add
-independent a priori information, such as the position of the ferromagnetic
+independent prior information, such as the position of the ferromagnetic
 particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
@@
   removing long-wavelength noise from the data.
-\item Apply a contrast stretching method to rescale the TGA to a new range
+\item Apply a contrast stretching method to re-scale the TGA to a new range
   defined by the lower and upper percentiles of the data in order to highlight
@@
 \item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
-  rescaled TGA data to estimate the position and size of data windows
+  re-scaled TGA data to estimate the position and size of data windows
   containing the signal of each particle.
@@
 respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
-and $z$ derivates will also be used in the Euler Deconvolution step described
+and $z$ derivatives will also be used in the Euler Deconvolution step described
 below, which is known to be highly sensitive to noise in the derivatives
@@
 Once we have obtained a TGA image, we apply a contrast stretching method to
-rescale the TGA values in order to highlight the weaker signals present in the
+re-scale the TGA values in order to highlight the weaker signals present in the
 image. This is a necessary step to make sure that the blob detection algorithm
@@
 
-The rescaled TGA image is then used as input for a Laplacian of Gaussian (LoG)
+The re-scaled TGA image is then used as input for a Laplacian of Gaussian (LoG)
 blob detection algorithm \citep{Kong2013}. This method is able to identify the
 location and size of multiple windows in the image containing ``blobs''. In our
-case, the blobs are the rescaled TGA field of each particle and the LoG method
+case, the blobs are the re-scaled TGA field of each particle and the LoG method
 detects the local TGA maxima. The LoG method is particularly well suited for
@@
 
-\begin{figure}[tbp]
+\begin{figure}[!t]
 \centering
@@
 uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
-and considering $\sigma$ = 15 nT.\\
+and considering $\sigma = \qty{15}{\nano\tesla}$.
 
@@
   \caption{Meh}
+  \label{tab_synthetic_simple_results}
 \end{table}
@@
 deconvolution method as an adequate technique to estimate the central positions
-that will be used as a priori information for inversion. This occurs mainly
+that will be used as prior information for inversion. This occurs mainly
 because, when well performed, the recovery of the horizontal coordinates of the

### 2023-02-20 paper/content.tex
Finish adding the full paper text to the repository

@@
 
+\subsection{Complex simulation: Testing applicability}
+
+This test represents a more complex scenario by simulating 100 sources randomly
+distributed in the imaged area of a synthetic thin section of 2000 x 1400 $\mu
+m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$
+spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real
+samples, the magnetic sources are modeled as spheres with different depths,
+radii, and magnetizations. The depths vary between 1 and 19 $\mu m$, while the
+radii range from 0.01 to 0.95 $\mu m$. The magnetizations of the sources have
+declination and inclination directions sampled from a pseudo-random Gaussian
+distribution with a mean of D, I = 45°, 45°, and a standard deviation of 8°.
+This randomness simulates the NRM found in real ferromagnetic particles that
+vary individually but average out to the inducing field direction. Finally, we
+contaminated the data with high-frequency normally-distributed pseudo-random
+noise with zero means and 5 nT standard deviations, as well as with
+low-frequency noise in the form of additional deep sources beyond the modeling
+domain. The noise-corrupted synthetic $b_z$ image is shown in
+Figure~\ref{E9td9j9aBB}a.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
+\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise.
+b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
+\label{e9td9j9abb}
+\end{figure}
+
+The result of the source detection method is shown in Figure~\ref{E9td9j9aBB}b,
+where 84 particles out of the original 100 were detected. The spatiality of the
+inversion results is one of the key advantages of magnetic microscopy over the
+classic techniques of paleomagnetism. Therefore, we present the inversion
+results spatially so that we can evaluate any patterns in their distribution.
+
+Figure~\ref{P8gMJ9mWpS} shows the difference between the estimated dipole
+moments and the true values for each of the 84 particles that were identified.
+Figure~\ref{P8gMJ9mWpS}c shows the R² coefficient of determination representing
+how well the dipolar model is able to fit the observed data in the given
+window. The depth and radius of each particle are represented by horizontal and
+vertical cross bars, respectively. The depth and radius are useful proxies for
+the width and amplitude of the magnetic signal of each particle, which is
+crucial to know when evaluating the inversion results.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\linewidth]{figures/ComplexComparison.png}
+\caption{
+The validation of the result obtained with the inversion was calculated for
+each individual particle based on the error between the real parameters modeled
+and their respective recovered values, being (a) the direction and (b)
+intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
+by comparing the forward model and the actual data. The depth and radius of the
+magnetic sources are also important factors that influence the final result,
+therefore, these data are given in the form of cross plots, with the vertical
+bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
+radius (0.01 - 0.95 $\\mu m$).
+}
+\label{p8gmj9mwps}
+\end{figure}
+
+The application in complex synthetic data allows observing the strengths and
+limitations of the proposed methodology. Some of the strengths that can be
+mentioned are: (i) the applied technique not only detects most of the modeled
+sources but also (ii) most of the recovered magnetic parameters have
+considerably low errors, especially in the directions, usually less than 5°
+(Figure~\ref{P8gMJ9mWpS}a). (iii) The magnetic moments obtained also tend to
+not deviate much from the real values (Figure~\ref{P8gMJ9mWpS}b) when
+R\textsuperscript{2} scores are high (\textgreater 0.95)
+(Figure~\ref{P8gMJ9mWpS}c). (iv) Shallow particles grouped in clusters are
+usually well individualized during window selection, as well as (v) some
+particles that produce a weak magnetic signal but isolated particles.
+
+The main limitations observed are: (i) the blob detection fails when there are
+sources too close, grouping them into the same window, thus causing an
+erroneous result both for Euler deconvolution and for the magnetic parameters.
+(ii) The very same occurs when there is a source under another, in this case,
+the magnetic signal is the sum of both. (iii) In clusters of larger and/or
+deeper particles, although the method individualizes them well, the magnetic
+signal of the neighboring particles can considerably influence the result of
+the inversion. Apparently, there is a direct relationship between the size and
+depth with the observed errors. It is clear from the cross bars in
+Figure~\ref{P8gMJ9mWpS} that deep particles and/or particles with small radii
+generate worse results essentially because they will produce smaller anomalous
+fields in the magnetic maps. Note nonetheless that even small particles when
+close to the surface are adequately modeled by our method.
+
+Figure~\ref{RDs2vUEqCI} shows stereoplots with the directions generated by the
+model and the recovered data. The mean directions modeled are coincident with
+the model and the distribution is coincident within the 95\% confidence cone.
+When filtered to include only data with R\textsuperscript{2} \textgreater 0.95
+the obtained directions are closer to the model average and less sparse.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\linewidth]{figures/ComplexStereo.png}
+\caption{
+a) Simulation of a thin section of rock with particles uniformly magnetized in
+the average direction of the induced field
+45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
+data, without any type of filtering, are sparse, but statistically generate the
+same average direction. c) It is still possible to filter only the directions
+of the magnetic sources with the best fitting determined by the coefficient of
+determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
+around the mean value.
+}
+\label{rds2vueqci}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Application to real data}
+
+To test whether the proposed method would be able to determine the
+magnetization directions and the magnetic moment of particles in natural
+samples, we selected a previously studied carbonate stalagmite sample from the
+Wintimdouine cave in the Agadir region (Morocco) \citep{Ait2019Hydro}. This
+speleothem contains both magnetite and hematite as the main carriers of
+magnetic remanence, as attested by thermomagnetic curves with temperature
+decays at {\textasciitilde}580 °C and {\textasciitilde}680 °C, and bimodal
+curves of isothermal remanent magnetization (IRM) acquisition (Carmo et al.,
+2019).
+
+In order to provide two distinct directions associated with the different
+magnetic mineral types in this sample, we applied two IRM pulse fields of 2.7 T
+and 0.3 T, respectively toward the +X and -X directions. In this way, the high
+coercivity grains (hematite) would point towards +X and the low coercivity ones
+(magnetite) would align in the -X direction.
+
+After remanence acquisition, we performed a magnetic map with the Quantum
+Diamond Microscope (QDM) at Harvard University over a sample section of
+approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{W1GfysVYnX}a) with a grid
+spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
+576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
+order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
+Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
+possible to determine the windows for 85 potential sources
+(Figure~\ref{W1GfysVYnX}b).
+
+\begin{figure}[tb]
+\centering
+\includegraphics[width=1\linewidth]{figures/RealData.png}
+\caption{
+a) Real sample data. b) Individual sources' window position (yellow squares)
+obtained with the blob detection algorithm applied on the total gradient map.
+}
+\label{w1gfysvynx}
+\end{figure}
+
+After applying the ED algorithm, we performed the inversion of the magnetic
+moment for each of the 85 windows selected previously. In order to reduce
+considerably the computation time, the inversions were done within each data
+window, instead of solving all sources parameters at the same time. We obtained
+the magnetic moment (not shown) and the direction for all 85 magnetic grains
+(Figure~\ref{NKOAMThaWA}a). Then, we calculated the residuals of the inversions
+in each window and subsequently the coefficient of determination
+R\textsuperscript{2}, which was used as a filter for the best directions
+obtained. We used a cut-off limit of the coefficient of determination at 0.7
+(Figure~\ref{NKOAMThaWA}b) EXPLICAR PORQUE USOU 0.7 AQUI E 0.95 NOS CASOS
+SINTÉTICOS. This filtering technique removed unreliable responses showing more
+clearly the expected directional clusters of hematite and magnetite crystals.
+NÃO SABEMOS SE OS PONTOS RETIRADOS SÃO `UNRELIABLE RESPONSES'\dots ALÉM DISSO,
+O FILTRO ELIMINA QUASE 50\% DAS FONTES IDENTIFICADAS, O QUE PODE SER UM
+PROBLEMA SE TIVERMOS QUE APLICAR EM OUTROS CASOS REAIS. USAR O TESTE DE
+NÃO-DIPOLARIDADE? TALVEZ SEJA MAIS INTERESSANTE, DADA A DISCUSSÃO QUE SEGUE.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
+\caption{
+a) The recovered data, without any type of filtering. b) Recovered data
+filtered by the coefficient of determination ($R^ 2 \\geq 0.7$), which shows
+two clusters of direction located on each pole of the stereogram.
+}
+\label{nkoamthawa}
+\end{figure}
+
+NESSA PARTE SERIA INTERESSANTE INCLUIR MAPAS COMO OS DA FIGURA 4B E 4C, COM A
+ESPACIALIDADE DOS AJUSTES E DISCUTIR DA SEGUINTE FORMA:
+
+\begin{enumerate}
+\item RESULTADOS EM FUNÇÃO DA QUALIDADE DO AJUSTE
+\item RESULTADOS EM FUNÇÃO DA DIPOLARIDADE DAS FONTES
+\item CONTEXTUALIZAR O SEU MÉTODO EM RELAÇÃO A OUTROS. COMO OS OUTROS ESTIMAM
+  OS MISFITS? QUE FILTROS USAM? QUAL A DIFERENÇA COM SUA ABORDAGEM? POR
+  ENQUANTO SOMENTE O TRABALHO DE CORTEZ ESTÁ COMENTADO -> COMPARAR COM
+  OS OUTROS MÉTODOS DE INVERSÃO (Fu, de Groot, Egli2000, Lima2007)
+\end{enumerate}
+
+The application of the proposed algorithm to natural samples gives some
+indications of its ability to circumvent the prominent problems described by
+\citep{CortesOrtuno2022} [QUAIS PROBLEMAS FORAM LISTADOS POR CORTÉS-ORTUÑO?],
+namely: (i)\dots, (ii)\dots, (iii)\dots
+
+the same authors showed that particles in the single vortex PSD state present
+more accurate inversion results when considering the non-dipole components for
+small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
+distances the dipole as approximations are remarkably accurate, as the
+higher-order moments decay rapidly with distance and therefore have less
+influence on the particle's magnetic signal. Thus, our approach can be
+considered reasonable for working with particle signals in SD (already a
+dipole) and PSD states. The latter happens due to the QDM sensor height being
+usually greater than 5 $\\mu m$, considering a particle on the immediate
+surface of the sample the higher-order moments are already quite attenuated.\}
+
+Despite the excellent signal/noise ratio that the SMM provided with the
+proximity of the sensor to the sample, it is worth mentioning that the
+measurement noise can still overshadow the responses of very weak/small, or
+deep particles, generating unreliable inversion results. Therefore, it is
+necessary to keep a check to determine if the inversion reached a satisfactory
+result, such as the coefficient of determination that we used or the
+signal-to-noise ratio presented by \citep{CortesOrtuno2022}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+
+We developed an efficient semi-automated method to determine the direction of
+magnetization of dipolar sources on a microscale, as well as the recovery of
+their magnetic moment. Being ideal for a reinterpretation for the application
+of methods of paleomagnetic studies using thin sections of rock samples. This
+would be an attempt to improve the quality of results obtained by isolating the
+responses of more reliable recorders of the Earth's geomagnetic field.
+
+We also present a new, faster, and cleaner way to solve the Euler equation in
+determining the positioning of magnetic anomaly sources using a pre-selection
+of magnetic anomaly source windows based on the Laplacian of the Gaussian
+applied to total gradient anomaly maps. In this way, reducing the numerous
+solutions to just one data window per source. After estimating the structural
+index ($n = 3$) by approximating the sources generating the magnetic anomaly to
+spheres/points, the Euler deconvolution is performed and the central position
+of each source is determined.
+
+The recovery of direction and magnetization we only need to assume that the
+sources have their central positions known (so we apply Euler deconvolution)
+and that their magnetizations are uniform. This last premise aligns with the
+theory of magnetically stable particles SD (and the PSD ones at a reasonable
+sensor height), which is the basis of classical paleomagnetism. Also, there is
+no need for any kind of prior knowledge other than the observed magnetic
+anomaly, and the structural index of the sources. Therefore, this method can be
+quickly replicated in a dataset of thin sections of rocks to obtain the
+distributions of magnetic directions of each source identified in the sample.
+
+The test using a simple synthetic sample shows the great capability of the
+method by retrieving not only the precise center positions, but also retrieving
+the magnetization directions and intensity even under the considerable effect
+of high-frequency noise (15 nT). While the complex synthetic sample data allows
+observing the applicability of the method developed in real samples that are
+more complex with varied magnetization directions and intensity, in addition to
+also taking into account the high and low-frequency noise and sources with
+variable sizes and depths.
+
+The real sample data positively answered the question of the algorithm's
+ability to deal with rocks thin-sections. But also, showed the acceptable
+capacity (within the adequate R$^2$ threshold) of retrieving different
+magnetization directions recorded by magnetic minerals with different
+coercivities and magnetic signal disparities even greater than predicted in the
+complex synthetic test.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data and code availability}
+
+The Python source code used to produce all results and figures presented here
+is available at \url{https://github.com/\GitHubRepository} and
+\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
+
+The image rescaling and blob detection though the Laplacian of Gaussian method
+were performed with the scikit-image library \citep{VanderWalt2014}. CITE OTHER
+SOFTWARE TOOLS USED. Matplotlib for figures, numpy and scipy for almost
+everything. Verde for the regional residual separation and other things.
+
+The QDM image data is available at CITE A DATAVERSE/FIGSHARE ARCHIVE under the
+CC-XX license.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-02-20 paper/content.tex
Add a caption for figure 1

@@
 \begin{equation}
-\|\vec{\mathbf{\nabla}}f(x, y, z)\|  = \sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}\ ,
+\|\vec{\mathbf{\nabla}}f(x, y, z)\|  = 
+\sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}
+\ ,
 \end{equation}
@@
 \begin{equation}
-\partial_x f(x, y, z) \approx \dfrac{f(x + \Delta x, y, z) - f(x - \Delta x, y, z)}{2 \Delta x} \ ,
+\partial_x f(x, y, z) \approx 
+\dfrac{f(x + \Delta x, y, z) - f(x - \Delta x, y, z)}{2 \Delta x} 
+\ ,
 \end{equation}
@@
 \begin{equation}
-\text{TGA}_{rescaled} = 2\left(\dfrac{\text{TGA} - v_{min}}{v_{max} - v_{min}}\right) - 1 \ ,
+\text{TGA}_{rescaled} = 
+2\left(\dfrac{\text{TGA} - v_{min}}{v_{max} - v_{min}}\right) - 1 
+\ ,
 \end{equation}
@@
 \includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
-\caption{Caption needed.}
+\caption{
+Schematic representation of the coordinates systems and modelling elements.
+The left panel shows the $x, y, z$ right-handed coordinate system with $z$ 
+pointing upward and away from the sample. A dipole with dipole moment vector 
+$\mathbf{\vec{m}}$ is also shown at coordinates $(x_c, y_c, z_c)$. The 
+observation points are located at regular intervals on an $x-y$ plane. 
+The right panel zooms in on the dipole and shows the dipole moment vector
+expressed in terms of inclination ($I$, positive downwards), declination
+($D$, angle with the $\hat{y}$ direction), and moment magnitude
+$m = \|\mathbf{m}\|$.
+}
 \label{fig_coordinate_systems}

### 2023-02-25 code/micromag.py
Add the exclude border feature in the anomaly detection function

@@ -313,7 +313,7 @@ def data_gradients(data):
 
 
 def detect_anomalies(
-    data, size_range, size_increment=2, nsizes=10, threshold=0.5, overlap=0.5
+    data, size_range, size_increment=2, nsizes=10, threshold=0.5, overlap=0.5, exclude_border=0
 ):
     """
     Run the blob detection and produce bounding boxes in data coordinates
@@ -327,6 +327,7 @@ def detect_anomalies(
         threshold=threshold,
         num_sigma=nsizes,
         overlap=overlap,
+        exclude_border= int(exclude_border / spacing),
     ).T
     blob_coords = (data.x.values[ix.astype("int")], data.y.values[iy.astype("int")])
     blob_sizes = sigma_pix * np.sqrt(2) * spacing * size_increment
@@ -336,7 +337,7 @@ def detect_anomalies(
     ]
     return windows
 
-
+    
 def euler_deconvolution(data, x_deriv, y_deriv, z_deriv):
     """
     Estimate the (x, y, z) position and base level by Euler Deconvolution

### 2023-02-27 code/micromag.py
Add signal-to-noise calculation in the micromag.py file

@@ -218,7 +218,8 @@ def dipole_moment_inversion(data, dipole_coordinates):
     # Estimate of the true error variance (since we'll never know it)
     chi_squared = residuals_sum_sq / (n_data - n_params)
     covariance = chi_squared * np.linalg.inv(hessian)
-    r2 = 1 - residuals_sum_sq / np.linalg.norm(d - d.mean()) ** 2
+    r2 = 1 - residuals_sum_sq / np.linalg.norm(d - d.mean()) ** 2  # determination coeficient (dimensionless)
+    SNR = 10*np.log10(np.var(d, ddof=1)/np.var(residuals, ddof=1)) # signal-to-noise ratio in decibels (dB)
 
     return dipole_moment, covariance, r2
 

### 2023-02-27 code/micromag.py
Add complex synthetic notebook

@@ -221,7 +221,7 @@ def dipole_moment_inversion(data, dipole_coordinates):
     r2 = 1 - residuals_sum_sq / np.linalg.norm(d - d.mean()) ** 2  # determination coeficient (dimensionless)
     SNR = 10*np.log10(np.var(d, ddof=1)/np.var(residuals, ddof=1)) # signal-to-noise ratio in decibels (dB)
 
-    return dipole_moment, covariance, r2
+    return dipole_moment, covariance, r2, SNR
 
 
 @numba.jit(nopython=True, parallel=True)

### 2023-02-27 paper/content.tex
Minor changes to the figure layout
New version of model setup figure
Includes the observation plane, the sample volume, and other tweaks.
Add R-squared and signal-to-noise ratio in the paper methodology

@@
 
-\begin{figure}[t]
+\begin{figure}[tb]
 \centering
@@
 The left panel shows the $x, y, z$ right-handed coordinate system with $z$
-pointing upward and away from the sample. A dipole with dipole moment vector 
-$\mathbf{\vec{m}}$ is also shown at coordinates $(x_c, y_c, z_c)$. The 
-observation points are located at regular intervals on an $x-y$ plane. 
-The right panel zooms in on the dipole and shows the dipole moment vector
-expressed in terms of inclination ($I$, positive downwards), declination
-($D$, angle with the $\hat{y}$ direction), and moment magnitude
-$m = \|\mathbf{m}\|$.
+pointing upward and away from the sample. The top surface of the sample defines
+the $z=0$ surface. A dipole with dipole moment vector $\mathbf{\vec{m}}$ is
+also shown at coordinates $(x_c, y_c, z_c)$. The observation points are located
+at regular intervals on an $x-y$ plane at a positive $z$ separation from the
+sample surface. The right panel zooms in on the dipole and shows the dipole
+moment vector expressed in terms of inclination ($I$, positive downwards),
+declination ($D$, angle with the $\hat{y}$ direction), and moment magnitude $m
+= \|\mathbf{m}\|$.
 }
@@
 declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
-by propagation of uncertainties
+by the propagation of uncertainties
 
@@
 \noindent
-These variances reflect the sensitivity of the estimated dipole moment to
-random noise in the magnetic field observations. However, they do not capture
-other, often larger, sources of uncertainty like systematic errors in the
-observations, data positioning errors, and the validity of the dipolar
-approximation. Therefore, we recommend that these estimated variances be
-treated with caution and should not be interpreted as ``the degree of certainty
-that the estimated values are the true values''.
+These variances reflect the sensitivity of the estimated dipole moment to random noise in the magnetic field observations.
+However, they do not capture other, often larger, sources of uncertainty like systematic errors in the observations, data positioning errors, and the validity of the dipolar approximation.
+Therefore, we recommend that these estimated variances be treated with caution and should not be interpreted as ``the degree of certainty that the estimated values are the true values''.
 
-[FALAR SOBRE O CALCULO DE R2]
+It is important to note that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters.
+\cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}).
+The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data.
+On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data.
+Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}).
+SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor.
+The higher the SNR (in decibels) values the better it will be the fit of the predicted model.
+For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise.
+Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.
 
-[INCLUIR A ESTIMATIVA DE NÃO-DIPOLARIDADE]
+\begin{equation}
+\label{R2}
+\begin{aligned}
+\large R^2 = 1 - \frac{ {\left( b_z - {b_{z}}_{dipole} \right)}^2 }{{\left( b_z - \bar{b_z} \right)}^2}
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\label{SNR}
+\begin{aligned}
+\large SNR = 10 \log_{10}{\left( \frac{{{\sigma}^2}_{dipole}}{{{\sigma}^2}_{residual}} \right)}
+\end{aligned}
+\end{equation}
 
@@
 
-\begin{figure}[tbp]
+\begin{figure}[!tb]
   \centering
@@
   \caption{
-  a) Synthetic data contaminated with psedo-random normal noise. b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
+    Synthetic data and the various processing steps performed prior to the
+    dipole moment inversion. 
+    a) The synthetic noise-corrupted $b_z$ observations at 
+    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
+    depths and dipole moment vectors 
+    (see Table~\ref{tab_synthetic_simple_results}).
+    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
+    attenuated short-wavelength noise.
+    c) The total gradient amplitude (TGA) calculated from the 
+    upward-continued data, which is able to concentrate the signal on top
+    of each dipolar source. 
+    d) The contrast-stretched TGA, highlighting the signal of all four
+    sources, including the weak central source.
+    e) The detected source bounding boxes (black squares) which correctly
+    identify the signal of all four sources.
+    f) The estimated source locations (colored circles) from Euler 
+    Deconvolution of the upward-continued data inside each bounding box. 
+    The color represents the difference between the true and estimated 
+    $z$ coordinates.
   }
@@
 
-\begin{figure}[!t]
+\begin{figure}[tb]
 \centering
@@
   \includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
-\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise.
-b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
+  \caption{
+    a) Complex synthetic data contaminated with  both high and low frequencies noise.
+b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
+  }
   \label{e9td9j9abb}

### 2023-02-28 paper/content.tex
Add the chi-square formula to the paper's methodology

@@
 
-It's important to note that these are not paleomagnetic declination and
-inclination angles, but are instead related to the sample coordinate system. To
-obtain the paleomagnetic direction, the dipole moment vector must be rotated to
-the sample field orientation prior to the application of
-Equation~\ref{eq_vector_to_incdec}.
+It is important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system.
+To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of Equation~\ref{eq_vector_to_incdec}.
 
-MISSING PARAGRAPH ABOUT THE COVARIANCE ESTIMATION AND $\sigma_0$.
+In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies and sensors limitations.
+This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used.
+Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples.
+Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).
+
+\begin{equation}
+  \label{chi_square}
+\begin{aligned}
+\large \sigma_0^2 = {\chi}^2 = \frac{\sum{\left( b_z - {b_{z}}_{dipole} \right)}^2}{N-m}
+\end{aligned}
+\end{equation}
 
@@
 
-It is important to note that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters.
+It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters.
 \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}).
@@
 \begin{aligned}
-\large R^2 = 1 - \frac{ {\left( b_z - {b_{z}}_{dipole} \right)}^2 }{{\left( b_z - \bar{b_z} \right)}^2}
+\large R^2 = 1 - \frac{ \sum{\left( b_z - {b_{z}}_{dipole} \right)}^2 }{\sum{\left( b_z - \bar{b_z} \right)}^2}
 \end{aligned}

### 2023-03-02 paper/content.tex

@@
 \noindent
-in which $(x_c, y_c, z_c)$ are the coordinates of the magnetic field source
-(Figure~\ref{fig_coordinate_systems}), $b$ is the base level representing a
-constant shift in the signal, and $\eta$ is the structural index corresponding
-to the nature of the source \citep{Reid1990}. This equation holds true for
-simple geometric sources, like spheres, dipoles, and vertical cylinders. Here,
-we assume that the magnetic particles are small enough and the sensor is far
-enough away that the sources can be represented by dipoles, yielding an
-$\eta=3$.
+in which $(x_c, y_c, z_c)$ are the coordinates of the magnetic field source (Figure~\ref{fig_coordinate_systems}), $b$ is the base level representing a constant shift in the signal, and $\eta$ is the structural index corresponding to the nature of the source \citep{Reid1990}.
+This equation holds true for simple geometric sources, like spheres, dipoles, and vertical cylinders.
+Here, we assume that the magnetic particles are small enough and the sensor is far enough away that the sources can be represented by dipoles, yielding an $\eta=3$.
 
-The inversion is performed by rearranging Equation~\ref{eq_euler_homogeneity}
-into a pseudo-parametric model with parameters $x_c$, $y_c$, $z_c$, and $b$
+The inversion is performed by rearranging Equation~\ref{eq_euler_homogeneity} into a pseudo-parametric model with parameters $x_c$, $y_c$, $z_c$, and $b$
 
@@
 
-Given a set of $N$ observations of the magnetic field as the harmonic function
-$f$ and its spatial derivatives, we can form the $N \times 4$ system of
-equations
+Given a set of $N$ observations of the magnetic field as the harmonic function $f$ and its spatial derivatives, we can form the $N \times 4$ system of equations
 
@@
 
-We can arrive at a solution to Equation~\ref{eq_euler_forward} by assuming that
-the three spatial derivatives of $f$ have negligible error and minimizing the
-misfit $\phi(\mathbf{p})$ between a pseudo-observation vector $\mathbf{h}^o$
-and the predictions $\mathbf{h}$. The least-squares misfit $\phi(\mathbf{p})$
-is defined as
+We can arrive at a solution to Equation~\ref{eq_euler_forward} by assuming that the three spatial derivatives of $f$ have negligible error and minimizing the misfit $\phi(\mathbf{p})$ between a pseudo-observation vector $\mathbf{h}^o$ and the predictions $\mathbf{h}$.
+The least-squares misfit $\phi(\mathbf{p})$ is defined as
 
@@
 \noindent
-in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian
-distance between the observation point $(x, y, z)$ and the source $(x_c, y_c,
-z_c)$ and $\mu_0$ is the vacuum magnetic permeability. Most magnetic
-microscopes provide measurements of only the vertical component $b_z$, which
-can be isolated from Equation~\ref{eq_vector_dipole_field} as
+in which $r = \sqrt{(x - x_c)^2 + (y - y_c)^2 + (z - z_c)^2}$ is the Cartesian distance between the observation point $(x, y, z)$ and the source $(x_c, y_c, z_c)$ and $\mu_0$ is the vacuum magnetic permeability.
+Most magnetic microscopes provide measurements of only the vertical component $b_z$, which can be isolated from Equation~\ref{eq_vector_dipole_field} as shown in Equation~\ref{eq_dipole_bz}, which is a similar approach to the uniform model proposed by \cite{Weiss2007}.
 
@@
 
-Given a set of $N$ observations of $b_z$ made inside a window containing a
-single source, we can form the $N \times 3$ linear equation system
+Given a set of $N$ observations of $b_z$ made inside a window containing a single source, we can form the $N \times 3$ linear equation system
 
@@
 
-In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies and sensors limitations.
+In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies, and sensor limitations.
 This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used.
@@
 For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise.
-Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.
+Thus, both $R^2$ and SNR techniques are appropriate to be used as criteria filtering for reliability for dipolar inversions.
 

### 2023-03-02 paper/content.tex
Rewrite the simple synthetic section of the paper

@@
 \begin{equation}
+\label{uncertanties}
 \begin{aligned}
@@
 
-We first applied our inversion workflow to synthetic data to evaluate its
-strengths and limitations. The first set of synthetic data is simple and
-intended to test the method's performance under ideal circumstances. The second
-set is more complex, with a greater number of magnetic particles and
-long-wavelength noise, and is intended to demonstrate the capabilities and
-limitations of the method under real-world scenarios.
+We first applied our inversion workflow to synthetic data to evaluate its strengths and limitations.
+The first set of synthetic data is simple and intended to test the method's performance under ideal circumstances.
+The second set is more complex, with a greater number of magnetic particles and long-wavelength noise, and is intended to demonstrate the capabilities and limitations of the method under real-world scenarios.
 
-The first synthetic model was performed by generating the vertical magnetic
-field derived from a simple set of four spheres with similar magnetization
-intensity and radius, but completely different magnetization directions,
-contaminated by high-frequency noise. This simplified test model is basically
-done to investigate the efficiency of the inversions used for Euler positioning
-and magnetization parameters, thus being a validation of the methodology.
+The first synthetic model was performed by generating the vertical magnetic field derived from a simple set of four spheres with similar magnetization intensity and radius, but completely different magnetization directions, contaminated by high-frequency noise.
+This simplified test model is basically done to investigate the efficiency of the inversions used for Euler positioning and magnetization parameters, thus being a validation of the methodology.
 
-The second model contains one hundred spheres with different radii and
-magnetization intensities but magnetized in a similar direction within one
-standard deviation. The magnetic field generated from these sources is
-corrupted by both low and high-frequency noise. The complexity of this
-synthetic data seeks to more faithfully emulate real magnetic microscopy data.
+The second model contains one hundred spheres with different radii and magnetization intensities but magnetized in a similar direction within one standard deviation.
+The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
+The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.
 
@@
 
-Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field
-$b_z$ over a synthetic rock section containing four uniformly magnetized
-spherical sources. The map covers a surface of $\qty{1000}{\um} \times
-\qty{1000}{\um}$ with
-data points in a regular grid of \qty{1}{\um} ($N = 10^6$ observations)
-obtained at a sensor-sample distance of \qty{5}{\um}. The magnetic field data is
-contaminated with a pseudo-random noise of normal Gaussian distribution with a
-zero mean and \qty{20}{\nano\tesla} standard deviation.
+The Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four uniformly magnetized spherical sources.
+The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$ with data points in a regular grid of approximate \qty{1}{\um} ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}.
+The magnetic field data is contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and \qty{20}{\nano\tesla} standard deviation.
 
-We first applied an upward continuation filter to smooth out high-frequency
-noise \citep{Blakely1996}, since it strongly affects the first derivatives of
-the potential field required by the Euler equation. Then, we calculated the
-magnetic total gradient (or horizontal gradient) filter and applied the blob
-detection algorithm to the total gradient map to obtain the position of the
-data window for each source (Figure~\ref{fig_coordinate_systems}b). The ED was
-run for each selected source by assuming the structural index of a
-sphere/punctual source, therefore obtaining the Cartesian coordinates of each
-source causing the magnetic potential anomaly in the observed data set (Table
-1).
+We first applied an upward continuation filter (Fig.~\ref{fig_synthetic_simple_data}b) to smooth out high-frequency noise \citep{Blakely1996}, since it strongly affects the first derivatives of the potential field required by the Euler equation.
+Then, we calculated the magnetic total gradient anomaly map (Fig.~\ref{fig_synthetic_simple_data}c), which is subjected to a stretch contrast filter to highlight as much as possible the weaker intensity sources (Fig.~\ref{fig_synthetic_simple_data}d),
+in order to facilitate the next step.
+Subsequently, we applied the blob detection algorithm to the contrasted total gradient map to obtain the position of the data window for each source (Fig.~\ref{fig_synthetic_simple_data}e).
+The ED was performed for each selected source by assuming the structural index of a sphere/punctual source, therefore obtaining the Cartesian coordinates (Fig.~\ref{fig_synthetic_simple_data}f) of each source causing the magnetic potential anomaly in the observed data set (Table~\ref{tab_synthetic_simple_results}).
 
@@
 \centering
-\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
+\includegraphics[width=0.6\linewidth]{figures/simple-synthetic-dipole-moment.png}
 \caption{
-  CAPTION NEEDED
+Comparison of true and estimated dipole magnetic moments and directions.
 }
@@
 
-The central positions of each source obtained with ED were used as an input
-parameter for inverting the vertical magnetic field. The inversion produced a
-least squares (or robust) approximation solution for the vector of Cartesian
-magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions
-(D and I) and intensity of magnetic moment $m$. We also obtained the
-uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
-and considering $\sigma = \qty{15}{\nano\tesla}$.
+The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field.
+The inversion produced a least squares approximation solution for the vector of Cartesian
+magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}).
+We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in the Table~\ref{tab_synthetic_simple_results}.
 
@@
 
-\citet{Oliveira2015Estimation} proved that the magnetization directions (D and
-I) recovered by the least squares estimator are sensitive to variations in the
-horizontal coordinates of the center of the magnetic sources, but are
-practically insensitive to variations in depth. Thus, they consider the Euler
-deconvolution method as an adequate technique to estimate the central positions
-that will be used as prior information for inversion. This occurs mainly
-because, when well performed, the recovery of the horizontal coordinates of the
-source central position is considerably accurate, while the vertical coordinate
-can undergo greater variation even though it still provides satisfactory
-results \citep{Silva20033D, Melo2013}.
+\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are
+practically insensitive to variations in depth.
+Thus, they consider the Euler deconvolution method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
+This occurs mainly
+because, when well performed, the recovery of the horizontal coordinates of the source central position is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
 
@@
 
-This test represents a more complex scenario by simulating 100 sources randomly
-distributed in the imaged area of a synthetic thin section of 2000 x 1400 $\mu
-m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$
-spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real
-samples, the magnetic sources are modeled as spheres with different depths,
-radii, and magnetizations. The depths vary between 1 and 19 $\mu m$, while the
-radii range from 0.01 to 0.95 $\mu m$. The magnetizations of the sources have
-declination and inclination directions sampled from a pseudo-random Gaussian
-distribution with a mean of D, I = 45°, 45°, and a standard deviation of 8°.
-This randomness simulates the NRM found in real ferromagnetic particles that
-vary individually but average out to the inducing field direction. Finally, we
-contaminated the data with high-frequency normally-distributed pseudo-random
-noise with zero means and 5 nT standard deviations, as well as with
-low-frequency noise in the form of additional deep sources beyond the modeling
-domain. The noise-corrupted synthetic $b_z$ image is shown in
-Figure~\ref{E9td9j9aBB}a.
+This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu
+m$.
+The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance.
+For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity.
+The depths vary between 1 and 20 $\mu m$, while the
+magnetic moment intensity range from $10^{-13}$ to $10^{-15}$ $A/m^2$.
+
+To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that
+vary individually but average out to the inducing field direction.
+The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 5°.
+While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, and a standard deviation of 5°.
+Finally, we contaminated the data with high-frequency normally-distributed pseudo-random
+noise with zero means and 20 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
+The noise-corrupted synthetic $b_z$ image is shown in
+Figure~\ref{complex-synthetic-data}a.
 
@@
   \centering
-  \includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
+  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
   \caption{
@@
   }
-  \label{e9td9j9abb}
+  \label{complex-synthetic-data}
 \end{figure}
 
-The result of the source detection method is shown in Figure~\ref{E9td9j9aBB}b,
-where 84 particles out of the original 100 were detected. The spatiality of the
-inversion results is one of the key advantages of magnetic microscopy over the
-classic techniques of paleomagnetism. Therefore, we present the inversion
-results spatially so that we can evaluate any patterns in their distribution.
+Since now the data have both high and low-frequency noise, we performed a $3^{rd}$ degree polynomial fitting to remove the low-frequency wavelength from the signal.
+Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b).
+Followed by the TGA map calcultaion (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
+The result of the source's window detection method is shown in Figure~\ref{complex-synthetic-data}e,
+where 97 particles out of the original 100 were detected.
+
+The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
+Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution.
+
+\textbf{FROM HERE!}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[!htbp]
 \centering
-\includegraphics[width=1\linewidth]{figures/ComplexComparison.png}
+\includegraphics[width=1\linewidth]{figures/complex-synthetic-comparison.png}
 \caption{
@@
 }
-\label{p8gmj9mwps}
+\label{complex-synthetic-comparison}
 \end{figure}
@@
 considerably low errors, especially in the directions, usually less than 5°
-(Figure~\ref{P8gMJ9mWpS}a). (iii) The magnetic moments obtained also tend to
-not deviate much from the real values (Figure~\ref{P8gMJ9mWpS}b) when
+(Figure~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained also tend to
+not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when
 R\textsuperscript{2} scores are high (\textgreater 0.95)
-(Figure~\ref{P8gMJ9mWpS}c). (iv) Shallow particles grouped in clusters are
+(Figure~\ref{complex-synthetic-comparison}c). (iv) Shallow particles grouped in clusters are
 usually well individualized during window selection, as well as (v) some
@@
 signal of the neighboring particles can considerably influence the result of
-the inversion. Apparently, there is a direct relationship between the size and
-depth with the observed errors. It is clear from the cross bars in
+the inversion. Apparently, there is a direct relationship between the size and depth with the observed errors. It is clear from the cross bars in
 Figure~\ref{P8gMJ9mWpS} that deep particles and/or particles with small radii
@@
 close to the surface are adequately modeled by our method.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
+\caption{
+a)
+}
+\label{complex-synthetic-fitting-test}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=1\linewidth]{figures/ComplexStereo.png}
+\includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
 \caption{
@@
 }
-\label{rds2vueqci}
+\label{complex-synthetic-stereograms}
 \end{figure}

### 2023-03-03 paper/content.tex
Add changes to the complex model section of the paper

@@
 \noindent
-The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into
-declination $D$, inclination $I$, and magnitude $m$, which are more intuitive
-quantities for interpreting paleomagnetic results, like so
+The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so
 
@@
 
-\begin{figure}[!tb]
+\begin{figure}[tb!]
   \centering
@@
 
-\begin{figure}[tb]
+\begin{figure}[tb!]
 \centering
-\includegraphics[width=0.6\linewidth]{figures/simple-synthetic-dipole-moment.png}
+\includegraphics[width=0.5\linewidth]{figures/simple-synthetic-dipole-moment.png}
 \caption{
@@
 The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field.
-The inversion produced a least squares approximation solution for the vector of Cartesian
-magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}).
-We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in the Table~\ref{tab_synthetic_simple_results}.
+The inversion produced a least squares approximation solution for the vector of Cartesian magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}).
+We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in Table~\ref{tab_synthetic_simple_results}.
 
@@
 
-\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are
-practically insensitive to variations in depth.
+\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
 Thus, they consider the Euler deconvolution method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
-This occurs mainly
-because, when well performed, the recovery of the horizontal coordinates of the source central position is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
+This occurs mainly because, when well performed, the recovery of the horizontal coordinates of the source central position is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
 
@@
 
-This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu
-m$.
+This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu m$.
 The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance.
 For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity.
-The depths vary between 1 and 20 $\mu m$, while the
-magnetic moment intensity range from $10^{-13}$ to $10^{-15}$ $A/m^2$.
+The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity range from $10^{-12}$ to $10^{-14}$ $Am^2$.
 
-To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that
-vary individually but average out to the inducing field direction.
-The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 5°.
-While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, and a standard deviation of 5°.
-Finally, we contaminated the data with high-frequency normally-distributed pseudo-random
-noise with zero means and 20 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
-The noise-corrupted synthetic $b_z$ image is shown in
-Figure~\ref{complex-synthetic-data}a.
+To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that vary individually but average out to the inducing field direction.
+The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 10°.
+While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, also with standard deviation of 10°.
+Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero means and 50 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
+The noise-corrupted synthetic $b_z$ image is shown in Figure~\ref{complex-synthetic-data}a.
 
@@
   \caption{
-    a) Complex synthetic data contaminated with  both high and low frequencies noise.
-b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
+    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at 
+    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated. 
+    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    c) The total gradient amplitude (TGA) calculated from the 
+    upward-continued data, which is able to concentrate the signal on top
+    of each dipolar source. 
+    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
+    e) The detected source bounding boxes (black squares) that correctly
+    encapsulate the signal of the sources.
+    f) The estimated source locations (colored circles) from Euler 
+    Deconvolution of the upward-continued data inside each bounding box. 
+    The color represents the difference between the true and estimated 
+    $z$ coordinates.
   }
@@
 
-Since now the data have both high and low-frequency noise, we performed a $3^{rd}$ degree polynomial fitting to remove the low-frequency wavelength from the signal.
+Since now the data have both high and low-frequency noise, we performed a $5^{th}$ degree polynomial fitting to remove the low-frequency wavelength from the signal.
 Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b).
-Followed by the TGA map calcultaion (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
-The result of the source's window detection method is shown in Figure~\ref{complex-synthetic-data}e,
-where 97 particles out of the original 100 were detected.
+Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
+The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.
 
@@
 
-\textbf{FROM HERE!}
+Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 97 particles that were identified and the model fitting tests.
+Firstly, we evaluate the magnetic direction misfits by calculating the module of the angular difference between the true and the estimated magnetization vectors (Fig.~\ref{complex-synthetic-comparison}a).
+Afterward, we calculate the dipole moment misfits in percentage (~$|~100 \left( m_{true} - m_{estimate}\right)~/~\left(m_{true}\right)~|$~), as shown in Figure~\ref{complex-synthetic-comparison}b).
+Then, the fitting tests were performed using the equations~\ref{R2}-~\ref{SNR} in an attempt to select which criterion best separates data with good fitting and low errors of direction and dipole moment.
+Figure~\ref{complex-synthetic-comparison}c shows the R² coefficient, or the \emph{D} parameter of the non-dipolarity test \citep{Fu2020}, representing how well the dipolar model is able to explain the observed data in the given window.
+On the other hand, the SNR is capable to express the power of the predicted model over its residual, therefore can select which sources are more "visible" by the sensor (Fig.~\ref{complex-synthetic-comparison}d).
+Consequently yielding results directly proportional to the R² coefficient.
 
-Figure~\ref{P8gMJ9mWpS} shows the difference between the estimated dipole
-moments and the true values for each of the 84 particles that were identified.
-Figure~\ref{P8gMJ9mWpS}c shows the R² coefficient of determination representing
-how well the dipolar model is able to fit the observed data in the given
-window. The depth and radius of each particle are represented by horizontal and
-vertical cross bars, respectively. The depth and radius are useful proxies for
-the width and amplitude of the magnetic signal of each particle, which is
-crucial to know when evaluating the inversion results.
-
-\begin{figure}[!htbp]
+\begin{figure}[htbp!]
 \centering
-\includegraphics[width=1\linewidth]{figures/complex-synthetic-comparison.png}
+\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
 \caption{
-The validation of the result obtained with the inversion was calculated for
-each individual particle based on the error between the real parameters modeled
-and their respective recovered values, being (a) the direction and (b)
-intensity of the magnetic moment, in addition to the R$^2$ score (c) obtained
-by comparing the forward model and the actual data. The depth and radius of the
-magnetic sources are also important factors that influence the final result,
-therefore, these data are given in the form of cross plots, with the vertical
-bar represented by the depth (1 - 19 $\\mu m$) and the horizontal bar by the
-radius (0.01 - 0.95 $\\mu m$).
+The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data.
+The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
 }
@@
 
-The application in complex synthetic data allows observing the strengths and
-limitations of the proposed methodology. Some of the strengths that can be
-mentioned are: (i) the applied technique not only detects most of the modeled
-sources but also (ii) most of the recovered magnetic parameters have
-considerably low errors, especially in the directions, usually less than 5°
-(Figure~\ref{complex-synthetic-comparison}a). (iii) The magnetic moments obtained also tend to
-not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when
-R\textsuperscript{2} scores are high (\textgreater 0.95)
-(Figure~\ref{complex-synthetic-comparison}c). (iv) Shallow particles grouped in clusters are
-usually well individualized during window selection, as well as (v) some
-particles that produce a weak magnetic signal but isolated particles.
+The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively.
+These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.
+The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology.
+Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
+(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
+(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some particles that produce a weak magnetic signal but isolated particles.
 
-The main limitations observed are: (i) the blob detection fails when there are
-sources too close, grouping them into the same window, thus causing an
-erroneous result both for Euler deconvolution and for the magnetic parameters.
-(ii) The very same occurs when there is a source under another, in this case,
-the magnetic signal is the sum of both. (iii) In clusters of larger and/or
-deeper particles, although the method individualizes them well, the magnetic
-signal of the neighboring particles can considerably influence the result of
-the inversion. Apparently, there is a direct relationship between the size and depth with the observed errors. It is clear from the cross bars in
-Figure~\ref{P8gMJ9mWpS} that deep particles and/or particles with small radii
-generate worse results essentially because they will produce smaller anomalous
-fields in the magnetic maps. Note nonetheless that even small particles when
-close to the surface are adequately modeled by our method.
+The main limitations observed are: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion.
+Apparently, there is a direct relationship between the dipole intensity and depth with the observed errors.
+It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps.
+Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise.
 
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
-\caption{
-a)
-}
-\label{complex-synthetic-fitting-test}
-\end{figure}
+%\begin{figure}[!htbp]
+%\centering
+%\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
+%\caption{
+%a)
+%}
+%\label{complex-synthetic-fitting-test}
+%\end{figure}
 
-Figure~\ref{RDs2vUEqCI} shows stereoplots with the directions generated by the
-model and the recovered data. The mean directions modeled are coincident with
-the model and the distribution is coincident within the 95\% confidence cone.
-When filtered to include only data with R\textsuperscript{2} \textgreater 0.95
-the obtained directions are closer to the model average and less sparse.
+Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each sources.
+The distribution of the estimated directions are coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
+When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
 
-\begin{figure}[!htbp]
+\begin{figure}[htbp!]
 \centering
@@
 \caption{
-a) Simulation of a thin section of rock with particles uniformly magnetized in
-the average direction of the induced field
-45{\textbackslash}textdegree/45{\textbackslash}textdegree. b) The recovered
-data, without any type of filtering, are sparse, but statistically generate the
-same average direction. c) It is still possible to filter only the directions
-of the magnetic sources with the best fitting determined by the coefficient of
-determination ($R^ 2 \\geq 0.95$) to ensure better grouping of the directions
-around the mean value.
+a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree.
+b) The estimated vector directions without any type of filtering.
+c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.95$) and signal-to-noise ratio (SNR $ \geq 10$).
 }
@@
 magnetic mineral types in this sample, we applied two IRM pulse fields of 2.7 T
-and 0.3 T, respectively toward the +X and -X directions. In this way, the high
-coercivity grains (hematite) would point towards +X and the low coercivity ones
-(magnetite) would align in the -X direction.
+and 0.3 T, respectively toward the +Y and -Y directions. In this way, the high
+coercivity grains (hematite) would point towards +Y and the low coercivity ones
+(magnetite) would align in the -Y direction.
 
@@
 a) The recovered data, without any type of filtering. b) Recovered data
-filtered by the coefficient of determination ($R^ 2 \\geq 0.7$), which shows
+filtered by the coefficient of determination ($R^ 2 \geq 0.7$), which shows
 two clusters of direction located on each pole of the stereogram.
@@
 dipole) and PSD states. The latter happens due to the QDM sensor height being
-usually greater than 5 $\\mu m$, considering a particle on the immediate
-surface of the sample the higher-order moments are already quite attenuated.\}
+usually greater than 5 $\mu m$, considering a particle on the immediate
+surface of the sample the higher-order moments are already quite attenuated.
 

### 2023-03-11 paper/content.tex
Updates from Overleaf

@@
 \begin{enumerate}
-\item Calculate the \textit{total gradient amplitude} (TGA), also known as the
-  3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical
-  component of the magnetic field. The TGA is entirely positive and tends to be
-  more concentrated on top of the magnetic field sources than the observed
-  magnetic field. The derivative calculation also acts as a high-pass filter,
-  removing long-wavelength noise from the data.
-\item Apply a contrast stretching method to re-scale the TGA to a new range
-  defined by the lower and upper percentiles of the data in order to highlight
-  the weaker signals, either coming from small or from deep-seated particles.
-\item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
-  re-scaled TGA data to estimate the position and size of data windows
-  containing the signal of each particle.
+\item Calculate the \textit{total gradient amplitude} (TGA), also known as the 3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical   component of the magnetic field.
+The TGA is entirely positive and tends to be more concentrated on top of the magnetic field sources than the observed magnetic field.
+The derivative calculation also acts as a high-pass filter, removing long-wavelength noise from the data.
+\item Apply a contrast stretching method to re-scale the TGA to a new range   defined by the lower and upper percentiles of the data in order to highlight the weaker signals, either coming from small or from deep-seated particles.
+%\item To enhance the quality of an image before the blob detection, we can also apply a common two-step approach that involves using a median filter and an unsharp mask filter \citep{VanderWalt2014}.
+The median filter reduces high-frequency noise (e.g., salt and pepper noise) in the image at the cost of smoothing slightly the edges, and the unsharp mask filter enhances the contrast and sharpness of edges.
+By applying a median filter followed by an unsharp mask filter, we can significantly improve the visual quality of an image while preserving the edges and the details.
+\item Use the Laplacian of Gaussian (LoG) method \citep{VanderWalt2014} on the   re-scaled TGA data to estimate the position and size of data windows containing the signal of each particle.
 \end{enumerate}
@@
     sources, including the weak central source.
-    e) The detected source bounding boxes (black squares) which correctly
+    e) The detected source bounding boxes (black squares) that correctly
     identify the signal of all four sources.
@@
 
-Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each sources.
-The distribution of the estimated directions are coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
-When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
+Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source.
+The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
+When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
 
@@
 Diamond Microscope (QDM) at Harvard University over a sample section of
-approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{W1GfysVYnX}a) with a grid
+approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
 spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
@@
 Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
-possible to determine the windows for 85 potential sources
-(Figure~\ref{W1GfysVYnX}b).
+possible to determine the windows for 103 potential sources
+(Figure~\ref{real-data}e).
 
@@
 \centering
-\includegraphics[width=1\linewidth]{figures/RealData.png}
+\includegraphics[width=1\linewidth]{figures/real-data.png}
 \caption{
@@
 }
-\label{w1gfysvynx}
+\label{real-data}
 \end{figure}
 
-After applying the ED algorithm, we performed the inversion of the magnetic
-moment for each of the 85 windows selected previously. In order to reduce
-considerably the computation time, the inversions were done within each data
-window, instead of solving all sources parameters at the same time. We obtained
-the magnetic moment (not shown) and the direction for all 85 magnetic grains
-(Figure~\ref{NKOAMThaWA}a). Then, we calculated the residuals of the inversions
-in each window and subsequently the coefficient of determination
-R\textsuperscript{2}, which was used as a filter for the best directions
-obtained. We used a cut-off limit of the coefficient of determination at 0.7
-(Figure~\ref{NKOAMThaWA}b) EXPLICAR PORQUE USOU 0.7 AQUI E 0.95 NOS CASOS
-SINTÉTICOS. This filtering technique removed unreliable responses showing more
-clearly the expected directional clusters of hematite and magnetite crystals.
-NÃO SABEMOS SE OS PONTOS RETIRADOS SÃO `UNRELIABLE RESPONSES'\dots ALÉM DISSO,
-O FILTRO ELIMINA QUASE 50\% DAS FONTES IDENTIFICADAS, O QUE PODE SER UM
-PROBLEMA SE TIVERMOS QUE APLICAR EM OUTROS CASOS REAIS. USAR O TESTE DE
-NÃO-DIPOLARIDADE? TALVEZ SEJA MAIS INTERESSANTE, DADA A DISCUSSÃO QUE SEGUE.
+After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 103 windows selected previously.
+In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time.
+We obtained the magnetic moment and the direction for all 103 magnetic grains (Figure~\ref{real-data-stereograms}a).
+Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
+We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than to 10.
+An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}.
+On the other hand, an SNR of 10 means that the dipolar signal is 10 times greater than the residual noise.
+By using these criteria, we ensured that the fit was sufficiently accurate and that the dipole model provided a reliable approximation of the original magnetic data.
+This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
 
@@
 \centering
-\includegraphics[width=1\linewidth]{figures/RealDataStereo.png}
+\includegraphics[width=1\linewidth]{figures/real-data-stereograms.png}
 \caption{
@@
 }
-\label{nkoamthawa}
+\label{real-data-stereograms}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Additional remarks}
+
+While the windows approach violates the fundamental theory of the inversion problem that requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the one reported by \cite{Weiss2007}.
+The latter involves thresholding the long-distance interaction of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations.
+In contrast to this approach, we employ the windows technique and isolate the main signal of the desired dipole while excluding the rest from the inversion domain.
+This technique allows us to obtain an approximation of the dipole moment components of each source within a few seconds.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 index ($n = 3$) by approximating the sources generating the magnetic anomaly to
-spheres/points, the Euler deconvolution is performed and the central position
+spheres/points, the Euler deconvolution is performed, and the central position
 of each source is determined.
@@
 
-The test using a simple synthetic sample shows the great capability of the
-method by retrieving not only the precise center positions, but also retrieving
-the magnetization directions and intensity even under the considerable effect
-of high-frequency noise (15 nT). While the complex synthetic sample data allows
-observing the applicability of the method developed in real samples that are
-more complex with varied magnetization directions and intensity, in addition to
-also taking into account the high and low-frequency noise and sources with
-variable sizes and depths.
+The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise (20 nT).
+While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable sizes and depths.
 
-The real sample data positively answered the question of the algorithm's
-ability to deal with rocks thin-sections. But also, showed the acceptable
+\textbf{The real sample data positively answered the question of the algorithm's
+ability to deal with rocks thin sections. But also, showed the acceptable
 capacity (within the adequate R$^2$ threshold) of retrieving different
@@
 coercivities and magnetic signal disparities even greater than predicted in the
-complex synthetic test.
+complex synthetic test.}
+
+In our study, we assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
 

### 2023-03-13 paper/content.tex
Updates from Overleaf

@@
 On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data.
-Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}).
+\cite{CortesOrtuno2021} use another approach for the evaluation of the predicted model fit, called signal-to-noise ratio (SNR), here we modified it to be given in decibels (Eq.~\ref{SNR}).
 SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor.
-The higher the SNR (in decibels) values the better it will be the fit of the predicted model.
+The higher the SNR values the better it will be the fit of the predicted model.
 For a signal to be “visible”, \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise.
-Thus, both $R^2$ and SNR techniques are appropriate to be used as criteria filtering for reliability for dipolar inversions.
+Thus, both $R^2$ and the concept of SNR are appropriate to be used as criteria filtering for reliability for dipolar inversions.
 
@@
   \end{center}
-  \caption{Meh}
+  \caption{Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
   \label{tab_synthetic_simple_results}
 \end{table}
-
-\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
-Thus, they consider the Euler deconvolution method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
-This occurs mainly because, when well performed, the recovery of the horizontal coordinates of the source central position is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
 
@@
 For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity.
-The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity range from $10^{-12}$ to $10^{-14}$ $Am^2$.
+The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity ranges from $10^{-12}$ to $10^{-14}$ $Am^2$.
 
@@
 While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, also with standard deviation of 10°.
-Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero means and 50 nT standard deviations, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
+Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and 50 nT standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
 The noise-corrupted synthetic $b_z$ image is shown in Figure~\ref{complex-synthetic-data}a.
@@
 Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
-The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.
+The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 97 particles out of the original 100 were detected.
 
@@
 Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution.
+The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively.
+These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.
 
@@
 \end{figure}
-
-The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively.
-These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.
-The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology.
-Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
-(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
-(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some particles that produce a weak magnetic signal but isolated particles.
-
-The main limitations observed are: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
-(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion.
-Apparently, there is a direct relationship between the dipole intensity and depth with the observed errors.
-It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps.
-Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise.
-
-%\begin{figure}[!htbp]
-%\centering
-%\includegraphics[width=1\linewidth]{figures/complex-synthetic-fitting-test.png}
-%\caption{
-%a)
-%}
-%\label{complex-synthetic-fitting-test}
-%\end{figure}
 
@@
 decays at {\textasciitilde}580 °C and {\textasciitilde}680 °C, and bimodal
-curves of isothermal remanent magnetization (IRM) acquisition (Carmo et al.,
-2019).
+curves of isothermal remanent magnetization (IRM) acquisition \citep{carmo2019speleothem}.
 
@@
 Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
-We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than to 10.
+We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 10.
 An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}.
 On the other hand, an SNR of 10 means that the dipolar signal is 10 times greater than the residual noise.
-By using these criteria, we ensured that the fit was sufficiently accurate and that the dipole model provided a reliable approximation of the original magnetic data.
+By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data.
 This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
@@
 a) The recovered data, without any type of filtering. b) Recovered data
-filtered by the coefficient of determination ($R^ 2 \geq 0.7$), which shows
+filtered by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 10$), which shows
 two clusters of direction located on each pole of the stereogram.
@@
 
-The application of the proposed algorithm to natural samples gives some
-indications of its ability to circumvent the prominent problems described by
-\citep{CortesOrtuno2022} [QUAIS PROBLEMAS FORAM LISTADOS POR CORTÉS-ORTUÑO?],
-namely: (i)\dots, (ii)\dots, (iii)\dots
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
 
-the same authors showed that particles in the single vortex PSD state present
-more accurate inversion results when considering the non-dipole components for
+\subsection{Prior information and uniqueness of solutions}
+% simple synthetic
+Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
+One way to circumvent the ambiguity is incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization.
+Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
+When the position of the source is known, it constrains the model to be as consistent as possible to the observed data, hence increasing the likelihood of obtaining unique solutions.
+\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
+Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
+This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
+This remark is also observed with the our simple synthetic samples where the horizontal positions estimated slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions.
+Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is cause by the ambiguity mentioned before.
+In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the main limitations of the technique.
+
+%complex synthetic
+The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology.
+Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
+(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
+(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
+The main limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion.
+As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
+It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps.
+Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
+
+\subsection{Reliability of dipole moment approximation}
+% real samples
+Our approach relies in the premise of assuming the magnetic anomaly within 
+the data window is a response of a dipolar source. The latter is true when working 
+with particle signals in the SD magnetic domain state, since they are uniform magnetized 
+particles with strong dipolar anomaly. However, \cite{Nagy2017} reported
+that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods
+of time, being the stabler and also with strongly non-dipolar characteristics. 
+Therefore application of the proposed algorithm to natural samples should fail for those PSD
+particles. \cite{CortesOrtuno2022} give important insights about the matter, they 
+showed that PSD state particles present more accurate inversion results when considering the non-dipole components for
 small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
@@
 influence on the particle's magnetic signal. Thus, our approach can be
-considered reasonable for working with particle signals in SD (already a
-dipole) and PSD states. The latter happens due to the QDM sensor height being
+considered reasonable for working with both particle SD and PSD states signals. 
+The latter happens mainly due to the sensor height being
 usually greater than 5 $\mu m$, considering a particle on the immediate
-surface of the sample the higher-order moments are already quite attenuated.
+surface of the sample the higher-order moments are already quite attenuated, thus 
+circumventing the prominent problems described for non-dipolar components.
 
@@
 necessary to keep a check to determine if the inversion reached a satisfactory
-result, such as the coefficient of determination that we used or the
-signal-to-noise ratio presented by \citep{CortesOrtuno2022}.
+result, such as the coefficient of determination and the
+signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Additional remarks}
-
-While the windows approach violates the fundamental theory of the inversion problem that requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the one reported by \cite{Weiss2007}.
-The latter involves thresholding the long-distance interaction of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations.
-In contrast to this approach, we employ the windows technique and isolate the main signal of the desired dipole while excluding the rest from the inversion domain.
-This technique allows us to obtain an approximation of the dipole moment components of each source within a few seconds.
+While the windows approach violates the fundamental theory of the inversion problem that 
+requires the sampled area to be finite and encapsulated by the inversion domain to ensure 
+the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the 
+one reported by \cite{Weiss2007}. The last-mentioned involves thresholding the long-distance interaction 
+of each dipole in the SMM data, which excludes the effect of other dipoles by setting their 
+contribution to zero, resulting in a sparse matrix that permits faster calculations. In contrast 
+to this approach, we employ the TGA map to select the windows and isolate the area containing 
+the main signal of the desired dipole, while the area out of the windows boundaries is less sensible to 
+variation in magnetic parameters of this particular source, hence we exclude them from the inversion 
+domain. This technique allows us to obtain the 3D positioning and an approximation of the dipole moment 
+components of more than a hundred sources within less than two seconds.
 
@@
 We developed an efficient semi-automated method to determine the direction of
-magnetization of dipolar sources on a microscale, as well as the recovery of
+magnetization of dipolar sources on a microscale, as well as the estimate of
 their magnetic moment. Being ideal for a reinterpretation for the application
@@
 determining the positioning of magnetic anomaly sources using a pre-selection
-of magnetic anomaly source windows based on the Laplacian of the Gaussian
+of magnetic anomaly source windows based on the Laplacian of Gaussian
 applied to total gradient anomaly maps. In this way, reducing the numerous
@@
 spheres/points, the Euler deconvolution is performed, and the central position
-of each source is determined.
+of each source is determined. Due to the similarity with aeromagnetic data, this
+approach can also be extrapolated for macro-scale studies.
 
-The recovery of direction and magnetization we only need to assume that the
+To recover magnetic direction and moment we only need to assume that the
 sources have their central positions known (so we apply Euler deconvolution)
-and that their magnetizations are uniform. This last premise aligns with the
+and that their magnetization are uniform. This last premise aligns with the
 theory of magnetically stable particles SD (and the PSD ones at a reasonable
@@
 
-The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise (20 nT).
+The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
 While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable sizes and depths.
-
-\textbf{The real sample data positively answered the question of the algorithm's
-ability to deal with rocks thin sections. But also, showed the acceptable
-capacity (within the adequate R$^2$ threshold) of retrieving different
-magnetization directions recorded by magnetic minerals with different
-coercivities and magnetic signal disparities even greater than predicted in the
-complex synthetic test.}
-
-In our study, we assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
+The real sample data positively answered the question of the algorithm's ability to deal with rocks thin sections.
+But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
+We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
 

### 2023-03-14 paper/content.tex
Add changes to the paper manuscript

@@
 
-The second model contains one hundred spheres with different radii and magnetization intensities but magnetized in a similar direction within one standard deviation.
+The second model contains one hundred spheres with different magnetization intensities magnetized in two stable directions and similar standard deviation.
 The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
@@
 Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
-The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 97 particles out of the original 100 were detected.
+The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.
 
@@
 
-Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 97 particles that were identified and the model fitting tests.
+Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 98 particles that were identified and the model fitting tests.
 Firstly, we evaluate the magnetic direction misfits by calculating the module of the angular difference between the true and the estimated magnetization vectors (Fig.~\ref{complex-synthetic-comparison}a).
@@
 \caption{
-a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree.
-b) The estimated vector directions without any type of filtering.
-c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.95$) and signal-to-noise ratio (SNR $ \geq 10$).
+a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized (dipolar sources) in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree.
+b) The estimated vector directions without filtering.
+c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.85$) and signal-to-noise ratio (SNR $ \geq 5$).
 }
@@
 \caption{
-a) Real sample data. b) Individual sources' window position (yellow squares)
-obtained with the blob detection algorithm applied on the total gradient map.
+    a) The real sample vertical component magnetic data $b_z$ observations at 
+    $z = \qty{5}{\micro\meter}$. 
+    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    c) The total gradient amplitude (TGA) calculated from the 
+    upward-continued data. 
+    d) The contrast-stretched TGA.
+    e) The detected source bounding boxes (black squares) that correctly
+    encapsulate the main signal of the sources.
+    f) The estimated source locations (colored circles) from Euler 
+    Deconvolution of the upward-continued data inside each bounding box. 
+    The color represents the estimated $z$ coordinates.
   }
@@
 Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
-We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 10.
+We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5.
 An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}.
-On the other hand, an SNR of 10 means that the dipolar signal is 10 times greater than the residual noise.
+On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise.
 By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data.
@@
 \caption{
-a) The recovered data, without any type of filtering. b) Recovered data
-filtered by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 10$), which shows
-two clusters of direction located on each pole of the stereogram.
+a) The estimated directions without filtering.
+b) Estimated directions filtered by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 5$), which shows two clusters of direction located on each pole of the stereogram.
 }
@@
 \end{figure}
-
-NESSA PARTE SERIA INTERESSANTE INCLUIR MAPAS COMO OS DA FIGURA 4B E 4C, COM A
-ESPACIALIDADE DOS AJUSTES E DISCUTIR DA SEGUINTE FORMA:
-
-\begin{enumerate}
-\item RESULTADOS EM FUNÇÃO DA QUALIDADE DO AJUSTE
-\item RESULTADOS EM FUNÇÃO DA DIPOLARIDADE DAS FONTES
-\item CONTEXTUALIZAR O SEU MÉTODO EM RELAÇÃO A OUTROS. COMO OS OUTROS ESTIMAM
-  OS MISFITS? QUE FILTROS USAM? QUAL A DIFERENÇA COM SUA ABORDAGEM? POR
-  ENQUANTO SOMENTE O TRABALHO DE CORTEZ ESTÁ COMENTADO -> COMPARAR COM
-  OS OUTROS MÉTODOS DE INVERSÃO (Fu, de Groot, Egli2000, Lima2007)
-\end{enumerate}
 
@@
 
-The image rescaling and blob detection though the Laplacian of Gaussian method
-were performed with the scikit-image library \citep{VanderWalt2014}. CITE OTHER
-SOFTWARE TOOLS USED. Matplotlib for figures, numpy and scipy for almost
-everything. Verde for the regional residual separation and other things.
+The image re-scaling and blob detection though the Laplacian of Gaussian method
+were performed with the scikit-image library \citep{VanderWalt2014}.
+We also used Matplotlib \citep{Hunter2007} for plotting the figures, numpy \citep{Harris2020} and scipy \citep{2020SciPy-NMeth} for all performed calculations.
+Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}.
+The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems.
+Loops were parallelized with the aid of Numba just-in-time compilation \citep{lam2015numba}.
+Lastly, the xarray library \citep{hoyer2017xarray} offered a fast and powerful tool to work with multi-dimensional datasets allowing an easy way to alteration, visualization and extraction of data with advanced indexing techniques.
 
@@
 \section{Acknowledgements}
-
-We are indebted to the developers and maintainers of the open-source software
-without which this work would not have been possible.
+This research project was supported by the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) - grant 162704/2021-6 and by the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) - grant 2021/08379-5, the opinions, hypotheses and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP.
+We also acknowledge the support of the Royal Society \textcolor{red}{[insert grant number]} for this research project.
+We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.

### 2023-03-17 paper/content.tex
Add changes in the paper manuscript

@@
 This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
+Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite outnumbers the hematite.
 
@@
 
-\subsection{Prior information and uniqueness of solutions}
-% simple synthetic
+\subsection{Prior Information and Uniqueness of Solutions}
 Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
@@
 When the position of the source is known, it constrains the model to be as consistent as possible to the observed data, hence increasing the likelihood of obtaining unique solutions.
-\citet{Oliveira2015Estimation} proved that the magnetization directions (D and I) recovered by the least squares estimator are sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
+\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
 Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
 This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
-This remark is also observed with the our simple synthetic samples where the horizontal positions estimated slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions.
-Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is cause by the ambiguity mentioned before.
-In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the main limitations of the technique.
+This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions.
+Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is probably caused by the ambiguities.
+In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the ED's main limitations.
 
-%complex synthetic
-The application in complex synthetic data allows observing the strengths and limitations of the proposed methodology.
-Some of the strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
-(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are high (e.g., $\geq 0.95$ and $\geq 10$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
+\subsection{A Critical Examination of Windows Approach}%: Identifying its Strengths and Limitations}
+
+Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
+In the first type of approach the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions and non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial  \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
+This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
+However, this assumption is not always true when dealing with complex samples with a magnetic mineral fabric with more than one stable directions, which leads to the same drawbacks as the classic paleomagnetic measurements using bulk sample.
+The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as microcomputed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021} .
+The latter further allows uniquely estimation of dipolar magnetic configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
+Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with microCT weaknesses.
+The MicroCT is a popular non-destructive technique for high resolution imaging of materials internal structures, and yet, it is accompanied of some limitations when it comes to the paleomagnetic studies: firstly, the technique has spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained the single-domain magnetite (Cnudde et al., 2006; Cnudde & Boone, 2013, de Groot 2018).
+The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation (Cnudde & Boone, 2013).
+But, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
+
+Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of mechanically select cropped data or the needing any type of additional information.
+However, to better examine its advantages and disadvantages we first need to point out the strengths and weaknesses of the technique used in the detection of sources,  The Laplacian of Gaussian (LoG) kernel (Marr and Hildreth (XXXX)).
+The LoG is a computer imaging technique that is able to identify regions where the intensity changes abruptly by convolving the image with a LoG filter, resulted of a combination of the Gaussian blur and Laplacian filter (CITE BOOK).
+The Laplacian filter is able to highlight the regions where the intensity changes in a rapidly way.
+On the other hand, the Gaussian blur is a smoothing filter for high-frequency noise, which reduces the likelihood to generate artifacts.
+Hence, the result of this LoG operation can identify blobs as regions above a certain threshold, this threshold crossing determines what are brighter spots (local maxima) surrounded by a darker background.
+It is also scale-invariant by detecting blobs of different sizes and intensities, a feature achieved by varying the sizes of the Gaussian filter.
+The advantages of the methodology are: (i) high-accuracy blob detection; (ii) scale-invariant for images with different intensities/sizes objects; while also being (iii) robust to the presence of noise due to the Gaussian smoothing filter.
+While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time consuming when dealing with larger images and (ii) the requirement of parameters adjustment, such as the threshold and the kernel sizes.
+
+The total gradient anomaly (TGA) might be considered the ideal image to be used as input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale).
+The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges.
+This technique is widely used in aeromagnetic surveys to determine sources’ boundaries by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
+Hence.
+The application for micromagnetic measurements comes with all the advantages and drawbacks previous mentioned, nonetheless the windows generated isolate the main magnetic signal’s region of each source.
+This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.
+
+The complex synthetic data allows a better observation of the strengths and limitations of the windows approach.
+The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
+(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
 (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
-The main limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
 (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion.
+(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
 As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
@@
 
-\subsection{Reliability of dipole moment approximation}
-% real samples
+\subsection{Reliability of Dipole Moment Approximation}\label{dipole-reliability}
+
 Our approach relies in the premise of assuming the magnetic anomaly within 
@@
 necessary to keep a check to determine if the inversion reached a satisfactory
-result, such as the coefficient of determination and the
+prediction, such as the coefficient of determination and the
 signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.
@@
 and that their magnetization are uniform. This last premise aligns with the
-theory of magnetically stable particles SD (and the PSD ones at a reasonable
-sensor height), which is the basis of classical paleomagnetism. Also, there is
+theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable
+sensor-sample height, which is the basis of classical paleomagnetism. Also, there is
 no need for any kind of prior knowledge other than the observed magnetic
@@
 
-The test using a simple synthetic sample shows the great capability of the method by retrieving not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
-While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable sizes and depths.
+The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
+While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
 The real sample data positively answered the question of the algorithm's ability to deal with rocks thin sections.
@@
 The image re-scaling and blob detection though the Laplacian of Gaussian method
-were performed with the scikit-image library \citep{VanderWalt2014}.
-We also used Matplotlib \citep{Hunter2007} for plotting the figures, numpy \citep{Harris2020} and scipy \citep{2020SciPy-NMeth} for all performed calculations.
+were performed with the Scikit-image library \citep{VanderWalt2014}.
+We also used Matplotlib \citep{Hunter2007} for plotting the figures and Mplstereonet \citep{xxxxx} for stereograms.
+Basic calculations were performed using Numpy \citep{Harris2020} and Scipy \citep{2020SciPy-NMeth}.
 Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}.
@@
 Loops were parallelized with the aid of Numba just-in-time compilation \citep{lam2015numba}.
-Lastly, the xarray library \citep{hoyer2017xarray} offered a fast and powerful tool to work with multi-dimensional datasets allowing an easy way to alteration, visualization and extraction of data with advanced indexing techniques.
+Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful tool for working with multi-dimensional datasets allowing an easy way of data visualization and extraction with advanced indexing techniques.
 
-The QDM image data is available at CITE A DATAVERSE/FIGSHARE ARCHIVE under the
-CC-XX license.
+The QDM image data is available at \textcolor{red}{CITE A DATAVERSE/FIGSHARE ARCHIVE under the CC-XX license}.
 
@@
 This research project was supported by the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) - grant 162704/2021-6 and by the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) - grant 2021/08379-5, the opinions, hypotheses and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP.
-We also acknowledge the support of the Royal Society \textcolor{red}{[insert grant number]} for this research project.
+We also acknowledge the support of the Royal Society ex \textcolor{red}{[insert grant number]} for this research project.
 We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.

### 2023-04-03 code/micromag.py
Change the stereoplots and add predicted data visualization

@@ -427,17 +427,20 @@ def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, ad
         scale=15,
         headlength=3, 
         headaxislength=3,
+        edgecolor='k',
+        linewidth = 0.35,
     )
     
     args.update(kwargs)
-    dir_quiver = ax.quiver(*positions[:2], u, v, color, **args)
+    dir_quiver = ax.quiver(*positions[:2], u, v, color, **args, zorder=1)
     
     # Make headless vectors at 90° to represent the amplitude
-    scale = amplitude / amplitude.max()
+    threshold_scale = abs(np.log10(amplitude))
+    scale = abs(threshold_scale-threshold_scale.max())/6 #amplitude / amplitude.max()
     angle = np.radians(declination + 90)
     u, v = scale * np.sin(angle), scale * np.cos(angle)    
     args.update(headlength=0, headwidth=1, headaxislength=0)
-    amp_quiver = ax.quiver(*positions[:2], u, v, color, **args)
+    amp_quiver = ax.quiver(*positions[:2], u, v, color, **args, zorder=0)
     
     if add_colorbar:
         plt.colorbar(dir_quiver, ax=ax, label="inclination (°)")

### 2023-04-03 paper/content.tex

@@
 \item Apply a contrast stretching method to re-scale the TGA to a new range   defined by the lower and upper percentiles of the data in order to highlight the weaker signals, either coming from small or from deep-seated particles.
-%\item To enhance the quality of an image before the blob detection, we can also apply a common two-step approach that involves using a median filter and an unsharp mask filter \citep{VanderWalt2014}.
-The median filter reduces high-frequency noise (e.g., salt and pepper noise) in the image at the cost of smoothing slightly the edges, and the unsharp mask filter enhances the contrast and sharpness of edges.
-By applying a median filter followed by an unsharp mask filter, we can significantly improve the visual quality of an image while preserving the edges and the details.
 \item Use the Laplacian of Gaussian (LoG) method \citep{VanderWalt2014} on the   re-scaled TGA data to estimate the position and size of data windows containing the signal of each particle.
@@
 \begin{bmatrix}
-{b_z}_1 \\ {b_z}_2 \\ \vdots \\ {b_z}_L
+{b_z}_1 \\ {b_z}_2 \\ \vdots \\ {b_z}_N
 \end{bmatrix}
@@
 \noindent
-The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so
+The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so \citep{Tauxe2018}
 
@@
 \begin{aligned}
-I &= \tan^{-1}\left(\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}}\right) \ , \\
-D &= \tan^{-1}\left(\dfrac{m_x}{m_y}\right) \ , \\
+I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
+D &= \tan^{-1}\dfrac{m_x}{m_y} \ , \\
 m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
@@
 
+\noindent
 It is important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system.
@@
 In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies, and sensor limitations.
-This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used.
-Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples.
-Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).
+This noise will affect the estimated parameter vector $\mathbf{\hat{m}}$, regardless of the method used.
+Assuming that the noise in the observed data is independent and normally distributed with zero mean and variance ${\sigma_0}^2$, we can estimate the variance of the parameters by propagation of uncertainties.
+In reality, the data variance  ${\sigma_0}^2$ is rarely known and must be estimated using the $\chi^2$ statistic \citep{Aster2019}
 
 \begin{equation}
-  \label{chi_square}
-\begin{aligned}
-\large \sigma_0^2 = {\chi}^2 = \frac{\sum{\left( b_z - {b_{z}}_{dipole} \right)}^2}{N-m}
-\end{aligned}
+\label{eq_chi_square}
+\hat{\sigma}_0^2 = {\chi}^2 = \dfrac{\|\mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}\|^2}{N - 3}\ ,
 \end{equation}
 
+\noindent
+in which $N - 3$  are the degrees-of-freedom. 
+The covariance matrix $\mathbf{C}$ of the estimated parameters is then given by \citep{Aster2019}
+
 \begin{equation}
-\label{lPOQaqlV3N}
-\mathbf{C} =
+\label{eq_covariance}
+\mathbf{C} 
+=
+\hat{\sigma}_0^2 (\mathbf{A}^T\mathbf{A})^{-1}
+=
 \begin{bmatrix}
@@
 \end{bmatrix}
-=
-\sigma_0^2 (\mathbf{A}^T\mathbf{A})^{-1}
+\ .
 \end{equation}
 
-From the main diagonal of $\mathbf{C}$ we can obtain the variances of the
-declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
-by the propagation of uncertainties
+\noindent 
+From the main diagonal of $\mathbf{C}$, we can obtain the variances of the 
+estimated declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
+by propagation of uncertainties from Equation~\ref{eq_vector_to_incdec}
 
 \begin{equation}
-\label{uncertanties}
+\label{eq_variances}
 \begin{aligned}
@@
 
-It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters.
-\cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}).
-The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data.
-On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data.
-\cite{CortesOrtuno2021} use another approach for the evaluation of the predicted model fit, called signal-to-noise ratio (SNR), here we modified it to be given in decibels (Eq.~\ref{SNR}).
-SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor.
-The higher the SNR values the better it will be the fit of the predicted model.
-For a signal to be “visible”, \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise.
-Thus, both $R^2$ and the concept of SNR are appropriate to be used as criteria filtering for reliability for dipolar inversions.
+Parameters retrieved during inversion procedures may not always explain the observed data perfectly.
+Hence, it is necessary to evaluate how well the predicted data is able to fit the observed data. 
+When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``non-dipolarity parameter'' ($D$). 
+We note that $D$ is equivalent to the coefficient of determination
 
 \begin{equation}
-\label{R2}
-\begin{aligned}
-\large R^2 = 1 - \frac{ \sum{\left( b_z - {b_{z}}_{dipole} \right)}^2 }{\sum{\left( b_z - \bar{b_z} \right)}^2}
-\end{aligned}
+\label{eq_r2}
+R^2 = 1 - \dfrac{\|\mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}\|^2}{\|\mathbf{d}^o - \bar{b}_z^o\|^2}\ ,
 \end{equation}
 
+\noindent
+in which $\bar{b}_z^o$ is the mean of the observed data.
+$R^2$ has a maximum value of 1, which indicates a perfect fit of the data. 
+Values close to 1 can therefore be interpreted to mean that a simple dipole model is able to explain the observed data. 
+On the other hand, low values of $R^2$ indicate that the dipole model is not able to explain the observed data.
+
+\citet{CortesOrtuno2021} use the ``signal-to-noise ratio'' (SNR) to evaluate the goodness of fit. 
+Here, we define the SNR in a logarithmic decibel scale to make it independent of the scale of the data
+
 \begin{equation}
-\label{SNR}
-\begin{aligned}
-\large SNR = 10 \log_{10}{\left( \frac{{{\sigma}^2}_{dipole}}{{{\sigma}^2}_{residual}} \right)}
-\end{aligned}
+\label{eq_snr}
+\text{SNR} = 10 \log_{10}\dfrac{\sigma^2_d}{\sigma^2_r}\ ,
 \end{equation}
+
+\noindent
+in which $\sigma^2_d$ is the variance of the observed data and $\sigma^2_r$ is the variance of the residuals $\mathbf{r} = \mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}$.
+The SNR is the trade-off between the signal and its associated noise, which we approximate by the inversion residuals. 
+The higher the SNR values (in decibels), the better the fit to the observed data. 
+For a signal to be ``visible'', \citet{Strum2014} suggest that $\text{SNR} \ge 3$, which means the signal is at least three times stronger than the noise.
+Here, we'll use both $R^2$ and SNR as criteria for filtering out unreliable estimates from our dipole moment inversions.
 
@@
 
-The first synthetic model was performed by generating the vertical magnetic field derived from a simple set of four spheres with similar magnetization intensity and radius, but completely different magnetization directions, contaminated by high-frequency noise.
-This simplified test model is basically done to investigate the efficiency of the inversions used for Euler positioning and magnetization parameters, thus being a validation of the methodology.
+The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise.
+The purpose of this model is to investigate the efficiency of the combination of Euler Deconvolution and the dipole moment inversion, thus being a validation of the methodology.
 
-The second model contains one hundred spheres with different magnetization intensities magnetized in two stable directions and similar standard deviation.
+The second model contains 100 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions. 
 The magnetic field generated from these sources is corrupted by both low and high-frequency noise. 
@@
   \caption{
-    Synthetic data and the various processing steps performed prior to the
-    dipole moment inversion. 
+    Simple synthetic data and the various processing steps performed prior to the dipole moment inversion. 
     a) The synthetic noise-corrupted $b_z$ observations at 
@@
 
-The Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four uniformly magnetized spherical sources.
-The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$ with data points in a regular grid of approximate \qty{1}{\um} ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}.
-The magnetic field data is contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and \qty{20}{\nano\tesla} standard deviation.
+Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four dipolar sources.
+The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$, with data points in a regular grid with approximately \qty{1}{\um} spacing ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}.
+The magnetic field data are contaminated with pseudo-random Gaussian noise with zero mean and \qty{20}{\nano\tesla} standard deviation.
 
-We first applied an upward continuation filter (Fig.~\ref{fig_synthetic_simple_data}b) to smooth out high-frequency noise \citep{Blakely1996}, since it strongly affects the first derivatives of the potential field required by the Euler equation.
-Then, we calculated the magnetic total gradient anomaly map (Fig.~\ref{fig_synthetic_simple_data}c), which is subjected to a stretch contrast filter to highlight as much as possible the weaker intensity sources (Fig.~\ref{fig_synthetic_simple_data}d),
-in order to facilitate the next step.
-Subsequently, we applied the blob detection algorithm to the contrasted total gradient map to obtain the position of the data window for each source (Fig.~\ref{fig_synthetic_simple_data}e).
-The ED was performed for each selected source by assuming the structural index of a sphere/punctual source, therefore obtaining the Cartesian coordinates (Fig.~\ref{fig_synthetic_simple_data}f) of each source causing the magnetic potential anomaly in the observed data set (Table~\ref{tab_synthetic_simple_results}).
+We first applied an upward continuation filter (Figure~\ref{fig_synthetic_simple_data}b) to smooth out the high-frequency noise \citep{Blakely1996}.
+This is important because it strongly affects the first derivatives of the field, which are required for the Euler Deconvolution. 
+Then, we calculated the total gradient amplitude (Figure~\ref{fig_synthetic_simple_data}c), which was then subjected to contrast stretching to highlight as much as possible the weaker intensity sources (Figure~\ref{fig_synthetic_simple_data}d).
+Subsequently, we applied the blob detection algorithm to the contrast-stretched total gradient amplitude to obtain the position of the data windows for each source (Figure~\ref{fig_synthetic_simple_data}e).
+Euler Deconvolution was then performed for each data window identified by assuming a structural index $\eta = 3$ of a point source, therefore obtaining the Cartesian coordinates (Figure~\ref{fig_synthetic_simple_data}f) of each source.
+Table~\ref{tab_synthetic_simple_results} shows the true and estimated values of the source coordinates for comparison.
 
@@
 
-The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field.
-The inversion produced a least squares approximation solution for the vector of Cartesian magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}).
-We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in Table~\ref{tab_synthetic_simple_results}.
+The positions of each source obtained with Euler Deconvolution were used as an input parameter for the dipole moment inversion. 
+The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
+Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.
 
-\begin{table}[t]
+\begin{table}[tb]
   \begin{center}
@@
   \end{center}
-  \caption{Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
+  \caption{
+  True and estimated source positions and dipole moments for the simple synthetic data application.
+  Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
   \label{tab_synthetic_simple_results}
@@
 
-This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu m$.
-The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance.
-For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity.
-The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity ranges from $10^{-12}$ to $10^{-14}$ $Am^2$.
+This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$. 
+The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance. 
+We contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and $\qty{50}{\nano\tesla}$ standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
 
-To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that vary individually but average out to the inducing field direction.
-The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 10°.
-While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, also with standard deviation of 10°.
-Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and 50 nT standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.
-The noise-corrupted synthetic $b_z$ image is shown in Figure~\ref{complex-synthetic-data}a.
+For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensities. 
+The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-12}$ to $\qty{e-14}{\ampere\m\squared}$. 
+The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
+To simulate this behaviour in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions. 
+The first group of sources ($M = 70$) are sampled from a distribution  with mean of $D = \ang{0}$ and $I = \ang{0}$ and standard deviation of $\ang{10}$. 
+The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$. 
+The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.
 
-\begin{figure}[t]
+\begin{figure}[tb!]
   \centering
@@
   \caption{
+    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
     a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at 
@@
 
-Since now the data have both high and low-frequency noise, we performed a $5^{th}$ degree polynomial fitting to remove the low-frequency wavelength from the signal.
-Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b).
-Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e).
-The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.
+Since now the data have both high and low-frequency noise, we first fit a $5^{th}$ degree polynomial to the data to remove the low-frequency noise. 
+We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
+TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
+A total of 98 sources out of the original 100 were successfully detected by our workflow.
 
-The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
-Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution.
-The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively.
-These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.
-
-Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 98 particles that were identified and the model fitting tests.
-Firstly, we evaluate the magnetic direction misfits by calculating the module of the angular difference between the true and the estimated magnetization vectors (Fig.~\ref{complex-synthetic-comparison}a).
-Afterward, we calculate the dipole moment misfits in percentage (~$|~100 \left( m_{true} - m_{estimate}\right)~/~\left(m_{true}\right)~|$~), as shown in Figure~\ref{complex-synthetic-comparison}b).
-Then, the fitting tests were performed using the equations~\ref{R2}-~\ref{SNR} in an attempt to select which criterion best separates data with good fitting and low errors of direction and dipole moment.
-Figure~\ref{complex-synthetic-comparison}c shows the R² coefficient, or the \emph{D} parameter of the non-dipolarity test \citep{Fu2020}, representing how well the dipolar model is able to explain the observed data in the given window.
-On the other hand, the SNR is capable to express the power of the predicted model over its residual, therefore can select which sources are more "visible" by the sensor (Fig.~\ref{complex-synthetic-comparison}d).
-Consequently yielding results directly proportional to the R² coefficient.
-
-\begin{figure}[htbp!]
+\begin{figure}[tb!]
 \centering
@@
 
-Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source.
-The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
-When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
+The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
+Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
+Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 98 sources that were identified and the differences between the estimated dipole moments and the true values.
+The depth and dipole moment amplitude of each source are represented by horizontal and vertical bars, respectively. 
+These two variables are useful proxies for the strength and spatial extent of the signal of each source,
+which can tell us about the limitations in strengths and sizes of the source signal that the technique is able to correctly invert.
+Figure~\ref{complex-synthetic-comparison}a shows the absolute value of the angular difference between the true and the estimated dipole moment vectors. 
+Figure~\ref{complex-synthetic-comparison}b shows the percentage difference between the true and estimated dipole moment magnitudes ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$). 
+Figure~\ref{complex-synthetic-comparison}c shows the $R^2$ coefficient (Equation~\ref{eq_r2}), which is equivalent to the non-dipolarity parameter of \citet{Fu2020} and represents how well the dipolar model is able to explain the observed data of each source.
+Figure~\ref{complex-synthetic-comparison}d shows the SNR (Equation~\ref{eq_snr}), which expresses the power of the observed data over that of the inversion residuals.
+High SNR values correspond to small inversion residuals which indicate that a dipolar model was able to explain the observed data.
+Consequently, the variation of SNR values is similar to that of the $R^2$ coefficient.
+Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
+Conversely, the correlation between errors in dipole moment magnititude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a good fit of the dipolar model.
+It is also noticeable that the majority of cases where the dipole moment direction error is large are associated with deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
+These results indicated that $R^2$ and SNR can be used as selection criteria to discard sources with likely high errors in the estimated dipole moment.
 
-\begin{figure}[htbp!]
+\begin{figure}[tb!]
 \centering
@@
 \end{figure}
+
+Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source.
+The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
+When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
 
@@
 
-\begin{figure}[tb]
+\begin{figure}[tb!]
 \centering
@@
 
-\subsection{Prior Information and Uniqueness of Solutions}
+\subsection{Prior information and uniqueness of solutions}
+
 Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
@@
 This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
-This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies very little misfits in the recovered magnetic directions.
-Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is probably caused by the ambiguities.
-In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise, since that high-frequency noise sensibility is one of the ED's main limitations.
+This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
+Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is probably caused by ambiguities. 
+In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.
 
-\subsection{A Critical Examination of Windows Approach}%: Identifying its Strengths and Limitations}
+\subsection{A critical examination of the source detection}
 
 Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
-In the first type of approach the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions and non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial  \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
+In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
 This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
-However, this assumption is not always true when dealing with complex samples with a magnetic mineral fabric with more than one stable directions, which leads to the same drawbacks as the classic paleomagnetic measurements using bulk sample.
-The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as microcomputed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021} .
-The latter further allows uniquely estimation of dipolar magnetic configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
-Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with microCT weaknesses.
-The MicroCT is a popular non-destructive technique for high resolution imaging of materials internal structures, and yet, it is accompanied of some limitations when it comes to the paleomagnetic studies: firstly, the technique has spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained the single-domain magnetite (Cnudde et al., 2006; Cnudde & Boone, 2013, de Groot 2018).
-The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation (Cnudde & Boone, 2013).
+However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
+The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}.
+The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
+Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used. 
+The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of materials' internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
+The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
 But, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
 
-Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of mechanically select cropped data or the needing any type of additional information.
-However, to better examine its advantages and disadvantages we first need to point out the strengths and weaknesses of the technique used in the detection of sources,  The Laplacian of Gaussian (LoG) kernel (Marr and Hildreth (XXXX)).
-The LoG is a computer imaging technique that is able to identify regions where the intensity changes abruptly by convolving the image with a LoG filter, resulted of a combination of the Gaussian blur and Laplacian filter (CITE BOOK).
-The Laplacian filter is able to highlight the regions where the intensity changes in a rapidly way.
+Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of mechanically selecting cropped data or needing any type of additional information.
+However, to better examine its advantages and disadvantages we first need to point out the strengths and weaknesses of the technique used in the detection of sources, the Laplacian of Gaussian (LoG) kernel \citep{Marr1980}.
+The LoG is a computer imaging technique that is able to identify regions where the intensity changes abruptly by convolving the image with the LoG filter, and is the result of the combination of the Gaussian blur and Laplacian filter \citep{gonzalez2018}.
+The Laplacian filter is able to highlight the regions where the intensity changes rapidly. 
 On the other hand, the Gaussian blur is a smoothing filter for high-frequency noise, which reduces the likelihood to generate artifacts. 
@@
 It is also scale-invariant by detecting blobs of different sizes and intensities, a feature achieved by varying the sizes of the Gaussian filter. 
-The advantages of the methodology are: (i) high-accuracy blob detection; (ii) scale-invariant for images with different intensities/sizes objects; while also being (iii) robust to the presence of noise due to the Gaussian smoothing filter.
-While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time consuming when dealing with larger images and (ii) the requirement of parameters adjustment, such as the threshold and the kernel sizes.
+The advantages of the methodology are (i) high-accuracy blob detection; (ii) scale-invariant for images with different intensities/sizes of objects; while also being (iii) robust to the presence of noise due to the Gaussian smoothing filter.
+While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time-consuming when dealing with larger images and (ii) the requirement of parameters adjustment, such as the threshold and the kernel sizes.
 
@@
 This technique is widely used in aeromagnetic surveys to determine sources’ boundaries by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
-Hence.
-The application for micromagnetic measurements comes with all the advantages and drawbacks previous mentioned, nonetheless the windows generated isolate the main magnetic signal’s region of each source.
+Hence. The application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window. 
+Nonetheless, the windows generated isolate the main magnetic signal’s region of each source. 
 This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.
 
-The complex synthetic data allows a better observation of the strengths and limitations of the windows approach.
+The complex synthetic data allows better observation of the strengths and limitations of the windows approach. 
 The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
-(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Fig.~\ref{complex-synthetic-comparison}b) when R\textsuperscript{2} and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Fig.~\ref{complex-synthetic-comparison}c-d).
+(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
 (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal. 
@@
 As expected, there is a direct relationship between the dipole intensity and depth with the observed errors. 
-It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce smaller anomalous fields in the magnetic maps.
-Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
+It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce weaker anomalous fields in the magnetic maps.
+Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near to the sensor.
 
-\subsection{Reliability of Dipole Moment Approximation}\label{dipole-reliability}
+\subsection{Reliability of dipole moment approximation}
+\label{dipole-reliability}
 
 Our approach relies in the premise of assuming the magnetic anomaly within 
-the data window is a response of a dipolar source. The latter is true when working 
-with particle signals in the SD magnetic domain state, since they are uniform magnetized 
-particles with strong dipolar anomaly. However, \cite{Nagy2017} reported
-that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods
-of time, being the stabler and also with strongly non-dipolar characteristics. 
-Therefore application of the proposed algorithm to natural samples should fail for those PSD
-particles. \cite{CortesOrtuno2022} give important insights about the matter, they 
-showed that PSD state particles present more accurate inversion results when considering the non-dipole components for
-small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor
-distances the dipole as approximations are remarkably accurate, as the
-higher-order moments decay rapidly with distance and therefore have less
-influence on the particle's magnetic signal. Thus, our approach can be
-considered reasonable for working with both particle SD and PSD states signals. 
-The latter happens mainly due to the sensor height being
-usually greater than 5 $\mu m$, considering a particle on the immediate
-surface of the sample the higher-order moments are already quite attenuated, thus 
-circumventing the prominent problems described for non-dipolar components.
+the data window is a response of a dipolar source. 
+The latter is true when working 
+with particle signals in the SD magnetic domain state since they are uniform magnetized particles with strong dipolar anomalies. 
+However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
+Therefore application of the proposed algorithm to natural samples should fail for those PSD particles. 
+\cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
+influence on the particle's magnetic signal. 
+Thus, our approach can be considered reasonable for working with both particle SD and PSD states signals. 
+The latter happens mainly due to the sensor height being usually greater than 5 $\mu m$, considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components.
 
-Despite the excellent signal/noise ratio that the SMM provided with the
+Despite the excellent signal-to-noise ratio that the SMM provided with the
 proximity of the sensor to the sample, it is worth mentioning that the
 measurement noise can still overshadow the responses of very weak/small, or
-deep particles, generating unreliable inversion results. Therefore, it is
-necessary to keep a check to determine if the inversion reached a satisfactory
-prediction, such as the coefficient of determination and the
+deep particles, generating unreliable inversion results. 
+Therefore, it is necessary to keep a check to determine if the inversion reached a satisfactory prediction, such as the coefficient of determination and the
 signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.
 
-While the windows approach violates the fundamental theory of the inversion problem that 
-requires the sampled area to be finite and encapsulated by the inversion domain to ensure 
-the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the 
-one reported by \cite{Weiss2007}. The last-mentioned involves thresholding the long-distance interaction 
-of each dipole in the SMM data, which excludes the effect of other dipoles by setting their 
-contribution to zero, resulting in a sparse matrix that permits faster calculations. In contrast 
-to this approach, we employ the TGA map to select the windows and isolate the area containing 
-the main signal of the desired dipole, while the area out of the windows boundaries is less sensible to 
-variation in magnetic parameters of this particular source, hence we exclude them from the inversion 
-domain. This technique allows us to obtain the 3D positioning and an approximation of the dipole moment 
-components of more than a hundred sources within less than two seconds.
+While the windows approach violates the fundamental theory of the inversion problem that  requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the  one reported by \cite{Weiss2007}.
+The last-mentioned involves thresholding the long-distance interaction 
+of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations. 
+In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensible to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
+This technique allows us to obtain the 3D positioning and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associate with the blob detection process.
 
@@
 
-We developed an efficient semi-automated method to determine the direction of
-magnetization of dipolar sources on a microscale, as well as the estimate of
-their magnetic moment. Being ideal for a reinterpretation for the application
-of methods of paleomagnetic studies using thin sections of rock samples. This
-would be an attempt to improve the quality of results obtained by isolating the
-responses of more reliable recorders of the Earth's geomagnetic field.
+We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the estimate of their magnetic moment. 
+Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples. 
+This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
 
-We also present a new, faster, and cleaner way to solve the Euler equation in
-determining the positioning of magnetic anomaly sources using a pre-selection
-of magnetic anomaly source windows based on the Laplacian of Gaussian
-applied to total gradient anomaly maps. In this way, reducing the numerous
-solutions to just one data window per source. After estimating the structural
-index ($n = 3$) by approximating the sources generating the magnetic anomaly to
-spheres/points, the Euler deconvolution is performed, and the central position
-of each source is determined. Due to the similarity with aeromagnetic data, this
-approach can also be extrapolated for macro-scale studies.
+We also present a new, faster, and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of Gaussian applied to total gradient anomaly maps.
+In this way, reducing the numerous solutions to just one data window per source. 
+After estimating the structural index ($n = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler Deconvolution is performed, and the central position of each source is determined.
+Due to the similarity with aeromagnetic data, this approach can also be extrapolated for macro-scale studies.
 
-To recover magnetic direction and moment we only need to assume that the
-sources have their central positions known (so we apply Euler deconvolution)
-and that their magnetization are uniform. This last premise aligns with the
-theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable
-sensor-sample height, which is the basis of classical paleomagnetism. Also, there is
-no need for any kind of prior knowledge other than the observed magnetic
-anomaly, and the structural index of the sources. Therefore, this method can be
-quickly replicated in a dataset of thin sections of rocks to obtain the
-distributions of magnetic directions of each source identified in the sample.
+To recover magnetic direction and moment we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetization is uniform. 
+This last premise aligns with the theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable sensor-sample height, which is the basis of classical paleomagnetism. 
+Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources. 
+Therefore, this method can be quickly replicated in a data set of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.
 
@@
 While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
-The real sample data positively answered the question of the algorithm's ability to deal with rocks thin sections.
+The real sample data positively answered the question of the algorithm's ability to deal with rocks' thin sections. 
 But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
@@
 
-The Python source code used to produce all results and figures presented here
-is available at \url{https://github.com/\GitHubRepository} and
-\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
+The Python source code used to produce all results and figures presented here is available at \url{https://github.com/\GitHubRepository} and \url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
+The QDM magnetic microscopy data are available at \textcolor{red}{CITE A DATAVERSE/FIGSHARE ARCHIVE under the CC-BY or CC-0 license}.
 
-The image re-scaling and blob detection though the Laplacian of Gaussian method
-were performed with the Scikit-image library \citep{VanderWalt2014}.
-We also used Matplotlib \citep{Hunter2007} for plotting the figures and Mplstereonet \citep{xxxxx} for stereograms.
+The image re-scaling and blob detection though the Laplacian of Gaussian method were performed with the scikit-image library \citep{VanderWalt2014}. 
+We also used matplotlib \citep{Hunter2007} for plotting the figures and mplstereonet \citep{mplstereonet} for stereograms. 
 Basic calculations were performed using Numpy \citep{Harris2020} and Scipy \citep{2020SciPy-NMeth}. 
@@
 The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems. 
-Loops were parallelized with the aid of Numba just-in-time compilation \citep{lam2015numba}.
+The Numba just-in-time compilation library \citep{lam2015numba} was used to speed-up calculations. 
 Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful tool for working with multi-dimensional datasets allowing an easy way of data visualization and extraction with advanced indexing techniques.
-
-The QDM image data is available at \textcolor{red}{CITE A DATAVERSE/FIGSHARE ARCHIVE under the CC-XX license}.
 
@@
 \section{Acknowledgements}
-This research project was supported by the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) - grant 162704/2021-6 and by the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) - grant 2021/08379-5, the opinions, hypotheses and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP.
-We also acknowledge the support of the Royal Society ex \textcolor{red}{[insert grant number]} for this research project.
+
 We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.
+This research was supported by 
+grant 162704/2021-6 from the Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq), 
+grant 2021/08379-5 from the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP),
+and grant IES\textbackslash{}R3\textbackslash{}213141 from the Royal Society. 
+The opinions, hypotheses, and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP.

### 2023-04-03 paper/content.tex
Add changes in the paper text

@@
 For a signal to be ``visible'', \citet{Strum2014} suggest that $\text{SNR} \ge 3$, which means the signal is at least three times stronger than the noise.
-Here, we'll use both $R^2$ and SNR as criteria for filtering out unreliable estimates from our dipole moment inversions.
+Here, we use both $R^2$ and SNR as criteria for filtering out unreliable estimates from our dipole moment inversions.
 
@@
 
-This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$. 
+This test represents a more complex scenario by simulating 103 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$. 
 The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance. 
@@
 The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
-To simulate this behaviour in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions. 
+To simulate this behavior in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions. 
 The first group of sources ($M = 70$) are sampled from a distribution  with mean of $D = \ang{0}$ and $I = \ang{0}$ and standard deviation of $\ang{10}$. 
 The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$.
+We also manually added 3 sources with higher dipole moments ($5x10^{-11}$) to further simulate the complexity observed in real data measurements.
 The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.
@@
     $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated. 
-    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
     c) The total gradient amplitude (TGA) calculated from the 
@@
 
-Since now the data have both high and low-frequency noise, we first fit a $5^{th}$ degree polynomial to the data to remove the low-frequency noise. 
+Since now the data have both high and low-frequency noise, we first fit a $3^{th}$ degree polynomial to the data to remove the low-frequency noise. 
 We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
 TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
-A total of 98 sources out of the original 100 were successfully detected by our workflow.
+A total of 99 sources out of the original 103 were successfully detected by our workflow.
 
@@
 Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
-Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 98 sources that were identified and the differences between the estimated dipole moments and the true values.
+Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 99 sources that were identified and the differences between the estimated dipole moments and the true values.
 The depth and dipole moment amplitude of each source are represented by horizontal and vertical bars, respectively. 
@@
 \includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
-\caption{
-a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized (dipolar sources) in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree.
-b) The estimated vector directions without filtering.
-c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.85$) and signal-to-noise ratio (SNR $ \geq 5$).
+\caption{ Comparison of true and estimated dipole magnetic moments and directions for the complex synthetic sample.
+a) Simulation of a thin section of rock with 103 particles uniformly magnetized (dipolar sources) by two different induced fields.
+The average directions of the induced fields are Dec=0\textdegree/Inc=0\textdegree and Dec=180\textdegree/Inc=0\textdegree, yielding two stable directions.
+b) All estimated vector directions of the identified sources ($M=99$).
+c) The Filtering criteria used to select the magnetic directions of the sources with the best fitting ($M=96$), determined by the coefficient of determination ($R^ 2 \geq 0.85$) and signal-to-noise ratio (SNR $ \geq 5$).
 }
@@
 Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
-possible to determine the windows for 103 potential sources
+possible to determine the windows for 75 potential sources
 (Figure~\ref{real-data}e).
@@
 \includegraphics[width=1\linewidth]{figures/real-data.png}
-\caption{
+\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
     a) The real sample vertical component magnetic data $b_z$ observations at 
     $z = \qty{5}{\micro\meter}$. 
-    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
     c) The total gradient amplitude (TGA) calculated from the 
@@
 
-After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 103 windows selected previously.
+After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 75 windows selected previously.
 In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time.
-We obtained the magnetic moment and the direction for all 103 magnetic grains (Figure~\ref{real-data-stereograms}a).
+We obtained the magnetic moment and the direction for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
 Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
 We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5.
-An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent as the non-dipolarity test approach \citep{Fu2020}.
+An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent to the non-dipolarity test approach \citep{Fu2020}.
 On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise.
 By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data.
+About 46 identified sources passed these criteria.
 This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
-Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite outnumbers the hematite.
+Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite grains outnumber the hematite ones.
 
@@
 \caption{
-a) The estimated directions without filtering.
-b) Estimated directions filtered by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 5$), which shows two clusters of direction located on each pole of the stereogram.
+Comparison of the estimated dipole magnetic moments and directions for the real data sample.
+a) All estimated directions without filtering ($M=75$).
+b) Estimated directions filtered ($M=46$) by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 5$), which shows two clusters of direction located on each pole of the stereogram.
 }
@@
 Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
-One way to circumvent the ambiguity is incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization.
+One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization.
 Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly. 
-When the position of the source is known, it constrains the model to be as consistent as possible to the observed data, hence increasing the likelihood of obtaining unique solutions. 
+When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions. 
 \citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
@@
 This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
-Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the source's depth, which is probably caused by ambiguities. 
+Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
 In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.
@@
 Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
-In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
+In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
 This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
@@
 Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used. 
-The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of materials' internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
+The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
 The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
@@
 The advantages of the methodology are (i) high-accuracy blob detection; (ii) scale-invariant for images with different intensities/sizes of objects; while also being (iii) robust to the presence of noise due to the Gaussian smoothing filter.
-While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time-consuming when dealing with larger images and (ii) the requirement of parameters adjustment, such as the threshold and the kernel sizes.
+While the main drawbacks of the LoG blob algorithms are: (i) being computationally expensive/time-consuming when dealing with larger images and (ii) the requirement of parameter adjustments, such as the threshold and the kernel sizes.
 
@@
 The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges. 
-This technique is widely used in aeromagnetic surveys to determine sources’ boundaries by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
+This technique is widely used in aeromagnetic surveys to determine the boundaries of sources by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
 Hence. The application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window. 
@@
 As expected, there is a direct relationship between the dipole intensity and depth with the observed errors. 
-It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep particles and/or particles with small magnetic intensity generate worse results essentially because they will produce weaker anomalous fields in the magnetic maps.
-Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near to the sensor.
+It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
+Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
 
@@
 However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
-Therefore application of the proposed algorithm to natural samples should fail for those PSD particles. 
+Therefore the application of the proposed algorithm to natural samples should fail for those PSD particles. 
 \cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
@@
 Despite the excellent signal-to-noise ratio that the SMM provided with the
-proximity of the sensor to the sample, it is worth mentioning that the
+the proximity of the sensor to the sample, it is worth mentioning that the
 measurement noise can still overshadow the responses of very weak/small, or
@@
 of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations. 
-In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensible to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
-This technique allows us to obtain the 3D positioning and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associate with the blob detection process.
+In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensitive to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
+This technique allows us to obtain the 3D positioning and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
 
@@
 
-The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions, but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
+The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
 While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
-The real sample data positively answered the question of the algorithm's ability to deal with rocks' thin sections. 
+The real sample data positively answered the question of the algorithm's ability to deal with thin sections of rocks. 
 But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
@@
 
-The image re-scaling and blob detection though the Laplacian of Gaussian method were performed with the scikit-image library \citep{VanderWalt2014}. 
+The image re-scaling and blob detection through the Laplacian of Gaussian method was performed with the scikit-image library \citep{VanderWalt2014}. 
 We also used matplotlib \citep{Hunter2007} for plotting the figures and mplstereonet \citep{mplstereonet} for stereograms. 

### 2023-04-21 paper/content.tex
Updates from Overleaf

@@
 
-Several branches of Earth Sciences have demonstrated the importance of the
-``spatiality" of the data on a microscopic scale, mainly in geochemistry and
-geochronology applications where it is possible to perform punctual analysis
+Several branches of Earth Sciences have demonstrated the importance of spatial resolution on a microscopic scale. For example, geochemistry and
+geochronology applications have benefited from point-wise analyses
 and compositional maps, allowing significant advances in the understanding of
@@
 Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
-in analyzing bulk samples, where the magnetic signal of a single specimen is
+of analyzing bulk samples, where the magnetic signal of a single specimen is
 the result of the sum of moments of a large assembly of ferromagnetic grains
@@
 and PSD grains, and techniques of step-wise thermal and magnetic treatments are
-needed to unveil the more stable and reliable magnetic record
+needed to unveil this more stable and reliable magnetic record
 \citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
-possibility of performing magnetic maps at the micro-scale and recovering the
+possibility of obtaining magnetic field maps at the micro-scale and recovering the
 magnetization of each grain, therefore enabling the separate analysis of stable
@@
 In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
-to recover from the magnetic images a large amount of individual magnetic
+to recover from the magnetic images a large number of individual magnetic
 moments, corresponding to at least tens of thousands of stable fine-grained
@@
 of multiple magnetic particles and can vary greatly in wavelength, strength,
-and spatial separation, depending on the NRM and location of each particle. We
+and spatial separation, depending on the natural remanent magnetization (NRM) and location of each particle. We
 usually assume that the signal measured by the magnetic microscope is the
@@
 below, which is known to be highly sensitive to noise in the derivatives
-\citep{Saleh2012Applying}. This is why e prefer the finite-differences based
+\citep{Saleh2012Applying}. This is why we prefer the finite-differences based
 derivatives, which are less prone to amplifying short-wavelength noise than
@@
 segment an aeromagnetic dataset into individual anomalies. Fortunately,
-magnetic microscopy images contain fewer elongated features (e.g., dikes and
+magnetic microscopy images often contain fewer elongated features (e.g., dikes and
 suture zones) and regional signals (e.g., Curie depth variations) that are
@@
 Hence, it is necessary to evaluate how well the predicted data is able to fit the observed data. 
-When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``non-dipolarity parameter'' ($D$). 
+When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``dipolarity parameter'' ($D$). 
 We note that $D$ is equivalent to the coefficient of determination
@@
 
-The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
+The spatial resolution of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
 Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
@@
 approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
-spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
+spacing of 2.35 $\mu$m and a sensor-sample distance of approximatly 5 $\mu$m, totaling
 576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
-order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
-Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
+order to avoid the influence of the Earth's magnetic field while the data was taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Fu2020,
+Glenn2017}.
+We applied a bias field of 0.9 mT during the measurement, which was periodically reversed to result in an effective background field of <1 µT.
+After applying the magnetic anomaly detection algorithm, it was
 possible to determine the windows for 75 potential sources
@@
 The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
-But, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
+In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
 

### 2023-04-21 paper/content.tex
Fix citations to software
Many of the bibtex items were incorrect.

@@
 
-The Python source code used to produce all results and figures presented here is available at \url{https://github.com/\GitHubRepository} and \url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
-The QDM magnetic microscopy data are available at \textcolor{red}{CITE A DATAVERSE/FIGSHARE ARCHIVE under the CC-BY or CC-0 license}.
+The Python source code used to produce all results and figures presented here
+is available at \url{https://github.com/\GitHubRepository} and
+\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
+The QDM magnetic microscopy data are available at \textcolor{red}{CITE A
+DATAVERSE/FIGSHARE ARCHIVE under the CC-BY or CC-0 license}.
 
-The image re-scaling and blob detection through the Laplacian of Gaussian method was performed with the scikit-image library \citep{VanderWalt2014}. 
-We also used matplotlib \citep{Hunter2007} for plotting the figures and mplstereonet \citep{mplstereonet} for stereograms. 
-Basic calculations were performed using Numpy \citep{Harris2020} and Scipy \citep{2020SciPy-NMeth}. 
-Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}. 
-The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems. 
-The Numba just-in-time compilation library \citep{lam2015numba} was used to speed-up calculations. 
-Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful tool for working with multi-dimensional datasets allowing an easy way of data visualization and extraction with advanced indexing techniques.
+The image re-scaling and blob detection through the Laplacian of Gaussian
+method were performed with the scikit-image library \citep{VanderWalt2014}.
+We also used matplotlib \citep{Hunter2007} and mplstereonet \citep{mplstereonet}
+or generating figures and stereograms.
+Basic calculations were performed using Numpy \citep{Harris2020} and Scipy
+\citep{2020SciPy-NMeth}.
+Verde \citep{verde2018} was used to generate data grids.
+Upward continuation was performed using Harmonica \citep{harmonica2020}.
+The Choclo library \citep{choclo2022} provided kernel functions used in the
+forward and inverse problems.
+The Numba just-in-time compilation library \citep{lam2015numba} was used to
+speed-up calculations.
+Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful
+tool for working with multi-dimensional datasets allowing an easy way of data
+visualization and extraction with advanced indexing techniques.
 

### 2023-04-21 paper/content.tex
Updates from Overleaf

@@
 are performed on a regular grid with evenly spaced grid points and at a
-constant height, and the data are contaminated with random Gaussian noise and
+constant height, and the data are contaminated with pseudorandom Gaussian noise and
 long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
@@
 576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
-order to avoid the influence of the Earth's magnetic field while the data was taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Fu2020,
+order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Lima2009, Fu2020,
 Glenn2017}.
-We applied a bias field of 0.9 mT during the measurement, which was periodically reversed to result in an effective background field of <1 µT.
+We applied a bias field of \qty{0.9}{\m\tesla} during the measurement, which was periodically reversed to result in an effective background field of <1 µT.
 After applying the magnetic anomaly detection algorithm, it was

### 2023-04-21 paper/content.tex
Incorporate latest edits from Gelson and Roger

@@
 a) Simulation of a thin section of rock with 103 particles uniformly magnetized (dipolar sources) by two different induced fields.
-The average directions of the induced fields are Dec=0\textdegree/Inc=0\textdegree and Dec=180\textdegree/Inc=0\textdegree, yielding two stable directions.
+The average directions of the induced fields are $D=\ang{0}$ and $I=\ang{0}$ and $D=\ang{180}$ and $I=\ang{0}$, yielding two stable directions.
 b) All estimated vector directions of the identified sources ($M=99$).
-c) The Filtering criteria used to select the magnetic directions of the sources with the best fitting ($M=96$), determined by the coefficient of determination ($R^ 2 \geq 0.85$) and signal-to-noise ratio (SNR $ \geq 5$).
+c) The Filtering criteria used to select the magnetic directions of the sources with the best fitting ($M=96$), determined by the coefficient of determination ($R^2 \geq 0.85$) and signal-to-noise ratio ($\text{SNR} \geq 5$).
 }
@@
 Diamond Microscope (QDM) at Harvard University over a sample section of
-approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
-spacing of 2.35 $\mu$m and a sensor-sample distance of approximatly 5 $\mu$m, totaling
-576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
-order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Lima2009, Fu2020,
+approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
+spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
+576,000 data points. The QDM is housed in a shielded room, in
+order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
 Glenn2017}.
-We applied a bias field of \qty{0.9}{\m\tesla} during the measurement, which was periodically reversed to result in an effective background field of <1 µT.
+We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.
 After applying the magnetic anomaly detection algorithm, it was
@@
     a) The real sample vertical component magnetic data $b_z$ observations at
-    $z = \qty{5}{\micro\meter}$.
-    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    $z = \qty{5}{\um}$.
+    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise, respectively.
     c) The total gradient amplitude (TGA) calculated from the
@@
 We obtained the magnetic moment and the direction for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
-Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination R\textsuperscript{2} and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
+Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination $R^2$ and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
 We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5.
-An $R^2$ value of 0.85 indicates that 85\% of the measured magnetic data is explained by the predicted dipole model, which is equivalent to the non-dipolarity test approach \citep{Fu2020}.
+An $R^2$ value of 0.85 indicates that \qty{85}{\percent} of the measured magnetic data is explained by the predicted dipole model, which is equivalent to the dipolarity test approach \citep{Fu2020}.
 On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise.
@@
 Despite the excellent signal-to-noise ratio that the SMM provided with the
-the proximity of the sensor to the sample, it is worth mentioning that the
+proximity of the sensor to the sample, it is worth mentioning that the
 measurement noise can still overshadow the responses of very weak/small, or

### 2023-04-21 code/micromag.py
Add a noise removal to the image enhancement
Put both the stretching and the noise removal into a function for easier
access.

@@ -7,8 +7,11 @@ Functions for performing the processing and inversion of the microscopy data.
 import numpy as np
 import xarray as xr
 import matplotlib.pyplot as plt
+import scipy.linalg
 import scipy.io
 import skimage.feature
+import skimage.exposure
+import skimage.restoration
 import numba
 import harmonica as hm
 import verde as vd
@@ -18,6 +21,18 @@ import choclo
 TESLA_TO_NANOTESLA = 1e9
 MICROMETER_TO_METER = 1e-6
 METER_TO_MICROMETER = 1e6
+
+
+def enhance_image(image, percentile=(5, 95)):
+    """
+    Apply constrast stretching and denoising to enhance an image.
+    """
+    enhanced = skimage.restoration.denoise_nl_means(
+        skimage.exposure.rescale_intensity(
+            image, in_range=tuple(np.percentile(image, percentile)),
+        ),
+    )
+    return enhanced
 
 
 def gaussian_noise(error, shape, seed=None):
@@ -197,7 +212,6 @@ def dipole_moment_inversion(data, dipole_coordinates):
     # Verde drops non-dimension coordinates so we have to add z back.
     # This is a bug in Verde.
     table["z"] = data.z.values.ravel()
-
     n_data = table.shape[0]
     n_params = 3
     A = np.empty((n_data, n_params))
@@ -214,8 +228,7 @@ def dipole_moment_inversion(data, dipole_coordinates):
     )
     hessian = A.T @ A
     neg_gradient = A.T @ d
-    dipole_moment = np.linalg.solve(hessian, neg_gradient)
-
+    dipole_moment = scipy.linalg.solve(hessian, neg_gradient, assume_a="pos")
     residuals = d - A @ dipole_moment
     residuals_sum_sq = np.sum(residuals**2)
     # Estimate of the true error variance (since we'll never know it)
@@ -432,7 +445,7 @@ def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, ad
     )
     
     args.update(kwargs)
-    dir_quiver = ax.quiver(*positions[:2], u, v, color, **args, zorder=1)
+    dir_quiver = ax.quiver(*positions[:2], u, v, color, **args)
     
     # Make headless vectors at 90° to represent the amplitude
     threshold_scale = abs(np.log10(amplitude))
[…]

### 2023-04-24 code/micromag.py
Add a function to plot the stereonets
Include a stereonet and a map plot of the simple synthetic to be more
consistent.

@@ -7,6 +7,7 @@ Functions for performing the processing and inversion of the microscopy data.
 import numpy as np
 import xarray as xr
 import matplotlib.pyplot as plt
+import mplstereonet
 import scipy.linalg
 import scipy.io
 import skimage.feature
@@ -449,7 +450,7 @@ def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, ad
     
     # Make headless vectors at 90° to represent the amplitude
     threshold_scale = abs(np.log10(amplitude))
-    scale = abs(threshold_scale-threshold_scale.max())/6 #amplitude / amplitude.max()
+    scale = abs(threshold_scale-threshold_scale.max()) #amplitude / amplitude.max()
     angle = np.radians(declination + 90)
     u, v = scale * np.sin(angle), scale * np.cos(angle)    
     args.update(headlength=0, headwidth=1, headaxislength=0)
@@ -462,3 +463,53 @@ def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, ad
         ax.quiverkey(amp_quiver, *key_coords, 1, label=f"{amplitude.max():.0e} A.m²\namplitude", labelpos="S")
                      
     return dir_quiver, amp_quiver
+
+
+def plot_stereonet(dipole_moments, ax=None, cmap="viridis", vmin=None, vmax=None, label="", add_ticks=True, **kwargs):
+    """
+    Plot the dipole moments in a stereonet.
+    
+    The moment magnitude is set as the color. 
+    Positive inclination symbols are solid, negative are just the outline.
+    """
+    if ax is None:
+        fig = plt.figure()
+        ax = fig.add_subplot(1, 1, 1, projection='stereonet')
+
+    ax.set_facecolor("#eeeeee") # color "#eeeeee"
+    ax.grid(linestyle="-", color="#cccccc", linewidth=1)
+    ax.set_longitude_grid_ends(90)
+    if add_ticks:
+        # Add ticks manually because mplstereonet doesn't work with subplots
+        ax.set_azimuth_ticks([])
+        ax.text(0.2, 1.65, '0°')
+        ax.text(0.2, -1.8, '180°')
+        ax.text(-2, -0.025, '270°')
+        ax.text(1.65, -0.025, '90°')
+    
+    if label and not label.endswith(" "):
+        label = label + " "
+    
+    inclination, declination, amplitude = vector_to_angles(dipole_moments)
+    
[…]

### 2023-05-15 paper/content.tex
Add a function to plot the stereonets
Include a stereonet and a map plot of the simple synthetic to be more
consistent.
Updates from Overleaf

@@
 The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise.
-The purpose of this model is to investigate the efficiency of the combination of Euler Deconvolution and the dipole moment inversion, thus being a validation of the methodology.
+The purpose of this model is to investigate the efficiency of the combination of Euler deconvolution and the dipole moment inversion, thus being a validation of the methodology.
 
-The second model contains 100 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions.
+The second model simulates a hundred sources with both dipolar and non-dipolar magnetic components and their vertical magnetic field ($b_z$) at different height levels, also corrupted with high-frequency noise.
+This section is carried out in order to assess the ability of the algorithm to deal with sources with strong non-dipolar components.
+
+The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions.
 The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
@@
 
-\subsection{Simple simulation: Validating the methodology}
+\subsection{Simple simulation: Validating the methodology for dipolar sources}
 
@@
 \centering
-\includegraphics[width=0.5\linewidth]{figures/simple-synthetic-dipole-moment.png}
+\includegraphics[width=\linewidth]{figures/simple-synthetic-dipole-moment.png}
 \caption{
@@
 
-The positions of each source obtained with Euler Deconvolution were used as an input parameter for the dipole moment inversion.
+The positions of each source obtained with Euler deconvolution were used as an input parameter for the dipole moment inversion.
 The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
@@
   True and estimated source positions and dipole moments for the simple synthetic data application.
-  Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
+  Each source modeled and recovered positioning and magnetization parameters by the least square estimator, respectively.}
   \label{tab_synthetic_simple_results}
 \end{table}
+
+\subsection{Simple simulation: Validating the methodology for non-dipolar sources}
+
+Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles are disregarded.
+However, in magnetic microscopy, where the sensor is positioned very close to the sample, these higher-order components might be detected.
+This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain.
+To assess the magnetic signal attenuation, simulations were conducted on particles with more complex magnetization at varying distances from the sensor.
+
+To simulate particles with non-dipole magnetization components, we specified a spherical volume with a radius of about 1 $\mu$m.
+Within this volume, we added 200 dipolar point particles with varying magnetization directions and magnetic moments.
+These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$.
+We also randomly generated the spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ...
+11 corresponds to the variation in depth of the particle.
+By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the Cartesian magnetization components for the spherical particle.
+The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions.
+The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.
+
+According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values, indicating low dipolarity.
+As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d).
+At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).
+
+\begin{figure}[tb!]
+  \centering
+  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic.png}
+  \caption{Caption: Simulated magnetic microscopy data for a spherical source with both dipolar and non-dipolar magnetic components. The distance from the sensor varies from 1 µm to 6 µm (a-f).}
+  \label{non-dipolarity-synthetic-data}
+\end{figure}
+
+To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions.
+Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data.
+The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively).
+As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero.
+However, when the sensor-source distance is small enough for there to be a strong contribution from higher-order components, a lower degree of dipolarity is observed, expressed as lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a).
+Consequently, in these cases, there are higher errors in the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which was expected since the inversion considers only the dipolar component.
+However, dipolarity significantly increases as the sensor distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
+
+\begin{figure}[tb!]
+  \centering
+  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-positioning.png}
+  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles.
+The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot.
+The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
+  \label{non-dipolarity-synthetic-data-positioning}
+\end{figure}
+
+\begin{figure}[tb!]
+  \centering
+  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-inversion.png}
+  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles.
+The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
+  \label{non-dipolarity-synthetic-data-inversion}
+\end{figure}
 
@@
     $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
-    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
+    b) Anomaly map after the upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise.
     c) The total gradient amplitude (TGA) calculated from the
@@
 
-Since now the data have both high and low-frequency noise, we first fit a $3^{th}$ degree polynomial to the data to remove the low-frequency noise.
 We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
@@
 
-Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source.
-The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
-When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).
+Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Figure~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Figure~\ref{complex-synthetic-stereograms}b) for each source.
+The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Figure~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
+When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Figure~\ref{complex-synthetic-stereograms}c).
 
@@
 We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.
-After applying the magnetic anomaly detection algorithm, it was
-possible to determine the windows for 75 potential sources
-(Figure~\ref{real-data}e).
+After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
+possible to determine the windows for 75 potential sources, as shown in Figure~\ref{real-data}e.
 
@@
     $z = \qty{5}{\um}$.
-    b) Residual anomaly map after the $3^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise, respectively.
+    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
     c) The total gradient amplitude (TGA) calculated from the
@@
 
-Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
+Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
 In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
@@
 The complex synthetic data allows better observation of the strengths and limitations of the windows approach.
-The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Fig.~\ref{complex-synthetic-comparison}a).
+The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
 (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).

### 2023-05-15 paper/content.tex
Add abstract to the paper

@@
 influence on the particle's magnetic signal.
-Thus, our approach can be considered reasonable for working with both particle SD and PSD states signals.
+Thus, our approach can be considered reasonable to work with both particle SD and PSD states signals.
 The latter happens mainly due to the sensor height being usually greater than 5 $\mu m$, considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components.
+This is corroborated by our non-dipolar synthetic sample showing the almost complete attenuation of non-dipolar components at distances greater than 5 $\mu m$.
 
@@
 
-The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
+The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise, for both dipolar and non-dipolar sources.
 While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.

### 2023-05-17 code/micromag.py
Add new functions for stereonets and vector plots

@@ -413,7 +413,10 @@ def load_qdm(path):
     return data
 
 
-def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, add_key=True, key_coords=(0.1, -0.1), **kwargs):
+def plot_dipole_moment(
+    positions, dipole_moments, ax=None, vmin=None, vmax=None, cmap="plasma", cmap_norm=plt.Normalize, linewidth=1.5,
+    add_colorbar=True, add_key=True, key_coords=(0.1, -0.1), **kwargs,
+):
     """
     Plot the dipole moments on a map represented by vectors.
     
@@ -427,45 +430,60 @@ def plot_dipole_moment(positions, dipole_moments, ax=None, add_colorbar=True, ad
       
     inclination, declination, amplitude = vector_to_angles(dipole_moments)
     
+    # Generate colors based on the amplitude values
+    norm = cmap_norm(vmin=vmin, vmax=vmax)
+    colors = plt.colormaps[cmap](norm(amplitude))
+    
+    positive_inc = inclination > 0
+    negative_inc = ~positive_inc
+    
     # Calculate the plot vector components
-    u, v = np.sin(np.radians(declination)), np.cos(np.radians(declination))
-    color = inclination
-    scale = vd.maxabs(color)
+    scale = 90 - np.abs(inclination)
+    u, v = scale * np.sin(np.radians(declination)), scale * np.cos(np.radians(declination))
     
     # Keyword arguments for the quiver plots
     args = dict(
-        cmap="seismic",
-        clim=(-scale, scale),
         pivot="mid",
         width=0.005, 
         scale=15,
-        headlength=3, 
-        headaxislength=3,
-        edgecolor='k',
-        linewidth = 0.35,
+        headlength=1.5, 
+        headaxislength=1.5,
+        headwidth=2,
+        minlength=1.5,
+    )    
+    args.update(kwargs)
+    
+    pos_quiver = ax.quiver(
+        positions[:2][0][positive_inc], 
+        positions[:2][1][positive_inc], 
+        u[positive_inc], 
+        v[positive_inc], 
+        color=colors[positive_inc], 
+        edgecolor='k', 
+        linewidth=0, 
+        **args,
+    )    
+    neg_quiver = ax.quiver(
+        positions[:2][0][negative_inc], 
+        positions[:2][1][negative_inc], 
+        u[negative_inc], 
[…]

### 2023-05-18 paper/abstract-plain.tex

Very small magnetic particles in rocks and other materials can store information about what the Earth’s magnetic field was like in the past. 
But not all particles are good recorders of this magnetic information, and some may have recorded different overlapping directions and strengths. 
So it is important to measure each particle separately in order to identify and separate the good recorders from the bad ones. 
A device called a ``quantum diamond microscope'' is able to measure the magnetic field near the surface of a rock sample at microscopic scale. 
We propose a new method for processing data from this microscope that is able to find out the individual magnetizations of large amounts small magnetic particles automatically.
We created a computer program to execute the method, which calculates the 3D position and magnetization of each particle using the simple model of a magnetic dipole. 
We tested the method on simulated data, using fake magnetic particles for which we know the correct magnetization and position, and real data, both of which showed good results in most cases. 
The method we created has the potential to enable the widespread study of the magnetism of natural materials with more detail than before.

### 2023-05-18 paper/abstract.tex

Paleomagnetic data are usually obtained from whole cylindric samples, where the signal results from the sum of magnetic moments from hundreds of thousands to millions of magnetic particles within the sample volume. This usually includes stable and unstable remanence carriers. Recently, magnetic microscopy techniques allowed the investigation of individual grains by directly imaging their magnetic field. However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data. We developed a fast, semi-automated algorithm capable of estimating the positioning and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data. This methodology is an overdetermined linear inverse problem using an approximation of point dipolar sources, for both position and magnetic moment estimations. It does not require any type of additional information about the sample or sources. Our algorithm works in three basic steps: (i) we apply image processing techniques to identify and isolate the data windows for each source; (ii) with that window data, the position of the sources can be estimated using Euler deconvolution; and finally (iii) using this positioning information the algorithm is able to estimate magnetic direction and intensity for each source. Sensitivity tests were run to estimate the stability of our routine to the depth of particles, signal-to-noise ratio, and non-dipolarity of the sources. Tests with simple synthetic data show the high effectiveness of the methodology for recovering the positioning and magnetic information for dipolar and non-dipolar sources. Complex synthetic data were devised to emulate real rock data. Results obtained on these models also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large set of particles. This is further confirmed through an application to real data in which we retrieve the expected bimodal isothermal remanent directions that were induced in the sample. Given its semi-automatic nature, its low processing cost, and the possibility of simultaneous inversion of the magnetic moment of a great number of magnetic particles, the methodology here proposed is a step forward in enabling paleomagnetic applications of magnetic microscopy.

### 2023-05-18 paper/content.tex

@@
 These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$.
-We also randomly generated the spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ...
+We also randomly generated spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ...
 11 corresponds to the variation in depth of the particle.
-By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the Cartesian magnetization components for the spherical particle.
+By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the cartesian magnetization components for the spherical particle.
 The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions.
@@
 
-According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values, indicating low dipolarity.
+According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values.
 As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d).
@@
 As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero.
-However, when the sensor-source distance is small enough for there to be a strong contribution from higher-order components, a lower degree of dipolarity is observed, expressed as lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a).
-Consequently, in these cases, there are higher errors in the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which was expected since the inversion considers only the dipolar component.
-However, dipolarity significantly increases as the sensor distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
+However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a).
+Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component.
+However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
 

### 2023-05-19 code/micromag.py
Simplify the non-dipolar test code

@@ -45,6 +45,28 @@ def gaussian_noise(error, shape, seed=None):
     return noise
 
 
+def nondipolar_source(
+    xc, yc, zc, position_std, inclination, declination, angle_std, 
+    amplitude, amplitude_std, n_particles=200, seed=None,
+):
+    """
+    Generate a non-dipolar source as an ensemble of random dipoles
+    """
+    rng = np.random.default_rng(seed)
+    # Make sure z is always < 0 (dipole is inside the sample)
+    dipole_coordinates = (
+        rng.normal(xc, position_std, n_particles),
+        rng.normal(yc, position_std, n_particles),
+        -np.abs(rng.normal(zc, position_std, n_particles)),
+    )
+    dipole_moments = angles_to_vector(
+        rng.normal(inclination, angle_std, n_particles),
+        rng.normal(declination, angle_std, n_particles),
+        rng.normal(amplitude, amplitude_std, n_particles),
+    )
+    return (dipole_coordinates, dipole_moments)
+
+
 def angles_to_vector(inclination, declination, amplitude):
     """
     Generate a 3-component vector from inclination, declination, and amplitude

### 2023-05-19 paper/abstract.tex
Updates from Overleaf

@@
 Paleomagnetic data are usually obtained from whole cylindric samples, where the signal results from the sum of magnetic moments from hundreds of thousands to millions of magnetic particles within the sample volume.
-This usually includes stable and unstable remanence carriers.
+This usually includes both stable and unstable remanence carriers.
 Recently, magnetic microscopy techniques allowed the investigation of individual grains by directly imaging their magnetic field. 
-However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data.
-We developed a fast, semi-automated algorithm capable of estimating the positioning and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data.
-This methodology is an overdetermined linear inverse problem using an approximation of point dipolar sources, for both position and magnetic moment estimations.
-It does not require any type of additional information about the sample or sources.
-Our algorithm works in three basic steps: (i) we apply image processing techniques to identify and isolate the data windows for each source; (ii) with that window data, the position of the sources can be estimated using Euler deconvolution; and finally (iii) using this positioning information the algorithm is able to estimate magnetic direction and intensity for each source.
+However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data, as well as by the large number of grains found in any one microscopy image.
+We present a fast, semi-automated algorithm capable of estimating the position and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data. 
+Our algorithm works in three steps: (i) we first apply image processing techniques to identify and isolate data window boundaries for each source; (ii) with these window boundaries, the position of the sources is estimated using Euler deconvolution; and finally (iii) using the  position information, the algorithm is able to estimate the magnetic dipole moment direction and intensity for each source through an overdetermined linear inverse problem using a dipolar approximation.
+The method does not require any type of additional information about the sample or the sources. 
 Sensitivity tests were run to estimate the stability of our routine to the depth of particles, signal-to-noise ratio, and non-dipolarity of the sources. 
-Tests with simple synthetic data show the high effectiveness of the methodology for recovering the positioning and magnetic information for dipolar and non-dipolar sources.
-Complex synthetic data were devised to emulate real rock data.
-Results obtained on these models also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large set of particles.
-This is further confirmed through an application to real data in which we retrieve the expected bimodal isothermal remanent directions that were induced in the sample.
+Tests with simple synthetic data show the high effectiveness of the methodology for recovering the position and magnetic information for both dipolar and non-dipolar sources. 
+More complex synthetic data including over 100 different magnetic particles were devised to emulate real rock data. 
+Results obtained on these data also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large number of particles. 
+This is further confirmed through an application to real data in which we are able to retrieve the expected bimodal isothermal remanent directions that were induced in the sample. 
 Given its semi-automatic nature, its low processing cost, and the possibility of simultaneous inversion of the magnetic moment of a great number of magnetic particles, the methodology here proposed is a step forward in enabling paleomagnetic applications of magnetic microscopy.

### 2023-05-19 paper/abstract-plain.tex

@@
 A device called a ``quantum diamond microscope'' is able to measure the magnetic field near the surface of a rock sample at microscopic scale. 
-We propose a new method for processing data from this microscope that is able to find out the individual magnetizations of large amounts small magnetic particles automatically.
+We propose a new method for processing data from this microscope that is able to find out the individual magnetizations of large amounts of small magnetic particles automatically.
 We created a computer program to execute the method, which calculates the 3D position and magnetization of each particle using the simple model of a magnetic dipole. 

### 2023-05-19 paper/content.tex

@@
 
-We first applied our inversion workflow to synthetic data to evaluate its strengths and limitations.
-The first set of synthetic data is simple and intended to test the method's performance under ideal circumstances.
-The second set is more complex, with a greater number of magnetic particles and long-wavelength noise, and is intended to demonstrate the capabilities and limitations of the method under real-world scenarios.
+We first applied our inversion workflow to three sets of synthetic data to evaluate its strengths and limitations.
+The datasets are produced by different models of varying complexity which were designed to assess different aspects of the method.
 
-The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise.
-The purpose of this model is to investigate the efficiency of the combination of Euler deconvolution and the dipole moment inversion, thus being a validation of the methodology.
+\begin{enumerate}
+\item \textbf{Method validation:} 
+The first model is composed of a set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations.
+The synthetic data consists of the vertical magnetic field ($b_z$) derived from this model and contaminated by pseudo-random high-frequency noise.
+The purpose of this simple model is to investigate the efficiency of the combination of the source detection method, Euler deconvolution, and the dipole moment inversion under ideal circumstances, thus serving as a validation of the methodology.
 
-The second model simulates a hundred sources with both dipolar and non-dipolar magnetic components and their vertical magnetic field ($b_z$) at different height levels, also corrupted with high-frequency noise.
-This section is carried out in order to assess the ability of the algorithm to deal with sources with strong non-dipolar components.
+\item \textbf{Applicability to non-dipolar sources:}
+The second model simulates a hundred sources with both dipolar and non-dipolar magnetic moments.
+Their vertical magnetic field ($b_z$) is calculated at different sensor-source distances
+and is also contaminated with pseudo-random high-frequency noise. 
+This model is used to assess the ability of the algorithm to deal with strong non-dipolar sources.
 
-The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions.
+\item \textbf{Applicability to real-world scenarios:}
+The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations clustered around two stable directions.
 The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
 The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.
+\end{enumerate}
 
-\subsection{Simple simulation: Validating the methodology for dipolar sources}
+\subsection{Method validation}
 
@@
     f) The estimated source locations (colored circles) from Euler
-    Deconvolution of the upward-continued data inside each bounding box.
-    The color represents the difference between the true and estimated
+    deconvolution of the upward-continued data inside each bounding box.
+    The color represents the difference between the true and the estimated
     $z$ coordinates.
@@
 We first applied an upward continuation filter (Figure~\ref{fig_synthetic_simple_data}b) to smooth out the high-frequency noise \citep{Blakely1996}.
-This is important because it strongly affects the first derivatives of the field, which are required for the Euler Deconvolution.
-Then, we calculated the total gradient amplitude (Figure~\ref{fig_synthetic_simple_data}c), which was then subjected to contrast stretching to highlight as much as possible the weaker intensity sources (Figure~\ref{fig_synthetic_simple_data}d).
+This is important because noise strongly affects the first derivatives of the field, which are required for the source detection algorithm and the Euler deconvolution.
+Then, we calculated the total gradient amplitude (Figure~\ref{fig_synthetic_simple_data}c), which was subjected to contrast stretching to highlight the weaker intensity sources as much as possible (Figure~\ref{fig_synthetic_simple_data}d).
 Subsequently, we applied the blob detection algorithm to the contrast-stretched total gradient amplitude to obtain the position of the data windows for each source (Figure~\ref{fig_synthetic_simple_data}e).
-Euler Deconvolution was then performed for each data window identified by assuming a structural index $\eta = 3$ of a point source, therefore obtaining the Cartesian coordinates (Figure~\ref{fig_synthetic_simple_data}f) of each source.
-Table~\ref{tab_synthetic_simple_results} shows the true and estimated values of the source coordinates for comparison.
+Euler deconvolution was then performed for each data window identified by assuming a structural index $\eta = 3$ of a point source, therefore obtaining the Cartesian coordinates (Figure~\ref{fig_synthetic_simple_data}f) of each source.
+For comparison, Table~\ref{tab_synthetic_simple_results} shows the true and estimated values of the source coordinates.
+
+\begin{table}[tb!]
+  \begin{center}
+    \small
+    \input{simple-synthetic-results.tex}
+  \end{center}
+  \caption{
+    True and estimated source positions and dipole moments for the method validation test through a simple synthetic data application.
+  }
+  \label{tab_synthetic_simple_results}
+\end{table}
 
@@
   \caption{
-Comparison of true and estimated dipole magnetic moments and directions.
+    Comparison of true and estimated dipole moments for the method validation test through a simple synthetic data application.
+    a) Stereonet showing the true (triangles) and estimated (circles) dipole moments. 
+    The colors are mapped to the dipole moment amplitude.
+    b) Grayscale map of the synthetic $b_z$ overlaid by the estimated dipole moment vectors.
+    The vector locations were derived from the Euler deconvolution results, their size is inversely proportional to the inclination $I$, their direction represents the declination $D$, and their colors are mapped to the dipole moment amplitude using the same colorscale as the stereonet.
+    In both graphs, solid symbols represent positive inclination while hollow symbols represent negative inclination.
   }
@@
 
-The positions of each source obtained with Euler deconvolution were used as an input parameter for the dipole moment inversion.
-The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
-Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.
+The positions of each source obtained with Euler deconvolution were then used as input for the dipole moment inversion.
+The estimated dipole moment vectors are shown in Figure~\ref{fig_synthetic_simple_results}.
+Figure~\ref{fig_synthetic_simple_results}a shows the estimated dipole moment, along with the corresponding true values, as a stereonet for better comparison of the true and estimated vector directions.
+Figure~\ref{fig_synthetic_simple_results}b shows the estimate dipole moments overlaid on a map of the synthetic $b_z$ to demonstrate the ability of our method to estimate a spatial distribution of dipole moments.
+For comparison, Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.
 
-\begin{table}[tb]
-  \begin{center}
-    \small
-    \input{simple-synthetic-results.tex}
-  \end{center}
-  \caption{
-  True and estimated source positions and dipole moments for the simple synthetic data application.
-  Each source modeled and recovered positioning and magnetization parameters by the least square estimator, respectively.}
-  \label{tab_synthetic_simple_results}
-\end{table}
+\subsection{Applicability to non-dipolar sources}
 
-\subsection{Simple simulation: Validating the methodology for non-dipolar sources}
+Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles can be disregarded because of the strong attenuation with distance of the magnetic fields.
+However, in magnetic microscopy, where the sensor is positioned only a few microns from the sample, these higher-order components might be detected. 
+This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain. 
+To assess the attenuation of these non-dipolar components and the applicability of our method, we conducted simulation on particles with more complex magnetization at varying distances from the sensor.
 
-Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles are disregarded.
-However, in magnetic microscopy, where the sensor is positioned very close to the sample, these higher-order components might be detected.
-This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain.
-To assess the magnetic signal attenuation, simulations were conducted on particles with more complex magnetization at varying distances from the sensor.
-
-To simulate particles with non-dipole magnetization components, we specified a spherical volume with a radius of about 1 $\mu$m.
-Within this volume, we added 200 dipolar point particles with varying magnetization directions and magnetic moments.
-These directions were generated randomly to follow a normal distribution centered on the direction Dec=90°/Inc=0°, with a magnetic moment of $10^{-14}$ Am$^2$.
-We also randomly generated spatial positions around a central position of $x_c=25~\mu$m, $y_c=25~\mu$m, and $z_c=\alpha~\mu$m, where $\alpha$ = 0, 1, ...
-11 corresponds to the variation in depth of the particle.
+To simulate particles with non-dipolar magnetization components, we specified a spherical volume with a radius of approximately \qty{1}{\um}. 
+Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes. 
+These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$, with a magnetic moment of $\qty{e-14}{\ampere\m\squared}$. 
+We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$ and $y_c=\qty{25}{\um}$.
+The vertical coordinate of the central position $z_c$ varied between \qty{0}{\um} and \qty{-11}{\um} in \qty{1}{\um} increments, leading to a total of 12 .
 By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the cartesian magnetization components for the spherical particle.
@@
 
-\subsection{Complex simulation: Testing applicability}
+\subsection{Applicability to real-world scenarios}
 

### 2023-05-19 paper/content.tex
Updates from Overleaf

@@
 This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain. 
-To assess the attenuation of these non-dipolar components and the applicability of our method, we conducted simulation on particles with more complex magnetization at varying distances from the sensor.
+To assess the attenuation of these non-dipolar components and the applicability of our method, we conducted a simulation on particles with more complex magnetization at varying sensor-sample distances.
 
@@
 Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes. 
-These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$, with a magnetic moment of $\qty{e-14}{\ampere\m\squared}$. 
-We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$ and $y_c=\qty{25}{\um}$.
-The vertical coordinate of the central position $z_c$ varied between \qty{0}{\um} and \qty{-11}{\um} in \qty{1}{\um} increments, leading to a total of 12 .
-By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the cartesian magnetization components for the spherical particle.
-The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions.
-The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.
+These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with standard deviation of \ang{10}.
+The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$. 
+We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with standard deviation of \qty{0.65}{\um}.
+The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole. 
+The centroid of the particle is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
+The synthetic vertical magnetic field $b_z$ of the non-dipolar source was calculated on regular grids with \qty{0.5}{\um} spacing.
+Each grid was located at a different sensor-sample distance $z$, varying between \qty{1}{\um} and \qty{10}{\um} in \qty{0.5}{\um} increments. 
+The synthetic data were corrupted by pseudo-random gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
+For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
+At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the particle.
 
-According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values.
-As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d).
-At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).
+Figure~\ref{non-dipolarity-synthetic-data} shows the synthetic $b_z$ of an example non-dipolar particle at variable source-sample distances.
+When the particle is close to the sensor (\qty{1-3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values.
+As the distance increases, the magnetic field is attenuated, particularly the non-dipolar components which decay more rapidly than the dipolar component.
+This results in an increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). 
+At distances above \qty{5}{\um}, there is practically only the contribution of the dipolar component, causing $R^2$ to approach its maximum value of 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).
 
@@
 
-To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions.
+We replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions.
 Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data.

### 2023-05-23 paper/content.tex
Updates from Overleaf

@@
 Figure~\ref{non-dipolarity-synthetic-data} shows the synthetic $b_z$ of an example non-dipolar particle at variable source-sample distances.
-When the particle is close to the sensor (\qty{1-3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values.
+When the particle is close to the sensor (\qtyrange{1}{3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values.
 As the distance increases, the magnetic field is attenuated, particularly the non-dipolar components which decay more rapidly than the dipolar component.

### 2023-05-31 paper/content.tex
Version submitted to EarthArXiv

@@
 Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes. 
-These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with standard deviation of \ang{10}.
+These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with a standard deviation of \ang{10}.
 The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$. 
@@
 Each grid was located at a different sensor-sample distance $z$, varying between \qty{1}{\um} and \qty{10}{\um} in \qty{0.5}{\um} increments. 
-The synthetic data were corrupted by pseudo-random gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
+The synthetic data were corrupted by pseudo-random Gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
 For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
@@
 \url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
-The QDM magnetic microscopy data are available at \textcolor{red}{CITE A
-DATAVERSE/FIGSHARE ARCHIVE under the CC-BY or CC-0 license}.
+The QDM magnetic microscopy data are available at~\url{https://figshare.com/articles/dataset/QDM_magnetic_microscopy_dataset_of_a_speleothem_from_Morocco/22965200} under the CC-0 license.
 

### 2023-05-31 paper/content.tex
Fix non-dipolarity figure paths
Remove the leading "paper/". Don't know why Overleaf is fine with this
but it fails to compile locally.

@@
   \centering
-  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic.png}
+  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic.png}
   \caption{Caption: Simulated magnetic microscopy data for a spherical source with both dipolar and non-dipolar magnetic components. The distance from the sensor varies from 1 µm to 6 µm (a-f).}
@@
   \centering
-  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-positioning.png}
+  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-positioning.png}
   \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles.
@@
   \centering
-  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-inversion.png}
+  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-inversion.png}
   \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles.

### 2023-06-02 paper/content.tex
Cite Janine's data with the DOI instead of the raw link

@@
 \url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
-The QDM magnetic microscopy data are available at~\url{https://figshare.com/articles/dataset/QDM_magnetic_microscopy_dataset_of_a_speleothem_from_Morocco/22965200} under the CC-0 license.
+The QDM magnetic microscopy data are available
+at~\url{https://doi.org/10.6084/m9.figshare.22965200.v1} under the CC-0 license.
 
@@
 
-We are indebted to the developers and maintainers of the open-source software without which this work would not have been possible.
+We are indebted to the developers and maintainers of the open-source software
+without which this work would not have been possible.
 This research was supported by
@@
 and grant IES\textbackslash{}R3\textbackslash{}213141 from the Royal Society.
-The opinions, hypotheses, and conclusions or recommendations expressed in this material are the responsibility of the authors and do not necessarily reflect the views of FAPESP.
+The opinions, hypotheses, and conclusions or recommendations expressed in this
+material are the responsibility of the authors and do not necessarily reflect
+the views of FAPESP.

### 2023-06-12 paper/abstract-plain.tex
Version submitted to G3

@@
-Very small magnetic particles in rocks and other materials can store information about what the Earth’s magnetic field was like in the past. 
+\noindent{Very small magnetic particles in rocks and other materials can store information about what the Earth’s magnetic field was like in the past. 
 But not all particles are good recorders of this magnetic information, and some may have recorded different overlapping directions and strengths. 
@@
 We tested the method on simulated data, using fake magnetic particles for which we know the correct magnetization and position, and real data, both of which showed good results in most cases. 
-The method we created has the potential to enable the widespread study of the magnetism of natural materials with more detail than before.
+The method we created has the potential to enable the widespread study of the magnetism of natural materials with more detail than before.}

### 2023-06-12 paper/abstract.tex
Version submitted to G3

--- 2023-05-18 paper/abstract.tex
@@
-Paleomagnetic data are usually obtained from whole cylindric samples, where the signal results from the sum of magnetic moments from hundreds of thousands to millions of magnetic particles within the sample volume.
-This usually includes stable and unstable remanence carriers.
-Recently, magnetic microscopy techniques allowed the investigation of individual grains by directly imaging their magnetic field.
-However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data.
-We developed a fast, semi-automated algorithm capable of estimating the positioning and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data.
-This methodology is an overdetermined linear inverse problem using an approximation of point dipolar sources, for both position and magnetic moment estimations.
-It does not require any type of additional information about the sample or sources.
-Our algorithm works in three basic steps: (i) we apply image processing techniques to identify and isolate the data windows for each source; (ii) with that window data, the position of the sources can be estimated using Euler deconvolution; and finally (iii) using this positioning information the algorithm is able to estimate magnetic direction and intensity for each source.
-Sensitivity tests were run to estimate the stability of our routine to the depth of particles, signal-to-noise ratio, and non-dipolarity of the sources.
-Tests with simple synthetic data show the high effectiveness of the methodology for recovering the positioning and magnetic information for dipolar and non-dipolar sources.
-Complex synthetic data were devised to emulate real rock data.
-Results obtained on these models also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large set of particles.
-This is further confirmed through an application to real data in which we retrieve the expected bimodal isothermal remanent directions that were induced in the sample.
-Given its semi-automatic nature, its low processing cost, and the possibility of simultaneous inversion of the magnetic moment of a great number of magnetic particles, the methodology here proposed is a step forward in enabling paleomagnetic applications of magnetic microscopy.
+% Paleomagnetic data are usually obtained from whole cylindric samples, where the signal results from the sum of magnetic moments from hundreds of thousands to millions of magnetic particles within the sample volume.
+% This usually includes both stable and unstable remanence carriers.
+% Recently, magnetic microscopy techniques allowed the investigation of individual grains by directly imaging their magnetic field. 
+% However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data, as well as by the large number of grains found in any one microscopy image.
+% We present a fast, semi-automated algorithm capable of estimating the position and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data. 
+% Our algorithm works in three steps: (i) we first apply image processing techniques to identify and isolate data window boundaries for each source; (ii) with these window boundaries, the position of the sources is estimated using Euler deconvolution; and finally (iii) using the  position information, the algorithm is able to estimate the magnetic dipole moment direction and intensity for each source through an overdetermined linear inverse problem using a dipolar approximation.
+% The method does not require any type of additional information about the sample or the sources. 
+% Sensitivity tests were run to estimate the stability of our routine to the depth of particles, signal-to-noise ratio, and non-dipolarity of the sources. 
+% Tests with simple synthetic data show the high effectiveness of the methodology for recovering the position and magnetic information for both dipolar and non-dipolar sources. 
+% More complex synthetic data including over 100 different magnetic particles were devised to emulate real rock data. 
+% Results obtained on these data also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large number of particles. 
+% This is further confirmed through an application to real data in which we are able to retrieve the expected bimodal isothermal remanent directions that were induced in the sample. 
+% Given its semi-automatic nature, its low processing cost, and the possibility of simultaneous inversion of the magnetic moment of a great number of magnetic particles, the methodology here proposed is a step forward in enabling paleomagnetic applications of magnetic microscopy.
+Paleomagnetic data is collected from bulk samples, containing a mixture of stable and unstable magnetic particles.
+Recently, magnetic microscopy techniques have allowed the examination of individual magnetic grains.
+However, accurately determining the magnetic moments of these grains is difficult and time-consuming due to the inherent ambiguity of potential field data and the large number of grains in each image.
+Here we introduce a fast and semi-automated algorithm that estimates the position and magnetization of each magnetic source solely based on magnetic microscopy data, without requiring any additional information.
+The algorithm follows a three-step process.
+Firstly, it employs image processing techniques to identify and isolate data window boundaries for each magnetic source.
+Secondly, the algorithm uses Euler deconvolution to estimate their positioning.
+Lastly, the algorithm solves an overdetermined linear inverse problem, using a dipolar approximation, to determine the direction and intensity of the magnetic dipole moment for each source.
+To validate the algorithm, we conducted tests analyzing particle depth, intensity, and non-dipolarity.
+Additionally, synthetic data experiments were performed to demonstrate the effectiveness of the methodology in recovering the position and magnetic information of both dipolar and non-dipolar sources.
+These experiments included complex samples designed to simulate real rock data.
+Then, we applied it to real data, where it accurately retrieved the expected directions induced in the sample.
+The semi-automated nature of our algorithm, combined with its low processing cost and ability to simultaneously analyze the magnetic moments of numerous particles, represents a significant advancement in facilitating paleomagnetic applications of magnetic microscopy.

### 2023-06-12 paper/content.tex
Add missing "f" in mplstereonet citation
Make a version for submission to an AGU journal
Need to put author information into the separate tex files since they
are in different formats. We'll have to change the citation style for
final submission but for initial one this is fine.
Version submitted to G3

@@
 a) Simulation of a thin section of rock with 103 particles uniformly magnetized (dipolar sources) by two different induced fields.
-The average directions of the induced fields are $D=\ang{0}$ and $I=\ang{0}$ and $D=\ang{180}$ and $I=\ang{0}$, yielding two stable directions.
+The average directions of the induced fields are $D=\ang{0}$ / $I=\ang{0}$ and $D=\ang{180}$ / $I=\ang{0}$, yielding two stable directions.
 b) All estimated vector directions of the identified sources ($M=99$).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data and code availability}
+\section*{Open Research}
 
@@
 We also used matplotlib \citep{Hunter2007} and mplstereonet \citep{mplstereonet}
-or generating figures and stereograms.
+for generating figures and stereograms.
 Basic calculations were performed using Numpy \citep{Harris2020} and Scipy
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgements}
+\section*{Acknowledgements}
 

### 2023-11-06 paper/content.tex

@@
 single-domain (SD) and vortex state grains (also called pseudo-single domain,
-PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
-multi-domain (MD) magnetic structures, which are less stable magnetic recorders
-\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
+PSD) with sizes below \qty{1}{\um} \citep{Berndt2016}, to large ($\gg \qty{1}{\um}$) grains with
+multi-domain (MD) magnetic structures, which are less stable magnetic recorders \citep{Dunlop1997}.
+These large MD grains usually conceal the signal of the SD
 and PSD grains, and techniques of step-wise thermal and magnetic treatments are
@@
 \begin{equation}
-x_c \partial_x f + y_c \partial_x f + z_c \partial_x f + \eta b
+x_c \partial_x f + y_c \partial_y f + z_c \partial_z f + \eta b
 =
@@
 I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
-D &= \tan^{-1}\dfrac{m_x}{m_y} \ , \\
+D &= \tan^{-1}\dfrac{m_y}{m_x} \ , \\
 m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
@@
 The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole.
-The centroid of the particle is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
+The centroid of the spherical volume is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
 The synthetic vertical magnetic field $b_z$ of the non-dipolar source was calculated on regular grids with \qty{0.5}{\um} spacing.
@@
 For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
-At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the particle.
+At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the spherical particle.
 
@@
 Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data.
-The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively).
+The effectiveness of position recovery was measured by comparing the centroid of the spherical volume with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively).
 As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero.
@@
 The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot.
-The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
+The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.
+The black dots represent outliers in the distributions.}
   \label{non-dipolarity-synthetic-data-positioning}
@@
   \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles.
-The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
+The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.
+The black dots represent outliers in the distributions.
+}
   \label{non-dipolarity-synthetic-data-inversion}
@@
 For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensities.
-The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-12}$ to $\qty{e-14}{\ampere\m\squared}$.
+The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-11}$ to $\qty{e-14}{\ampere\m\squared}$.
 The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
@@
 The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$.
-We also manually added 3 sources with higher dipole moments ($5x10^{-11}$) to further simulate the complexity observed in real data measurements.
+We also manually added 3 sources with higher dipole moments ($5$x$10^{-11}$) to further simulate the complexity observed in real data measurements.
 The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.
@@
 TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
-A total of 99 sources out of the original 103 were successfully detected by our workflow.
+A total of 99 sources out of the original 103 were successfully detected in approximately 8 seconds by our algorithm.
+It further determined the 3D positions and dipole moments of these sources in just 1.5 seconds, all while running on an Intel(R) Core(TM) i7-2670QM CPU 2.20GHz with 16 GB of DDR3L 1333 MHz RAM.
+Four sources remained unidentified (black stars, Figure~\ref{complex-synthetic-data}f) due to specific challenges, that arose from two primary factors.
+First, three of these sources either were overlapped by or were in close proximity to other neighboring sources, making it inherently difficult to distinguish and isolate them.
+Second, the identification of one of these sources was impeded by its considerable depth, which led to substantial signal attenuation, further exacerbating the difficulties associated with source recognition.
 
@@
 The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data.
-The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
+The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-11}$ to $10^{-14}$ $Am^2$).
 }
@@
 576,000 data points. The QDM is housed in a shielded room, in
-order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
+order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
 Glenn2017}.
@@
 After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
-possible to determine the windows for 75 potential sources, as shown in Figure~\ref{real-data}e.
+possible to determine the windows for 100 potential sources (within 3 seconds), in which 75 were filtered with coherent ED position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.
 
@@
 
-After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 75 windows selected previously.
-In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time.
-We obtained the magnetic moment and the direction for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
+In order to reduce considerably the computation time, the ED and magnetic moment inversions were done within each data window, instead of solving all sources parameters at the same time.
+We obtained (within 2.5 seconds) the position and dipole moment for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
 Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination $R^2$ and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
@@
 Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
-One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization.
+One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of a known source of magnetization.
 Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
@@
 However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
-The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}.
+The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021, Kosters2023}.
 The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
@@
 The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
-The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
+The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals (although assigning to them negligible magnetization), as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
 In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
@@
 This technique is widely used in aeromagnetic surveys to determine the boundaries of sources by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
-Hence. The application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window.
+Hence, the application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window.
 Nonetheless, the windows generated isolate the main magnetic signal’s region of each source.
@@
 
-The complex synthetic data allows better observation of the strengths and limitations of the windows approach.
-The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
-(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
-(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
-The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
-(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
-As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
+The complex synthetic data allows better observation of the strengths and limitations of the windows approach. The main strengths that can be mentioned are: 
+% (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
+% (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
+% (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
+\begin{enumerate}[label=\roman*)]
+  \item The applied technique detects most of the modeled sources;
+  \item The majority of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a);
+  \item The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d);
+  \item Shallow particles grouped in clusters are usually well individualized during window selection; as well as
+  \item Some isolated particles that produce a weak magnetic signal.
+\end{enumerate}
+
 It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
 Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
+So we can point out the major limitations observed were:
+% (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+% (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+% (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
+% As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
+
+\begin{enumerate}[label=\roman*)]
+  \item  the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters;
+  \item  The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+  \item In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
+As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
+\end{enumerate}
 
@@
 Therefore, it is necessary to keep a check to determine if the inversion reached a satisfactory prediction, such as the coefficient of determination and the
-signal-to-noise ratio suggested by \citep{CortesOrtuno2021}.
+signal-to-noise ratio suggested by \cite{CortesOrtuno2021}.
 
@@
 In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensitive to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
-This technique allows us to obtain the 3D positioning and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
+This technique allows us to obtain the 3D position and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
 
@@
 
-We also present a new, faster, and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of Gaussian applied to total gradient anomaly maps.
+We also present a new, faster, and cleaner way to solve the Euler equation in determining the position of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of Gaussian applied to total gradient anomaly maps.
 In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index ($n = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler Deconvolution is performed, and the central position of each source is determined.
+After estimating the structural index ($\eta = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler Deconvolution is performed, and the central position of each source is determined.
 Due to the similarity with aeromagnetic data, this approach can also be extrapolated for macro-scale studies.

### 2023-11-09 paper/content.tex
Updates from Overleaf

@@
 
+\subsection{Applicability to different grain concentration scenarios}
+
+In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted multiple scenario tests (with 15 repetitions each) by increasing the concentrations of magnetic grains.
+Figure XX.A depicts the percentage of particle detection ($100($detected particles / total particles$)$) by the algorithm, with the median of the distribution represented by the red line.
+The same figure also presents the percentage of windows whose inversion results meet the filtering criteria of R-squared greater than or equal to 0.85 and SNR greater than or equal to 5, with the median represented by the blue line.
+
+As the number of particles increases, there is a consistent decrease in the percentage of source detection, particularly due to the spatial constraints of the algorithm, which require magnetic sources to be sparsely distributed for optimal detection.
+However, as shown in Figure XX.B, by calculating the angular misfit between the mean direction of the model and the mean direction of the detected windows, it is observed that for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains.
+Nonetheless, when applying the filtering criteria, this misfit tends to approach zero.
+
+This observation highlights the algorithm's ability to effectively filter out spurious detection and improve the reliability of source detection, particularly in scenarios with higher particle concentrations.
+These findings underscore the algorithm's robustness in handling varying sample conditions and its capacity to adapt to different levels of particle density.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Prior information and uniqueness of solutions}
-
-Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
-One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of a known source of magnetization.
-Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
-When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions.
-\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
-Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
-This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
-This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
-Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
-In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.
-
-\subsection{A critical examination of the source detection}
-
 Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
@@
 In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
+
+LINK THE NEXT PARAGRAPH
+
+\subsection{NEW TITLE} %A critical examination of the source detection
 
@@
 The complex synthetic data allows better observation of the strengths and limitations of the windows approach. The main strengths that can be mentioned are: 
-% (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
-% (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
-% (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
-\begin{enumerate}[label=\roman*)]
-  \item The applied technique detects most of the modeled sources;
-  \item The majority of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a);
-  \item The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d);
-  \item Shallow particles grouped in clusters are usually well individualized during window selection; as well as
-  \item Some isolated particles that produce a weak magnetic signal.
-\end{enumerate}
+(i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
+(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
+(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
+% \begin{enumerate}[label=\roman*)]
+%   \item The applied technique detects most of the modeled sources;
+%   \item The majority of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a);
+%   \item The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d);
+%   \item Shallow particles grouped in clusters are usually well individualized during window selection; as well as
+%   \item Some isolated particles that produce a weak magnetic signal.
+% \end{enumerate}
 
@@
 So we can point out the major limitations observed were:
-% (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
-% (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-% (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
-% As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
+(i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
+(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
+As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
 
-\begin{enumerate}[label=\roman*)]
-  \item  the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters;
-  \item  The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-  \item In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
+% \begin{enumerate}[label=\roman*)]
+%   \item  the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters;
+%   \item  The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
+%   \item In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
 As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
-\end{enumerate}
+% \end{enumerate}
 
-\subsection{Reliability of dipole moment approximation}
+\subsection{Critical assessment of source position determination} %Prior information and uniqueness of solutions
+
+Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
+One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of a known source of magnetization.
+Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
+When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions.
+\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
+Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
+This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
+
+This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
+Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
+In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.
+
+\subsection{Critical assessment of dipole moment approximation} %Reliability of dipole moment approximation
 \label{dipole-reliability}
@@
 However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
-Therefore the application of the proposed algorithm to natural samples should fail for those PSD particles.
+Therefore the application of the proposed algorithm to natural samples should fail for domains bigger than PSD state.
+In these instances, where sources may exhibit higher-order magnetic anomalies influence such as quadrupole or octupole \citep[e.g.,][]{CortesOrtuno2021, Koster2023lava}.
+In such cases, the dipole model fitting process may not yield satisfactory results.
+Consequently, the presence of higher-order anomalies within the magnetic sources can impact the accuracy of our inversion results.
+
 \cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less

### 2023-11-10 paper/content.tex
Initial paper revisions

@@
 Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
-Conversely, the correlation between errors in dipole moment magnititude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a good fit of the dipolar model.
-It is also noticeable that the majority of cases where the dipole moment direction error is large are associated with deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
+Conversely, the correlation between errors in dipole moment magnitude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a reasonable fit by dipolar model.
+It is also noticeable that the majority of cases where the direction misfit is given by deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
 These results indicated that $R^2$ and SNR can be used as selection criteria to discard sources with likely high errors in the estimated dipole moment.
@@
 In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted multiple scenario tests (with 15 repetitions each) by increasing the concentrations of magnetic grains.
-Figure XX.A depicts the percentage of particle detection ($100($detected particles / total particles$)$) by the algorithm, with the median of the distribution represented by the red line.
-The same figure also presents the percentage of windows whose inversion results meet the filtering criteria of R-squared greater than or equal to 0.85 and SNR greater than or equal to 5, with the median represented by the blue line.
-
+Figure~\ref{grain-concentration}a depicts the percentage of particle detection by the algorithm, with the median of the distribution represented by the red line.
+The same figure also presents the percentage of windows whose inversion results meet the filtering criteria of $R^2 \geq 0.85$ and $SNR \geq 5$, with the median represented by the blue line.
 As the number of particles increases, there is a consistent decrease in the percentage of source detection, particularly due to the spatial constraints of the algorithm, which require magnetic sources to be sparsely distributed for optimal detection.
-However, as shown in Figure XX.B, by calculating the angular misfit between the mean direction of the model and the mean direction of the detected windows, it is observed that for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains.
+However, as shown in Figure~\ref{grain-concentration}b, by calculating the angular misfit between the vector sum direction of the model and the vector sum direction of the detected windows, it is observed that for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains.
 Nonetheless, when applying the filtering criteria, this misfit tends to approach zero.
@@
 These findings underscore the algorithm's robustness in handling varying sample conditions and its capacity to adapt to different levels of particle density.
+
+\begin{figure}[tb!]
+  \centering
+  \includegraphics[width=1\linewidth]{paper/figures/grain-concentration.png}
+  \caption{ 
+  Different grains simulations randomly replicated (N=15) to assess the effectiveness of the algorithm to detect the magnetic sources.
+a) The efficacy of the detection was measured by percentage of sources identified ($100 \left( N_{detected~sources} ~/~ N_{true~sources} \right)$) and showed as box-plots for both unfiltered detection (median represented as the red line) and filtered detection ($R^2 \geq 0.85$ and $SNR \geq 5$, blue line).
+b) The same representation is displayed for the angular misfit between the true vector sum and both results for the filtered and unfiltered sum of vectors detected.
+The blue/red dots represent outliers in the distributions.
+  }
+  \label{grain-concentration}
+\end{figure}
 
@@
 However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
-The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021, Kosters2023}.
+The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021, Koster2023}.
 The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
 Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
-The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
+The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of $\mu m$, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
 The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals (although assigning to them negligible magnetization), as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
@@
 
-LINK THE NEXT PARAGRAPH
-
-\subsection{NEW TITLE} %A critical examination of the source detection
+\subsection{TGA-guided windows: magnetic source detection using LoG Kernel} %A critical examination of the source detection
 
@@
 
-The complex synthetic data allows better observation of the strengths and limitations of the windows approach. The main strengths that can be mentioned are: 
-(i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
-(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
-(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
-% \begin{enumerate}[label=\roman*)]
-%   \item The applied technique detects most of the modeled sources;
-%   \item The majority of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a);
-%   \item The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d);
-%   \item Shallow particles grouped in clusters are usually well individualized during window selection; as well as
-%   \item Some isolated particles that produce a weak magnetic signal.
-% \end{enumerate}
-
-It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
-Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.
-So we can point out the major limitations observed were:
-(i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
-(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
-As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
-
-% \begin{enumerate}[label=\roman*)]
-%   \item  the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters;
-%   \item  The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
-%   \item In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
-As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
-% \end{enumerate}
+While the windows approach violates the fundamental theory of the inversion problem that  requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the  one reported by \cite{Weiss2007}.
+The last-mentioned involves thresholding the long-distance interaction
+of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations.
+In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensitive to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
+This technique allows us to obtain the 3D position and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
+
+Another main limitation arises from the spatial constraints inherent to our approach.
+Specifically, the blob detection struggles when dealing with sources that are closely spaced or overlapping, in the last case, it is unable to discern the magnetic sources.
+Through multiple tests (Figure~\ref{detection-map}), we have found that, for shallow sources, with sensor-sample height $\leq 5 \mu m$, a minimum separation distance of approximately 14 $\mu m$ is necessary to achieve successful source detection.
+This distance steadily increases for deeper seated sources, requiring around 20 $\mu m$ of separation for sensor-sample height of 25 $\mu m$.
+This immensely impacts the algorithm's detection capacity, as the particle count escalates, there is a persistent decline in the rate of successful source detection, as shown in Figure~\ref{grain-concentration}a.
+In essence, the algorithm's effectiveness diminishes as sources become more densely packed, posing a challenge in scenarios where particle density is high (e.g., extrusive rocks).
+On the other hand, as shown in our complex synthetic and real rock samples the technique could be densely applied to rocks with a lower concentration of magnetic grains (e.g., carbonates), due to its high successful rate for detection of sources.
+
+\begin{figure}[tb!]
+\centering
+\includegraphics[width=0.5\linewidth]{paper/figures/detection-map.png}
+\caption{
+Simulation to assess the algorithm's ability to discern between two sources, with different horizontal separation and varying sensor-sample heights.
+The black line represents the boundary where the algorithm's is capable of identify two sources.
+}
+\label{detection-map}
+\end{figure}
 
@@
 Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
-In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.
+Despite the fact that we use the ED original formulation dedicated to dipolar sources ($\eta = 3$), the technique did not present significant difficulties in estimating the 3D position of non-dipolar sources.
+This adaptability allows for an extension of its application to magnetic particles with a strong influence of higher-order magnetic anomalies.
+Lastly, as shown in the complex synthetic sample, the ED can reliably estimated the position of well-individualized sources, however when dealing with clustered particles the Euler's solutions start to deviate from the true positions.
+This deviation is particularly notable in the z-coordinate, which is showed by \cite{Oliveira2015Estimation} to not affect the magnetization direction estimation.
+However, the scenarios with closely spaced magnetic sources, where the inherent assumptions of Euler's method encounter challenges in accurately capturing the complex interactions of magnetic field anomaly caused by each nearby source, greatly interfering in the dipole intensity estimation.
+
+In summary, in order to estimate the Cartesian position as precisely as possible the ED must be executed within a data window containing only one magnetic source and the lowest amount possible of noise, since the high-frequency noise sensibility is also one of the ED's limitations.
+As these assumptions deviate from the ideal case, the ED estimates also become less accurate.
 
@@
 The latter is true when working
-with particle signals in the SD magnetic domain state since they are uniform magnetized particles with strong dipolar anomalies.
+with particle signals in the SD magnetic domain state since they are uniform magnetized particles \citep{Dunlop1997} with strong dipolar anomalies.
 However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
-Therefore the application of the proposed algorithm to natural samples should fail for domains bigger than PSD state.
-In these instances, where sources may exhibit higher-order magnetic anomalies influence such as quadrupole or octupole \citep[e.g.,][]{CortesOrtuno2021, Koster2023lava}.
-In such cases, the dipole model fitting process may not yield satisfactory results.
+Hence, the implementation of the proposed algorithm in natural samples is expected to be unsuccessful in domains other than the SD state.
+In these instances, where sources may exhibit higher-order magnetic anomalies influence, such as quadrupole or octupole \citep[e.g.,][]{CortesOrtuno2021}, the dipole model fitting process may not yield satisfactory results.
 Consequently, the presence of higher-order anomalies within the magnetic sources can impact the accuracy of our inversion results.
@@
 deep particles, generating unreliable inversion results.
-Therefore, it is necessary to keep a check to determine if the inversion reached a satisfactory prediction, such as the coefficient of determination and the
+Therefore, it is necessary to keep a check to determine if the inversion reached a satisfactory prediction, such as the coefficient of determination \citep[dipolarity test, ][]{Fu2020} and the
 signal-to-noise ratio suggested by \cite{CortesOrtuno2021}.
-
-While the windows approach violates the fundamental theory of the inversion problem that  requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the  one reported by \cite{Weiss2007}.
-The last-mentioned involves thresholding the long-distance interaction
-of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations.
-In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensitive to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
-This technique allows us to obtain the 3D position and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
+This filtering process is better observed in the complex synthetic data where it becomes evident the direct relationship between the poorly estimated dipole moment and direction with the lowest values for both $R^2$ and SNR scores (Figure~\ref{complex-synthetic-comparison}).
 

### 2023-11-21 paper/content.tex
Updates from Overleaf

@@
 
-To recover magnetic direction and moment we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetization is uniform.
+To recover magnetic direction and moment we only need to assume that for each data window there is one source with it's central positions known (so we apply Euler deconvolution) and the magnetization is uniform.
 This last premise aligns with the theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable sensor-sample height, which is the basis of classical paleomagnetism.

### 2023-11-24 paper/abstract.tex

@@
-% Paleomagnetic data are usually obtained from whole cylindric samples, where the signal results from the sum of magnetic moments from hundreds of thousands to millions of magnetic particles within the sample volume.
-% This usually includes both stable and unstable remanence carriers.
-% Recently, magnetic microscopy techniques allowed the investigation of individual grains by directly imaging their magnetic field. 
-% However, the determination of the magnetic moments of individual grains is hindered by the intrinsic ambiguity in the inversion of potential field data, as well as by the large number of grains found in any one microscopy image.
-% We present a fast, semi-automated algorithm capable of estimating the position and magnetization of each ferromagnetic (l.s) source using only the magnetic microscopy data. 
-% Our algorithm works in three steps: (i) we first apply image processing techniques to identify and isolate data window boundaries for each source; (ii) with these window boundaries, the position of the sources is estimated using Euler deconvolution; and finally (iii) using the  position information, the algorithm is able to estimate the magnetic dipole moment direction and intensity for each source through an overdetermined linear inverse problem using a dipolar approximation.
-% The method does not require any type of additional information about the sample or the sources. 
-% Sensitivity tests were run to estimate the stability of our routine to the depth of particles, signal-to-noise ratio, and non-dipolarity of the sources. 
-% Tests with simple synthetic data show the high effectiveness of the methodology for recovering the position and magnetic information for both dipolar and non-dipolar sources. 
-% More complex synthetic data including over 100 different magnetic particles were devised to emulate real rock data. 
-% Results obtained on these data also show the feasibility and robustness of the algorithm to semi-automatically estimate the position and magnetic moment of a large number of particles. 
-% This is further confirmed through an application to real data in which we are able to retrieve the expected bimodal isothermal remanent directions that were induced in the sample. 
-% Given its semi-automatic nature, its low processing cost, and the possibility of simultaneous inversion of the magnetic moment of a great number of magnetic particles, the methodology here proposed is a step forward in enabling paleomagnetic applications of magnetic microscopy.
 Paleomagnetic data is collected from bulk samples, containing a mixture of stable and unstable magnetic particles. 
@@
 These experiments included complex samples designed to simulate real rock data. 
-Then, we applied it to real data, where it accurately retrieved the expected directions induced in the sample.
+While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 16 and \qty{24}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
+However, the applicability of the method is still limited to particles in the single- or pseudosingle-domain range.
+When applied to real data, our method is able to accurately retrieved the expected directions induced in the sample. 
 The semi-automated nature of our algorithm, combined with its low processing cost and ability to simultaneously analyze the magnetic moments of numerous particles, represents a significant advancement in facilitating paleomagnetic applications of magnetic microscopy.

### 2023-12-01 paper/abstract.tex
Finished paper review after R1

@@
 These experiments included complex samples designed to simulate real rock data. 
-While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 16 and \qty{24}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
+While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 14 and \qty{20}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
 However, the applicability of the method is still limited to particles in the single- or pseudosingle-domain range.

### 2023-12-01 paper/content.tex
Add a working rule for making diffs
Finished paper review after R1

--- 2023-11-10 paper/content.tex
@@
 These large MD grains usually conceal the signal of the SD
-and PSD grains, and techniques of step-wise thermal and magnetic treatments are
+and PSD grains and techniques of step-wise thermal and magnetic treatments are
 needed to unveil this more stable and reliable magnetic record
@@
 grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
-remanence vector \citep[e.g., ][]{Berndt2016}. Nowadays, with the development of
+remanence vector \citep{Berndt2016}. Nowadays, with the development of
 magnetic microscopy techniques, this task is no longer limited by the
-resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
-Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
+resolution of magnetic microscopes \citep[\textit{e.g.}, ][]{Fu2020, Weiss2007, DeGroot2018,
+Glenn2017, Lima2014, Reis2016}, but essentially by the intrinsic problem presented by the
 ambiguity in the inversion of potential field data \citep{Barbosa2011,
@@
 DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
-X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
+X-ray tomography \citep[\textit{e.g.}, ][]{Maldanis2020} are not readily available and
 too time-consuming to be routinely used in paleomagnetic studies.
@@
 Another route to be explored in the inversion of magnetic microscopy images is
-to obtain all the information, i.e. the magnetic moment and the position of the
-sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
+to obtain all the information, \textit{i.e.} the magnetic moment and the position of the
+sources, from the magnetic data itself \citep[\textit{e.g.}, ][]{Fu2020}. For that, we can
 explore the techniques developed in exploration geophysics, in spite of the
@@
   particle based on the magnetic field measurements and the assumption of a
-  dipolar source. This can be achieved by applying the Euler Deconvolution
+  dipolar source. This can be achieved by applying the Euler deconvolution
   method to the data segment identified in step 1.
@@
 below, which is known to be highly sensitive to noise in the derivatives
-\citep{Saleh2012Applying}. This is why we prefer the finite-differences based
+\citep{Saleh2012Applying}. This is why we prefer the finite-differences-based
 derivatives, which are less prone to amplifying short-wavelength noise than
@@
 segment an aeromagnetic dataset into individual anomalies. Fortunately,
-magnetic microscopy images often contain fewer elongated features (e.g., dikes and
-suture zones) and regional signals (e.g., Curie depth variations) that are
+magnetic microscopy images often contain fewer elongated features (\textit{e.g.}, dikes and
+suture zones) and regional signals (\textit{e.g.}, Curie depth variations) that are
 difficult to separate. This makes it possible for us to produce isolated
@@
 \caption{
-Schematic representation of the coordinates systems and modelling elements.
+Schematic representation of the coordinates systems and modeling elements.
 The left panel shows the $x, y, z$ right-handed coordinate system with $z$
@@
 
-Once the source position is known and we can assume that it is approximately
-spherical or dipolar, we can apply the method developed by
+Once the source's position is known, and assuming it is a dipole, we can apply the method developed by
 \citet{Oliveira2015Estimation} to estimate the dipole moment vector
@@
 estimated declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
-by propagation of uncertainties from Equation~\ref{eq_vector_to_incdec}
+by the propagation of uncertainties from Equation~\ref{eq_vector_to_incdec}
 
@@
 
-We first applied our inversion workflow to three sets of synthetic data to evaluate its strengths and limitations.
+We first applied our inversion workflow to four sets of synthetic data to evaluate its strengths and limitations.
 The datasets are produced by different models of varying complexity which were designed to assess different aspects of the method.
@@
 The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.
+
+\item \textbf{Applicability to different grain concentration scenarios:}
+The fourth model assesses the algorithm's capability to detect magnetic sources in samples with different magnetic particle concentrations.
+Several scenario tests were conducted, with progressively increasing magnetic grain concentrations.
+In parallel with this approach, two dipolar sources were gradually separated, also at different sensor heights, until the algorithm could effectively distinguish the signals from both sources.
+This additional modeling provides insights into the algorithm's performance in scenarios where magnetic sources are closely spaced, complementing the modeling with higher particle density.
+
 \end{enumerate}
@@
 Figure~\ref{fig_synthetic_simple_results}a shows the estimated dipole moment, along with the corresponding true values, as a stereonet for better comparison of the true and estimated vector directions.
-Figure~\ref{fig_synthetic_simple_results}b shows the estimate dipole moments overlaid on a map of the synthetic $b_z$ to demonstrate the ability of our method to estimate a spatial distribution of dipole moments.
-For comparison, Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.
+Figure~\ref{fig_synthetic_simple_results}b shows the estimated dipole moments overlaid on a map of the synthetic $b_z$ to demonstrate the ability of our method to estimate a spatial distribution of dipole moments.
+For comparison, Table~\ref{tab_synthetic_simple_results} also shows the true and estimated dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.
 
@@
 The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$.
-We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with standard deviation of \qty{0.65}{\um}.
+We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with a standard deviation of \qty{0.65}{\um}.
 The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole.
@@
 Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data.
-The effectiveness of position recovery was measured by comparing the centroid of the spherical volume with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively).
+The effectiveness of position recovery was measured by comparing the centroid of the spherical volume with the solution of the Euler deconvolution for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively).
 As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero.
@@
 Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component.
-However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
+However, dipolarity significantly increases as the sensor-to-sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
 
@@
 The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$.
-We also manually added 3 sources with higher dipole moments ($5$x$10^{-11}$) to further simulate the complexity observed in real data measurements.
+We also manually added 3 sources with higher dipole moments ($5 \times 10^{-11}$) to further simulate the complexity observed in real data measurements.
 The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.
@@
 TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
-A total of 99 sources out of the original 103 were successfully detected in approximately 8 seconds by our algorithm.
-It further determined the 3D positions and dipole moments of these sources in just 1.5 seconds, all while running on an Intel(R) Core(TM) i7-2670QM CPU 2.20GHz with 16 GB of DDR3L 1333 MHz RAM.
-Four sources remained unidentified (black stars, Figure~\ref{complex-synthetic-data}f) due to specific challenges, that arose from two primary factors.
-First, three of these sources either were overlapped by or were in close proximity to other neighboring sources, making it inherently difficult to distinguish and isolate them.
-Second, the identification of one of these sources was impeded by its considerable depth, which led to substantial signal attenuation, further exacerbating the difficulties associated with source recognition.
+The Euler deconvolution and dipole moment inversion took approximately 1.5 seconds to compute, while
+the source detection algorithm took approximately 8 seconds, on a laptop with an Intel(R) Core(TM) i7-2670QM CPU 2.20GHz with 16 GB of DDR3L 1333 MHz RAM.
+
+A total of 99 sources out of the original 103 were successfully detected.
+Four sources remained unidentified (black stars in Figure~\ref{complex-synthetic-data}f) due to specific challenges, that arose from two primary factors:
+
+\begin{enumerate}
+    \item Three of these sources either overlapped with or were in close proximity to other neighboring sources, making it inherently difficult to distinguish and isolate them.
+    \item The identification of one of these sources was impeded by its considerable depth, which led to substantial signal attenuation, further exacerbating the difficulties associated with source recognition.
+\end{enumerate}
 
@@
 The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data.
-The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-11}$ to $10^{-14}$ $Am^2$).
+The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - \qty{20}{\um}) and the horizontal bar by the dipole moment amplitude ($10^{-11}$ to $\qty{e-14}{\ampere\m\squared}$).
 }
@@
 Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
-Conversely, the correlation between errors in dipole moment magnitude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a reasonable fit by dipolar model.
+Conversely, the correlation between errors in dipole moment magnitude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a reasonable fit by a dipolar model.
 It is also noticeable that the majority of cases where the direction misfit is given by deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
@@
 The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Figure~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window.
-When filtered to include only data with R\textsuperscript{2} \textgreater 0.85 and SNR \textgreater 5 the obtained direction distribution is closer to the true distribution (Figure~\ref{complex-synthetic-stereograms}c).
+When filtered to include only data with $R^2 \geq 0.85$ and $\text{SNR} \geq 5$ the obtained direction distribution is closer to the true distribution (Figure~\ref{complex-synthetic-stereograms}c).
 
@@
 
-In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted multiple scenario tests (with 15 repetitions each) by increasing the concentrations of magnetic grains.
-Figure~\ref{grain-concentration}a depicts the percentage of particle detection by the algorithm, with the median of the distribution represented by the red line.
-The same figure also presents the percentage of windows whose inversion results meet the filtering criteria of $R^2 \geq 0.85$ and $SNR \geq 5$, with the median represented by the blue line.
-As the number of particles increases, there is a consistent decrease in the percentage of source detection, particularly due to the spatial constraints of the algorithm, which require magnetic sources to be sparsely distributed for optimal detection.
-However, as shown in Figure~\ref{grain-concentration}b, by calculating the angular misfit between the vector sum direction of the model and the vector sum direction of the detected windows, it is observed that for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains.
-Nonetheless, when applying the filtering criteria, this misfit tends to approach zero.
-
-This observation highlights the algorithm's ability to effectively filter out spurious detection and improve the reliability of source detection, particularly in scenarios with higher particle concentrations.
+In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted a test of our algorithm on multiple synthetic datasets with increasing concentrations of randomly distributed magnetic grains.
+For each concentration, we generated 15 different random grain distributions.
+Figure~\ref{grain-concentration}a depicts the percentage of particles detected by the algorithm, with the median of the distribution represented by the red line.
+The same figure also presents the percentage of particles whose inversion results meet the filtering criteria of $R^2 \geq 0.85$ and $\text{SNR} \geq 5$, with the median represented by the blue line.
+As the number of particles increases, there is a consistent decrease in the percentage of sources detected.
+This is expected because of the spatial constraints of the algorithm, which require magnetic sources to be spatially separated for the detection algorithm to identify them.
+As shown in Figure~\ref{grain-concentration}b, by calculating the angular misfit between the vector sum direction of the model and the vector sum direction of the detected windows, it is observed that, for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains.
+Nonetheless, this angular misfit tends to approach zero when the filtering criteria are applied, regardless of the particle concentration.
+
+This observation highlights the algorithm's ability to effectively filter out spurious sources and improve the reliability of the dipole moment estimation, particularly in scenarios with higher particle concentrations.
 These findings underscore the algorithm's robustness in handling varying sample conditions and its capacity to adapt to different levels of particle density.
-
-\begin{figure}[tb!]
-  \centering
-  \includegraphics[width=1\linewidth]{paper/figures/grain-concentration.png}
+However, the same may not hold true for particle populations with many different dipole moment directions.
+
+In addition to the test above, another synthetic data test was implemented using a gradual separation (between 0 and \qty{50}{\um}) of two dipolar sources.
+We also repeated the calculations for gradually increasing (between 0 and \qty{25}{\um}) the distance between the sources and the sensor.
+We then tracked when the source detection algorithm was able to find the two separate sources and when it found a single source.
+Figure~\ref{detection-map} illustrates the algorithm's performance concerning the separation of magnetic sources and varying sensor distances.
+In areas where the algorithm successfully discerns two distinct magnetic sources, the grid is shaded in blue.
+Conversely, the region shaded in red denotes instances where the algorithm detected only a single source with a data window encompassing the signal of both sources.
+In the case of shallow sources, the minimal distance necessary for the effective detection of both signals is approximately \qty{14}{\um}.
+This minimal distance exhibits a consistent increase with the sensor height, reaching up to approximately \qty{20}{\um} for the maximum modeled sensor distance.
+
+\begin{figure}[tb!]
+  \centering
+  \includegraphics[width=1\linewidth]{figures/grain-concentration.png}
   \caption{ 
-  Different grains simulations randomly replicated (N=15) to assess the effectiveness of the algorithm to detect the magnetic sources.
-a) The efficacy of the detection was measured by percentage of sources identified ($100 \left( N_{detected~sources} ~/~ N_{true~sources} \right)$) and showed as box-plots for both unfiltered detection (median represented as the red line) and filtered detection ($R^2 \geq 0.85$ and $SNR \geq 5$, blue line).
+  Different grain simulations were randomly replicated (N=15) to assess the effectiveness of the algorithm to detect the magnetic sources.
+a) The efficacy of the detection was measured by the percentage of sources identified ($100 \left( N_{detected} ~/~ N_{true} \right)$) and showed as box-plots for both unfiltered detection (median represented as the red line) and filtered detection ($R^2 \geq 0.85$ and $SNR \geq 5$, blue line).
 b) The same representation is displayed for the angular misfit between the true vector sum and both results for the filtered and unfiltered sum of vectors detected.
@@
   \label{grain-concentration}
+\end{figure}
+
+\begin{figure}[tb!]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/detection-map.png}
+\caption{
+Simulation to assess the algorithm's ability to discern between two sources, with different horizontal separations and varying sensor-sample heights.
+The blue-shaded region signifies the successful detection of two distinct sources, while a red-shaded region indicates the detection of a single source due to closely spaced sources.
+The black line represents the boundary between these two regions.
+}
+\label{detection-map}
 \end{figure}
@@
 After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
-possible to determine the windows for 100 potential sources (within 3 seconds), in which 75 were filtered with coherent ED position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.
+possible to determine the windows for 100 potential sources, of which 75 remain after filtering for coherent Euler deconvolution position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.
 
@@
 
-In order to reduce considerably the computation time, the ED and magnetic moment inversions were done within each data window, instead of solving all sources parameters at the same time.
-We obtained (within 2.5 seconds) the position and dipole moment for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
+In order to reduce the computation time, the Euler deconvolution and magnetic moment inversions were done within each data window, instead of solving all sources parameters at the same time.
+We obtained the position and dipole moment for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a).
 Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination $R^2$ and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained.
@@
 About 46 identified sources passed these criteria.
-This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
+This filtering technique removed the models with poor fit to the data, which includes the ones that were too corrupted with noise.
+The filtered results show more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b).
 Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite grains outnumber the hematite ones.
@@
 
-Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
-In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
-This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
-However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
-The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021, Koster2023}.
-The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
-Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
-The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of $\mu m$, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
-The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals (although assigning to them negligible magnetization), as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
+Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem of micromagnetic data and, for the purpose of comparison, we separate them into two categories based on the main estimated parameter by the inversion procedure.
+In the first type of approach, the main goal is usually to estimate an average magnetization by inverting for the superficial magnetization of the whole sample, commonly by assuming unidirectional or uniform magnetization \citep[\textit{e.g.},][]{Weiss2007}.
+There have been significant efforts to enhance the performance of such methods in the spatial domain \citep[\textit{e.g.},][]{Myre2019} and the frequency domain  \citep[\textit{e.g.},][]{Lima2013}.
+This methodology can be used to estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
+However, this assumption is not always true when dealing with complex samples (\textit{i.e.}, more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
+The second type of approach has the goal of finding the magnetic properties of individual sources, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[\textit{e.g.},][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[\textit{e.g.},][]{Fabian2019, DeGroot2018, DeGroot2021, Koster2023}.
+The latter further allows unique estimation of magnetic moment configuration of even higher orders components through a spherical harmonic expansion constrained by micromagnetic models \citep[\textit{e.g.},][]{CortesOrtuno2021, CortesOrtuno2022}.
+Such techniques come with some difficulties, such as having to manually select the data for inversion or dealing with the limitations of the tomography methods.
+For example, microCT provides high-resolution imaging of internal structures, but it is accompanied by some limitations when it comes to paleomagnetic studies in particular.
+The technique has a spatial resolution on the order of a few micrometers, which is not sufficient to directly image the fine-grained single-domain magnetites \citep{DeGroot2018}.
+The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013},  though the subsequent inversion may assign to them negligible magnetization.
 In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
 
-\subsection{TGA-guided windows: magnetic source detection using LoG Kernel} %A critical examination of the source detection
-
-Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of mechanically selecting cropped data or needing any type of additional information.
-However, to better examine its advantages and disadvantages we first need to point out the strengths and weaknesses of the technique used in the detection of sources, the Laplacian of Gaussian (LoG) kernel \citep{Marr1980}.
+The methodology proposed here aims to add additional position information to constrain the dipole moment inverse problem without requiring external, expensive, and time-consuming data acquisitions.
+We also seek to automate as much of the processing as possible to allow large-scale applications of magnetic microscopy, which will be required if it is to be used routinely in paleomagnetic studies.
+Below, we discuss the strengths and limitations of each aspect of the proposed methodology in light of the various synthetic data tests that were performed.
+
+\subsection{TGA-guided windows: magnetic source detection using LoG Kernel}
+
+Our proposed methodology has the goal of finding each individual source’s dipole moment components without the trouble of manually selecting cropped data or needing any type of additional information.
+To better examine its advantages and disadvantages, we first need to point out the strengths and weaknesses of the technique used in the detection of sources, the Laplacian of Gaussian (LoG) kernel \citep{Marr1980}.
 The LoG is a computer imaging technique that is able to identify regions where the intensity changes abruptly by convolving the image with the LoG filter, and is the result of the combination of the Gaussian blur and Laplacian filter \citep{gonzalez2018}.
 The Laplacian filter is able to highlight the regions where the intensity changes rapidly.
-On the other hand, the Gaussian blur is a smoothing filter for high-frequency noise, which reduces the likelihood to generate artifacts.
+On the other hand, the Gaussian blur is a smoothing filter for high-frequency noise, which reduces the likelihood of generating artifacts.
 Hence, the result of this LoG operation can identify blobs as regions above a certain threshold, this threshold crossing determines what are brighter spots (local maxima) surrounded by a darker background.
@@
 
-The total gradient anomaly (TGA) might be considered the ideal image to be used as input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale).
-The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges.
-This technique is widely used in aeromagnetic surveys to determine the boundaries of sources by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
-Hence, the application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window.
-Nonetheless, the windows generated isolate the main magnetic signal’s region of each source.
-This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.
-
-While the windows approach violates the fundamental theory of the inversion problem that  requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013,Lima2013}, our technique is similar to the  one reported by \cite{Weiss2007}.
-The last-mentioned involves thresholding the long-distance interaction
+We consider the total gradient amplitude (TGA) to be the ideal input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale).
+The TGA highlights the subsurface sources by generating a map that is entirely positive and where the signal is concentrated on top of the sources.
+This technique is widely used in aeromagnetic surveys to aid in mapping the boundaries of sources.
+The windows generated from the TGA map isolate the main magnetic signal for each source.
+This guarantees that both Euler deconvolution and dipole moment inversion are performed using the most important parts of the signal, balancing accurate parameter estimation and fast run-time due to the use of fewer data points.
+
+While the windows approach violates the fundamental theory of the inversion problem that requires the sampled area to be finite and encapsulated by the inversion domain to ensure the uniqueness of results \citep{Baratchart2013, Lima2013}, our results do not present any practical issues and are able to correctly recover the position and dipole moment of the sources, even with slightly truncated data.
+Our technique is similar to the one reported by \cite{Weiss2007},
+which involves thresholding the long-distance interaction
 of each dipole in the SMM data, which excludes the effect of other dipoles by setting their contribution to zero, resulting in a sparse matrix that permits faster calculations.
-In contrast to this approach, we employ the TGA map to select the windows and isolate the area containing the main signal of the desired dipole, while the area out of the boundaries of the window is less sensitive to variation in magnetic parameters of this particular source, hence we exclude them from the inversion domain.
-This technique allows us to obtain the 3D position and an approximation of the dipole moment components of hundreds of sources within a few seconds, while the inversion is fast the time bottleneck of our methodology is associated with the blob detection process.
+In contrast to this approach, we apply the source detection to a TGA map, which concentrates the signal above each particle, to select the windows that isolate the area containing the main signal of the desired dipole.
+The area out of the boundaries of the window is less sensitive to variation in the magnetic parameters of the source, hence we may exclude them from the inversion domain without ill effects.
+This technique allows us to obtain the 3D position and an approximation of the dipole moment components of hundreds of sources in a computationally efficient way.
+In fact, the main time bottleneck of our methodology is not the inversion but the source detection process.
 
@@
 Specifically, the blob detection struggles when dealing with sources that are closely spaced or overlapping, in the last case, it is unable to discern the magnetic sources.
-Through multiple tests (Figure~\ref{detection-map}), we have found that, for shallow sources, with sensor-sample height $\leq 5 \mu m$, a minimum separation distance of approximately 14 $\mu m$ is necessary to achieve successful source detection.
-This distance steadily increases for deeper seated sources, requiring around 20 $\mu m$ of separation for sensor-sample height of 25 $\mu m$.
+Through multiple tests (Figure~\ref{detection-map}), we have found that, for shallow sources, with sensor-sample height $\leq \qty{5}{\um}$, a minimum separation distance of approximately \qty{14}{\um} is necessary to achieve successful source detection.
+This distance steadily increases for deeper seated sources, requiring around \qty{20}{\um} of separation for the sensor-sample height of \qty{25}{\um}.
 This immensely impacts the algorithm's detection capacity, as the particle count escalates, there is a persistent decline in the rate of successful source detection, as shown in Figure~\ref{grain-concentration}a.
-In essence, the algorithm's effectiveness diminishes as sources become more densely packed, posing a challenge in scenarios where particle density is high (e.g., extrusive rocks).
-On the other hand, as shown in our complex synthetic and real rock samples the technique could be densely applied to rocks with a lower concentration of magnetic grains (e.g., carbonates), due to its high successful rate for detection of sources.
-
-\begin{figure}[tb!]
-\centering
-\includegraphics[width=0.5\linewidth]{paper/figures/detection-map.png}
-\caption{
-Simulation to assess the algorithm's ability to discern between two sources, with different horizontal separation and varying sensor-sample heights.
-The black line represents the boundary where the algorithm's is capable of identify two sources.
-}
-\label{detection-map}
-\end{figure}
-
-\subsection{Critical assessment of source position determination} %Prior information and uniqueness of solutions
-
-Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
-One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of a known source of magnetization.
-Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
-When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions.
-\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
-Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
-This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
-
-This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
-Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
-Despite the fact that we use the ED original formulation dedicated to dipolar sources ($\eta = 3$), the technique did not present significant difficulties in estimating the 3D position of non-dipolar sources.
+In essence, the algorithm's effectiveness diminishes as sources become more densely packed, posing a challenge in scenarios where particle density is high (\textit{e.g.}, extrusive rocks).
+On the other hand, as shown in our complex synthetic and real rock samples the technique could be densely applied to rocks with a lower concentration of magnetic grains (\textit{e.g.}, carbonates), due to its high successful rate for detection of sources.
+
+\subsection{Critical assessment of source position determination}
+
+Working with potential field data is challenging due to the ambiguity inherent to data modeling.
+To obtain unique and reliable results from data inversion, it is necessary to provide as much prior information as possible.
+One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of the source of magnetization.
+\citet{Oliveira2015Estimation} showed that the magnetization direction recovered by a least-squares inversion with a spherical approximation is sensitive to variations in the horizontal coordinates of the center of the magnetic sources, but is practically insensitive to variations in depth.
+They propose the Euler deconvolution method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
+This occurs mainly because the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
+This remark is also better observed in our simple synthetic sample where the estimated horizontal positions are close to the true values, which implies small misfit values in the recovered magnetic directions.
+Although the estimated magnetic moment amplitude for said sample is satisfactory, this parameter is more affected by the variations in the depth of the source due to the inherent ambiguity between depth and moment amplitude.
+
+Despite using a structural index $\eta = 3$ for the Euler deconvolution (indicating dipolar sources) , the technique did not present significant difficulties in estimating the 3D position of non-dipolar sources for source-sensor separations higher than around \qty{2.5}{\um} (Figure~\ref{non-dipolarity-synthetic-data-positioning}).
 This adaptability allows for an extension of its application to magnetic particles with a strong influence of higher-order magnetic anomalies.
-Lastly, as shown in the complex synthetic sample, the ED can reliably estimated the position of well-individualized sources, however when dealing with clustered particles the Euler's solutions start to deviate from the true positions.
-This deviation is particularly notable in the z-coordinate, which is showed by \cite{Oliveira2015Estimation} to not affect the magnetization direction estimation.
-However, the scenarios with closely spaced magnetic sources, where the inherent assumptions of Euler's method encounter challenges in accurately capturing the complex interactions of magnetic field anomaly caused by each nearby source, greatly interfering in the dipole intensity estimation.
-
-In summary, in order to estimate the Cartesian position as precisely as possible the ED must be executed within a data window containing only one magnetic source and the lowest amount possible of noise, since the high-frequency noise sensibility is also one of the ED's limitations.
-As these assumptions deviate from the ideal case, the ED estimates also become less accurate.
-
-\subsection{Critical assessment of dipole moment approximation} %Reliability of dipole moment approximation
+Lastly, as shown in the complex synthetic sample, the Euler deconvolution can reliably estimate the position of well-individualized sources.
+When dealing with clustered particles, however, the Euler deconvolution solutions start to deviate from the true positions.
+This deviation is particularly notable in the z-coordinate, which is shown by \cite{Oliveira2015Estimation} to not affect the magnetization direction estimation, but can negatively influence the dipole moment amplitude estimation.
+
+In summary, Euler deconvolution must ideally be executed within a data window containing only one magnetic source and the lowest amount possible of noise in order to accurately estimate the source position.
+We have shown that our method is able to satisfy these conditions for a decent amount of sources by upward-continuation of the data prior to derivative calculation and by use of the source detection method.
+
+\subsection{Critical assessment of dipole moment approximation}
 \label{dipole-reliability}
 
-Our approach relies in the premise of assuming the magnetic anomaly within
+Our approach relies on the premise of assuming the magnetic anomaly within
 the data window is a response of a dipolar source.
 The latter is true when working
-with particle signals in the SD magnetic domain state since they are uniform magnetized particles \citep{Dunlop1997} with strong dipolar anomalies.
-However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
-Hence, the implementation of the proposed algorithm in natural samples is expected to be unsuccessful in domains other than the SD state.
-In these instances, where sources may exhibit higher-order magnetic anomalies influence, such as quadrupole or octupole \citep[e.g.,][]{CortesOrtuno2021}, the dipole model fitting process may not yield satisfactory results.
-Consequently, the presence of higher-order anomalies within the magnetic sources can impact the accuracy of our inversion results.
-
-\cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
+with particle signals in the single domain state since they are uniformly magnetized particles \citep{Dunlop1997} with strong dipolar anomalies.
+However, \cite{Nagy2017} reported that particles within the pseudo-single domain state can record the paleomagnetic field for longer periods of time than single domain ones, but also present strongly non-dipolar characteristics.
+Hence, the application of the proposed algorithm in natural samples is expected to be unsuccessful in states other than the single domain state unless sources are sufficiently far from the sensor to be approximated by dipoles.
+In instances where sources exhibit strong higher-order magnetic anomalies, such as quadrupole or octupole \citep[\textit{e.g.},][]{CortesOrtuno2021}, even at larger source-sample separations, the dipole model fitting process may not yield satisfactory results.
+Consequently, the presence of strong higher-order anomalies within the magnetic sources can impact the accuracy of our inversion results.
+
+\cite{CortesOrtuno2022} showed that PSD state particles present more accurate inversion results when considering the non-dipolar components for small sample-sensor distances (\textless 1 $\mu$m).
+For larger sensor distances, the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
 influence on the particle's magnetic signal.
-Thus, our approach can be considered reasonable to work with both particle SD and PSD states signals.
-The latter happens mainly due to the sensor height being usually greater than 5 $\mu m$, considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components.
-This is corroborated by our non-dipolar synthetic sample showing the almost complete attenuation of non-dipolar components at distances greater than 5 $\mu m$.
+Thus, our approach can be considered reasonable to work with both particle SD and PSD state signals.
+The latter happens mainly due to the sensor height being usually greater than \qty{5}{\um} for QDM data.
+Considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components.
+This is corroborated by our non-dipolar synthetic sample showing the almost complete attenuation of non-dipolar components at distances greater than \qty{5}{\um}.
 
@@
 deep particles, generating unreliable inversion results.
-Therefore, it is necessary to keep a check to determine if the inversion reached a satisfactory prediction, such as the coefficient of determination \citep[dipolarity test, ][]{Fu2020} and the
+Therefore, it is necessary to verify that the inversion reached a satisfactory prediction, such as the coefficient of determination \citep[dipolarity test, ][]{Fu2020} and the
 signal-to-noise ratio suggested by \cite{CortesOrtuno2021}.
@@
 We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the estimate of their magnetic moment.
-Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
+It is ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
 This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
 
-We also present a new, faster, and cleaner way to solve the Euler equation in determining the position of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of Gaussian applied to total gradient anomaly maps.
-In this way, reducing the numerous solutions to just one data window per source.
-After estimating the structural index ($\eta = 3$) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler Deconvolution is performed, and the central position of each source is determined.
-Due to the similarity with aeromagnetic data, this approach can also be extrapolated for macro-scale studies.
-
-To recover magnetic direction and moment we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetization is uniform.
-This last premise aligns with the theory of magnetically stable particles SD, and by extension the PSD ones at a reasonable sensor-sample height, which is the basis of classical paleomagnetism.
-Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources.
-Therefore, this method can be quickly replicated in a data set of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.
-
-The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise, for both dipolar and non-dipolar sources.
-While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
-The real sample data positively answered the question of the algorithm's ability to deal with thin sections of rocks.
-But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
+We also present a new way to solve the Euler deconvolution problem for determining the position of magnetic anomaly sources.
+Instead of the traditional moving window approach, we select data windows based on the Laplacian of Gaussian method applied to total gradient amplitude maps.
+In this way, each window will ideally contain a single source and we are able to reduce the usually numerous spurious solutions to just a single solution per source.
+This approach could also be adapted for traditional aeromagnetic data studies in cases where the sources are approximately spherical or only slightly elongated.
+
+To recover the dipole moment, we assume that there is one source for each data window, that its central position is known (through Euler deconvolution), and that its magnetization is uniform.
+This last premise aligns with magnetically stable SD particles and with PSD ones at a reasonable sensor-sample separation, which is the basis of classical paleomagnetism.
+Also, there is no need for any prior knowledge other than the observed magnetic anomaly and the structural index of the sources (which is related to the dipolar approximation).
+Therefore, this method can be quickly applied to a set of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.
+
+The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity for both dipolar and non-dipolar sources, even under the effect of high-frequency noise.
+The complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
+The real data application positively answered the question of the algorithm's ability to deal with the real-world signals of thin sections of rocks.
+It also showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal intensity disparities that were even greater than simulated in the complex synthetic test.
 We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
+
+We expect that this method can be widely applied to magnetic microscopy studies involving particles in the SD and PSD domains.
+The method can be applied in full as presented here or its individual components (source detection, Euler deconvolution, dipole moment inversion) can be combined with existing or future methods.
+There are still issues to be overcome with regard to situations where the signal of two or more sources overlap significantly, when non-dipolar effects are strong even at larger source-sensor separations, and how to best combine and benchmark the inversion results against microCT and micromagnetic modeling studies.
 
@@
 
-The Python source code used to produce all results and figures presented here
-is available at \url{https://github.com/\GitHubRepository} and
-\url{https://doi.org/\ArchiveRepository} under the MIT open-source license.
+The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}\footnote{Also avaliable on GitHub: \url{https://github.com/\GitHubRepository}} under the MIT and CC-BY licenses.
 The QDM magnetic microscopy data are available
-at~\url{https://doi.org/10.6084/m9.figshare.22965200.v1} under the CC-0 license.
+from \citet{janinedata} under the CC-0 license.
 
@@
 speed-up calculations.
-Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful
+Lastly, the xarray library \citep{hoyer2017xarray} offered a fast and powerful
 tool for working with multi-dimensional datasets allowing an easy way of data
@@
 
+The authors would like to thank the editor Joshua Feinberg and two anonymous reviewers for their contributions which greatly improved our paper.
 We are indebted to the developers and maintainers of the open-source software
@@
 grant 2021/08379-5 from the Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP),
+grant PRPI 22.1.09345.01.2 from Universidade de São Paulo,
 and grant IES\textbackslash{}R3\textbackslash{}213141 from the Royal Society.

### 2023-12-01 paper/abstract.tex
Updates from Overleaf

@@
+% Paleomagnetic data is collected from bulk samples, containing a mixture of stable and unstable magnetic particles. 
+% Recently, magnetic microscopy techniques have allowed the examination of individual magnetic grains. 
+% However, accurately determining the magnetic moments of these grains is difficult and time-consuming due to the inherent ambiguity of potential field data and the large number of grains in each image.
+% Here we introduce a fast and semi-automated algorithm that estimates the position and magnetization of each magnetic source solely based on magnetic microscopy data, without requiring any additional information.
+% The algorithm follows a three-step process. 
+% Firstly, it employs image processing techniques to identify and isolate data window boundaries for each magnetic source. 
+% Secondly, the algorithm uses Euler deconvolution to estimate their positioning. 
+% Lastly, the algorithm solves an overdetermined linear inverse problem, using a dipolar approximation, to determine the direction and intensity of the magnetic dipole moment for each source. 
+% To validate the algorithm, we conducted tests analyzing particle depth, intensity, and non-dipolarity. 
+% Additionally, synthetic data experiments were performed to demonstrate the effectiveness of the methodology in recovering the position and magnetic information of both dipolar and non-dipolar sources.
+% These experiments included complex samples designed to simulate real rock data. 
+% While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 14 and \qty{20}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
+% However, the applicability of the method is still limited to particles in the single- or pseudosingle-domain range.
+% When applied to real data, our method is able to accurately retrieved the expected directions induced in the sample. 
+% The semi-automated nature of our algorithm, combined with its low processing cost and ability to simultaneously analyze the magnetic moments of numerous particles, represents a significant advancement in facilitating paleomagnetic applications of magnetic microscopy.
+
 Paleomagnetic data is collected from bulk samples, containing a mixture of stable and unstable magnetic particles.
@@
 These experiments included complex samples designed to simulate real rock data.
-While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 14 and \qty{20}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
-However, the applicability of the method is still limited to particles in the single- or pseudosingle-domain range.
-When applied to real data, our method is able to accurately retrieved the expected directions induced in the sample. 
+Then, we applied it to real data, where it accurately retrieved the expected directions induced in the sample.
 The semi-automated nature of our algorithm, combined with its low processing cost and ability to simultaneously analyze the magnetic moments of numerous particles, represents a significant advancement in facilitating paleomagnetic applications of magnetic microscopy.

### 2023-12-08 paper/content.tex
Fix position of real data figure in preprint
Update references and remove footnote

@@
 
-After remanence acquisition, we performed a magnetic map with the Quantum
-Diamond Microscope (QDM) at Harvard University over a sample section of
-approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
-spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
-576,000 data points. The QDM is housed in a shielded room, in
-order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
-Glenn2017}.
-We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.
-After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
-possible to determine the windows for 100 potential sources, of which 75 remain after filtering for coherent Euler deconvolution position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.
-
-\begin{figure}[tb!]
+\begin{figure}[ph!]
 \centering
@@
 
+After remanence acquisition, we performed a magnetic map with the Quantum
+Diamond Microscope (QDM) at Harvard University over a sample section of
+approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
+spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
+576,000 data points. The QDM is housed in a shielded room, in
+order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
+Glenn2017}.
+We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.
+After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
+possible to determine the windows for 100 potential sources, of which 75 remain after filtering for coherent Euler deconvolution position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.
+
+\begin{figure}[tb!]
+\centering
+\includegraphics[width=1\linewidth]{figures/real-data-stereograms.png}
+\caption{
+Comparison of the estimated dipole magnetic moments and directions for the real data sample.
+a) All estimated directions without filtering ($M=75$).
+b) Estimated directions filtered ($M=46$) by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 5$), which shows two clusters of direction located on each pole of the stereogram.
+}
+\label{real-data-stereograms}
+\end{figure}
+
 In order to reduce the computation time, the Euler deconvolution and magnetic moment inversions were done within each data window, instead of solving all sources parameters at the same time.
@@
 Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite grains outnumber the hematite ones.
-
-\begin{figure}[tb!]
-\centering
-\includegraphics[width=1\linewidth]{figures/real-data-stereograms.png}
-\caption{
-Comparison of the estimated dipole magnetic moments and directions for the real data sample.
-a) All estimated directions without filtering ($M=75$).
-b) Estimated directions filtered ($M=46$) by the coefficient of determination ($\geq 0.85$) and SNR ($\geq 5$), which shows two clusters of direction located on each pole of the stereogram.
-}
-\label{real-data-stereograms}
-\end{figure}
 
@@
 
-The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}\footnote{Also avaliable on GitHub: \url{https://github.com/\GitHubRepository}} under the MIT and CC-BY licenses.
+The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, also available on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
 The QDM magnetic microscopy data are available

### 2023-12-08 paper/content.tex
Update the Open Research section

@@
 
-The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, also available on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
+The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, which can also be found on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
 The QDM magnetic microscopy data are available

### 2024-03-21 paper/abstract.tex
Point out the limitation in the method in the abstract

--- 2023-12-01 paper/abstract.tex
@@
-Paleomagnetic data is collected from bulk samples, containing a mixture of stable and unstable magnetic particles. 
-Recently, magnetic microscopy techniques have allowed the examination of individual magnetic grains. 
-However, accurately determining the magnetic moments of these grains is difficult and time-consuming due to the inherent ambiguity of potential field data and the large number of grains in each image.
-Here we introduce a fast and semi-automated algorithm that estimates the position and magnetization of each magnetic source solely based on magnetic microscopy data, without requiring any additional information.
-The algorithm follows a three-step process. 
-Firstly, it employs image processing techniques to identify and isolate data window boundaries for each magnetic source. 
-Secondly, the algorithm uses Euler deconvolution to estimate their positioning. 
-Lastly, the algorithm solves an overdetermined linear inverse problem, using a dipolar approximation, to determine the direction and intensity of the magnetic dipole moment for each source. 
-To validate the algorithm, we conducted tests analyzing particle depth, intensity, and non-dipolarity. 
-Additionally, synthetic data experiments were performed to demonstrate the effectiveness of the methodology in recovering the position and magnetic information of both dipolar and non-dipolar sources.
-These experiments included complex samples designed to simulate real rock data. 
-While our underlying assumption is that of dipolar and spatially separated magnetic grains, our results show that the method is capable of automatically identifying individual dipolar sources that are at least between 14 and \qty{20}{\mu\meter} apart and can accurately recover the dipole moment and position of non-dipolar sources that are at least \qty{5}{\mu\meter} from the sensor.
-However, the applicability of the method is still limited to particles in the single- or pseudosingle-domain range.
-When applied to real data, our method is able to accurately retrieved the expected directions induced in the sample. 
-The semi-automated nature of our algorithm, combined with its low processing cost and ability to simultaneously analyze the magnetic moments of numerous particles, represents a significant advancement in facilitating paleomagnetic applications of magnetic microscopy.
+Paleomagnetic data is collected from bulk samples, containing a mixture of
+stable and unstable magnetic particles. Recently, magnetic microscopy
+techniques have allowed the examination of individual magnetic grains. However,
+accurately determining the magnetic moments of these grains is difficult and
+time-consuming due to the inherent ambiguity of the data and the large number
+of grains in each image. Here we introduce a fast and semi-automated algorithm
+that estimates the position and magnetization of dipolar sources solely based
+on the magnetic microscopy data. The algorithm follows a three-step process: 1)
+employ image processing techniques to identify and isolate data windows for
+each magnetic source; 2) use Euler Deconvolution to estimate the position of
+each source; 3) solve a linear inverse problem to estimate the dipole moment of
+each source. To validate the algorithm, we conducted synthetic data tests,
+including varying particle concentrations and non-dipolarity. The tests show
+that our method is able to accurately recover the position and dipole moment of
+particles that are at least \qty{15}{\um} apart for a source-sensor separation
+of \qty{5}{\um}. For grain concentrations of 6250 grains/mm³, our method is
+able to detect over 60\% of the particles present in the data. We applied the
+method to real data of a speleothem sample, where it accurately retrieved the
+expected directions induced in the sample. The semi-automated nature of our
+algorithm, combined with its low processing cost and ability to determine the
+magnetic moments of numerous particles, represents a significant advancement in
+facilitating paleomagnetic applications of magnetic microscopy.

### 2024-03-21 paper/content.tex
Incorporate reviewer comments

@@
 
-\item \textbf{Applicability to real-world scenarios:}
-The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations clustered around two stable directions.
+\item \textbf{Applicability to more complex scenarios:}
+The third model is inspired on typical speleothem datasets.
+It contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations clustered around two stable directions.
 The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
@@
 
-\subsection{Applicability to real-world scenarios}
-
-This test represents a more complex scenario by simulating 103 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$.
+\subsection{Applicability to more complex scenarios}
+
+This test represents a more complex scenario by simulating typical grain distributions found in speleothem datasets.
+The model is comprised of 103 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$.
 The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance.
@@
 
-In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted a test of our algorithm on multiple synthetic datasets with increasing concentrations of randomly distributed magnetic grains.
+In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted a test of our algorithm on multiple synthetic datasets with increasing concentrations of randomly distributed magnetic grains in a volume of $2000 \times 2000 \times \qty{20}{\um}$.
 For each concentration, we generated 15 different random grain distributions.
@@
   \centering
-  \includegraphics[width=1\linewidth]{figures/grain-concentration.png}
+  \includegraphics[width=1\linewidth]{figures/grain_concentration.png}
   \caption{
@@
 
-We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the estimate of their magnetic moment.
-It is ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
-This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.
+We developed an efficient semi-automated method to determine the position and dipole moments of dipolar sources on a microscale.
+The method is an advancement towards the application of magnetic microscopy to paleomagnetic studies using thin sections.
+A possible application is the isolation of the responses of more reliable recorders of the Earth's geomagnetic field from those of less reliable ones.
 
@@
 This approach could also be adapted for traditional aeromagnetic data studies in cases where the sources are approximately spherical or only slightly elongated.
+The source detection method is able to correctly isolate sources that are at
+least \qty{15}{\um} apart for a source-sensor separation of \qty{5}{\um}.
+For grain concentrations of 6250 grains/mm³, our method is
+able to detect over 60\% of the particles present in the data.
 
@@
 
-The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity for both dipolar and non-dipolar sources, even under the effect of high-frequency noise.
-The complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
-The real data application positively answered the question of the algorithm's ability to deal with the real-world signals of thin sections of rocks.
-It also showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal intensity disparities that were even greater than simulated in the complex synthetic test.
+The test using a simple synthetic sample shows the capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity for both dipolar and non-dipolar sources, even under the effect of high-frequency noise.
+The test on a more complex synthetic sample highlights the applicability of the method in datasets resembling those obtained from speleothems.
+The data are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
+The application to a real speleothem dataset positively answered the question of the algorithm's ability to deal with the real-world signals and noise.
+It also showed the capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal intensity disparities.
 We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
 
-We expect that this method can be widely applied to magnetic microscopy studies involving particles in the SD and PSD domains.
+We expect that this method can be widely applied to magnetic microscopy studies involving particles in the SD and PSD domains, particularly where grain concentrations are at or below 6000-10000 grains/mm³.
 The method can be applied in full as presented here or its individual components (source detection, Euler deconvolution, dipole moment inversion) can be combined with existing or future methods.

### 2024-04-01 paper/content.tex
Fix captions with upward continuation results
They said that the continuation was to suppress long wavelength noise,
which it can't do.

@@
     $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
-    b) Anomaly map after the upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise.
+    b) Anomaly map after upward-continuation to $z = \qty{10}{\micro\meter}$ to attenuate short-wavelength noise.
     c) The total gradient amplitude (TGA) calculated from the
@@
     $z = \qty{5}{\um}$.
-    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
+    b) Anomaly map after upward-continuation to $z = \qty{10}{\um}$ to attenuate short-wavelength noise.
     c) The total gradient amplitude (TGA) calculated from the

### 2024-04-17 paper/content.tex
Add sentence explaining that we don't use windows at the borders
To avoid truncation effects
Add published DOI, fix Gelson's name, and minor edits to the text

@@
   gradient amplitude}) and image processing (histogram stretching and
-  equalization) and segmentation methods (watershed segmentation).
+  equalization) and segmentation methods.
 \item \textbf{Position estimation}: Estimate the 3D position of a magnetic
@@
 magnetic microscopy, the computation is fast and only needs to be performed
-once per image.
+once per image. To avoid issues of source truncation in the following steps, we
+exclude windows that are on or close to the borders of the datasets.
 
@@
 \begin{aligned}
-I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
-D &= \tan^{-1}\dfrac{m_y}{m_x} \ , \\
+I &= -\tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
+D &= \tan^{-1}\dfrac{m_x}{m_y} \ , \\
 m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
